### 2018-09-22 main.tex
All key files, programs and data. Still need to write a good description though.

\title{Busch, Khakhalin. Intrinsic temporal tuning}

%\documentclass[twocolumn]{article}
\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[top=0.85in,left=1.5in,right=1.5in,footskip=0.75in]{geometry} % For one-column version
%\usepackage[top=0.85in,left=1in,right=1.0in,footskip=0.75in]{geometry} % For two-column version
% marginparwidth=2in

\usepackage{helvet} % Set font to Arial-like
\renewcommand{\familydefault}{\sfdefault} % Force this font

\usepackage[round, sort, numbers, authoryear]{natbib} % Reference manager, round citations
% \usepackage[super]{natbib} % Nature-style citations
% \setcitestyle{citesep={,}} % For nature-style, comma instead of ;

%\usepackage[switch,pagewise]{lineno} % Numbered lines for two columns
\usepackage[pagewise]{lineno} % Numbered lines for one column
\usepackage{xcolor}
\renewcommand{\linenumberfont}{\normalfont\bfseries\small\color{lightgray}}

% \usepackage{hyperref} % good for urls, but it also URLizes references
\definecolor{linkcolor}{rgb}{0.2,0.6,0.7} % Neuron-style link color
\usepackage[colorlinks=true,citecolor=linkcolor,urlcolor=blue]{hyperref}%
%\usepackage{url}

% improves typesetting in LaTeX
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% text layout
\raggedright
%\textwidth 6in 
%\textheight 9in
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

% adjust caption style
\usepackage[aboveskip=5mm,labelfont=bf,labelsep=period,singlelinecheck=off]{caption}

% this is required to include graphics
\usepackage{graphicx}

% Multicolumns
\setlength{\columnsep}{1cm}

% Headers and footers
\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
\cfoot{} % To kill footer page numbers

\begin{document} % --------------------- Document start ----------------

%TC:ignore 
% The comment above is for texcount to ignore this text.
% It will ignore everything until the endignore pair, and so on.
% We need to get down to 4500 words in the main text.

\linenumbers % Comment to suppress line numbers

% title goes here:
%\twocolumn[
\begin{flushleft}
{\Large
\textbf\newline{Intrinsic temporal tuning of neurons in the optic tectum is shaped by multisensory experience}
}
\newline
% authors go here:
\\
Silas E. Busch\textsuperscript{1},
Arseny S. Khakhalin\textsuperscript{1,*}
\\
\bigskip
{1} Biology Program, Bard College, Annandale-on-Hudson, NY.

* Correspondence: khakhalin@bard.edu

\section*{Abstract}
% 150 words (149 as or Aug 07)

Homeostatic intrinsic plasticity is often described as an adjustment of neuronal excitability to maintain stable spiking output. Here we report that intrinsic plasticity in the tectum of Xenopus tadpoles also supports temporal tuning, wherein neurons independently adjust spiking responses to fast and slow patterns of synaptic activation. Using the dynamic clamp technique, and five different types of visual, acoustic, and multisensory conditioning, we show that in tadpoles exposed to light flashes, tectal neurons became selective for fast synaptic inputs, while neurons exposed to looming and multisensory stimuli remained responsive to longer inputs. We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties in tectal cells, as neurons that naturally received fast synaptic inputs tended to be most responsive to long-lasting synaptic conductances, and the other way around. These results expand our understanding of plasticity in the brain, and inform future work on the mechanisms of sensorimotor transformation.

% Acoustic stimuli had different effects when delivered alone, or when combined with visual stimuli.

%\textbf{Keywords}: homeostatic plasticity, intrinsic plasticity, temporal tuning, optic tectum, network development, dynamic clamp

\section*{Significance statement}
% 140 words (limit 150)
%TC:endignore
With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, researchers largely concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning. Here we show that in a sensory network in Xenopus tadpoles, different neurons do not just differ in overall excitability, but are also tuned, and respond stronger, to either short or long synaptic inputs. This temporal tuning tended to be opposite to the actual dynamics of synaptic inputs each cell received, such that neurons that normally received shorter inputs generated stronger spiking in response to longer testing currents, and the other way around. This new observation fits with other phenomena related to optimal encoding, and shows that even in networks that do not generate oscillations, neurons actively reshape their temporal selectivity, to optimize their impact on distributed calculations. 
%TC:ignore 
\bigskip

\end{flushleft} % Only relevant for two-column documents, but doesn't hurt
%] % End of one-column region

\section*{Introduction}
% Sep 04: 645 words (limit 650)

It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity, yet biological neurons are tuned in ways that go well beyond adjusting one “strength” value per synapse. Cells within the same network often demonstrate variability of activation thresholds \citep{kole2012}, production of bursts \citep{popovic2011}, inactivation by strong inputs \citep{bianchi2012}, and more. This diversity of tuning relies on coordinated changes of many parameters across a complex, multivariate landscape \citep{oleary2013}, as neuronal phenotypes are shaped by sensory experiences, and adjusted by modulatory inputs \citep{evans2015}. The dysregulation of intrinsic plasticity can affect network dynamics \citep{tien2018}, and lead to a loss of function \citep{marcelin2009}. However, for many networks, it is still unclear whether variation in intrinsic phenotypes is primarily a result of excitability calibration, or whether it is a defining aspect of network topology and architecture \citep{titley2017}.

The optic tectum of the \textit{Xenopus} tadpole is an ideal model for exploring these questions: it is a highly malleable distributed network of about $10^4$ neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}. In development, tectal neurons acquire diverse intrinsic and synaptic phenotypes, that are also shaped by sensory experiences \citep{xu2011,ciarleglio2015}. Circuits in the tectum can learn and reproduce the temporal dynamics of inputs to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which is more likely to involve intrinsic temporal tuning \citep{narayanan2008,beatty2014}. Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, and is one of the targets for intrinsic plasticity \citep{bianchi2012}.

In this study, we asked two specific questions about the properties of intrinsic plasticity in tectal networks. First, whether intrinsic plasticity is limited to changes in excitability, or whether it is more nuanced and can differentially adjust neuronal responsiveness to inputs with different dynamics. Second, whether changes in intrinsic properties in the tectum are a homeostatic response to each cell's history of synaptic activation, or if they are independent of synaptic properties. In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and also, despite a thorough search, we did not detect signs of temporal tuning (ibid,  figures 2, 4). However, we propose that the standard current-clamp protocols used in previous studies \citep{pratt2007,hamodi2014} were not adequate to detect important changes in the function of voltage-gated channels (see "Discussion").

Here we show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness, and supports temporal selectivity that can be reshaped by sensory experience. Furthermore, we show that the tuning of intrinsic properties is coordinated with the duration of synaptic inputs received by each cell. These results rely on two methodological innovations: first, instead of using current injections, we employed the dynamic clamp technique, which allowed a more realistic simulation of synaptic conductances \citep{prinz2004}. Second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols, and compared their effects on intrinsic tuning. The use of different sensory modalities also gave us insight into an unrelated, but equally intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at the traces left by multisensory stimuli in the tectum of freely behaving tadpoles.

\section*{Results}

\subsection*{Changes in excitability in response to sensory stimulation}

Our first question was whether our stimulation protocols caused changes in intrinsic excitability of tectal neurons. From previous studies, we knew that in tadpoles exposed to four hours of LED flashes tectal neurons became more excitable \citep{aizenman2003,ciarleglio2015}. However, the stimuli we used were weaker, and similar to those used in behavioral experiments \citep{khakhalin2014,james2015,truszkowski2017}. We presented a checkerboard pattern that inverted once a second either instantaneously (Fig. 1C left, dubbed “Flash”), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares; Fig. 1C right; dubbed “Looming”; see “Methods”).

\begin{figure*}
\includegraphics[width=\linewidth]{fig1.png}
\caption{
Overview of experimental design, and summary of dynamic clamp results. (\textbf{A}). Positions of tectal neurons that were recorded. (\textbf{B}). Sample data from a dynamic clamp experiment. Bottom row: the dynamics of conductances G(t) of four different durations simulated by the dynamic clamp system. Middle row: the currents I(t) dynamically injected into a cell based on conductances of 4 different durations and 3 different amplitudes. Top row: resulting voltage traces V(t) that were recorded and analyzed. (\textbf{C}). A schematic of visual conditioning, in “Flash” (left) and “Looming” (right) groups. (\textbf{D}). The number of spikes produced by all neurons in all experiments, split by input peak conductance, and plotted against conductance duration. Black lines show respective averages. (\textbf{E}). A summary of data from (d), presented as averages and 95\% confidence intervals.}
\end{figure*}

After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Fig. 1A), and counted spikes produced in dynamic clamp, in response to simulated synaptic conductances of different durations and amplitudes (Fig. 1B). We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see "Methods"). Contrary to our expectations, when tadpoles were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Fig. 1D, left column; F(1,677)=30.4, p=5e-8; n cells=28, 29). Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25), which was likewise unexpected. In the tadpole tectum, looming stimuli are known to elicit stronger responses compared to instantaneous inversions \citep{khakhalin2014}, yet the suppression yielded by looming stimuli was weaker.

We then looked at how an increase in transmembrane conductance translated into increased spike output of neurons, to map their amplitude tuning, or amplitude transfer function. Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve, and did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively). The difference in amplitude tuning between these two types of stimulation was not significant (F(1,641)=3.5; p=0.06).

These results show that prolonged stimulation had an effect on intrinsic excitability, but its direction was opposite to what was previously described \citep{aizenman2003,ciarleglio2015}, as neurons became less excitable. Moreover, while looming stimuli are known to be more salient, both behaviorally and physiologically \citep{khakhalin2014}, they had a weaker long-term effect on neuronal excitability in comparison to less salient flashes. We conjecture that the difference in the direction of change is due to our stimuli being weaker than those used in earlier studies (see Discussion), and we further explore the difference between flashes and looming stimuli below.

\subsection*{Changes in intrinsic temporal tuning}

We then examined whether different types of sensory activation would differentially reshape temporal intrinsic tuning in tectal neurons. As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs. Alternatively, shorter stimuli could reshape the network, making neurons better adjusted to working with short bursts of activation, as  previously described for synaptic processing \citep{aizenman2007} and recurrent activity in the tectum \citep{pratt2007,shen2011}.

Across input conductances of different lengths (100, 200, 500, and 1000 ms), neurons exposed to flashes and looming stimuli responded differently than in control (F(1, 677)=25.1; p=7e-7; and F(1,629)=12.0; p=6e-4 respectively). In control neurons, longer inputs typically evoked stronger spiking, whereas neurons from stimulated animals had flatter tuning curves, with a plateau, or even a decrease in spike number for longer conductance injections (Fig 1E). In essence, while control neurons “preferred” longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006). This suggests that unlike the  change in overall intrinsic excitability, the average temporal retuning was “adaptive” rather than “homeostatic”, as neurons exposed to shorter stimuli (flashes) became more equipped to process shorter activation patterns.

\subsection*{Effects of acoustic and multisensory stimulation}

While the optic tectum (known as superior colliculus in mammals) is often described as a primarily visual area, it is also involved in heavy multisensory computations \citep{stein2014}. In tadpoles, it integrates visual information with inputs from mechanosensory, auditory, and lateral line modalities \citep{deeg2009,pratt2009,hiramoto2009,felch2016,truszkowski2017}, but the logic of this integration is still unclear. We wondered whether acoustic stimuli would reshape intrinsic properties of tectal neurons, and whether this retuning would be similar to that produced by visual stimuli.

To test this question, we exposed tadpoles to four hours of behaviorally salient “click” sounds \citep{james2015,truszkowski2017}, provided at the same frequency (every second) as visual stimuli in the first set of experiments. We found (Fig 1D, E) that exposure to startle-inducing sounds (group “Sound”) did not lead to significant changes in either average spikiness (0.8$\pm$0.7 spikes; F(1,689)=1.7; p=0.2; n=28, 30), amplitude transfer function (F(1,689)=2.0; p=0.2), or temporal tuning curve (F(1,689)=2.0; p=0.2). This suggests that acoustic stimuli did not strongly activate tectal circuits during conditioning, despite being more behaviorally salient (for our stimuli, at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}). As one possible explanation, auditory and mechanosensory inputs may have different cellular or subcellular targets in the tectum \citep{bollmann2009}, or they may differently recruit tectal inhibitory circuits \citep{liu2016,hamodi2016}.

We then combined visual and acoustic stimuli in two different ways and looked at the effects of multisensory stimulation on the intrinsic properties of tectal neurons. For some animals, we synchronized the instantaneous checkerboard inversions (flashes) with sound clicks (dubbed “Sync”), while for others we staggered visual and acoustic stimuli by half a period (500 ms; dubbed “Async”). We found (Fig 1D, E) that, after four hours of multisensory stimulation, tectal neurons were more excitable than after visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for sync and async respectively). Compared to the “Flash” group, the tuning curves in multisensory groups were less flat, with a stronger effect in the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively). This suggests that on their own sound clicks had little effect on tectal excitability, but when added to visual flashes, sound clicks negated effects of retuning that visual stimulation would have had (Fig 2C).

\begin{figure*}[!t]
\includegraphics[width=\linewidth]{fig2.png}
\caption{
Quantification of changes in temporal tuning in response to sensory experience. (\textbf{A}). An illustration of how “Temporal tuning” and “Amplitude tuning” values were calculated. For the temporal tuning measure, the value of zero corresponds to linear dependency (blue line), positive values - to an accelerating, supralinear curve (red), and negative values - to a plateau-shaped curve (purple, yellow). For amplitude tuning, higher values correspond to faster increase in spiking with increased conductance. (\textbf{B}). Amplitude tuning of neurons across different experimental groups. (\textbf{C}). Temporal tuning and average spikiness of neurons in different experimental groups; in each plot all neurons across all groups are shown in gray, while neurons from one target group are shown in color; means are shown as black dots; ellipses represent 95\% normal confidence regions. Two outliers (top right corner) are brought within the axes limits. (\textbf{D}). Same data as in (C), shown as averages for each group, with 95\% confidence intervals. Black arrows show the effects of sound clicks, when they were added to control, and when they were added to “Flashes”, to form two types of multisensory stimuli.}
\end{figure*}

\subsection*{Changes in average neuronal tuning, and tuning variability}

To visualize and interpret differences in neuronal tuning, we quantified each of the three aspects of intrinsic tuning (average spikiness, amplitude tuning, and temporal tuning) with one value per neuron (see Methods). We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value of "temporal tuning" (Fig. 2A). The numerical values of these "tuning coefficients" are not interpretable, but they capture the character of tuning curves for each neuron (Fig. 2A). All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Fig. 2C); F(5,160)=4.8, p=4e-4 for amplitude tuning (Fig. 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Fig. 2C).

A visual comparison of neuronal tuning in different experimental groups (Fig 2C) shows that acoustic stimulation had opposite effects when provided on its own (without visual stimulation) than when added to visual flashes. Compared to control neurons, cells exposed to sound had lower amplitude tuning coefficients (flatter curve, Cohen’s d=$-$0.29), and more negative (curving down, d=$-$0.27) temporal tuning coefficients. In contrast, when sounds were added to flashes, both transfer functions became less flat (d=0.65 and 0.26 for "Async" compared to “Flash”, for amplitude and temporal tuning respectively), and more like curves for control neurons. Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Fig. 2D), but negated the effect of visual stimulation when combined with it. This may imply that multisensory integration in the tectum is dominated by inhibition (see Discussion). Note also that looming stimuli had a weaker effect on neuronal tuning compared to flashes, both in terms of amplitude (d=0.44) and temporal tuning (d=0.22).

Describing neuronal tuning with only few variables allowed us to compare cell-to-cell variability of tuning in different experimental groups. We found that this variability decreased as neurons were modulated away from the baseline (Bartlett test p=2e-9 for amplitude tuning, p=1e-9 for temporal tuning; Fig. 2D). Groups that were significantly different in average values also had different variances (F-test with p$<$0.05), such as Control vs. Flash and Control vs. Looming for both amplitude and temporal tuning. This expands on a finding in our previous study \citep{ciarleglio2015} that prolonged patterned stimulation reduces diversity of tuning profiles in the network, reshaping them according to the spatiotemporal characteristics of the stimulus, with stronger stimuli having stronger effects on tuning diversity.

\subsection*{Changes in synaptic properties}

To see whether prolonged sensory stimulation affected synaptic inputs received by tectal neurons, we recorded evoked excitatory postsynaptic currents in response to optic chiasm stimulation. We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Fig. 3B) differed across experimental groups (Fig. 3A; F(5,161)=3.2, p=0.009). Both Sync and Async multisensory groups had larger early synaptic currents than the Control group (Tukey p=0.03 and 0.04; Cohen d=0.46 and 0.74 on log-transformed data respectively). The amplitude of late synaptic currents–produced by recurrent network activation (15-145 ms after the stimulus)–did not differ across groups.

\begin{figure*}[!t]
\includegraphics[width=\linewidth]{fig3.png}
\caption{Changes in synaptic transmission, and co-tuning of synaptic and intrinsic neuronal properties. (\textbf{A}). Amplitudes of early monosynaptic inputs to tectal neurons in all experimental groups (given in log scale, with outliers brought within the axes limits). (\textbf{B}). A sample synaptic recording, showing all traces (green) and an average trace (blue). The black bars show the areas at which early monosynaptic and late polysynaptic currents were measured; the vertical position of each bar represents the respective average current. The second, longer bar does not completely fit within the figure at this scale. (\textbf{C}). Synaptic current duration (vertical axis) was mostly defined by the amplitude of early monosynaptic inputs (horizontal axis). (\textbf{D}). Synaptic current duration was different between experimental groups (see the text). (\textbf{E}). Across experiments, average temporal tuning in each group positively correlated with the average durations of synaptic currents they received. (\textbf{F}). Within experimental groups, temporal tuning of individual neurons negatively correlated with the duration of synaptic currents they received. Axes show within-group deviations of temporal tuning and synaptic current duration from respective averages for each group. (\textbf{G}). Raw tuning and synaptic duration values for each treatment group, with linear regression lines.}
\end{figure*}

Neurons with different contribution of early and late synaptic responses naturally had different synaptic current duration, which we quantified for every cell as a “center of mass” of the current within the first 700 ms after optic chiasm stimulation (see “Methods”). As expected, cells with strong monosynaptic inputs had shorter synaptic currents, while polysynaptic activity made synaptic currents longer (Figure 3C; p=2e-16, r=$-$0.78, n=168). We found that the synaptic current duration was different across treatment groups (Fig. 3D; F(5,163)=6.3, p=2e-5). Cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24 and 304$\pm$40 ms respectively), indicating that prolonged sensory activation with short, frequent stimuli, reshaped synaptic transmission in the tectum, making it faster, because of selective potentiation of visual inputs from the eye.

\subsection*{Co-tuning of synaptic and intrinsic properties}

To see whether intrinsic and synaptic temporal properties of tectal cells coordinated with each other, we compared intrinsic temporal tuning of every neuron (that is, whether it preferred longer or shorter simulated synaptic inputs in dynamic clamp experiments) to the actual duration of synaptic inputs it received during in-vitro stimulation of the optic chiasm. We found that on average, cells exposed to stronger sensory stimuli preferred shorter synaptic inputs, and also received shorter synaptic inputs, leading to a positive correlation between average synaptic and intrinsic properties for each group (Fig. 3E; r=0.89, p=0.02, n=5). This means that \textit{between} treatment groups, changes in synaptic and intrinsic properties were adaptively coordinated, and the stronger was the average change in synaptic transmission, the more cells reshaped their intrinsic properties to adjust to this change.

In contrast, \textit{within} each experimental group, cells that preferred shorter synaptic inputs tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03). We calculated differences between the properties of each individual cell and the average for the experimental group it belonged to, and showed these "deviations from respective averages" on one plot (Fig. 3F). Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (r=$-$0.18, p=0.03, n=151). This means that individual neurons tended to homeostatically tune their intrinsic properties away from the statistics of their inputs, increasing their ability to respond to unusual patterns of synaptic activation.

%Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.04, p=0.7, n=151). This is a textbook example of a so called "Simpsons paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.

To better understand the interplay between the stimulation-induced retuning of the entire tectal network, and tuning of individual cells within each network, we looked at the interaction of intrinsic and synaptic temporal properties separately for each treatment group (Fig. 3G). The co-tuning seemed present in Control, Looming, and Sound groups (r=$-$0.11, $-$0.36, and $-$0.47), but was absent in all groups that experienced flashes in any form (r=0.27, $-$0.01, and 0.01 for Flash, Sync, and Async groups respectively). If three slow, and three fast (Flash-like) groups were combined into two larger "supergroups", the Control-Looming-Sound neurons exhibited a homeostatic negative correlation between synaptic duration and intrinsic temporal tuning (r=$-$0.29, p=0.01, n=70), while the Flash-Sync-Async neurons lacked cells preferring slow stimuli, and so lacked the co-tuning (r=0.08, p=0.50, n=80). This suggests that when fast visual stimulation made the tectal network selective to short activation patterns, it happened not because all neurons uniformly changed their properties, but because a particular subset of neurons, namely those that receive strong direct inputs from the retina and weak recurrent inputs, become less excitable. Normally these neurons experience fast synaptic inputs, but are most responsive to slow conductances; in overstimulated networks however they became selective to fast conductances.

For amplitude tuning, the interaction between synaptic and intrinsic parameters of tectal cells was inconclusive. The amplitude of early synaptic responses and intrinsic amplitude tuning formally correlated on a full dataset (p=0.03, r=$-$0.17, n=151), but the correlation disappeared (p$>$0.05) when the highly non-normal amplitude data was log-transformed, or when 4 extreme values (out of 135 total) were removed. When analyzed separately, the between-groups and within-groups correlations were also insignificant. A similar analysis for amplitudes of late synaptic currents also did not yield reliable results.

\subsection*{The mechanisms behind temporal intrinsic plasticity}

Knowing that tectal neurons can tune to inputs of different temporal dynamics, we then investigated the cellular mechanisms that could underlie this tuning. For each cell, we used a sequence of voltage steps (Fig. 4A) to activate Na and K conductances, and quantified ionic current amplitudes and activation potentials (Fig. 4B) as it was done in earlier studies \citep{ciarleglio2015}. Together with cell membrane resistance (Rm) and capacitance (Cm) it gave us eight intrinsic parameters for every cell: peak amplitudes for sodium current, early (transient) potassium current, and late (stable) potassium current (INa, IKt, IKs respectively), and activation potentials for these three currents (VNa, VKt, and VKs).

\begin{figure}[!t]
\centering
\includegraphics[width=3.2in]{fig4.png}
\caption{Electrophysiological properties of individual neurons, compared to their spiking in current and dynamic clamp experiments. (\textbf{A}). Sample curves for a voltage step experiment; black bars show the areas used to average Na (bottom) and transient K (top) currents (see Methods). (\textbf{B}). Processing of ionic currents data, with IV-curves translated into two parameters (threshold potential and peak current) for each ionic conductance. (\textbf{C}). Sample data from a current clamp experiment; spikes are marked with black dots. (\textbf{D}). Estimations of spikiness from current clamp experiments (horizontal axis) and dynamic clamp experiments (vertical axis) correlate. (\textbf{E}). One of the explanatory correlations between neuronal spiking in current clamp experiments and an ionic current (in this case, peak Na current). (\textbf{F}). Similar correlation for the dynamic clamp experiments.}
\end{figure}

We ran a stepwise generalized linear model selection analysis (R package stepAIC, \citealt{venables2013}) to explain the intrinsic tuning of cells recorded in all experimental groups through these eight variables. We found that the average spikiness (after compensation for position within the tectum; see Methods) was best described by a combination of sodium peak current (INa) and membrane resistance (Rm) variables, but these variables explained only 8\% and 2\% of cell-to-cell variance respectively (F(1,130)=11.3, and F(1,130)=4.5; Fig. 3E). Together, all eight cellular parameters described only 13\% of variance in average spikiness. The temporal tuning value was best explained by sodium current activation potential and membrane resistance (VNa: 7\%, F(1,147)=10.7; Rm: 2\%, F(1,147)=3.1), with all eight variables explaining only 11\% of total variance. For amplitude tuning, the proposed best model included peak sodium current (INa: 6\%, F(1,163)=10.0) and sodium activation potential (VNa: 2\%, F(1,1,163)=3.5), with all eight variables accounting for 10\% of variance. This very low total explained variance suggests that while ionic currents and their activation potentials clearly affected intrinsic tuning of tectal cells, most cell-to-cell variability in intrinsic phenotypes stemmed from some other properties that were different between cells. In agreement with this assessment, the effect of experimental group on either mean spiking, temporal, or amplitude tuning curves remained significant even after compensating for all 8 intrinsic properties (sequential sum of squares analysis of variance p=0.03, 0.001, and 0.003 respectively), suggesting that changes in tuning across experimental groups was mediated by other factors.

\subsection*{A comparison between dynamic clamp and current clump experiments}

The inability to predict spiking of tectal neurons through their isolated electrophysiological properties was unexpected, and stood in a seeming contradiction with our previous study \citep{ciarleglio2015}. Fortunately, in the current study, we recorded spiking traces in response to “classic” current steps (Fig. 4C), which allowed a direct comparison between the results of current clamp and dynamic clamp protocols. Across all cells, the maximal number of spikes observed during current step injections correlated with the average number of spikes in dynamic clamp experiments (Fig. 4D; r=0.46, p=2e-9, n=152). In agreement with \citep{ciarleglio2015}, spiking in current clamp experiments correlated with peak sodium (INa: r=0.42, p=2e-8, n=152; Fig. 4F) and stable potassium currents (IKs: r=0.39, p=2e-7), as well as activation potential for sodium current (VNa: r=0.24, p=0.02). Overall, the 8 intrinsic variables described above (Rm, Cm, three peak currents, and three activation potentials) explained 61\% of cell-to-cell variability in the maximal number of spikes from current clamp experiments, comparable to 49\% reported in our previous study \citep{ciarleglio2015}, and noticeably higher than 13\% for dynamic clamp experiments.

We can therefore conclude that our set of eight cellular parameters can better predict spiking during current step injections (61\% of variance) than in dynamic clamp experiments (13\% of variance). This suggests the existence of internal properties that strongly affect spiking in dynamic clamp experiments, but are inaccessible through standard current and voltage step protocols (see Discussion). Our hypothesis is indirectly supported by two more observations: that of the eight cellular parameters only one was significantly (p$<$0.05) different across treatment groups (NaV: F(5,175)=3.7, p=0.003), and that the number of spikes detected in current clamp experiments did not differ across experimental groups (F(5,165)=0.8, p=0.6).

\subsection*{Effects of position within the tectum}

In all analyses presented above, we adjusted cell properties for rostro-caudal and media-lateral position of each cell within the tectum, as in tadpoles both intrinsic \citep{hamodi2014} and synaptic properties \citep{wu1996,khakhalin2012} differ between older (rostro-medial) and younger (caudal, lateral) parts of the developing tectum. Most cell properties we measured correlated (p$<$0.05, after correction for treatment group differences) with either medial or rostral position within the tectum (medial: membrane capacitance r=$-$0.17, membrane resistance r=0.25, sodium current activation potential r=$-$0.30, stable potassium current r=$-$0.16, early synaptic amplitude r=$-$0.22, synaptic current duration r=0.29; rostral: peak sodium current r=0.18, late synaptic amplitude r=0.11; n between 168 and 183). Curiously, neither of the three measures of intrinsic tuning (average spikiness, temporal tuning, and amplitude tuning) correlated with position (p$>$0.1, n=168). This suggests that while low-level properties of each cell depended on its age, its spiking phenotype was age-independent. Thus, different cells seemed to achieve similar spiking behaviors through different combinations of underlying parameters, relying on the principle of “parameter degeneracy” \citep{prinz2004degeneracy,drion2015}.

\section*{Discussion}
% Sep 04: 731 words with citations

In this study we show that different sensory stimuli differentially retuned neurons in the optic tectum of \textit{Xenopus} tadpoles, inducing changes in both their temporal tuning, and amplitude transfer functions. This addresses our first question and shows that intrinsic plasticity does not simply adjust neuronal spikiness, but can regulate selectivity for inputs of different dynamics. In answer to our second question, we show that synaptic and intrinsic temporal properties of neurons are homeostatically co-tuned, and that this co-tuning is affected by sensory experience.

In contrast with earlier studies that report increased excitability post-stimulation \citep{aizenman2003,dong2009,ciarleglio2015}, we found that sensory stimulation led to a suppression of spiking. We suggest that the visual stimulation used in earlier studies, which was provided with a LED box, was so bright and of high contrast that it caused a suppression of retinal synaptic inputs via a polyamine block of AMPA receptors \citep{aizenman2003}. This suppression triggered a “second-order” homeostatic compensation \citep{turrigiano2011,tien2018}, making neurons spikier. In our current experiments, synaptic inputs were not suppressed, and neuronal activation during sensory conditioning was stronger than in control, causing intrinsic spikiness to decrease.

The difference between the dynamic clamp results (that were affected by stimulation, but could not be explained through low-level intrinsic parameters) and the results obtained in current- and voltage-clamp experiments (that were not affected by stimulation, yet better coordinated with intrinsic parameters) may be interpreted in two ways. We could assume that dynamic clamp in the soma provided a bad approximation for the peripheral synaptic inputs, as space clamp error is more pronounced for fast voltage fluctuations than for constant current injection \citep{spruston1993,prinz2004}. We however find this hypothesis unlikely, as dynamic clamp responses were consistently different in animals with different sensory history, which suggests that we have captured some important aspects of intrinsic diversity, even if our estimations were biased. More likely, intrinsic excitability is affected by properties that are not accessible by standard voltage and current clamp protocols, such as axon initial segment relocation, or targeted modulation of axonal voltage-gated channels \citep{grubb2010,kole2012}. In cells with excitable dendrites, channels of the axon initial segment may constitute only a small fraction of all voltage-gated channels, yet have a disproportionately large effect on the spiking output of the cell, including its temporal tuning \citep{kole2007,hamada2016}. Furthermore, prolonged current injections in the soma are likely to inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channels recovery during burst firing \citep{popovic2011,kole2012}. This effect would still affect spiking in more realistic dynamic clamp experiments.

Overall, we present a novel case of temporal selectivity in non-oscillatory neurons in a distributed sensory network, and demonstrate that intrinsic temporal tuning of neural cells correlates with their synaptic properties. It is particularly interesting that the temporal co-tuning we observed was homeostatic in nature, as cells tended to be selective for inputs of dynamics they did not usually experience. We hypothesize that this homeostatic adjustment of temporal tuning is the reason why this tuning was so easily disrupted by strong visual stimulation, when for a few hours we drastically changed the statistics of inputs received by every cell. Tuning to "unusual stimuli" at the level of individual neurons fits into the narrative of information transfer maximization \citep{brenner2000} and network criticality \citep{rubinov2011}, wherein every element of a network tries to locally maximize its influence over the overall computation. This may have intriguing consequences for the function and development of sensory networks in the brain, which can be further probed by computational modeling \citep{khakhalin2014,jang2016}, and verified in experiments. We also suspect that any cell with a sufficiently large dendritic tree would be able to tune its temporal intrinsic selectivity the way we describe. We expect that in most cases these changes would not be noticeable in experiments with standard voltage- and current-clamp protocols, but can be probed with a dynamic clamp technique. It would therefore be intriguing to see whether our results will replicate in other sensory systems, such as the mammalian cortex.

%Our findings lead to several verifiable predictions. As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014,jang2016}, a change in temporal tuning should affect collision detection thresholds, which can be predicted in a model, and verified experimentally. Similarly, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it would be likely to reduce peak activation in vivo.

% tectal oscillations were described both in post-metamorphic frogs \citep{baranauskas2012}, and in non-amphibian species \citep{sridharan2011,goddard2012,grossberg2016}.

\section*{Acknowledgements}

We would like to thank Carlos Aizenman (Brown University), Justin Hulbert (Bard College), and Kara Pratt (University of Wyoming) for their feedback on this paper drafts. Part of this work was supported by the Bard Summer Research Institute (BSRI) program.

% \section*{Declaration of Interests}

The authors have no conflicts of interest to disclose.

\section*{Author Contributions}

S.E.B.: Conception and design, acquisition of data, analysis and interpretation of data, drafting and revising the article.

A.S.Kh.: Conception and design, analysis and interpretation of data, figure preparation, drafting and revising the article.

\section*{Materials and Methods}

% All data reported in this study, as well as the code used for its analysis, is available from the corresponding author (A.S.Kh.) upon request.

\subsection*{Housing and sensory conditioning}

All experimental protocols were in accordance with Bard College Institutional Animal Care and Use Committee (IACUC), and National Institutes of Health (NIH) guidelines. Animals were purchased from Nasco (Fort Atkinson, WI, USA) at developmental stages 44-47, and raised to stages 48-49 on a 12/12 h light/dark cycle at 18 $^{\circ}$C.

In the beginning of each experiment, a tadpole was put in a Petri dish (diameter of 10 cm) filled with 1-1.2 cm of tadpole rearing medium, placed on top of a CRT monitor, with two speakers connected to the Petri dish with short wooden struts \citep{james2015,truszkowski2017}, and kept there for 4 hours. The tadpole was visually isolated from the rest of the room with a cardboard box surrounding the apparatus. For Control and Sound groups, the monitor was on, but showed a uniform 50\% gray background. For Flash, Sync and Async groups the screen showed a black-and-white checkerboard pattern, with each square in the pattern being 14 mm wide; this pattern flipped (inverted) every 1 second. For the Looming group, the inversion of the pattern was not instantaneous, but lasted for one second, with old black squares linearly shrinking into white background, and new black squares appearing and linearly expanding in the middle of each white square (Fig. 1C). The stimulation program was written in JavaScript, using the p5.js library \citep{mccarthy2015}, and is available at \url{http://faculty.bard.edu/~akhakhal/checker_flash_ding.html} . For Sound, Sync, and Async groups a broad-spectrum sound click was delivered through the speakers every 1 second, with left and right speakers playing the same waveform, but inverted. Formally the click was generated as a 5 ms pulse of 100 Hz sine wave, but it was also distorted by the non-linearities in the system. The sound volume was calibrated to be about 2 times higher than the threshold volume, which means that it reliably evoked startle responses with about 80\% success ratio, at least at the beginning for the conditioning protocol. For the Sync group, the sound clicks and the checkerboard inversions were synchronized, while for the Async group they were offset by 500 ms (half a period).

\subsection*{Electrophysiology}

Immediately after sensory conditioning, tadpoles were anesthetized in 0.02\% tricaine methanesulfanate (MS-222). Dorsal commissures were cut, the brain was dissected out \citep{aizenman2003,ciarleglio2015}, and placed in the recording chamber filled with artificial cerebrospinal fluid (in mM: 115 NaCl, 4 KCl, 3 CaCl2, 3 MgCl2, 5 HEPES, 10 glucose, 10 $\mu$M glycine; pH 7.2, osmolarity 255 mOsm). All chemicals were obtained from Sigma (Sigma-Aldrich, St. Louis, MO). The ventricular membrane was removed (suctioned) using a broken glass electrode. Cells were visualized with a Nikon (Tokyo, Japan) Eclipse FN1 light microscope with a 40x water immersion objective. Recordings were restricted to the middle of the tectum, as in earlier studies \citep{ciarleglio2015}, from 25\% to 53\% of brain half-width medially from the lateral edge, and from 36\% to 69\% of tectum length rostrally from the caudal edge of the tectum (Fig. 1A). Care was taken to record only from “deep” primary tectal cells (that are located superficially in our preparation), and not from MV cells \citep{pratt2009} or superficial layer cells (that are located deep in the tectum in our preparation) \citep{liu2016}. Glass electrodes (1.5x0.86 mm borosilicate glass; Sutter instruments, Novato, CA) were pulled on a Sutter P-1000 puller (Sutter instruments), to a tip resistance of 8-12 MOhm. The elecrodes were filled with intracellular saline (in mM: 100 K-gluconate, 5 NaCl, 8 KCl, 1.5 MgCl2, 20 HEPES, 10 EGTA, 2 ATP, 0.3 GTP; pH 7.2, osmolarity 255 mOsm). Electrodes were placed in an Axon headstage (Molecular Devices, Sunnyvale, CA), controlled by a motorized micromanipulator (MX7600, Siskiyou, Grants Pass, OR). Whole cell patch clamp was established as usual \citep{ciarleglio2015}, with typical final access resistance of 30 MOhm, and membrane resistance Rm of 0.33 GOhm. Signals were measured with an Axon Instruments MultiClamp 700B amplifier (Axon Instruments, Foster City, CA), filtered with a 5 kHz band-pass filter, and digitized at 10 kHz a CED Power1401-3 Digitizer (Cambridge Electronic Design; Cambridge, England). For synaptic stimulation, a bipolar stimulating electrode (Warner Instruments, Hamden, CT) was placed on the optic chiasm [Wu 1996]; stimuli were controlled by the CED digitizer, and were delivered by A.M.P.I. stimulus isolator (AMPI, Jerusalem, Israel).

Each neuron was subjected to a series of electrophysiological measurements protocols (see below for details), closely matching experimental protocols from \citep{ciarleglio2015}. For each cell, we measured membrane resistance Rm and capacitance Cm in voltage clamp mode, and then (1) ran a series of voltage steps to measure ionic currents; (2) in current clamp mode, ran a series of current steps to assess cell spiking; (3) in dynamic clamp mode, subjected the cell to different conductance injections; (4) finally, if the cell was still in a good health, ran a synaptic protocol with optic chiasm stimulation. All data was processed offline using custom Matlab scripts (Mathworks, Natick, MA), and analyzed in R. In total, we recorded from 188 neurons in 35 tadpoles; of these, 159 cells had readings from all 4 protocols, while 12 lacked synaptic recordings; these 12 cells were scattered across all 6 experimental groups. After the recording was over, the position of each recorded cell was visualized with a 10x microscope, marked on a screen, measured in medial and rostral directions, relative to the most lateral caudal point of the tectum, and converted into percentage \citep{hamodi2014}.

\subsection*{Voltage steps protocol}

The baseline membrane potential was set at $-$60 mV (in this manuscript, the voltages are not adjusted for junction potential, which is expected to be equal to $-$12 mV for this combination of external and internal solutions). After Cm and Rm were measured with a standard seal test, cells were subjected to 11 voltage steps (square pulses), each 500 ms long, and 10 mV higher than the previous one, with 500 ms of baseline voltage between the steps. Each trial also contained a 50 ms long test pre-step of $-$10 mV relative to the baseline. During analysis, we averaged transition currents evoked by the leading and trailing edges of the pre-step, then scaled, and subtracted them from the current responses to the main step. For remaining active currents, we measured average currents during 0.4-2.7 ms after the step (Na current), 5.7-19.7 ms after the step (Kt, or transient potassium current), and 430-490 ms (Ks, or stable potassium current). This approach is standard for recordings from the Xenpus tectum, as ionic currents are slow enough to be separated temporally \citep{aizenman2003}. The ionic conductances were quantified as is \citep{ciarleglio2015}. For each cell, the values of current as a function of voltage were fit with an empirical parametric equation:

$$I(v) = c \cdot \exp(x/b_1)/(1+\exp(-(a-x)/b_2))$$

\noindent for Na and Kt currents (sigmoid, followed by exponential decay, inactivating), and a different equation:

$$I(v)=\max(0,\exp((x-a)/b)-e)\cdot c+d$$

\noindent for Ks current (a shifted piece of exponentially increasing curve with its lower part cut off; not inactivating). For equations with inactivation, we used its $I_{max}$ value at a measure of amplitude, and $v_a$ on the rising front such $I(v_a)=I_{max}/2$ as the threshold potential. For curves without inactivation (Ks) we used $I_{max}$ and the first non-zero point ($v_a=a+\log(e)\cdot b$) for the same purpose.

As a preliminary verification of our results, we compared the overall structure of our new dataset with the dataset from the 2015 study \citep{ciarleglio2015}. The eight cellular parameters described above showed similar pattern of coordination in both datasets: 23 pairwise correlations out of 35 total were significant (p$<$0.05) in this dataset, compared to 21 out of 35 in the 2015 study. The average absolute value of correlation coefficient was r=0.38 in this study, compared to r=0.32 in 2015 study. This suggests that the datasets are similar and representative of true internal variability in the tectum.

\subsection*{Current steps protocol}

For the current steps protocol, we switched each cell to current clamp mode, and adjusted the stable holding current to bring the resting membrane potential to about $-$60 mV. We then subjected the cell to 10 current pulses 150 ms each, delivered every 1 s, with currents ranging from 0 to 180 pA, in 20 pA increments. Cells that did not produce at least one spike in this experiment were considered not-excitable, and were not included in the dataset. The largest number of spikes produced in response to a single current injection was estimated offline, manually, using a custom Matlab data browser that blinded the researcher to the identity of the cell. As a control, spikes were also detected automatically, using the filtering and thresholding approach that was used in \citep{ciarleglio2015}; in 78\% of cells both manual and automated estimations matched, in remaining 22\% of cells the mismatch was either due to artifacts on the rising front being auto-detected as spikes, or due to spike broadening that fell below the threshold for the adaptive filter. The number of cells in which manual spike detection disagreed with automated detection did not differ across groups (6.1$\pm$1.7; p=0.5, exact Fisher test).

\subsection*{Dynamic clamp protocol}

For dynamic clamp experiments, each cell was held at $-$50 mV baseline potential, and was stimulated with 12 different “conductance injections”, each repeated 5 times. Conductance curves were generated with a formula $G=g\frac{t}{\tau}\exp(1-\frac{t}{\tau})$ , known as “alpha synapse”, where $g$ and $\tau$ are conductance and decay parameters respectively \citep{destexhe1994}. We used four different values of $\tau$, to represent four typical patterns of synaptic activation: 20 ms, corresponding to the total curve length (decay to 10\ of the peak value) of about 100 ms, to approximate short monosynaptic inputs \citep{ciarleglio2015}; 40 ms, corresponding to the total curve length of about 200 ms, as for a typical in-vitro stimulus with polysynaptic activation \citep{xu2011}; 100 ms, to mimic in-vivo inputs to the tectum in response to abrupt disappearance of light (“dark-flash”) \citep{khakhalin2014}; and 200 ms, to mimic retinal inputs in response to a 1 second-long linear looming stimulus \citep{khakhalin2014}. Actual decay times to 10\% of peak amplitude were 98, 196, 489, and 978 ms respectively. The value of $g$ was adjusted so that conductance curves peaked at 3 target conductances of 0.2, 0.5, and 1 nS. With the cell clamped at $-$50 mV, these conductances would have induced currents that peaked at 10, 25, and 50 pA respectively, matching the range of peak synaptic currents observed in \citep{xu2011,khakhalin2014,ciarleglio2015}.

For each cell, for each of 60 trials, spikes were counted manually, blindly, and independently by both authors, using a custom Matlab data browser script. There was a 98.5\% agreement between spike number estimations on a trace-by-trace basis. All cases of disagreement (usually $\pm$1 spike) were due to later action potentials becoming broader and smaller in amplitude, which made them ambiguous. We ran sensitivity analyses of main effects reported in this paper separately on both estimations, and got qualitatively identical results. Numerically, we went with consensus numbers that in each case followed the higher estimation for the number of spikes.

To quantify the “shape” of spiking responses to conductances of different duration (temporal tuning), for every cell we encoded curve duration as an ordinal value (from 1 to 4), fit the spike data as a function of response duration with a quadratic formula ($y = ax^2 + bx +c$), and used the quadratic coefficient $a$ as the measure of response non-linearity. While the units and absolute values of this coefficient are not interpretable, it captures the shape of the response curve well, and allows for easy comparisons between cells (Fig. 2A). The case of $a=0$ corresponds to spiking output linearly increasing with duration increase; $a>0$ means supralinear preference for long conductances (curving up); about $-0.25<a<0$ corresponds to a plateau-shaped curves, while $a<-0.25$ would mean heavy spike inactivation for longer conductance injections.

\subsection*{Synaptic recordings}

For synaptic recordings, we switched cells back to voltage clamp mode, holding the membrane potential at $-$45 mV, to isolate excitatory synaptic currents. Optic chiasm shocks were delivered 10 times, every 20 s, with stimulation strength between 0.05 and 0.4 mA, and pulse length of 0.2 us. In each experiment, we would first find stimulation strength that evoked consistent synaptic responses in the cell we patched, then increased it by 20\%, and kept it constant for all cells recorded from this brain. Recordings were processed offline; for each trial we used the average current between 5 and 15 ms as a measure of monosynaptic response amplitude, and current between 15 and 145 ms as a measure of polysynaptic response amplitude \citep{ciarleglio2015}. The weighted duration of synaptic responses was calculated as the “center of mass” under the first 700 ms of the curve:

$$\displaystyle l=\int\limits_{0 \leq t \leq T}{I(t)\, t \, dt} \; \Big/ \int\limits_{0 \leq t \leq T}{I(t) \, dt}$$

\subsection*{Statistics and reporting}

To analyze the numbers of spikes observed in dynamic clamp experiments, we averaged spike numbers across 5 repetitions for each combination of conductance curve duration and amplitude, which resulted in 12 values per cell, and then used sequential sum of squares repeated measures analysis of variance. Both different condunctance amplitudes and curve durations were represented as ordinal values, and differences between experimental groups were assessed as interactions with the experimental group factor. To verify the validity of this approach, we also ran a maximal likelihood mixed-effects model with type III interaction terms, as implemented in R package “lmer”, with “lmerTest” extension to get access to Satterthwaite degrees of freedom and p-value estimations \citep{kuznetsova2017}. The results of both methods were numerically very similar.

For comparisons or summative values and individual cell parameters between experimental groups we report p-values of fixed effect sequential sum of squares linear model (ancova), in which rostral and medial coordinates of each cell within the tectum are included as covariates, and experimental group - as the main factor. All comparisons and correlations between cell parameters are performed on values corrected for cell position within the tectum. Position correction was based on a two-way linear regression model without interaction. For five variables that were distributed extremely non-normally, this correction for position was performed on transformed values (original values were transformed, linearly adjusted, and then transformed back): for early and late mean synaptic amplitudes we used a transformation $a'=log(1-a)$; for the variability of synaptic amplitudes $s'=log(1+s)$; for temporal tuning $y_t' = \sqrt{y_t}$ . Where appropriate, we performed the analysis with and without extreme outliers, and reported the difference. All analyses presented in the paper were also verified in mixed model analyses, with animal id included as a random factor.

\nolinenumbers
\bibliographystyle{apalike} % For author-year
%\bibliographystyle{unsrtnat} % For Nature-style
\bibliography{refs}

%TC:endignore
\end{document}

### 2018-09-22 dynamic_alpha_curve_tester.m

@@ -1,0 +1,26 @@
+function dynamic_alpha_curve_tester
+% dynamic_alpha_curve_tester
+% Tests shapes of alpha curves
+
+tauSet = [20, 40, 100, 200];
+t = 0:1:2000;
+
+figure('Color','w');
+for(q=1:4)
+    tau = tauSet(q);
+    y = (t/tau).*exp(1-(t/tau));
+    y = y/max(y);
+
+    tmax = find(y==1);
+    t90 = find(y>0.1,1,'last');
+
+    subplot(2,2,q);
+    hold on;
+    plot(t,y);
+    plot(t90,y(t90),'r.');
+    text(t90+100,y(t90),num2str(round(t90)),'Color','red');
+    hold off;
+    title(['tau = ' num2str(tau)]);
+end
+
+end

### 2018-09-22 dynamic_dynamic_reader.m

@@ -1,0 +1,240 @@
+function dynamic_dynamic_reader()
+% Actually reads dynamic clamp data, and lets the user count spikes.
+
+% Jun 06 2018: Updated.
+
+map = dynamic_what_is_where();
+% useful fields: folder, id, prefix, dynamic
+nCells = length(map.id);
+cellList=1:nCells;
+%cellList = 103:105;   % Uncomment for roubleshooting
+
+folderName = 'C:\_Data\_Silas\';
+
+mapId = [];
+mapFolder = [];
+mapPrefix = [];
+mapFile = [];
+S = [];                                 % Create the global data structure
+
+for(iCell=cellList)
+    if(~isnan(map.dynamic(iCell)) & (map.group(iCell)<=5)) % Only leave meaningful cells in the group
+        mapId = [mapId; map.id(iCell)];
+        mapFolder = [mapFolder; map.folder(iCell)];
+        mapPrefix = [mapPrefix; map.prefix(iCell)];
+        mapFile = [mapFile; map.dynamic(iCell)];
+    end
+end
+
+
+%%% ----------------- Now all the data is loaded and we can browse through it
+
+% fprintf('.... Started\n');
+hF = figure;
+fpos = get(hF,'Position');
+set(hF,'Position',[fpos(1)-fpos(3)/2 fpos(2) fpos(3)*2 fpos(4)]); drawnow; % Without 'drawnow' returns an error every now and then (when position is requested before being finalized)
+set(hF,'WindowButtonMotionFcn',@hoverfunction,'ButtonDownFcn',@mousepressfunction,'KeyPressFcn',@keyfunction,'ResizeFcn',@resizefunction);
+S.hA = axes;
+set(S.hA,'XLim',[0 2]);         % Only show first 20% of the curve
+hold on; % Pre-create high level graphic objects here
+S.hPmouse = plot(1,1,'g-');     % Future mouse coursor
+S.hPdata = plot(1,1,'b-');      % Future data
+hold off;
+
+% Set mouse function for all created objects, as axes function won't work for them
+set(S.hPmouse,'ButtonDownFcn',@mousepressfunction);
+
+% Initialize global variables here
+S.flagUpdate = 1;               % When set to 1, the main function will be called
+S.flagMakeFigure = 0;           % When this is set to 1, it generates a figure
+S.readNewFile = 1;              % Set to 1 when it's time to read a new file
[…]

### 2018-09-22 dynamic_iv_reader.m

@@ -1,0 +1,263 @@
+function dynamic_iv_reader()
+% function dynamic_iv_reader
+%
+% reads and processes IV curve files for Silas' data.
+
+% Oct 29 2017: last improved
+
+folderName = 'C:\_Data\_Silas\';
+showFigures = 1;                    % Whether figures are to be shown
+consoleOutput = 1;                  % Whether reading files should be reported
+doFit = 0;                          % If fancy exponential fit is to be used. Set to 0 if averaging is enough
+
+map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
+% S has the following fields that are all arrays:
+% id, group, prefix, folder (cell array), x, y 
+% iv, minis, istep, dynamic, synaptic - these all contain the file number
+
+nCells = length(map.id);
+cellList=1:nCells;
+
+cellList = 51; % Uncomment for testing. First 2 rows don't have an iv file
+
+z_l =  [100 450];           % Zero level
+prestep_l =  [504 1000];    % Test step area
+step_l = [2303 7302];       % Voltage step area
+na_l = [2307 2330];     % Window for Na current peak measurement
+kt_l = [2360 2500];     %            K transient mean
+ks_l = [6600 7200];     %            K stable mean
+v_prestep = -10;            % Voltage pre-step amplitude (that small one in the beginning), mV
+v_baseline = -60;           % Voltage baseline, mV
+v = (0:10)*10;              % Test voltage steps, mV
+bag = [];                   % That's where data will be collected
+
+fit_f = fittype('exp(-x/a)*b+c','independent','x');         % Fitting parameters; only important of doFit is set to 1
+fit_s = fitoptions('Method','NonlinearLeastSquares',...
+               'Lower',     [1      0       0],...
+               'Upper',     [1000   1000    1000],...
+               'Startpoint',[100  	10      10]);
+
+nCells = length(cellList);
+for(iCell=cellList)
+    if(~isnan(map.iv(iCell)))
+        fileName = [folderName map.folder{iCell} '\' num2str(map.prefix(iCell)) '_' sprintf('%03d',map.iv(iCell)) '.cfs'];
+        if(consoleOutput)
+            fprintf('%4d \t%4d \t%10s \t%s\n',iCell,map.id(iCell),map.folder{iCell},fileName);
+        end
[…]

### 2018-09-22 dynamic_minis_reader.m

@@ -1,0 +1,87 @@
+function dynamic_minis_reader()
+% function dynamic_synaptic_reader
+%
+% reads and processes minis files from Silas' data.
+
+% Dec 20 17: Modified from dynamic_iv_reader
+% Jan 09 18: Curve fit for the alpha curve
+% Jan 12 18: Modified from dynamic_synaptic_reader
+
+folderName = 'C:\_Data\_Silas\';
+showFigures = 1;                    % Whether figures are to be shown
+doFit = 1;                          % Whether curve fit needs to be performed (it may be rather slow)
+consoleOutput = 1;                  % Whether reading files should be reported
+
+map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
+% S has the following fields that are all arrays:
+% id, group, prefix, folder (cell array), x, y 
+% iv, minis, istep, dynamic, synaptic - these all contain the file number
+
+nCells = length(map.id);
+cellList=1:nCells;
+badCells = [];                            % 84: recorded in CC
+cellList = setdiff(cellList,badCells);
+% cellList = 57;                            % Uncomment for testing (to work with one recording only)
+cellList = [123 131 188 195 203]+10;   % Selected cells for testing (complicated curve shapes)
+nCells = length(cellList);
+
+x_zero =  [100 999];                        % Region ot measure zero level
+
+bag = [];                                   % That's where the data will be collected
+
+for(iCell=cellList)
+    if(~isnan(map.synaptic(iCell)))
+        fileName = [folderName map.folder{iCell} '\' num2str(map.prefix(iCell)) '_' sprintf('%03d',map.minis(iCell)) '.cfs'];
+        if(consoleOutput)
+            fprintf('%4d \t%4d \t%10s \t%s\n',iCell,map.id(iCell),map.folder{iCell},fileName);
+        end
+        ds = cfsload(fileName);         % Data structure with all data and info from the file
+        % res = ds;                     % Only keep uncommented if debugging
+        if(~isfield(ds,'data'))
+            fprintf('Warning: cannot read file %03d in folder %s\n',map.iv(iCell),map.folder{iCell});
+            continue
+        end
+        nSweeps = ds.info.sections;        
+        iCh = 1;                        % Which channel to use. I just happen to know it's 1
+        y = [];
+        for(iSweep=1:nSweeps)
[…]

### 2018-09-22 dynamic_steps_reader.m

@@ -1,0 +1,154 @@
+function dynamic_steps_reader()
+% function dynamic_synaptic_reader
+%
+% reads and processes current step files from Silas' data.
+
+% Dec 20 17: Modified from dynamic_iv_reader
+% Jan 09 18: Curve fit for the alpha curve
+% Jan 12 18: Modified from dynamic_synaptic_reader
+% Jun 06 18: Raw visualization added
+% Jun 12 18: Small improvements in vis
+
+folderName = 'C:\_Data\_Silas\';
+showFigures = 1;                    % Whether figures are to be shown
+figureType = 'pile';                % 'full', 'pile', or 'train'
+consoleOutput = 1;                  % Whether reading files should be reported
+
+map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
+% S has the following fields that are all arrays:
+% id, group, prefix, folder (cell array), x, y 
+% iv, minis, istep, dynamic, synaptic - these all contain the file number
+
+nCells = length(map.id);
+cellList=1:nCells;
+badCells = [];                              % 84: recorded in CC
+cellList = setdiff(cellList,badCells);
+cellList = 180:190;                         % Uncomment for testing (to work with selected few recordings only)
+% cellList = [141 198 205];                 % Some random cells for testing
+nCells = length(cellList);
+
+xZero =  [10 4900];                         % Region ot measure zero level
+xSignal = [5005 7000];                      % Region of the actual signal
+
+zThreshold = 0.02;                          % Spike detection threshold. 0.03 is kinda medium; 0.05 is conservative, 0.02 permissive
+
+bag = [];                                   % That's where the data will be collected
+
+for(iCell=cellList)
+    if(~isnan(map.synaptic(iCell)))
+        fileName = [folderName map.folder{iCell} '\' num2str(map.prefix(iCell)) '_' sprintf('%03d',map.istep(iCell)) '.cfs'];
+        if(consoleOutput)
+            fprintf('%4d \t%4d \t%10s \t%s\n',iCell,map.id(iCell),map.folder{iCell},fileName);
+        end
+        ds = cfsload(fileName);         % Data structure with all data and info from the file
+        % res = ds;                     % Only keep uncommented if debugging
+        if(~isfield(ds,'data'))
+            fprintf('Warning: cannot read file %03d in folder %s\n',map.iv(iCell),map.folder{iCell});
+            continue
+        end
[…]

### 2018-09-22 dynamic_synaptic_reader.m

@@ -1,0 +1,141 @@
+function dynamic_synaptic_reader()
+% function dynamic_synaptic_reader
+%
+% reads and processes synaptic files from Silas' data.
+
+% Dec 20 17: Modified from dynamic_iv_reader
+% Jan 09 18: Curve fit for the alpha curve
+
+folderName = 'C:\_Data\_Silas\';
+showFigures = 1;                    % Whether figures are to be shown
+doFit = 1;                          % Whether curve fit needs to be performed (it may be rather slow)
+consoleOutput = 1;                  % Whether reading files should be reported
+
+map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
+% S has the following fields that are all arrays:
+% id, group, prefix, folder (cell array), x, y 
+% iv, minis, istep, dynamic, synaptic - these all contain the file number
+
+nCells = length(map.id);
+cellList=1:nCells;
+badCells = [84];                            % 84: recorded in CC
+cellList = setdiff(cellList,badCells);
+cellList = 57;                            % Uncomment for testing (to work with one recording only)
+cellList = [123 131 188 195 203];   % Selected cells for testing (complicated curve shapes)
+nCells = length(cellList);
+
+x_zero =  [100 999];                        % Region ot measure zero level
+x_end = 9999;                               % Last x point
+x_end_fit = x_end;                          % last point to fit (may be shorter than the full fit)
+x_show = [2600 x_end];                      % Region to show on a plot
+x_art = 3003;                               % Artifact position
+x_art_safe = 3010;                          % By this point the artifact is almost zero
+x_mono = x_art + [5 15]*10 + [0 -1];        % Monosynaptic area, after [ciarleglio khakhalin 2015]
+x_poly = x_art + [15 145]*10;               % Polysynaptic area
+
+% g*t/tau*exp(1-t/tau)
+fitToUse = 'single';
+switch fitToUse
+    case 'single'
+        fit_f = fittype('min(0,-a*(x-b)/c*exp(1-(x-b)/c))','independent','x');         % Fitting parameters for double alpha-curve fit
+        fit_s = fitoptions('Method','NonlinearLeastSquares',...
+               'Lower',     [0      0          1       ],...
+               'Upper',     [Inf    200       1000     ],...
[…]

### 2018-09-22 dynamic_temporal_reader.m

@@ -1,0 +1,66 @@
+function S = dynamic_temporal_reader(S)
+% dynamic_temporal_reader(S)
+%
+% Reads Silas'es files.
+
+% Mar 08 2016: Created
+% Apr 11 2016: general update, + processing data.
+% Apr 12 2016: updated for new numerical cells.
+
+if(nargin<1) % No inputs - need to read the file
+    fprintf('No inputs received , need to read the Excel file... ');
+    fileName = 'C:\Users\Arseny\Documents\5_Dynamic clamp\Summer16 full data.xlsx';
+    % fileName = 'C:\Users\Arseny\Documents\5_Dynamic clamp\Data\Naive dataset.xlsx';
+    [dn,dt] = xlsread(fileName,'data');
+
+    % res.n = num; res.t = text;
+
+    nCells = size(dn,2)/3;
+    if(nCells~=round(nCells))
+        error('Cannot guess the number of cells');
+    end
+
+    for(iCell=1:nCells)
+        col = 1+(iCell-1)*3;    % Column at which the numerical data starts
+        S{iCell}.group = dn(1,col);
+        S{iCell}.data = dn(3:end,col+(0:2));
+        S{iCell}.name = dn(2,col);
+    end
+    fprintf('Done.\n');
+else
+    fprintf('Data provided as an argument, so NOT reading the file.\n');
+end
+
+
+%%% ------------- Writing reformatted outputs to a TXT file
+
+nCells = length(S);
+bagL = [];  % Labels for string data: Cell name
+bagN = [];  % Storage for numerical data: group (0:4), amplitude (1:3), shape (1:4), set (1:5), nSpikes
+for(iCell=1:nCells)
+    for(iRep=1:5) % 5 repetitions, arranged vertically, 4 rows in each
+        temp = sum(sum(S{iCell}.data((1:4)+(iRep-1)*4,:)));
+        if(~isnan(temp))
+            for(iAmp=1:3)
+                for(iShape=1:4)
+                    bagL = [bagL; S{iCell}.name];
+                    bagN = [bagN; S{iCell}.group iAmp iShape iRep S{iCell}.data(iShape+(iRep-1)*4,iAmp)];
+                end
+            end
+        else
+            fprintf('Incomplete repetition found: cell %d repetition %d\n',iCell,iRep);
+        end
+    end
+end
+
[…]

### 2018-09-22 dynamic_what_is_where.m

@@ -1,0 +1,560 @@
+function S = dynamic_what_is_where()
+% S = dynamic_what_is_where()
+%
+% Returns a structure with all info about what is stored where
+% S has the following fields that are all arrays:
+% id, group, prefix, folder (cell array), x, y 
+% iv, minis, istep, dynamic, synaptic - these all contain the file number
+
+% Oct 30 2017: Updated, after file attribution was cleaned somewhat (based in IV mistakes)
+
+S = [];
+S.folder = folder_list();
+a = big_array();
+
+S.id = a(:,1);
+S.group = a(:,2);
+S.x = a(:,3);
+S.y = a(:,4);
+S.prefix = a(:,5);
+S.iv = a(:,6);
+S.minis = a(:,7);
+S.istep = a(:,8);
+S.dynamic = a(:,9);
+S.synaptic = a(:,10);
+
+end
+
+function res = big_array()
+
+% Rows that were edited:
+% 137	3	183	188	20160209	6	7	8	9	10 - dynamic removed (seems incomplete; crashes the reader)
+% 141	3	177	188	20160209	25	26	27	28	29 - dynamic and synaptic swapped
+% 187	0	154	203	20160301	0	1	2	3	4  - dynamic removed (crashes the reader)
+% 230	2	150	174	20160318	44	45	46	47	48 - dynamic removed (crashes the reader)
+% 256	4	193	201	20160322	34	35	36	37	38 - dynamic removed (crashes the reader)
+% 258	4	183	223	20160322	44	45	46	47	48 - dynamic removed (crashes the reader)
+
+res = [
+1	8	121	188	20151009	NaN	NaN	NaN	NaN	NaN
+2	8	117	183	20151009	NaN	NaN	NaN	NaN	NaN
+3	8	144	187	20151009	2	3	11	12	NaN
+4	8	130	151	20151009	4	5	14	15	NaN
+5	8	219	224	20151009	6	7	16	17	NaN
+6	8	124	174	20151009	11	12	19	21	NaN
+7	8	167	114	20151020	0	1	0	1	NaN
+8	8	133	160	20151020	2	3	2	3	NaN
[…]

### 2018-09-22 silas_othervars.R

@@ -1,0 +1,688 @@
+# Silas everything that is not spikes analyzer
+# version May 24 2018
+# install.packages("lme4") # This one is required for lmerTest to work
+# install.packages("lmerTest")
+# install.packages("effsize")
+require("effsize")
+library(ggplot2)
+library(dplyr)
+library(ggbeeswarm)
+library(reshape2)
+library(MASS) # Model selection
+#require(lme4); detach("package:lme4",unload=T)
+library(lmerTest)
+#install.packages("viridis")
+require(viridis)
+rm(list = ls())  # Clear workspace
+
+# ----- Read the data ----
+d = read.table("C:/Users/Arseny/Documents/5_Dynamic clamp/mainInput 20180119.txt",header=T)
+d = mutate(d,group = reorder(group, groupid))
+# d_full = d                # Save a copy just in case
+
+names(d)
+d = subset(d,group %in% c('Control','Crash','Flash','Sound','Sync','Async'))
+d = mutate(d, group = recode_factor(group,'Control'='Control','Flash'='Flash','Crash'='Looming',
+                                    'Sound'='Sound','Sync'='Sync','Async'='Async'))
+
+# Estimations from the tectal photo and drawing:
+# Lower lip is about rostral of 325 (actually it's more like caudal)
+# Rostral end of tectum is rostral of about 0
+# Tectum edge is medial of about 375 (actually it's more like lateral )
+# Tectum midline is medial of about -25
+
+d$rostral = 1 - d$rostral/325
+d$medial = 1 - (d$medial + 25)/375
+
+# Now qplot(medial,rostral) will look like left tectum
+# "medial" is indeed how medial everything is
+# and "rostral" is indeed how rostral it is
+
+mean(d$rostral,na.rm=T)
+sd(d$rostral,na.rm=T)
+min(d$rostral,na.rm=T)
+max(d$rostral,na.rm=T)
+mean(d$medial,na.rm=T)
+sd(d$medial,na.rm=T)
+min(d$medial,na.rm=T)
+max(d$medial,na.rm=T)
+
+d$rm = d$rm/10  # Units mistake in the original dataset. Now it's in GOhm
+
[…]

### 2018-09-22 silas_spikes_plot_2017.R

@@ -1,0 +1,273 @@
+# Silas spiking data analyzer
+# version Oct 30 2017
+require(ggplot2)
+require(dplyr)
+require(reshape2)
+library(lmerTest)
+rm(list = ls())  # Clear workspace
+
+# ----- Read and prepare spike data ----
+d = read.table("C:/Users/Arseny/Documents/5_Dynamic clamp/out 20171025.txt",header=T)
+d = subset(d,is.element(Group,c(0,1,2,3,4,5))) # Remove slow and naive
+d = mutate(d,Group = recode_factor(Group,"0"="Control","2"="Flash","1"="Looming",
+                "3"="Sound","4"="Sync","5"="Async","6"="Slowc","7"="Slowf","8"="Naive"))
+d = mutate(d,ShapeName = recode_factor(Shape,"1"="100","2"="200","3"="500","4"="1000"))
+
+# Only leave good new crashes and flashes; exclude the bad old ones
+# (where "bad old" are all old cells that don't belong to Naive group)
+d$Old = ifelse(d$Cell<=102,"Old","New") # TRUE if the cell is old
+d$Old = factor(d$Old)
+d = subset(d,Old=="New")
+# d = subset(d,(is.element(Group,"Naive")) | (Old=="New"))
+
+
+# ----- Some simple analysis  ----
+# Count cell numbers:
+summarize(group_by(d,Group,Old), count = length(unique(Cell)))
+names(d)
+
+ds = summarize(group_by(d,Cell,Amp,Shape),Spikes=mean(Spikes))
+
+# Fit spike-curves, to quantify them with 3 parameters for each cell
+d1 = d %>% group_by(Cell) %>% 
+  do(fsa=lm(Spikes ~ (Amp-1),.),
+     fss=lm(Spikes~Shape+I(Shape^2),.),
+     ms=mean(.$Spikes)) %>% as_data_frame() %>%
+  summarize(Cell=Cell,ms=ms,sa=coef(fsa)[2],ss=coef(fss)[3],ms2=coef(fsa)[1])
+head(d1)
+# Sence-check if mean term is different than simple mean
+ggplot() + theme_bw() + geom_point(data=d1,aes(ms,ms2)) # Basically the same, doesn't matter
+
+# Testbed for these strange lm formulas
+t = c(1,2,3,4)-1
+y = c(0,1,2,3); lm(y~t + I(t^2)) # 0 (linear)
[…]

### 2018-09-22 silas_othervars.R
Update silas_othervars.R
Change data reference to local

@@ -16,7 +16,7 @@ require(viridis)
 rm(list = ls())  # Clear workspace
 
 # ----- Read the data ----
-d = read.table("C:/Users/Arseny/Documents/5_Dynamic clamp/mainInput 20180119.txt",header=T)
+d = read.table("data_mainInput.txt",header=T)
 d = mutate(d,group = reorder(group, groupid))
 # d_full = d                # Save a copy just in case
 

### 2018-09-22 silas_spikes_plot_2017.R
spikes_plot : change data ref to local

@@ -7,7 +7,7 @@ library(lmerTest)
 rm(list = ls())  # Clear workspace
 
 # ----- Read and prepare spike data ----
-d = read.table("C:/Users/Arseny/Documents/5_Dynamic clamp/out 20171025.txt",header=T)
+d = read.table("data_outDataset.txt",header=T)
 d = subset(d,is.element(Group,c(0,1,2,3,4,5))) # Remove slow and naive
 d = mutate(d,Group = recode_factor(Group,"0"="Control","2"="Flash","1"="Looming",
                 "3"="Sound","4"="Sync","5"="Async","6"="Slowc","7"="Slowf","8"="Naive"))

### 2018-11-29 silas_othervars.R
Comments made more readable

@@ -26,13 +26,13 @@ d = mutate(d, group = recode_factor(group,'Control'='Control','Flash'='Flash','C
                                     'Sound'='Sound','Sync'='Sync','Async'='Async'))
 
 # Estimations from the tectal photo and drawing:
-# Lower lip is about rostral of 325 (actually it's more like caudal)
-# Rostral end of tectum is rostral of about 0
-# Tectum edge is medial of about 375 (actually it's more like lateral )
-# Tectum midline is medial of about -25
+# Lower lip is has "rostral" of about 325 (which means that original numbers should have been called "caudal")
+# Rostral end of tectum has "rostral" of about 0
+# Tectum edge has "medial" of about 375 (which means that it shold have been called "medial")
+# Tectum midline has "medial" of about -25
 
-d$rostral = 1 - d$rostral/325
-d$medial = 1 - (d$medial + 25)/375
+d$rostral = 1 - d$rostral/325        # Move to true "rostral", and from screen units to %
+d$medial = 1 - (d$medial + 25)/375   # Move to true "medial"
 
 # Now qplot(medial,rostral) will look like left tectum
 # "medial" is indeed how medial everything is

### 2018-11-29 silas_spikes_plot_2017.R

@@ -1,5 +1,6 @@
-# Silas spiking data analyzer
+# Dynamic Clamp spiking data analyzer
 # version Oct 30 2017
+
 require(ggplot2)
 require(dplyr)
 require(reshape2)
@@ -38,7 +39,7 @@ head(d1)
 # Sence-check if mean term is different than simple mean
 ggplot() + theme_bw() + geom_point(data=d1,aes(ms,ms2)) # Basically the same, doesn't matter
 
-# Testbed for these strange lm formulas
+# Testbed for quadratic lm formulas we use:
 t = c(1,2,3,4)-1
 y = c(0,1,2,3); lm(y~t + I(t^2)) # 0 (linear)
 y = c(0,1,1,1); lm(y~t + I(t^2)) # -0.25 (plato)
@@ -86,7 +87,7 @@ ggplot(mutate(d2,ssgroup=floor(ss*5))) + theme_bw() +
 #   geom_point(alpha=0.2,size=3) +
 #   theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank());
 
-### Summary at treatment level (very aggregated)
+### Summary at a treatment level (very aggregated)
 # Summary plot with CI error bars (aka "main plot of the poster")
 d_sum = summarize(group_by(d,Group,Amp,Shape),
             sn = ShapeName[1],

### 2018-11-29 main.tex
paper: minor edits

@@
 \section*{Significance statement}
-% 140 words (limit 150)
+% 119 words (limit 120)
 %TC:endignore
-With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, researchers largely concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning.
-Here we show that in a sensory network in Xenopus tadpoles, different neurons do not just differ in overall excitability, but are also tuned, and respond stronger, to either short or long synaptic inputs.
-This temporal tuning tended to be opposite to the actual dynamics of synaptic inputs each cell received, such that neurons that normally received shorter inputs generated stronger spiking in response to longer testing currents, and the other way around.
-This new observation fits with other phenomena related to optimal encoding, and shows that even in networks that do not generate oscillations, neurons actively reshape their temporal selectivity, to optimize their impact on distributed calculations.
+With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, most researchers concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning.
+Here we show that in a sensory network in Xenopus tadpoles, different neurons are tuned, and respond stronger, to either short or long synaptic inputs.
+This tuning tended to be opposite to the actual dynamics of synaptic inputs each cell received, such that neurons that normally receive shorter inputs generated stronger spiking in response to longer testing currents, and the other way around.
+This observation shows that even in networks that do not generate oscillations, neurons reshape their temporal selectivity, to optimize their impact on distributed calculations.
 %TC:ignore 
@@
 
+All analysis scripts, and summary data for every cell, can be found at:  \url{https://github.com/khakhalin/Dynamic-clamp-2018}
+
 \subsection*{Changes in excitability in response to sensory stimulation}
@@
 However, the stimuli we used were weaker, and similar to those used in behavioral experiments \citep{khakhalin2014,james2015,truszkowski2017}.
-We presented a checkerboard pattern that inverted once a second either instantaneously (Fig.
-1C left, dubbed “Flash”), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares; Fig.
-1C right; dubbed “Looming”; see “Methods”).
+We presented a checkerboard pattern that inverted once a second either instantaneously (Figure 1C left, dubbed “Flash”), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares; Figure 1C right; dubbed “Looming”; see “Methods”).
 
@@
 
-After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Fig.
-1A), and counted spikes produced in dynamic clamp, in response to simulated synaptic conductances of different durations and amplitudes (Fig.
-1B).
+After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Figure 1A), and counted spikes produced in dynamic clamp, in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B).
 We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see "Methods").
-Contrary to our expectations, when tadpoles were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Fig.
-1D, left column; F(1,677)=30.4, p=5e-8; n cells=28, 29).
+Contrary to our expectations, when tadpoles were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8; n cells=28, 29).
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25), which was likewise unexpected.
@@
 To visualize and interpret differences in neuronal tuning, we quantified each of the three aspects of intrinsic tuning (average spikiness, amplitude tuning, and temporal tuning) with one value per neuron (see Methods).
-We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value of "temporal tuning" (Fig.
-2A).
-The numerical values of these "tuning coefficients" are not interpretable, but they capture the character of tuning curves for each neuron (Fig.
-2A).
-All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Fig.
-2C); F(5,160)=4.8, p=4e-4 for amplitude tuning (Fig.
-2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Fig.
-2C).
+We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value of "temporal tuning" (Figure 2A).
+The numerical values of these "tuning coefficients" are not interpretable, but they capture the character of tuning curves for each neuron (Figure 2A).
+All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Figure 2C); F(5,160)=4.8, p=4e-4 for amplitude tuning (Figure 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Figure 2C).
 
@@
 In contrast, when sounds were added to flashes, both transfer functions became less flat (d=0.65 and 0.26 for "Async" compared to “Flash”, for amplitude and temporal tuning respectively), and more like curves for control neurons.
-Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Fig.
-2D), but negated the effect of visual stimulation when combined with it.
+Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Figure 2D), but negated the effect of visual stimulation when combined with it.
 This may imply that multisensory integration in the tectum is dominated by inhibition (see Discussion).
@@
 Describing neuronal tuning with only few variables allowed us to compare cell-to-cell variability of tuning in different experimental groups.
-We found that this variability decreased as neurons were modulated away from the baseline (Bartlett test p=2e-9 for amplitude tuning, p=1e-9 for temporal tuning; Fig.
-2D).
+We found that this variability decreased as neurons were modulated away from the baseline (Bartlett test p=2e-9 for amplitude tuning, p=1e-9 for temporal tuning; Figure 2D).
 Groups that were significantly different in average values also had different variances (F-test with p$<$0.05), such as Control vs.
@@
 To see whether prolonged sensory stimulation affected synaptic inputs received by tectal neurons, we recorded evoked excitatory postsynaptic currents in response to optic chiasm stimulation.
-We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Fig.
-3B) differed across experimental groups (Fig.
-3A; F(5,161)=3.2, p=0.009).
+We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Figure 3B) differed across experimental groups (Figure 3A; F(5,161)=3.2, p=0.009).
 Both Sync and Async multisensory groups had larger early synaptic currents than the Control group (Tukey p=0.03 and 0.04; Cohen d=0.46 and 0.74 on log-transformed data respectively).
@@
 As expected, cells with strong monosynaptic inputs had shorter synaptic currents, while polysynaptic activity made synaptic currents longer (Figure 3C; p=2e-16, r=$-$0.78, n=168).
-We found that the synaptic current duration was different across treatment groups (Fig.
-3D; F(5,163)=6.3, p=2e-5).
+We found that the synaptic current duration was different across treatment groups (Figure 3D; F(5,163)=6.3, p=2e-5).
 Cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24 and 304$\pm$40 ms respectively), indicating that prolonged sensory activation with short, frequent stimuli, reshaped synaptic transmission in the tectum, making it faster, because of selective potentiation of visual inputs from the eye.
@@
 To see whether intrinsic and synaptic temporal properties of tectal cells coordinated with each other, we compared intrinsic temporal tuning of every neuron (that is, whether it preferred longer or shorter simulated synaptic inputs in dynamic clamp experiments) to the actual duration of synaptic inputs it received during in-vitro stimulation of the optic chiasm.
-We found that on average, cells exposed to stronger sensory stimuli preferred shorter synaptic inputs, and also received shorter synaptic inputs, leading to a positive correlation between average synaptic and intrinsic properties for each group (Fig.
-3E; r=0.89, p=0.02, n=5).
+We found that on average, cells exposed to stronger sensory stimuli preferred shorter synaptic inputs, and also received shorter synaptic inputs, leading to a positive correlation between average synaptic and intrinsic properties for each group (Figure 3E; r=0.89, p=0.02, n=5).
 This means that \textit{between} treatment groups, changes in synaptic and intrinsic properties were adaptively coordinated, and the stronger was the average change in synaptic transmission, the more cells reshaped their intrinsic properties to adjust to this change.
@@
 In contrast, \textit{within} each experimental group, cells that preferred shorter synaptic inputs tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
-We calculated differences between the properties of each individual cell and the average for the experimental group it belonged to, and showed these "deviations from respective averages" on one plot (Fig.
-3F).
+We calculated differences between the properties of each individual cell and the average for the experimental group it belonged to, and showed these "deviations from respective averages" on one plot (Figure 3F).
 Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (r=$-$0.18, p=0.03, n=151).
@@
 
-%Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.04, p=0.7, n=151).
+%%% --- This section was commented out in all official submissions
+Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.04, p=0.7, n=151).
 This is a textbook example of a so called "Simpsons paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.
 
-To better understand the interplay between the stimulation-induced retuning of the entire tectal network, and tuning of individual cells within each network, we looked at the interaction of intrinsic and synaptic temporal properties separately for each treatment group (Fig.
-3G).
+To better understand the interplay between the stimulation-induced retuning of the entire tectal network, and tuning of individual cells within each network, we looked at the interaction of intrinsic and synaptic temporal properties separately for each treatment group (Figure 3G).
 The co-tuning seemed present in Control, Looming, and Sound groups (r=$-$0.11, $-$0.36, and $-$0.47), but was absent in all groups that experienced flashes in any form (r=0.27, $-$0.01, and 0.01 for Flash, Sync, and Async groups respectively).
@@
 Knowing that tectal neurons can tune to inputs of different temporal dynamics, we then investigated the cellular mechanisms that could underlie this tuning.
-For each cell, we used a sequence of voltage steps (Fig.
-4A) to activate Na and K conductances, and quantified ionic current amplitudes and activation potentials (Fig.
-4B) as it was done in earlier studies \citep{ciarleglio2015}.
+For each cell, we used a sequence of voltage steps (Figure 4A) to activate Na and K conductances, and quantified ionic current amplitudes and activation potentials (Figure 4B) as it was done in earlier studies \citep{ciarleglio2015}.
 Together with cell membrane resistance (Rm) and capacitance (Cm) it gave us eight intrinsic parameters for every cell: peak amplitudes for sodium current, early (transient) potassium current, and late (stable) potassium current (INa, IKt, IKs respectively), and activation potentials for these three currents (VNa, VKt, and VKs).
@@
 We ran a stepwise generalized linear model selection analysis (R package stepAIC, \citealt{venables2013}) to explain the intrinsic tuning of cells recorded in all experimental groups through these eight variables.
-We found that the average spikiness (after compensation for position within the tectum; see Methods) was best described by a combination of sodium peak current (INa) and membrane resistance (Rm) variables, but these variables explained only 8\% and 2\% of cell-to-cell variance respectively (F(1,130)=11.3, and F(1,130)=4.5; Fig.
-3E).
+We found that the average spikiness (after compensation for position within the tectum; see Methods) was best described by a combination of sodium peak current (INa) and membrane resistance (Rm) variables, but these variables explained only 8\% and 2\% of cell-to-cell variance respectively (F(1,130)=11.3, and F(1,130)=4.5; Figure 3E).
 Together, all eight cellular parameters described only 13\% of variance in average spikiness.
@@
 The inability to predict spiking of tectal neurons through their isolated electrophysiological properties was unexpected, and stood in a seeming contradiction with our previous study \citep{ciarleglio2015}.
-Fortunately, in the current study, we recorded spiking traces in response to “classic” current steps (Fig.
-4C), which allowed a direct comparison between the results of current clamp and dynamic clamp protocols.
-Across all cells, the maximal number of spikes observed during current step injections correlated with the average number of spikes in dynamic clamp experiments (Fig.
-4D; r=0.46, p=2e-9, n=152).
-In agreement with \citep{ciarleglio2015}, spiking in current clamp experiments correlated with peak sodium (INa: r=0.42, p=2e-8, n=152; Fig.
-4F) and stable potassium currents (IKs: r=0.39, p=2e-7), as well as activation potential for sodium current (VNa: r=0.24, p=0.02).
+Fortunately, in the current study, we recorded spiking traces in response to “classic” current steps (Figure 4C), which allowed a direct comparison between the results of current clamp and dynamic clamp protocols.
+Across all cells, the maximal number of spikes observed during current step injections correlated with the average number of spikes in dynamic clamp experiments (Figure 4D; r=0.46, p=2e-9, n=152).
+In agreement with \citep{ciarleglio2015}, spiking in current clamp experiments correlated with peak sodium (INa: r=0.42, p=2e-8, n=152; Figure 4F) and stable potassium currents (IKs: r=0.39, p=2e-7), as well as activation potential for sodium current (VNa: r=0.24, p=0.02).
 Overall, the 8 intrinsic variables described above (Rm, Cm, three peak currents, and three activation potentials) explained 61\% of cell-to-cell variability in the maximal number of spikes from current clamp experiments, comparable to 49\% reported in our previous study \citep{ciarleglio2015}, and noticeably higher than 13\% for dynamic clamp experiments.
@@
 
+% Excplicitly say: because our resources are limited, in this study we did not address the mechanisms of this phenomenon, but we have two working hypotheses that we describe here.
+One, that maybe Na channels are modulated (phosphorylated?), or new channels are introduced, which changes inactivation dynamics.
+Another, that maybe there's a partial decoupling of different cellular compartments (dendritic tree, soma, and axon initial segment), either via minor but electrophysiologically important changes in cell morphology [ref], or via modulation of persistent K and Na channels [ref?] or both.
+
+%Our findings lead to several verifiable predictions.
+As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014,jang2016}, a change in temporal tuning should affect collision detection thresholds, which can be predicted in a model, and verified experimentally.
+Similarly, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it would be likely to reduce peak activation in vivo.
+
 Overall, we present a novel case of temporal selectivity in non-oscillatory neurons in a distributed sensory network, and demonstrate that intrinsic temporal tuning of neural cells correlates with their synaptic properties.
@@
 It would therefore be intriguing to see whether our results will replicate in other sensory systems, such as the mammalian cortex.
-
-%Our findings lead to several verifiable predictions.
-As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014,jang2016}, a change in temporal tuning should affect collision detection thresholds, which can be predicted in a model, and verified experimentally.
-Similarly, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it would be likely to reduce peak activation in vivo.
 
@@
 For Flash, Sync and Async groups the screen showed a black-and-white checkerboard pattern, with each square in the pattern being 14 mm wide; this pattern flipped (inverted) every 1 second.
-For the Looming group, the inversion of the pattern was not instantaneous, but lasted for one second, with old black squares linearly shrinking into white background, and new black squares appearing and linearly expanding in the middle of each white square (Fig.
-1C).
+For the Looming group, the inversion of the pattern was not instantaneous, but lasted for one second, with old black squares linearly shrinking into white background, and new black squares appearing and linearly expanding in the middle of each white square (Figure 1C).
 The stimulation program was written in JavaScript, using the p5.js library \citep{mccarthy2015}, and is available at \url{http://faculty.bard.edu/~akhakhal/checker_flash_ding.html} .
@@
 Cells were visualized with a Nikon (Tokyo, Japan) Eclipse FN1 light microscope with a 40x water immersion objective.
-Recordings were restricted to the middle of the tectum, as in earlier studies \citep{ciarleglio2015}, from 25\% to 53\% of brain half-width medially from the lateral edge, and from 36\% to 69\% of tectum length rostrally from the caudal edge of the tectum (Fig.
-1A).
+Recordings were restricted to the middle of the tectum, as in earlier studies \citep{ciarleglio2015}, from 25\% to 53\% of brain half-width medially from the lateral edge, and from 36\% to 69\% of tectum length rostrally from the caudal edge of the tectum (Figure 1A).
 Care was taken to record only from “deep” primary tectal cells (that are located superficially in our preparation), and not from MV cells \citep{pratt2009} or superficial layer cells (that are located deep in the tectum in our preparation) \citep{liu2016}.
@@
 To quantify the “shape” of spiking responses to conductances of different duration (temporal tuning), for every cell we encoded curve duration as an ordinal value (from 1 to 4), fit the spike data as a function of response duration with a quadratic formula ($y = ax^2 + bx +c$), and used the quadratic coefficient $a$ as the measure of response non-linearity.
-While the units and absolute values of this coefficient are not interpretable, it captures the shape of the response curve well, and allows for easy comparisons between cells (Fig.
-2A).
+While the units and absolute values of this coefficient are not interpretable, it captures the shape of the response curve well, and allows for easy comparisons between cells (Figure 2A).
 The case of $a=0$ corresponds to spiking output linearly increasing with duration increase; $a>0$ means supralinear preference for long conductances (curving up); about $-0.25<a<0$ corresponds to a plateau-shaped curves, while $a<-0.25$ would mean heavy spike inactivation for longer conductance injections.

### 2018-12-02 reviews and responses.md
+ reviews and responses

Reviews and Author's Responses for (Busch Khakhalin 2018)
======================

This is a collection of reviews and feedbacks, both official and unofficial, for different working copies of this paper. Reviews are split into paragraphs, and Author's responses and comments are shown after each paragraph, as indented text. Reviews, and responses to these revivews, are given in reverese chronological order.

# J Neurosci (rejection), 2018 Nov 01

These reviews were received on Nov 1st 2018 from J Neurosci, as it rejected the paper.

Even though the paper was rejected, we decided to

## Reviewer #1 (Rationale for Significance Rating for Authors (Required)):

The study is full of clever ideas and technical expertise, but it is too phenomenological and descriptive at this point, lacking a systematic step by step dissection of the underlying mechanisms. The hypothesis is fascinating but it isn't really tested directly.

This paper takes advantage of the Xenopus laevis tadpole optic tectum as a model system for examining how prolonged (4h) exposure to specific forms of conditioning sensory input to a neuron alter its intrinsic excitability and tuning for firing action potentials. Using the dynamic clamp method the authors show that cells exposed to intensive (presumably brief) visual (but not other sensory) stimulation shift their preferred input to favor shorter-lasting synaptic inputs, which the authors describe as "adaptive" plasticity that allows the cell to fire in response to the stimuli which it recently experienced. They also discovered a so-called homeostatic plasticity within conditioning groups such that those cells that have brief rapid responses to optic chiasm stimulation tended to prefer long slow inputs whereas cells with slower repsonses seemed to be tuned to brief inputs. None of these properties correlated with position in the tectum and therefore with presumptive cellular maturation.

Although the central question and ideas that make up this paper are very interesting and potentially constitute a very new way of thinking about plasticity of intrinsic excitability, the paper is almost entirely descriptive and phenomenological, with a number of holistic inferences that, although thought provoking, are not necessary covered withing the scope of the experiments presented. For example, the idea that adaptive vs. homeostatic mechanisms are at play infers too much of a desired outcome for the system without any real justification for such an attribution, especially without having characterized the actual network responses to the conditioning stimuli used. Maybe the plasticity doesn't serve the purpose of making the cells more sensitive or regulating dynamic range. Perhaps it does something useful but unanticipated for the network as it functions in the entire animal. We don't know and shouldn't presume. Also there were numerous points where the data presented here disagree with previous publications by the senior author and although some handwaving explanations were provided, no actual experimental evidence for these differences was presented.

A reasonable attempt was made explain the conditioning changes observed at a more mechanistic level, but at least for the dynamic clamp experiments the authors were unable to account for their observations based on traditional mechanisms for regulation of intrinsic excitability. Overall the paper is fascinating and introduces a potentially interesting new way of thinking about plasticity, but doesn't quite provide enough of a mechanistic underpinning nor of a functional context for the model. It comes across as a slightly contrived set of systematic observations. The paper has a few minor technical issues, but suffers mainly from failing to systematically test any hypothesis in a satisfying and reductionist way. The paper would likely be better suited either for a more specialized cellular neurophysiology journal or, if the narrative can be tightened up to clearly convey its novelty,for a short format high-impact report.

### Specific points:

1.	Page 2, Line 29 the word "thorough" is not appropriate here. If the search had been thorough, an answer would have been found. Instead "extensive" may be more appropriate.

2.	Page 2-3, The dynamic clamp is not very commonly used. It would be useful to provide more detail about how it differs from simple step injections of current and why this might matter.

3.	Page 3 line 18, "when tadpoles were exposed to" -> "in tadpoles that had been exposed to"

4.	The statistical tests applied throughout the paper are unclear and need more explanation. The number of degrees of freedom (e.g, 667) seems far too high, suggesting that multiple recordings from the same cell under different conditions are being treated as independent N. However recordings from the same cell under different temporal or amplitude conditions are far from independent measurements. It seems that a two-way or even three-way ANOVA might be the best approach for examining the variables of conditioning stimulus and response property.

5.	Page 5 line 19 "This suggests that unlike the change in overall intrinsic excitability, the average temporal retuning was "adaptive" rather than "homeostatic", as neurons exposed to shorter stimuli (flashes) became more equipped to process shorter activation patterns." While it is appealing to give a name to this form of plasticity, the looming stimulus, which can be thought of as slower than the flash nonetheless caused a similar type of shift in response preference in the neurons, which runs counter the notion that there exists a meaningful dichotomy of adaptive vs. homeostatic change here.

6.	Figure 2B Amplitude is misspelled.

7.	The narrative logic on page 9 lines 11-22 is confusing. How does homeostatic plasticity, if it truly is at play here, "increase their ability to respond to unusual patterns of synaptic activation." If anything wouldn't homeostasis decrease dynamic range by pushing all cells toward a central set point?

8.	Page 12 the section on position within the tectum feels like it was just tacked onto the end of the paper. This should be integrated earlier in the paper perhaps to go with figure 1A.

9. The formatting of the manuscript is not correct for J Neurosci.

## Reviewer #2 (Rationale for Significance Rating for Authors (Required)):

There is indeed some merit in the goals of the study (to see if adaptation changes with experience in addition to conductance/response gains), but it has so many technical problems at present that it would need to be radically different (perhaps with experiments and analysis re-done) to perhaps be of interest to the broad readership of J Neuroscience.

The manuscript by Khakhalin and Busch describes the impact of experience on the intrinsic response properties of tectal neurons in the developing tadpole. The authors describe a surprising phenomenon: not only is the response gain of the conductance response altered by experience (in a homeostatic manner, if we imagine that the experience produces increased activity, which isn't shown), but the adaptation of the response is also impacted. The authors then go on to make some arguments, in my opinion unconvincing, that properties of the duration of the polysynaptic response to an optic chiasm shock are related to these intrinsic properties.

The paper is, in my opinion, hard to read because the authors are often not clear about what they mean, refer to previous parts of the paper assuming the reader has a perfect memory or is willing to turn back and forth across pages, and use non-traditional terminology. In addition, the statistically analysis appears to be pooling many data points from non-independent cells, rendering many of the conclusions invalid. Further, the experiments intended to measure intrinsic properties (in Figures 1 and 2) appear to have been performed without synaptic blockers, so the the adaptation that they measure could be in the circuit (inhibitory recruitment) instead of in the intrinsic properties.

There is indeed some merit in the goals of the study (to see if adaptation changes with experience in addition to conductance/response gains), but it has so many technical problems at present that it would need to be radically different (perhaps with experiments and analysis re-done) to perhaps be of interest to the broad readership of J Neuroscience.

### Speficic points:

Introduction:

Page 3, line 23: Sentences that begin "First" and "Second" need subjects

Page 3, line 34: "spikiness" -> not a precise word. "Changes in f-I curve", perhaps? Or "Average firing rate"?

Page 3: "traces left by multi sensory stimuli in the tectum of freely behaving tadpoles" -> unclear what is meant by the this sentence until later; suggest re-word

Results

Page 4, line 6 "the stimuli we used were weaker" What is meant, the stimuli in the previous studies were weaker, or the stimuli in the present study? Maybe say the previous stimuli were very high contrast and did not reflect contrasts used in behavioral studies. Here, we presented a checkerboard"...

Page 4 line 19 "spiky" again, imprecise

Page 4, lines 21-24. I'm really confused about the degrees of freedom. Are you all loading in all observations from all cells? If so, the assumption of the statistical test that these are independent observations is violated. Many of these values were measured in the same cells with different current levels, so they are clearly not independent measurements. The analysis should essentially contain one observation per cell. (One "gain" value or number of spikes to some stimulus, etc..) Or could do a multi-variate ANOVA...

Page 4: Lines 27, 28: This sentence is missing conjunctions "in order to map their amplitude transfer function" ?

Page 4: Lines 27, 28: What exactly is meant by the amplitude transfer function or amplitude tuning? Is there an equation?

Page 4, lines 27 - 33: what figure panels are being described here?

Page 6, lines 10-20. The authors point out that the amount of response adaptation in the conductance vs. number of spike curves varies as a function of the stimulus that the animal was exposed to. While it is true that this information can be gleaned by examining Figure 1E, the authors would be well served to make a second index, such as an adaptation index, in a panel F. This would really drive home the points the authors would like the reader to take away from the Figure. (I missed it the first time through, I just saw the reduced gain in Fig. 1E, not the adaptation.)

Page 6, lines 10-20. Need to cite Figure 1E

Page 6, line 22: "homologous to superior colliculus"

Page 7, line 3: [after multi sensory stimulation], "tectal neurons were more excitable than after visual stimulation alone). Many issues. The average number of spikes is reported..is this across all conductance curve conditions or just one of them? Next, in Fig 1E, "sync" and "flash" and "looming" all look pretty similar to each other. What are the degrees of freedom? Again, they seem very high like each condition might be being treated as independent.

More stats: Are these multiple comparisons across conditions done in an unbiased manner, like with a Bonferroni correction or an ANOVA? It seems not.

Page 8, lines 2-12. "Average firing rate" is a more common term than "spikiness". How about "gain" for amplitude tuning? I see that the authors are using the parameter a to indicate the non-linearity in the tuning curve. For "temporal tuning", why not use "adaptation index" or something like that, that could be plotted in Figure 1F? The "temporal tuning" is a measure of non-linearity, but it is not very intuitive. (It is not "incorrect" as the authors have it now, but I think it would be hard for the interdisciplinary readership of J Neuroscience to get on board easily.)

Figure 2: Units needed for Y axis on A, B (units of a are spikes per conductance squared and units of amplitude tuning are spikes/conductance)

Page 8, about line 9: It is false that the numerical values are not interpretable, they are in an equation and have units.

Page 8, line 16-19: Cohen's D tells the discriminability rather than whether there is a difference between two quantities. A test like the Hoteling-2 test can provide significance measures for whether the means of the data in 2C are significant.

Page 8, lines 26-35: Rather than only saying that groups that were significantly different in average values were also significantly different in variability, name the groups again. (Otherwise the reader has to jump all around.)

Figure 2B and Figure 3A, 3D don't show any post-hoc comparisons among the groups. Which groups differ? I see it in the text but it is hard to take it home.

Figure 3E and G: how can we reconcile these accounts? In each of the groups (3G), there is at best a very weak relationship between temporal tuning and synaptic duration. Somehow, if you take the means of all of these groups, you can fit a line through them (Figure 3E). Why is that the right thing to do? Aren't the field of individual points (partially-transparent background) and the data plotted in 3G the relative quantities?

Figure 3C shows that monosynaptic amplitude and synaptic duration are correlated, as one would expect from the definition of synaptic duration (center of mass). Basically, as the monosynaptic amplitude gets bigger, the center of mass will shift earlier and earlier. So what independent information is really being conveyed in the synaptic duration? The correlation in 3C is so strong, I don't see that it is truly an independent quantity that teaches us something beyond the monosynaptic input strength. The monosynaptic input strength is much more defined, why not use that for examining correlation with temporal tuning (or adaptation index), average firing rate, and gain. The "synaptic duration" isn't really a measure of synaptic duration, which makes Page 10, lines 3-23 really hard to interpret.

Figure 3G, page 10 lines 24-40. Creation of "super groups" is totally bogus. This part should be dropped. I see no strong significant relationship between temporal tuning and synaptic duration, and am not convinced synaptic duration is a meaningful quantity.

I am very confused by Figure 4. Is it supposed to tell us that average firing rate is correlated with sodium channel conductances? Why is this experiment being done? What do we learn about the brain? I mean this genuinely, I feel I do not understand what the authors are trying to say that is novel. Of course we would expect such a relationship.

Why not show the 8 parameter model fit of the current tuning curves?

Page 11, "the mechanisms behind temporal intrinsic plasticity". I'm confused. This section and Figure 4 seems to focus on average firing rate / spikiness rather than the temporal tuning parameter. So why the heading?

Discussion:

Page 13, lines 18 - 24: the authors refer to the questions they asked in the introduction, without re-describing them. The reader cannot possibly remember and is forced to page back and forth. The writing must be so much better.

"intrinsic plasticity does not simply adjust neuronal spikiness, but can regulate selectivity for inputs of different dynamics". How are the input dynamics different? I only see that monosynaptic magnitude is different across the conditions. The duration parameter does not reflect duration, just a weighted average of where the most input arrives, and is not related to the whole duration of synaptic input in a manner independent of the initial volley of input.)

"we show that synaptic and intrinsic temporal properties of neurons are homeostatically co-tuned" what does this mean?

# eLife (rejection), 2018 Aug 17

...While both BRE members found much to like about the manuscript, they found it dense going. But they both felt this paper belongs in a more specialized journal. A comment from one of them: 
The authors pose two questions in the introduction: 1. Is intrinsic plasticity limited to changes in excitability? 2. Whether intrinsic plasticity is a response to synaptic activation? There are data in other systems that make these questions "straw men". We know from the STG that intrinsic plasticity is not limited to change in spikiness alone and that there are several other parameters such as bursts, rebounds, spike widths etc which can and do get altered in the short and long term. There are also plenty of examples where one ion channel expression is co-regulated with another type of ion channel, or by slow action of growth factors, hormones and other neuromodulators. These are examples of intrinsic plasticity not governed by fast synaptic transmission alone.

  This is of course true, but while many types of intricate effects of intrinsic plasticity are described in small networks, and especially in oscillatory networks, such as the STG, it is less common to consider these non-trivial effects in large feed-forward excitatory networks, such as networks in the cortex, or superior colliculus. It is natural for researchers to limit the complexity of their conceptual and computational models, and it is probably fair to say that as the number of neurons involved in a model increases, researchers typically shift their attention from intrinsic mechanisms to connectomic approaches, approximating neural networks as a collection of nodes, linked with synapses of different strengths (e.g: Cline 2008; Kirby 2013). Even realistic biophysical models that represent neurons as multi compartment systems with active dendritic currents often don't assume that these active currents may be modulated in response to activation (Moldwin 2018). When machine learning approaches are used as a model for brain development, intrinsic excitability is reflected in these models, as a change in activation function of each artificial neuron (Marblestone 2016). This type of modeling implicitly assumes, however, that outside of obviously oscillatory networks (spinal cord, thalamus, etc.), intrisic excitability in biological networks is largely confined to overall changes in neuronal "resonsiveness".

  Here we show that even for large-scale feed-forward networks that do not seem to rely on oscillations, changes in intrinsic excitability go well beyond variations in "spikness". We think that it is an interesting observation, that may have far-reaching effects on network computations, and network development. We also predict that similar effects of temporal tuning may be observed in other systems, such as mammalian cortex.

  References:

  Cline, H., & Haas, K. (2008). The regulation of dendritic arbor development and plasticity by glutamatergic synaptic input: a review of the synaptotrophic hypothesis. The Journal of physiology, 586(6), 1509-1517.

  Kirkby, L. A., Sack, G. S., Firl, A., & Feller, M. B. (2013). A role for correlated spontaneous activity in the assembly of neural circuits. Neuron, 80(5), 1129-1144.

  Marblestone, A. H., Wayne, G., & Kording, K. P. (2016). Toward an integration of deep learning and neuroscience. Frontiers in computational neuroscience, 10, 94.

  Moldwin, T., & Segev, I. (2018). Perceptron learning and classification in a modeled cortical pyramidal cell. bioRxiv, 464826

That aside, the authors make a big deal out of 'temporal tuning' but to me from fig 1 this looks like non-preference towards syn duration more than preference for any temporal window, as argued by the authors (compare fig 1E panels).

  We think that a preference or non-preference for a certain synaptic duration can be described as a change in temporal selectivity. In the optic tectum, this temporal tuning is not as obvious as it would have been for an oscillatory network, as tectal neurons don't seem to express typical ionic currents associated with oscillatory networks (such as the h-current). Still, one can argue that it only makes our discovery more interesting: we show that neurons can change their temporal properties, even though they don't seem to be equipped with currents most researchers associate with temporal selectivity.

There are other methodological issues as well: Did they randomize the order of injections?

  No, the order of injections was always the same; it is now decribed in the "Methods".

Is a syn current that is more than 250 ms long 'monosynaptic' ?

  We did not quite understand the question, but generally, for this model, monosynaptic component peaks at about 5-20 ms, and is over by 50-100 ms, as described in the "Methods" section.

### 2018-12-02 reviews and responses.md
reviews: indentation fixed?

@@
 This is a collection of reviews and feedbacks, both official and unofficial, for different working copies of this paper.
-Reviews are split into paragraphs, and Author's responses and comments are shown after each paragraph, as indented text.
+Reviews are split into paragraphs, and Author's responses and comments are shown after each paragraph.
 Reviews, and responses to these revivews, are given in reverese chronological order.
@@
 
-...While both BRE members found much to like about the manuscript, they found it dense going. But they both felt this paper belongs in a more specialized journal. A comment from one of them: 
+> ...While both BRE members found much to like about the manuscript, they found it dense going. But they both felt this paper belongs in a more specialized journal. A comment from one of them: 
 The authors pose two questions in the introduction: 1.
@@
 
-That aside, the authors make a big deal out of 'temporal tuning' but to me from fig 1 this looks like non-preference towards syn duration more than preference for any temporal window, as argued by the authors (compare fig 1E panels).
+> That aside, the authors make a big deal out of 'temporal tuning' but to me from fig 1 this looks like non-preference towards syn duration more than preference for any temporal window, as argued by the authors (compare fig 1E panels).
 
@@
 
-There are other methodological issues as well: Did they randomize the order of injections?
+> There are other methodological issues as well: Did they randomize the order of injections?
 
@@
 
-Is a syn current that is more than 250 ms long 'monosynaptic' ?
+> Is a syn current that is more than 250 ms long 'monosynaptic' ?
 

### 2018-12-02 reviews and responses.md
reviews: gen response reviewer 1

@@
 
-These reviews were received on Nov 1st 2018 from J Neurosci, as it rejected the paper.
+These reviews were received on Nov 1st 2018 from J Neurosci, as this paper was rejected by the editors.
 
-Even though the paper was rejected, we decided to
+Even though the paper was rejected, we decided to include these reviews to our next submission, and to this repository, and provide our responses to each of the critiques.
 
@@
 
-The study is full of clever ideas and technical expertise, but it is too phenomenological and descriptive at this point, lacking a systematic step by step dissection of the underlying mechanisms.
+> The study is full of clever ideas and technical expertise, but it is too phenomenological and descriptive at this point, lacking a systematic step by step dissection of the underlying mechanisms.
 The hypothesis is fascinating but it isn't really tested directly.
 
-This paper takes advantage of the Xenopus laevis tadpole optic tectum as a model system for examining how prolonged (4h) exposure to specific forms of conditioning sensory input to a neuron alter its intrinsic excitability and tuning for firing action potentials.
+> This paper takes advantage of the Xenopus laevis tadpole optic tectum as a model system for examining how prolonged (4h) exposure to specific forms of conditioning sensory input to a neuron alter its intrinsic excitability and tuning for firing action potentials.
 Using the dynamic clamp method the authors show that cells exposed to intensive (presumably brief) visual (but not other sensory) stimulation shift their preferred input to favor shorter-lasting synaptic inputs, which the authors describe as "adaptive" plasticity that allows the cell to fire in response to the stimuli which it recently experienced.
@@
 
-Although the central question and ideas that make up this paper are very interesting and potentially constitute a very new way of thinking about plasticity of intrinsic excitability, the paper is almost entirely descriptive and phenomenological, with a number of holistic inferences that, although thought provoking, are not necessary covered withing the scope of the experiments presented.
+> Although the central question and ideas that make up this paper are very interesting and potentially constitute a very new way of thinking about plasticity of intrinsic excitability, the paper is almost entirely descriptive and phenomenological, with a number of holistic inferences that, although thought provoking, are not necessary covered withing the scope of the experiments presented.
 For example, the idea that adaptive vs.
@@
 
-A reasonable attempt was made explain the conditioning changes observed at a more mechanistic level, but at least for the dynamic clamp experiments the authors were unable to account for their observations based on traditional mechanisms for regulation of intrinsic excitability.
+> A reasonable attempt was made explain the conditioning changes observed at a more mechanistic level, but at least for the dynamic clamp experiments the authors were unable to account for their observations based on traditional mechanisms for regulation of intrinsic excitability.
 Overall the paper is fascinating and introduces a potentially interesting new way of thinking about plasticity, but doesn't quite provide enough of a mechanistic underpinning nor of a functional context for the model.
@@
 The paper has a few minor technical issues, but suffers mainly from failing to systematically test any hypothesis in a satisfying and reductionist way.
-The paper would likely be better suited either for a more specialized cellular neurophysiology journal or, if the narrative can be tightened up to clearly convey its novelty,for a short format high-impact report.
+The paper would likely be better suited either for a more specialized cellular neurophysiology journal or, if the narrative can be tightened up to clearly convey its novelty, for a short format high-impact report.
+
+We are grateful for the kind words, and agree with the assessment that our paper is largely phenomenological.
+Unfortunatelly, in a small teaching-oriented college, we simply cannot run most experiments needed to probe the mechanisms of intrinsic temporal tuning.
+We cannot perform in-vivo experiments with sensory stimulation; and cannot measure or change gene expression in isolated tectal cells.
+Even a detailed electrophysiological study of isolated ionic currents would have taken extra 2-3 years, so we decided to publish this phenomenological report, in a hope that the very phenomenon we describe is interesting enough to be followed up by other labs, potentially in different models.
+
+In this, updated version of the paper, we are trying to be more explicit about possible next steps other researches could take to study the mechanisms of the curious phenomenon we discovered.
 

### 2018-12-02 reviews and responses.md
reviews: test for specific comments
R files renamed
reviews: stats

@@
-Reviews and Author's Responses for (Busch Khakhalin 2018)
+Reviews and Authors' Responses for (Busch Khakhalin 2018)
 ======================
@@
 
-1.	Page 2, Line 29 the word "thorough" is not appropriate here. If the search had been thorough, an answer would have been found. Instead "extensive" may be more appropriate.
+> 1.	Page 2, Line 29 the word "thorough" is not appropriate here. If the search had been thorough, an answer would have been found. Instead "extensive" may be more appropriate.
+
+Replaced.
 
@@
 
-3.	Page 3 line 18, "when tadpoles were exposed to" -> "in tadpoles that had been exposed to"
+> 3.	Page 3 line 18, "when tadpoles were exposed to" -> "in tadpoles that had been exposed to"
 
-4.	The statistical tests applied throughout the paper are unclear and need more explanation.
+Replaced.
+
+> 4.	The statistical tests applied throughout the paper are unclear and need more explanation.
 The number of degrees of freedom (e.g, 667) seems far too high, suggesting that multiple recordings from the same cell under different conditions are being treated as independent N.
@@
 It seems that a two-way or even three-way ANOVA might be the best approach for examining the variables of conditioning stimulus and response property.
+
+The number of degrees of freedom in question comes from a full linear model, and does mean that we treated different conditions as independent.
+Typically, to compare the numer of spikes in two conditions we used a 3-way ANCOVA (injection amplitude and duration as ordinal variables; group id as a nominal variable) with interactions, and repeated measures (wieh cell id included as a nominal variable).
+For example, for a comparison of "Control" group to "Sound" group we used the following R code (see **dynamic_spikes_plot.R** for the full code):
+
+ds = subset(d,is.element(Group,c("Control","Sound")))
+summary(aov(data=ds,Spikes~Shape*Amp + Shape*Group + Amp*Group + Cell*Shape*Amp))
+
+We now included several brief descriptions of our models in the "Results" section; improved the description in the "Methods" section; and included several references to the "Methods" section in the "Results" section, to hint that the reader may find full information there.
 

### 2018-12-02 reviews and responses.md
reviews: code formatting
reviews: code formatting, try 2
reviews: code formatting try 3

@@
 Typically, to compare the numer of spikes in two conditions we used a 3-way ANCOVA (injection amplitude and duration as ordinal variables; group id as a nominal variable) with interactions, and repeated measures (wieh cell id included as a nominal variable).
-For example, for a comparison of "Control" group to "Sound" group we used the following R code (see **dynamic_spikes_plot.R** for the full code):
+For example, for a comparison of "Control" group to "Sound" group we used the following R code (see `dynamic_spikes_plot.R` for the full code):
 
-ds = subset(d,is.element(Group,c("Control","Sound")))
-summary(aov(data=ds,Spikes~Shape*Amp + Shape*Group + Amp*Group + Cell*Shape*Amp))
+```ds = subset(d,is.element(Group,c("Control","Sound")))
+summary(aov(data=ds,Spikes~Shape*Amp + Shape*Group + Amp*Group + Cell*Shape*Amp))```
 

### 2018-12-02 main.tex
tex update

@@
 Second, whether changes in intrinsic properties in the tectum are a homeostatic response to each cell's history of synaptic activation, or if they are independent of synaptic properties.
-In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and also, despite a thorough search, we did not detect signs of temporal tuning (ibid,  figures 2, 4).
+In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and also, despite an extensive search, we did not detect signs of temporal tuning (ibid,  figures 2, 4).
 However, we propose that the standard current-clamp protocols used in previous studies \citep{pratt2007,hamodi2014} were not adequate to detect important changes in the function of voltage-gated channels (see "Discussion").
@@
 We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see "Methods").
-Contrary to our expectations, when tadpoles were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8; n cells=28, 29).
+Contrary to our expectations, in tadpoles that were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, 4-way fixed effects linear model with interactions and repeated measures, see "Methods" for a detailed description of models; n cells=28, 29).
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25), which was likewise unexpected.
@@
 The numerical values of these "tuning coefficients" are not interpretable, but they capture the character of tuning curves for each neuron (Figure 2A).
-All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Figure 2C); F(5,160)=4.8, p=4e-4 for amplitude tuning (Figure 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Figure 2C).
+All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Figure 2C; see "Methods" for model description); F(5,160)=4.8, p=4e-4 for amplitude tuning (Figure 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Figure 2C).
 
@@
 
-To analyze the numbers of spikes observed in dynamic clamp experiments, we averaged spike numbers across 5 repetitions for each combination of conductance curve duration and amplitude, which resulted in 12 values per cell, and then used sequential sum of squares repeated measures analysis of variance.
-Both different condunctance amplitudes and curve durations were represented as ordinal values, and differences between experimental groups were assessed as interactions with the experimental group factor.
+To analyze the numbers of spikes observed in dynamic clamp experiments (Figure 1), we first averaged the number of generated spikes across 5 repetitions for each combination of conductance curve duration and amplitude, which resulted in 12 values per cell.
+Then we used sequential sum of squares analysis of variance with repeated measures.
+Both different condunctance curve amplitudes and durations were represented as ordinal values, and differences between experimental groups were assessed as interactions between these ordinal values and the factor variable encoding the experimental group.
+Cell id was included as a fixed factor interaction, as in repeated measures or blocking analysis of variance.
 To verify the validity of this approach, we also ran a maximal likelihood mixed-effects model with type III interaction terms, as implemented in R package “lmer”, with “lmerTest” extension to get access to Satterthwaite degrees of freedom and p-value estimations \citep{kuznetsova2017}.

### 2018-12-03 reviews and responses.md
reviews: code formatting try 4
reviews: more responses + reformatted

@@
 
-Replaced.
+Correction accepted.
 
-2.	Page 2-3, The dynamic clamp is not very commonly used. It would be useful to provide more detail about how it differs from simple step injections of current and why this might matter.
+> 2.	Page 2-3, The dynamic clamp is not very commonly used. It would be useful to provide more detail about how it differs from simple step injections of current and why this might matter.
 
@@
 
-Replaced.
+Correction accepted.
 
@@
 
-```ds = subset(d,is.element(Group,c("Control","Sound")))
-summary(aov(data=ds,Spikes~Shape*Amp + Shape*Group + Amp*Group + Cell*Shape*Amp))```
+```R
+ds = subset(d,is.element(Group,c("Control","Sound")))
+summary(aov(data=ds,Spikes~Shape*Amp + Shape*Group + Amp*Group + Cell*Shape*Amp))
+```
 
-We now included several brief descriptions of our models in the "Results" section; improved the description in the "Methods" section; and included several references to the "Methods" section in the "Results" section, to hint that the reader may find full information there.
+We now included a brief description of our model in the "Results" section; improved the description in the "Methods" section; and added several referrals to the "Methods" section in the "Results" section, to hint that the reader may find full information there.
+In particular, in the sentence that reports the first F-value for this study, we now added the following commentary:
 
-5.	Page 5 line 19 "This suggests that unlike the change in overall intrinsic excitability, the average temporal retuning was "adaptive" rather than "homeostatic", as neurons exposed to shorter stimuli (flashes) became more equipped to process shorter activation patterns." While it is appealing to give a name to this form of plasticity, the looming stimulus, which can be thought of as slower than the flash nonetheless caused a similar type of shift in response preference in the neurons, which runs counter the notion that there exists a meaningful dichotomy of adaptive vs.
+F(1,677)=30.4, p=5e-8, n cells=28, 29.
+Here and below, when F-values are reported, we use 4-way fixed effects analysis of variance with selected interactions, and cell id included as repeated measures factor, see "Methods" for a detailed description.
+
+> 5.	Page 5 line 19 "This suggests that unlike the change in overall intrinsic excitability, the average temporal retuning was "adaptive" rather than "homeostatic", as neurons exposed to shorter stimuli (flashes) became more equipped to process shorter activation patterns." While it is appealing to give a name to this form of plasticity, the looming stimulus, which can be thought of as slower than the flash nonetheless caused a similar type of shift in response preference in the neurons, which runs counter the notion that there exists a meaningful dichotomy of adaptive vs.
 homeostatic change here.
 
-6.	Figure 2B Amplitude is misspelled.
+> 6.	Figure 2B Amplitude is misspelled.
 
-7.	The narrative logic on page 9 lines 11-22 is confusing.
+> 7.	The narrative logic on page 9 lines 11-22 is confusing.
 How does homeostatic plasticity, if it truly is at play here, "increase their ability to respond to unusual patterns of synaptic activation." If anything wouldn't homeostasis decrease dynamic range by pushing all cells toward a central set point?
 
-8.	Page 12 the section on position within the tectum feels like it was just tacked onto the end of the paper. This should be integrated earlier in the paper perhaps to go with figure 1A.
-
-9. The formatting of the manuscript is not correct for J Neurosci.
+> 8.	Page 12 the section on position within the tectum feels like it was just tacked onto the end of the paper. This should be integrated earlier in the paper perhaps to go with figure 1A.
 
@@
 
-There is indeed some merit in the goals of the study (to see if adaptation changes with experience in addition to conductance/response gains), but it has so many technical problems at present that it would need to be radically different (perhaps with experiments and analysis re-done) to perhaps be of interest to the broad readership of J Neuroscience.
+> There is indeed some merit in the goals of the study (to see if adaptation changes with experience in addition to conductance/response gains), but it has so many technical problems at present that it would need to be radically different (perhaps with experiments and analysis re-done) to perhaps be of interest to the broad readership of J Neuroscience.
 
-The manuscript by Khakhalin and Busch describes the impact of experience on the intrinsic response properties of tectal neurons in the developing tadpole.
+> The manuscript by Khakhalin and Busch describes the impact of experience on the intrinsic response properties of tectal neurons in the developing tadpole.
 The authors describe a surprising phenomenon: not only is the response gain of the conductance response altered by experience (in a homeostatic manner, if we imagine that the experience produces increased activity, which isn't shown), but the adaptation of the response is also impacted.
@@
 
-### Speficic points:
+### Specific points:
 

### 2018-12-03 main.tex
tex: stats descriptions

@@
 We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see "Methods").
-Contrary to our expectations, in tadpoles that were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, 4-way fixed effects linear model with interactions and repeated measures, see "Methods" for a detailed description of models; n cells=28, 29).
+Contrary to our expectations, in tadpoles that were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29.
+Here and below, when F-values are reported, we use 4-way fixed effects analysis of variance with selected interactions, and cell id included as repeated measures factor, see "Methods" for a detailed description).
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25), which was likewise unexpected.
@@
 To see whether prolonged sensory stimulation affected synaptic inputs received by tectal neurons, we recorded evoked excitatory postsynaptic currents in response to optic chiasm stimulation.
-We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Figure 3B) differed across experimental groups (Figure 3A; F(5,161)=3.2, p=0.009).
+We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Figure 3B) differed across experimental groups (Figure 3A; F(5,161)=3.2, p=0.009; see "Methods" for a description of the linear model we used).
 Both Sync and Async multisensory groups had larger early synaptic currents than the Control group (Tukey p=0.03 and 0.04; Cohen d=0.46 and 0.74 on log-transformed data respectively).
@@
 
-To analyze the numbers of spikes observed in dynamic clamp experiments (Figure 1), we first averaged the number of generated spikes across 5 repetitions for each combination of conductance curve duration and amplitude, which resulted in 12 values per cell.
+To analyze the numbers of spikes observed in dynamic clamp experiments (Figure 1), we first averaged the number of generated spikes across 5 protocol repetitions, for each cell, and for each combination of conductance curve duration and amplitude, which resulted in 12 values per cell.
 Then we used sequential sum of squares analysis of variance with repeated measures.
-Both different condunctance curve amplitudes and durations were represented as ordinal values, and differences between experimental groups were assessed as interactions between these ordinal values and the factor variable encoding the experimental group.
-Cell id was included as a fixed factor interaction, as in repeated measures or blocking analysis of variance.
+Both different conductance curve amplitudes and durations were represented as ordinal values (1 to 3 for amplitudes, 1 to 4 for durations).
+Differences between experimental groups were assessed as interactions between these ordinal values and the factor variable encoding the experimental group, as we were interested in response shapes (reflected by interactions) rather than average values of spikiness (reflected by independent terms).
+Cell ids were included in the analysis as a fixed factor for repeated measures analysis of variance (also equivalent to analysis of variance with blocking).
 To verify the validity of this approach, we also ran a maximal likelihood mixed-effects model with type III interaction terms, as implemented in R package “lmer”, with “lmerTest” extension to get access to Satterthwaite degrees of freedom and p-value estimations \citep{kuznetsova2017}.
@@
 
-For comparisons or summative values and individual cell parameters between experimental groups we report p-values of fixed effect sequential sum of squares linear model (ancova), in which rostral and medial coordinates of each cell within the tectum are included as covariates, and experimental group - as the main factor.
+For the comparison or summative descriptions of tuning, and other electrophysiological cell parameters between experimental groups, we report p-values of fixed effect sequential sum of squares linear model (ancova), in which rostral and medial coordinates of each cell within the tectum are included as covariates, and experimental group is used as the main factor.
 All comparisons and correlations between cell parameters are performed on values corrected for cell position within the tectum.
 Position correction was based on a two-way linear regression model without interaction.
-For five variables that were distributed extremely non-normally, this correction for position was performed on transformed values (original values were transformed, linearly adjusted, and then transformed back): for early and late mean synaptic amplitudes we used a transformation $a'=log(1-a)$; for the variability of synaptic amplitudes $s'=log(1+s)$; for temporal tuning $y_t' = \sqrt{y_t}$ .
+For five variables that were distributed extremely non-normally, this correction for position was performed on transformed values (original values were transformed to normally distributed proxy values, linearly adjusted, and then transformed back): for early and late mean synaptic amplitudes we used a transformation $a'=log(1-a)$; for the variability of synaptic amplitudes $s'=log(1+s)$; for temporal tuning $y_t' = \sqrt{y_t}$ .
 Where appropriate, we performed the analysis with and without extreme outliers, and reported the difference.
-All analyses presented in the paper were also verified in mixed model analyses, with animal id included as a random factor.
+All analyses presented in the paper were also verified in mixed model analyses, with animal id included as a random factor; the results of these mixed models analyses were similar to that of a fixed model, and are not reported.
 

### 2018-12-05 reviews and responses.md
reviews: reformatting
tex: stats descriptions
responses: + comments on references

@@
 
-# J Neurosci (rejection), 2018 Nov 01
+# J Neurosci rejection letter, 2018 Nov 01
 
@@
 The paper would likely be better suited either for a more specialized cellular neurophysiology journal or, if the narrative can be tightened up to clearly convey its novelty, for a short format high-impact report.
+
+&nbsp;
 
@@
 
-The paper is, in my opinion, hard to read because the authors are often not clear about what they mean, refer to previous parts of the paper assuming the reader has a perfect memory or is willing to turn back and forth across pages, and use non-traditional terminology.
+> The paper is, in my opinion, hard to read because the authors are often not clear about what they mean, refer to previous parts of the paper assuming the reader has a perfect memory or is willing to turn back and forth across pages, and use non-traditional terminology.
 In addition, the statistically analysis appears to be pooling many data points from non-independent cells, rendering many of the conclusions invalid.
@@
 
-There is indeed some merit in the goals of the study (to see if adaptation changes with experience in addition to conductance/response gains), but it has so many technical problems at present that it would need to be radically different (perhaps with experiments and analysis re-done) to perhaps be of interest to the broad readership of J Neuroscience.
+> There is indeed some merit in the goals of the study (to see if adaptation changes with experience in addition to conductance/response gains), but it has so many technical problems at present that it would need to be radically different (perhaps with experiments and analysis re-done) to perhaps be of interest to the broad readership of J Neuroscience.
+
+&nbsp;
+
+Regarding references to previous parts, thank you for pointing it out!
+We now tried to link different parts of the paper more tightly together, by reminding the reader about previously made statements every time we make a reference.
 
@@
 
-Page 7, line 3: [after multi sensory stimulation], "tectal neurons were more excitable than after visual stimulation alone).
+Page 7, line 3: after multi sensory stimulation, "tectal neurons were more excitable than after visual stimulation alone).
 Many issues.
@@
 
-# eLife (rejection), 2018 Aug 17
+# eLife rejection letter, 2018 Aug 17
 

### 2018-12-05 reviews and responses.md
responses: grammar

@@
 
-Introduction:
+> Introduction:
 
-Page 3, line 23: Sentences that begin "First" and "Second" need subjects
+> Page 3, line 23: Sentences that begin "First" and "Second" need subjects
 
-Page 3, line 34: "spikiness" -> not a precise word. "Changes in f-I curve", perhaps? Or "Average firing rate"?
+We now repeated "we asked" in both sentences, making "we" the subject.
 
-Page 3: "traces left by multi sensory stimuli in the tectum of freely behaving tadpoles" -> unclear what is meant by the this sentence until later; suggest re-word
+> Page 3, line 34: "spikiness" -> not a precise word. "Changes in f-I curve", perhaps? Or "Average firing rate"?
+
+> Page 3: "traces left by multi sensory stimuli in the tectum of freely behaving tadpoles" -> unclear what is meant by the this sentence until later; suggest re-word
 

### 2018-12-06 reviews and responses.md
responses: minor editing

@@
 
-# J Neurosci rejection letter, 2018 Nov 01
+# Reviews from J Neurosci, 2018 Nov 01 (rejection letter)
 
@@
 
-## Reviewer #1 (Rationale for Significance Rating for Authors (Required)):
+## Reviewer #1
 
@@
 
-## Reviewer #2 (Rationale for Significance Rating for Authors (Required)):
+## Reviewer #2
 
@@
 
-We now repeated "we asked" in both sentences, making "we" the subject.
+We now added "we asked" to both sentences, making "we" a subject.
 
@@
 
-# eLife rejection letter, 2018 Aug 17
+# Reviews from eLife, 2018 Aug 17 (rejection letter)
 
 > ...While both BRE members found much to like about the manuscript, they found it dense going. But they both felt this paper belongs in a more specialized journal. A comment from one of them:
-The authors pose two questions in the introduction: 1.
+
+> The authors pose two questions in the introduction: 1.
 Is intrinsic plasticity limited to changes in excitability?

### 2018-12-06 main.tex
tex: discussion, some intro, new refs

@@
 
-It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity, yet biological neurons are tuned in ways that go well beyond adjusting one “strength” value per synapse.
-Cells within the same network often demonstrate variability of activation thresholds \citep{kole2012}, production of bursts \citep{popovic2011}, inactivation by strong inputs \citep{bianchi2012}, and more.
+% Intro: be more specific that we're not talking about STG or spinal.
+That in FF intrinsic is often underplayed, and that the same is tru for neuro-inspired machine learning.
+Link to Markram?
+Check the response to elife rejection
+
+% Intro and discussion: see older versions, check whether there's anything good there
+
+% Intro: remind how dynamic clamp works
+
+% Explain why homeostatic plasticity in a feature space makes a network more sensitive to unusual stimuli
+
+It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network}.
+Biological neurons, however, are tuned in ways that go well beyond adjusting one “strength” value per synapse: cells within the same network often demonstrate variability of activation thresholds \citep{kole2012}, production of bursts \citep{popovic2011}, inactivation by strong inputs \citep{bianchi2012}, and more.
 This diversity of tuning relies on coordinated changes of many parameters across a complex, multivariate landscape \citep{oleary2013}, as neuronal phenotypes are shaped by sensory experiences, and adjusted by modulatory inputs \citep{evans2015}.
 The dysregulation of intrinsic plasticity can affect network dynamics \citep{tien2018}, and lead to a loss of function \citep{marcelin2009}.
-However, for many networks, it is still unclear whether variation in intrinsic phenotypes is primarily a result of excitability calibration, or whether it is a defining aspect of network topology and architecture \citep{titley2017}.
+And yet, for many networks, it is still unclear whether variation in intrinsic phenotypes is primarily a result of excitability calibration, or whether it is a defining aspect of network topology and architecture \citep{titley2017}.
 
@@
 In this study, we asked two specific questions about the properties of intrinsic plasticity in tectal networks.
-First, whether intrinsic plasticity is limited to changes in excitability, or whether it is more nuanced and can differentially adjust neuronal responsiveness to inputs with different dynamics.
-Second, whether changes in intrinsic properties in the tectum are a homeostatic response to each cell's history of synaptic activation, or if they are independent of synaptic properties.
+First, we asked whether intrinsic plasticity is limited to changes in excitability, or whether it is more nuanced and can differentially adjust neuronal responsiveness to inputs with different dynamics.
+Second, we checked whether changes in intrinsic properties in the tectum are a homeostatic response to each cell's history of synaptic activation, or if they are independent of synaptic properties.
 In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and also, despite an extensive search, we did not detect signs of temporal tuning (ibid,  figures 2, 4).
@@
 Contrary to our expectations, in tadpoles that were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29.
-Here and below, when F-values are reported, we use 4-way fixed effects analysis of variance with selected interactions, and cell id included as repeated measures factor, see "Methods" for a detailed description).
+Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell id is used as a repeated measures factor; see "Methods" for a detailed description).
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25), which was likewise unexpected.
@@
 Curiously, neither of the three measures of intrinsic tuning (average spikiness, temporal tuning, and amplitude tuning) correlated with position (p$>$0.1, n=168).
-This suggests that while low-level properties of each cell depended on its age, its spiking phenotype was age-independent.
+This may suggest that while low-level properties of each cell depended on its age, its spiking phenotype was age-independent.
 Thus, different cells seemed to achieve similar spiking behaviors through different combinations of underlying parameters, relying on the principle of “parameter degeneracy” \citep{prinz2004degeneracy,drion2015}.
@@
 \section*{Discussion}
-% Sep 04: 731 words with citations
 
-In this study we show that different sensory stimuli differentially retuned neurons in the optic tectum of \textit{Xenopus} tadpoles, inducing changes in both their temporal tuning, and amplitude transfer functions.
-This addresses our first question and shows that intrinsic plasticity does not simply adjust neuronal spikiness, but can regulate selectivity for inputs of different dynamics.
-In answer to our second question, we show that synaptic and intrinsic temporal properties of neurons are homeostatically co-tuned, and that this co-tuning is affected by sensory experience.
+In this study we show that different sensory stimuli retuned neurons in the optic tectum of \textit{Xenopus} tadpoles in different ways, inducing changes in both their temporal tuning, and amplitude transfer functions.
+This addresses our first question about the functional scope of intrinsic plasticity in the optic tectum, and shows that it goes well beyond simple adjustments of neuronal spikiness.
 
+As our technical resources are rather limited, in this study we do not explicitly address the mechanisms of newly discovered intrinsic temporal tuning.
+We can however offer two working hypotheses that may explain these results.
+As tadpole tectal cells do not express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic currents inactivation in different cells.
+One obvious way of tuning ionic channel inactivation would be for every cell to modulate sodium or transient potassium currents via channel phosphorylation, or by changing the expression of different channel variants, to shift their inactivation dynamics \citep{frank2003nachannels,goldwyn2018a_current}.
+To test this hypothesis, one would need to induce changes in temporal tuning, similarly to how we did it in this paper, but then pharmacologically isolate different ionic currents, and then directly measure their inactivation dynamics.
+
+Another hypothetical mechanism that can underlie our current results is inspired by a yet unexplained finding from our earlier study \citep{ciarleglio2015}: namely, that one of the key electrophysiological parameters regulating excitability of tectal cells is cell membrane capacitance (Cm).
+Traditionally, cell capacitance is thought of as a relatively immutable parameter that describes cell morphology, and can even be used to estimate its size, yet in the tadpole tectum, we found it to drop both with age, and after strong sensory stimulation, even though cells don't seem to change their visual appearance (\citealt{ciarleglio2015}, Figure 7D).
+An intriguing possibility is that these changes in cell capacitance may be due to electiric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic arbor, soma, and axon initial segment \citep{bollmann2009}.
+This differential uncoupling may be achieved through either minor changes in cell morphology, or through target modulation of sodium and potassium channels at key points between the compartments, which would introduce shunting, and so strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.
+One way to test this hypothesis could be to perform immunostaining of cleared tectum preparation after sensory stimulation, and if any changes in the distribution of sodium and potassium channels is discovered, to validate the effect of these changes in a computational model.
+
+In answer to our second question, about whether intrinsic and synaptic properties of tectal cells are in any way coordinated, here we show that intrinsic and synaptic temporal properties are co-tuned in the tectum, and moreover, that this co-tuning can be modified by sensory experience.
 In contrast with earlier studies that report increased excitability post-stimulation \citep{aizenman2003,dong2009,ciarleglio2015}, we found that sensory stimulation led to a suppression of spiking.
-We suggest that the visual stimulation used in earlier studies, which was provided with a LED box, was so bright and of high contrast that it caused a suppression of retinal synaptic inputs via a polyamine block of AMPA receptors \citep{aizenman2003}.
-This suppression triggered a “second-order” homeostatic compensation \citep{turrigiano2011,tien2018}, making neurons spikier.
-In our current experiments, synaptic inputs were not suppressed, and neuronal activation during sensory conditioning was stronger than in control, causing intrinsic spikiness to decrease.
+The reason for that, most probably, is that the visual stimulation used in earlier studies was provided with a LED box, which was so bright and of so high contrast that it caused a suppression of retinal synaptic inputs via a polyamine block of AMPA receptors \citep{aizenman2003}.
+This suppression then triggered a “second-order” homeostatic compensation \citep{turrigiano2011,tien2018}, making neurons spikier.
+In our current experiments, however, synaptic inputs were not suppressed, and neuronal activation during sensory conditioning was stronger than in control, causing a decrease in intrinsic spikiness.
 
-The difference between the dynamic clamp results (that were affected by stimulation, but could not be explained through low-level intrinsic parameters) and the results obtained in current- and voltage-clamp experiments (that were not affected by stimulation, yet better coordinated with intrinsic parameters) may be interpreted in two ways.
-We could assume that dynamic clamp in the soma provided a bad approximation for the peripheral synaptic inputs, as space clamp error is more pronounced for fast voltage fluctuations than for constant current injection \citep{spruston1993,prinz2004}.
-We however find this hypothesis unlikely, as dynamic clamp responses were consistently different in animals with different sensory history, which suggests that we have captured some important aspects of intrinsic diversity, even if our estimations were biased.
-More likely, intrinsic excitability is affected by properties that are not accessible by standard voltage and current clamp protocols, such as axon initial segment relocation, or targeted modulation of axonal voltage-gated channels \citep{grubb2010,kole2012}.
-In cells with excitable dendrites, channels of the axon initial segment may constitute only a small fraction of all voltage-gated channels, yet have a disproportionately large effect on the spiking output of the cell, including its temporal tuning \citep{kole2007,hamada2016}.
-Furthermore, prolonged current injections in the soma are likely to inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channels recovery during burst firing \citep{popovic2011,kole2012}.
-This effect would still affect spiking in more realistic dynamic clamp experiments.
+Our study described an important difference between the dynamic clamp results (that were affected by stimulation, but could not be explained through low-level intrinsic parameters) and the results obtained in "classical" slow clamp experiments (that were not affected by stimulation, yet better coordinated with intrinsic parameters).
+This different may be interpreted in two ways.
+One possible interpretation is to assume that dynamic clamp in the soma provided a bad approximation of peripheral synaptic inputs, as space clamp error is more pronounced for fast voltage fluctuations than for constant current injection \citep{spruston1993,prinz2004}.
+We however find this hypothesis unlikely, as dynamic clamp responses were consistently different in animals with different sensory history, which suggests that at the very least, we have captured some important aspects of intrinsic diversity, even if our estimations were biased.
 
-% Excplicitly say: because our resources are limited, in this study we did not address the mechanisms of this phenomenon, but we have two working hypotheses that we describe here.
-One, that maybe Na channels are modulated (phosphorylated?), or new channels are introduced, which changes inactivation dynamics.
-Another, that maybe there's a partial decoupling of different cellular compartments (dendritic tree, soma, and axon initial segment), either via minor but electrophysiologically important changes in cell morphology [ref], or via modulation of persistent K and Na channels [ref?] or both.
+Alternatively, and in our opinion more likely, intrinsic excitability of tectal cells is affected by properties that are not easily accessible by standard slow voltage and current clamp protocols, such as axon initial segment relocation, or targeted modulation of axonal voltage-gated channels we described above \citep{grubb2010activity,kole2012}.
+In cells with excitable dendrites, channels of the axon initial segment may constitute only a small fraction of all voltage-gated channels, yet have a disproportionately large effect on the spiking output of the cell, and on its temporal tuning \citep{kole2007,hamada2016}.
+Furthermore, prolonged current injections in the soma are likely to quickly inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channels recovery during burst firing \citep{popovic2011,kole2012}.
+Converestly, this effect would still affect spiking in more realistic, fast dynamic clamp experiments.
 
-%Our findings lead to several verifiable predictions.
-As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014,jang2016}, a change in temporal tuning should affect collision detection thresholds, which can be predicted in a model, and verified experimentally.
-Similarly, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it would be likely to reduce peak activation in vivo.
+Our findings lead to several verifiable predictions.
+As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014,jang2016}, a change in temporal tuning should affect collision detection dynamics, which can be verified experimentally.
+More specifically, we predict that visual stimulation that retunes neurons to faster stimuli (Flash) would make tadpoles selectively less responsive to slow collisions, and increase the latency of collision avoidance, due to non-linear dynamics of retinal activation for realistic looming stimuli that is slow in the beginning, and fast towards the end \citep{jang2016}.
+These changes in intrinsic temporal tuning would also reshape the connectivity of tectal networks, as fast-inactivating cells would not support short recurrent loops within the network, thus promoting long-ranged polysynaptic connectivity \citep{fiete2010stdp,clopath2010stdp}.
+Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it would be likely to reduce peak activation in vivo.
 
-Overall, we present a novel case of temporal selectivity in non-oscillatory neurons in a distributed sensory network, and demonstrate that intrinsic temporal tuning of neural cells correlates with their synaptic properties.
+% An internal comment: technically, Dong 2009 tested collision avoidance after visual stimulation, and got a somewhat opposite result: better avoidance of large dots (roughly equivalent to slow collisions), and worse avoidance to small dots (roughtly equivalent to fast collisions).
+But then, he used LED that we now know (Ciarleglio 2015) to have an opposite effect on intrinsic excitability, so it's hard to argue that Dong 2009 was a veryfication of our prediction.
+It is way too confusing.
+
+To sum up, we present a novel case of temporal selectivity in non-oscillatory neurons in a distributed sensory network, and demonstrate that intrinsic temporal tuning of neural cells correlates with their synaptic properties.
 It is particularly interesting that the temporal co-tuning we observed was homeostatic in nature, as cells tended to be selective for inputs of dynamics they did not usually experience.
@@
 We expect that in most cases these changes would not be noticeable in experiments with standard voltage- and current-clamp protocols, but can be probed with a dynamic clamp technique.
-It would therefore be intriguing to see whether our results will replicate in other sensory systems, such as the mammalian cortex.
+It would therefore be very interesting to see whether our results will replicate in other sensory systems, such as the mammalian cortex.
 

### 2018-12-07 reviews and responses.md
tex: updates intro, results

@@
 
-Correction accepted.
+Corrected.
 
@@
 
+Thank you for reminding us about that! We now added a one-sentence description of dynamic clamp into the last paragraph of the intro section:
+
+"Unlike for more common voltage and current clamp techniques, in dynamic clamp, the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time."
+
 > 3.	Page 3 line 18, "when tadpoles were exposed to" -> "in tadpoles that had been exposed to"
 
-Correction accepted.
+Corrected.
 
@@
 
+We think that there exists a certain dichotomy here, but we agree that our description of it was not clear enough. We now replaced it with the following, longer exposition:
+
+"...This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, each follow different logic, and cannot be easily described by a blanket statement.
+The overall excitability is "homeostatic", as in response to stronger stimulation neurons became less excitable.
+The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively more responsive to shorter stimuli, and so presumably more equipped to process faster activation patterns."
+
 > 6.	Figure 2B Amplitude is misspelled.
+
+Corrected now.
 
@@
 How does homeostatic plasticity, if it truly is at play here, "increase their ability to respond to unusual patterns of synaptic activation." If anything wouldn't homeostasis decrease dynamic range by pushing all cells toward a central set point?
+
+We think that the word "homeostatic" might have been misleading in this context. We updated this sentence:
+
+"This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, increasing their ability to respond to unusual patterns of synaptic activation."
 
@@
 
-Results
+> Results
 
-Page 4, line 6 "the stimuli we used were weaker" What is meant, the stimuli in the previous studies were weaker, or the stimuli in the present study?
+> Page 4, line 6 "the stimuli we used were weaker" What is meant, the stimuli in the previous studies were weaker, or the stimuli in the present study?
 Maybe say the previous stimuli were very high contrast and did not reflect contrasts used in behavioral studies.
@@
 
-Page 4 line 19 "spiky" again, imprecise
+> Page 4 line 19 "spiky" again, imprecise
 
-Page 4, lines 21-24.
+> Page 4, lines 21-24.
 I'm really confused about the degrees of freedom.
@@
 
-Page 4: Lines 27, 28: This sentence is missing conjunctions "in order to map their amplitude transfer function" ?
+> Page 4: Lines 27, 28: This sentence is missing conjunctions "in order to map their amplitude transfer function" ?
 
-Page 4: Lines 27, 28: What exactly is meant by the amplitude transfer function or amplitude tuning? Is there an equation?
+> Page 4: Lines 27, 28: What exactly is meant by the amplitude transfer function or amplitude tuning? Is there an equation?
 
-Page 4, lines 27 - 33: what figure panels are being described here?
+> Page 4, lines 27 - 33: what figure panels are being described here?
 
-Page 6, lines 10-20.
+> Page 6, lines 10-20.
 The authors point out that the amount of response adaptation in the conductance vs.
@@
 
-Page 6, lines 10-20. Need to cite Figure 1E
+> Page 6, lines 10-20. Need to cite Figure 1E
 
-Page 6, line 22: "homologous to superior colliculus"
+> Page 6, line 22: "homologous to superior colliculus"
 
-Page 7, line 3: after multi sensory stimulation, "tectal neurons were more excitable than after visual stimulation alone).
+> Page 7, line 3: after multi sensory stimulation, "tectal neurons were more excitable than after visual stimulation alone).
 Many issues.
@@
 
-More stats: Are these multiple comparisons across conditions done in an unbiased manner, like with a Bonferroni correction or an ANOVA? It seems not.
+> More stats: Are these multiple comparisons across conditions done in an unbiased manner, like with a Bonferroni correction or an ANOVA? It seems not.
 
-Page 8, lines 2-12.
+> Page 8, lines 2-12.
 "Average firing rate" is a more common term than "spikiness".
@@
 
-Figure 2: Units needed for Y axis on A, B (units of a are spikes per conductance squared and units of amplitude tuning are spikes/conductance)
+> Figure 2: Units needed for Y axis on A, B (units of a are spikes per conductance squared and units of amplitude tuning are spikes/conductance)
 
-Page 8, about line 9: It is false that the numerical values are not interpretable, they are in an equation and have units.
+> Page 8, about line 9: It is false that the numerical values are not interpretable, they are in an equation and have units.
 
-Page 8, line 16-19: Cohen's D tells the discriminability rather than whether there is a difference between two quantities.
+> Page 8, line 16-19: Cohen's D tells the discriminability rather than whether there is a difference between two quantities.
 A test like the Hoteling-2 test can provide significance measures for whether the means of the data in 2C are significant.
 
-Page 8, lines 26-35: Rather than only saying that groups that were significantly different in average values were also significantly different in variability, name the groups again.
+> Page 8, lines 26-35: Rather than only saying that groups that were significantly different in average values were also significantly different in variability, name the groups again.
 (Otherwise the reader has to jump all around.)
 
-Figure 2B and Figure 3A, 3D don't show any post-hoc comparisons among the groups. Which groups differ? I see it in the text but it is hard to take it home.
+> Figure 2B and Figure 3A, 3D don't show any post-hoc comparisons among the groups. Which groups differ? I see it in the text but it is hard to take it home.
 
-Figure 3E and G: how can we reconcile these accounts?
+> Figure 3E and G: how can we reconcile these accounts?
 In each of the groups (3G), there is at best a very weak relationship between temporal tuning and synaptic duration.
@@
 
-Figure 3C shows that monosynaptic amplitude and synaptic duration are correlated, as one would expect from the definition of synaptic duration (center of mass).
+> Figure 3C shows that monosynaptic amplitude and synaptic duration are correlated, as one would expect from the definition of synaptic duration (center of mass).
 Basically, as the monosynaptic amplitude gets bigger, the center of mass will shift earlier and earlier.
@@
 
-Figure 3G, page 10 lines 24-40.
+> Figure 3G, page 10 lines 24-40.
 Creation of "super groups" is totally bogus.
@@
 
-I am very confused by Figure 4.
+> I am very confused by Figure 4.
 Is it supposed to tell us that average firing rate is correlated with sodium channel conductances?
@@
 
-Why not show the 8 parameter model fit of the current tuning curves?
+> Why not show the 8 parameter model fit of the current tuning curves?
 
-Page 11, "the mechanisms behind temporal intrinsic plasticity".
+> Page 11, "the mechanisms behind temporal intrinsic plasticity".
 I'm confused.
@@
 
-Discussion:
+> Discussion:
 
-Page 13, lines 18 - 24: the authors refer to the questions they asked in the introduction, without re-describing them.
+> Page 13, lines 18 - 24: the authors refer to the questions they asked in the introduction, without re-describing them.
 The reader cannot possibly remember and is forced to page back and forth.
@@
 
-"intrinsic plasticity does not simply adjust neuronal spikiness, but can regulate selectivity for inputs of different dynamics".
+> "intrinsic plasticity does not simply adjust neuronal spikiness, but can regulate selectivity for inputs of different dynamics".
 How are the input dynamics different?
@@
 
-"we show that synaptic and intrinsic temporal properties of neurons are homeostatically co-tuned" what does this mean?
+> "we show that synaptic and intrinsic temporal properties of neurons are homeostatically co-tuned" what does this mean?
 

### 2018-12-08 main.tex

@@
 
-\linenumbers % Comment to suppress line numbers
+\linenumbers % Comment this to suppress line numbers
 
@@
 This tuning tended to be opposite to the actual dynamics of synaptic inputs each cell received, such that neurons that normally receive shorter inputs generated stronger spiking in response to longer testing currents, and the other way around.
-This observation shows that even in networks that do not generate oscillations, neurons reshape their temporal selectivity, to optimize their impact on distributed calculations.
+This observation shows that even in networks that don't generate oscillations, neurons reshape their temporal selectivity, to optimize their impact on distributed calculations.
 %TC:ignore 
@@
 Check the response to elife rejection
-
-% Intro and discussion: see older versions, check whether there's anything good there
-
-% Intro: remind how dynamic clamp works
 
@@
 Furthermore, we show that the tuning of intrinsic properties is coordinated with the duration of synaptic inputs received by each cell.
-These results rely on two methodological innovations: first, instead of using current injections, we employed the dynamic clamp technique, which allowed a more realistic simulation of synaptic conductances \citep{prinz2004}.
-Second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols, and compared their effects on intrinsic tuning.
+These results rely on two methodological innovations.
+First, instead of using current injections, we employed the dynamic clamp technique, which allowed a more realistic simulation of synaptic conductances \citep{prinz2004}.
+Unlike for more common voltage and current clamp techniques, in dynamic clamp, the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time.
+And second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols, and compared their effects on intrinsic tuning.
 The use of different sensory modalities also gave us insight into an unrelated, but equally intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at the traces left by multisensory stimuli in the tectum of freely behaving tadpoles.
@@
 In essence, while control neurons “preferred” longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
-This suggests that unlike the  change in overall intrinsic excitability, the average temporal retuning was “adaptive” rather than “homeostatic”, as neurons exposed to shorter stimuli (flashes) became more equipped to process shorter activation patterns.
+This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, each follow different logic, and cannot be easily described by a blanket statement.
+The overall excitability is "homeostatic", as in response to stronger stimulation neurons became less excitable.
+The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively more responsive to shorter stimuli, and so presumably more equipped to process faster activation patterns.
 
@@
 Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (r=$-$0.18, p=0.03, n=151).
-This means that individual neurons tended to homeostatically tune their intrinsic properties away from the statistics of their inputs, increasing their ability to respond to unusual patterns of synaptic activation.
+This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, increasing their ability to respond to unusual patterns of synaptic activation.
 
 %%% --- This section was commented out in all official submissions
+
 Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.04, p=0.7, n=151).
@@
 
-In all analyses presented above, we adjusted cell properties for rostro-caudal and media-lateral position of each cell within the tectum, as in tadpoles both intrinsic \citep{hamodi2014} and synaptic properties \citep{wu1996,khakhalin2012} differ between older (rostro-medial) and younger (caudal, lateral) parts of the developing tectum.
-Most cell properties we measured correlated (p$<$0.05, after correction for treatment group differences) with either medial or rostral position within the tectum (medial: membrane capacitance r=$-$0.17, membrane resistance r=0.25, sodium current activation potential r=$-$0.30, stable potassium current r=$-$0.16, early synaptic amplitude r=$-$0.22, synaptic current duration r=0.29; rostral: peak sodium current r=0.18, late synaptic amplitude r=0.11; n between 168 and 183).
+In all analyses presented above, we adjusted cell properties for rostro-caudal and media-lateral position of each cell within the tectum, as in tadpoles both intrinsic \citep{hamodi2014} and synaptic properties \citep{wu1996,khakhalin2012} are known to differ between older (rostro-medial) and younger (caudal, lateral) parts of the developing tectum.
+In this study, most cell properties we measured correlated (p$<$0.05, after correction for treatment group differences) with either medial or rostral position within the tectum (medial: membrane capacitance r=$-$0.17, membrane resistance r=0.25, sodium current activation potential r=$-$0.30, stable potassium current r=$-$0.16, early synaptic amplitude r=$-$0.22, synaptic current duration r=0.29; rostral: peak sodium current r=0.18, late synaptic amplitude r=0.11; n between 168 and 183).
 Curiously, neither of the three measures of intrinsic tuning (average spikiness, temporal tuning, and amplitude tuning) correlated with position (p$>$0.1, n=168).
-This may suggest that while low-level properties of each cell depended on its age, its spiking phenotype was age-independent.
+This may suggest that while low-level properties of tectal cells depended on their age, their spiking phenotypes were largely age-independent.
 Thus, different cells seemed to achieve similar spiking behaviors through different combinations of underlying parameters, relying on the principle of “parameter degeneracy” \citep{prinz2004degeneracy,drion2015}.
@@
 
-As our technical resources are rather limited, in this study we do not explicitly address the mechanisms of newly discovered intrinsic temporal tuning.
+As our technical resources are rather limited, in this study we don't explicitly address the mechanisms of newly discovered intrinsic temporal tuning.
 We can however offer two working hypotheses that may explain these results.
-As tadpole tectal cells do not express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic currents inactivation in different cells.
+As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic currents inactivation in different cells.
 One obvious way of tuning ionic channel inactivation would be for every cell to modulate sodium or transient potassium currents via channel phosphorylation, or by changing the expression of different channel variants, to shift their inactivation dynamics \citep{frank2003nachannels,goldwyn2018a_current}.
@@
 An intriguing possibility is that these changes in cell capacitance may be due to electiric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic arbor, soma, and axon initial segment \citep{bollmann2009}.
-This differential uncoupling may be achieved through either minor changes in cell morphology, or through target modulation of sodium and potassium channels at key points between the compartments, which would introduce shunting, and so strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.
+This differential uncoupling may be achieved through either minor changes in cell morphology \citep{leterrier2018axon}, or through target modulation of sodium and potassium channels at key points between the compartments, which would introduce shunting, and so strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.
 One way to test this hypothesis could be to perform immunostaining of cleared tectum preparation after sensory stimulation, and if any changes in the distribution of sodium and potassium channels is discovered, to validate the effect of these changes in a computational model.

### 2018-12-08 reviews and responses.md
responses to reviewers: 2 more
responses: general for reviewer 2

@@
 
-Corrected now.
+Fixed.
 
@@
 
-We think that the word "homeostatic" might have been misleading in this context. We updated this sentence:
+We agree that the word "homeostatic" was confusing in this context. We now simplified the sentence:
 
@@
 
-Regarding references to previous parts, thank you for pointing it out!
+On references to previous parts, thank you for pointing it out!
 We now tried to link different parts of the paper more tightly together, by reminding the reader about previously made statements every time we make a reference.
+
+On statistical analysis: we do not pool data points from non-independent cells, but used a repeated measures analysis, verified by mixed model analysis (see Methods, as well as corrections described in our responses to Reviewer 1).
+
+On synaptic blockers: it is true that we measured intrinsic properties without synaptic blockers, but this is considered a standard practice in this preparation, as most earlier studies measured IV curves without synaptic blockers (Aizenman ..
+Cline 2002; Aizenman ..
+Cline 2003; James ..
+Aizenman 2015; Ciarleglio Khakhalin ..
+Aizenman 2015).
+What makes this practice possible is a relatively weak recruitment of polysynaptic activity after activation of a single tectal cell (Bell ..
+Aizenman 2011).
 

### 2018-12-08 reviews and responses.md
minor: homeostatic passage

@@
 
-"...This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, each follow different logic, and cannot be easily described by a blanket statement.
-The overall excitability is "homeostatic", as in response to stronger stimulation neurons became less excitable.
-The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively more responsive to shorter stimuli, and so presumably more equipped to process faster activation patterns."
+"...
+This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, follow two different kinds of logic.
+The overall excitability is homeostatic, as neurons became less excitable in response to stronger stimulation.
+The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively *more* responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a homeostatic retuning.
+We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation."
 

### 2018-12-08 main.tex
minor: homeostatic passage

@@
 In essence, while control neurons “preferred” longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
-This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, each follow different logic, and cannot be easily described by a blanket statement.
-The overall excitability is "homeostatic", as in response to stronger stimulation neurons became less excitable.
-The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively more responsive to shorter stimuli, and so presumably more equipped to process faster activation patterns.
+This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, follow two different kinds of logic.
+The overall excitability is homeostatic, as neurons became less excitable in response to stronger stimulation.
+The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a fully homeostatic retuning.
+We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation.
 
@@
 It is particularly interesting that the temporal co-tuning we observed was homeostatic in nature, as cells tended to be selective for inputs of dynamics they did not usually experience.
-We hypothesize that this homeostatic adjustment of temporal tuning is the reason why this tuning was so easily disrupted by strong visual stimulation, when for a few hours we drastically changed the statistics of inputs received by every cell.
+We hypothesize that this adjustment of temporal tuning is the reason why this tuning was so easily disrupted by strong visual stimulation, when for a few hours we drastically changed the statistics of inputs received by every cell.
 Tuning to "unusual stimuli" at the level of individual neurons fits into the narrative of information transfer maximization \citep{brenner2000} and network criticality \citep{rubinov2011}, wherein every element of a network tries to locally maximize its influence over the overall computation.

### 2018-12-08 reviews and responses.md
responses: TODO sketches for reviewer 2

@@
 
-F(1,677)=30.4, p=5e-8, n cells=28, 29.
-Here and below, when F-values are reported, we use 4-way fixed effects analysis of variance with selected interactions, and cell id included as repeated measures factor, see "Methods" for a detailed description.
+"F(1,677)=30.4, p=5e-8, n cells=28, 29.
+Here and below, when F-values are reported, we use 4-way fixed effects analysis of variance with selected interactions, and cell id included as repeated measures factor, see "Methods" for a detailed description."
 
@@
 
+1) As described above, we used a family of similar generalized linear models, followed by F-test for the analysis of variance, to compare across conditions.
+This type of analysis may be loosely referred to as ANOVA, although most textbooks would not recommend referring our models as an "ANOVA", as it included two ordinal variables, and a factor to account for repeated measures.
+
+2) It is true that in our analysis we compared several pairs of conditions: Flash to Control, Looming to Control, Flash to Looming, Sound to Control, Flash to Sync, and Flash to Async.
+However, all of these comparisons were easily interpretable, as they form a logical progression of stimuli.
+These planned comparisons consistuted a small share of all possible post-hoc comparisons between groups that one could have run on this data (6 out of 30 possible pairs).
+Typically, for planned comparisons, researchers do not use an adjustment for multiple comparisons.
+
+3) Finally, in this paper we report exact numbers all p-values, instead of indicating whether they were above or below any arbitrary threshold.
+This gives the reader the freedom to interpret our data against any significance threshold of their choice.
+As expected, some p-values were larger, and some were smaller, but we are confident that our overall conclusions are reasonable, expecially if comparing different pieces of evidence across the entire study.
+
+Together, this makes us reasonably confident that a Bonferroni correction would be unnecessarily punitive for this type of analysis.
+
 > Page 8, lines 2-12.
@@
 
+---------- TODO ----------- : Argue that average firing rate is usually applied to actual firing rate (either long-term, or instaneous) in realistic situations (in-vivo, or during spontaneous activity), while we look at a rather artificial excitability index.
+Gain and adaptation index should be included in the text, when "tunings" are introduced, but I prefer retaining original "tunings" for repeated use.
+
 > Figure 2: Units needed for Y axis on A, B (units of a are spikes per conductance squared and units of amplitude tuning are spikes/conductance)
+
+---------- TODO ----------- : This is not true, both parameters are dimensionless, as both conductance and amplitude are treated as ordinal values. Reiterate this.
 
@@
 
+We now replaced "not interpretable" with "not easily interpretable".
+We wanted our readers to know that a comparison of these values can be interpreted very easily, while exact numbers (say, 0.82) do not carry that much narrative weight.
+
 > Page 8, line 16-19: Cohen's D tells the discriminability rather than whether there is a difference between two quantities.
 A test like the Hoteling-2 test can provide significance measures for whether the means of the data in 2C are significant.
+
+We report Cohen's d values as a measure of effect sizes, not as a quantification of significance.
+
+---------- TODO ----------- : try Hoteling t-squared test
 
@@
 
+---------- TODO ----------- : Add asterisks to figures?
+
 > Figure 3E and G: how can we reconcile these accounts?
@@
 Aren't the field of individual points (partially-transparent background) and the data plotted in 3G the relative quantities?
+
+---------- TODO ----------- : Perhaps this will be more clear now, as the Simpson's praradox paragraph is back.
+Maybe we shoudl also add 1-2 more interpretative sentences to the Simpsons paradox paragraph?
+Also, do we need a reference there?
 
@@
 
+On the correlation between monosynaptic amplitude and synaptic duration: this is a very valid observation, and it is also exactly what we claim in the text:
+
+"As expected, cells with strong monosynaptic inputs had shorter synaptic currents, while polysynaptic activity made synaptic currents longer"
+
+---------- TODO ----------- : Add a paragraph to the paper, explaining that synaptic duration is necessary, as it is what allows us to compare apples to apples, as we fit the synaptic currents exactly with a waveform we used to assess temporal tuning in dynamic clamp experiments.
+Then reiterate, and cite this paragraph here.
+
 > Figure 3G, page 10 lines 24-40.
@@
 I see no strong significant relationship between temporal tuning and synaptic duration, and am not convinced synaptic duration is a meaningful quantity.
+
+---------- TODO ----------- : See whether it is possible to use a different method here.
+The goal is to illustrate the fact that the weak correlation observed on full data is entirely driven by 3 "fast" datasets.
+Would some sort of a Tukey-like test work here?
 
@@
 
+---------- TODO ----------- : Change the description; bring attention to the fact that the correlation exists (as predicted), but is also very bad (surprisinigly bad, in fact).
+Or maybe indeed drop it, and replace it with models predicting temporal and
+
 > Why not show the 8 parameter model fit of the current tuning curves?
+
+---------- TODO ----------- : Do they mean a correlation-like plot that has model projection on X and estimations on Y? That would be interesting: do it.
 
@@
 So why the heading?
+
+---------- TODO ----------- : The section is mostly about mechanisms, but Fig 4 for now is not; once we introduce new fit-figures, we'll be able to claim it.
 

### 2018-12-09 dynamic_spikes_plot.R
Spikes analysis: tidied up

@@ -1,14 +1,16 @@
 # Dynamic Clamp spiking data analyzer
-# version Oct 30 2017
+# version Dec 09 2018
 
 require(ggplot2)
 require(dplyr)
 require(reshape2)
-library(lmerTest)
+# install.packages("lmerTest") # Mixed ANOVAs
+require(lmerTest)
+
 rm(list = ls())  # Clear workspace
 
 # ----- Read and prepare spike data ----
-d = read.table("data_outDataset.txt",header=T)
+d = read.table("Dynamic-clamp-2018-git/Data/data_outDataset.txt",header=T) # Update the path as necessary
 d = subset(d,is.element(Group,c(0,1,2,3,4,5))) # Remove slow and naive
 d = mutate(d,Group = recode_factor(Group,"0"="Control","2"="Flash","1"="Looming",
                 "3"="Sound","4"="Sync","5"="Async","6"="Slowc","7"="Slowf","8"="Naive"))
@@ -16,27 +18,32 @@ d = mutate(d,ShapeName = recode_factor(Shape,"1"="100","2"="200","3"="500","4"="
 
 # Only leave good new crashes and flashes; exclude the bad old ones
 # (where "bad old" are all old cells that don't belong to Naive group)
-d$Old = ifelse(d$Cell<=102,"Old","New") # TRUE if the cell is old
-d$Old = factor(d$Old)
+d$Old = factor(ifelse(d$Cell<=102,"Old","New")) # TRUE if the cell is old
 d = subset(d,Old=="New")
-# d = subset(d,(is.element(Group,"Naive")) | (Old=="New"))
-
+d = dplyr::select(d,-Old) # Cleanup, drop this column
 
 # ----- Some simple analysis  ----
-# Count cell numbers:
-summarize(group_by(d,Group,Old), count = length(unique(Cell)))
+summarize(group_by(d,Group), count = length(unique(Cell))) # Count cell numbers
 names(d)
 
 ds = summarize(group_by(d,Cell,Amp,Shape),Spikes=mean(Spikes))
 
 # Fit spike-curves, to quantify them with 3 parameters for each cell
+# Here: ms : mean spikes
+# sa : amplitude tuning
+# ss : temporal (shape) tuning
+# ms2 : another estimation for mean spiking
 d1 = d %>% group_by(Cell) %>% 
-  do(fsa=lm(Spikes ~ (Amp-1),.),
[…]

### 2018-12-09 dynamic_other_vars.R
Other analysis: + Hotelling test

@@ -1,22 +1,25 @@
-# Silas everything that is not spikes analyzer
-# version May 24 2018
+# Dynamic study of intrinsic plasticity:
+# Analysis of everything that isn't raw spike data.
+# Version Dec 09 2018
+
 # install.packages("lme4") # This one is required for lmerTest to work
 # install.packages("lmerTest")
 # install.packages("effsize")
-require("effsize")
-library(ggplot2)
-library(dplyr)
-library(ggbeeswarm)
-library(reshape2)
-library(MASS) # Model selection
+require(effsize)
+require(ggplot2)
+require(dplyr)
+require(ggbeeswarm)
+require(reshape2)
+require(MASS) # Model selection
 #require(lme4); detach("package:lme4",unload=T)
-library(lmerTest)
+require(lmerTest)
 #install.packages("viridis")
 require(viridis)
+
 rm(list = ls())  # Clear workspace
 
 # ----- Read the data ----
-d = read.table("data_mainInput.txt",header=T)
+d = read.table("Dynamic-clamp-2018-git/Data/data_mainInput.txt",header=T)
 d = mutate(d,group = reorder(group, groupid))
 # d_full = d                # Save a copy just in case
 
@@ -34,6 +37,8 @@ d = mutate(d, group = recode_factor(group,'Control'='Control','Flash'='Flash','C
 d$rostral = 1 - d$rostral/325        # Move to true "rostral", and from screen units to %
 d$medial = 1 - (d$medial + 25)/375   # Move to true "medial"
 
+d$rm = d$rm/10  # Units mistake in the original dataset. Now it's in GOhm
+
 # Now qplot(medial,rostral) will look like left tectum
 # "medial" is indeed how medial everything is
 # and "rostral" is indeed how rostral it is
@@ -46,8 +51,6 @@ mean(d$medial,na.rm=T)
 sd(d$medial,na.rm=T)
 min(d$medial,na.rm=T)
 max(d$medial,na.rm=T)
-
-d$rm = d$rm/10  # Units mistake in the original dataset. Now it's in GOhm
 
 # Tucking down two extreme outlier cells. Only use for visualizations, not for analysis.
 ggplot(data=d) + theme_bw() + geom_point(aes(samp,sbend))
[…]

### 2018-12-09 reviews and responses.md
Analysis: within-group synaptic to intrinsic corr

@@
 
-We report Cohen's d values as a measure of effect sizes, not as a quantification of significance.
-
----------- TODO ----------- : try Hoteling t-squared test
+We initially reported Cohen's d values as a measure of effect sizes, not as a quantification of significance.
+Now we also ran Hotelling t-squared tests on 2D sets of points, representing amplitude and temporal tuning values for different cells.
 
@@
 
----------- TODO ----------- : See whether it is possible to use a different method here.
-The goal is to illustrate the fact that the weak correlation observed on full data is entirely driven by 3 "fast" datasets.
-Would some sort of a Tukey-like test work here?
+---------- TODO ----------- : Explain that essentially we are talking about strongly reshaped vs.
+weakly reshaped protocols.
+As we do not have apriory information about what protocols are inherently stronger, we can try to use Fig 2D to separate them into subgroups: weakly affected (Control, Sound, Looming) and storngly reshaped (Flash & both multisensory).
+Explain that it was the reason for creating "supergroups".
+Also downplay "supergroups", and remove this word.
+Make it more casual.
 

### 2018-12-09 dynamic_other_vars.R

@@ -380,12 +380,12 @@ d_prepared = dclean %>%
   dplyr::select(group,samp,sbend)
 summary(d_prepared)
 
-fit = hotelling.test(.~group, data=d_prepared, pair=c("Control","Flash")); fit # 0.001
-fit = hotelling.test(.~group, data=d_prepared, pair=c("Control","Looming")); fit # 0.01
-fit = hotelling.test(.~group, data=d_prepared, pair=c("Flash","Looming")); fit # 0.1
-fit = hotelling.test(.~group, data=d_prepared, pair=c("Control","Sound")); fit # 0.2
-fit = hotelling.test(.~group, data=d_prepared, pair=c("Flash","Sync")); fit # 0.2
-fit = hotelling.test(.~group, data=d_prepared, pair=c("Flash","Async")); fit # 0.051
+fit = hotelling.test(.~group, data=d_prepared, pair=c("Control","Flash"), perm=T); fit # 0.0002
+fit = hotelling.test(.~group, data=d_prepared, pair=c("Control","Looming"), perm=T); fit # 0.01
+fit = hotelling.test(.~group, data=d_prepared, pair=c("Flash","Looming"), perm=T); fit # 0.1
+fit = hotelling.test(.~group, data=d_prepared, pair=c("Control","Sound"), perm=T); fit # 0.2
+fit = hotelling.test(.~group, data=d_prepared, pair=c("Flash","Sync"), perm=T); fit # 0.2
+fit = hotelling.test(.~group, data=d_prepared, pair=c("Flash","Async"), perm=T); fit # 0.04
 
 
 # --- IV analysis
@@ -564,6 +564,7 @@ ggplot(data=d) + geom_density(aes(log(1+poly_s)))
 # Same plot after compensation:
 ggplot(data=dadj,aes(group,log(1-mono_m))) + geom_beeswarm(color="blue",alpha=0.2) + theme_bw() + 
   stat_summary(fun.y=mean,geom="point")
+
 # ANCOVAs on transformed:
 # (relies on previouisly compensated dadj dataframe)
 summary(aov(data=d,log(1-mono_m)~medial+rostral+group)) # yes, 0.001
@@ -628,7 +629,7 @@ ggplot(data=dres,aes(lat_m,sbend,color=group)) + geom_point(shape=1) +
[…]

### 2018-12-09 reviews and responses.md
responses: minor notes on stats

@@
 We initially reported Cohen's d values as a measure of effect sizes, not as a quantification of significance.
-Now we also ran Hotelling t-squared tests on 2D sets of points, representing amplitude and temporal tuning values for different cells.
+Now we also ran Hotelling t-squared tests on 2D sets of points, representing amplitude and temporal tuning values for different cells, across different groups.
 
@@
 Make it more casual.
+
+Or maybe indeed just drop it.
+Leave two sentences: one listing r values, and another one mentioning that the negative correlation that exists for full data is entirely driven by these 3 groups, but not by those other 3 groups.
 

### 2018-12-09 main.tex
responses: minor notes on stats

@@
 We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value of "temporal tuning" (Figure 2A).
-The numerical values of these "tuning coefficients" are not interpretable, but they capture the character of tuning curves for each neuron (Figure 2A).
+The numerical values of these "tuning coefficients" are not easily interpretable, but they capture the character of tuning curves for each neuron (Figure 2A).
 All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Figure 2C; see "Methods" for model description); F(5,160)=4.8, p=4e-4 for amplitude tuning (Figure 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Figure 2C).
@@
 A visual comparison of neuronal tuning in different experimental groups (Fig 2C) shows that acoustic stimulation had opposite effects when provided on its own (without visual stimulation) than when added to visual flashes.
-Compared to control neurons, cells exposed to sound had lower amplitude tuning coefficients (flatter curve, Cohen’s d=$-$0.29), and more negative (curving down, d=$-$0.27) temporal tuning coefficients.
-In contrast, when sounds were added to flashes, both transfer functions became less flat (d=0.65 and 0.26 for "Async" compared to “Flash”, for amplitude and temporal tuning respectively), and more like curves for control neurons.
+Compared to control neurons, cells exposed to sound had slightly lower amplitude tuning coefficients (flatter curve, Cohen’s d=$-$0.29), and more negative (curving down, d=$-$0.27) temporal tuning coefficients (Hotelling t-squared test p=0.2).
+When sounds were added to flashes, however, both transfer functions became less flat (d=0.65 and 0.26 for "Async" compared to “Flash”, for amplitude and temporal tuning respectively), and more like curves for control neurons (Hotteling test p=0.04).
 Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Figure 2D), but negated the effect of visual stimulation when combined with it.
 This may imply that multisensory integration in the tectum is dominated by inhibition (see Discussion).
-Note also that looming stimuli had a weaker effect on neuronal tuning compared to flashes, both in terms of amplitude (d=0.44) and temporal tuning (d=0.22).
+Note also that looming stimuli seemed to have weaker effects on neuronal tuning compared to flashes, both in terms of amplitude (d=0.44) and temporal tuning (d=0.22).
 
@@
 
-%%% --- This section was commented out in all official submissions
+%%% --- This section below was commented out in prior submissions
 
@@
 To better understand the interplay between the stimulation-induced retuning of the entire tectal network, and tuning of individual cells within each network, we looked at the interaction of intrinsic and synaptic temporal properties separately for each treatment group (Figure 3G).
-The co-tuning seemed present in Control, Looming, and Sound groups (r=$-$0.11, $-$0.36, and $-$0.47), but was absent in all groups that experienced flashes in any form (r=0.27, $-$0.01, and 0.01 for Flash, Sync, and Async groups respectively).
+The co-tuning seemed present in Control, Looming, and Sound groups (r=$-$0.11, $-$0.36, and $-$0.47), but was absent in groups that experienced flashes, and so were subjected to stronger retuning (r=0.27, $-$0.01, and 0.01 for Flash, Sync, and Async groups respectively).
 If three slow, and three fast (Flash-like) groups were combined into two larger "supergroups", the Control-Looming-Sound neurons exhibited a homeostatic negative correlation between synaptic duration and intrinsic temporal tuning (r=$-$0.29, p=0.01, n=70), while the Flash-Sync-Async neurons lacked cells preferring slow stimuli, and so lacked the co-tuning (r=0.08, p=0.50, n=80).
@@
 
-Knowing that tectal neurons can tune to inputs of different temporal dynamics, we then investigated the cellular mechanisms that could underlie this tuning.
+Knowing that tectal neurons can tune to inputs of different temporal dynamics, we then tried to identify the cellular mechanisms underlying this tuning.
 For each cell, we used a sequence of voltage steps (Figure 4A) to activate Na and K conductances, and quantified ionic current amplitudes and activation potentials (Figure 4B) as it was done in earlier studies \citep{ciarleglio2015}.

### 2018-12-10 reviews and responses.md
reviews: general reviews

@@
 
-We now added "we asked" to both sentences, making "we" a subject.
+We now added "we asked" to both sentences, which makes "we" a subject.
 
 > Page 3, line 34: "spikiness" -> not a precise word. "Changes in f-I curve", perhaps? Or "Average firing rate"?
+
+We think that this word well reflects the nature of the property we are describing (the property of being easily excitable, and able to generate spikes), and we also think that we define it rather precisely within thiss paper.
+We prefer it to other alternatives, as they are rather too general ("intrinsic excitability") or too bulky ("ability to produce spikes in response to stimulation").
+
+Of the two options offered by the reviewer, the first one ("Changes in f-I curve") is both too long, and does not reflect the nature of our measure, as with it we are trying to assess average ability to produce spikes, not a change of any sort.
+The second one sounds good and standard, but is actually somewhat misleading, as the term "Avereage firing rate" is defined rather precisely as the average rate at which a neuron fires in the network; usually either in the context of in-vivo recordings, or in-vitro spontaneous activity.
+Accordingly, a true "Average firing rate" for our neurons would depend both on their intrinsic properties (perhaps the measure we call "spikness here"), *and* the strength of their synaptic inputs, as well as their position within the network.
+In short, while "Average firing rate" is an important property, in this study we did not address it, nor had an opportunity to observe a proxy for it.
 
@@
 
+------------ TODO ----------- : Can we still change something to make it a tad more precise? And then say that it is precise enough?
+
 > Page 4, lines 21-24.
@@
 
+We did in fact run a linear model with repeated measures that may be vaguely described as multi-variate ANOVA; see responses above.
+
 > Page 4: Lines 27, 28: This sentence is missing conjunctions "in order to map their amplitude transfer function" ?
@@
 > Page 4: Lines 27, 28: What exactly is meant by the amplitude transfer function or amplitude tuning? Is there an equation?
+
+-------------------- TODO -------------------: Make sure this piece refers to the equation again.
 
@@
 
+Correction accepted.
+
 > Page 7, line 3: after multi sensory stimulation, "tectal neurons were more excitable than after visual stimulation alone).
@@
 The average number of spikes is reported..is this across all conductance curve conditions or just one of them?
-Next, in Fig 1E, "sync" and "flash" and "looming" all look pretty similar to each other.
-What are the degrees of freedom?
-Again, they seem very high like each condition might be being treated as independent.
+
+> Next, in Fig 1E, "sync" and "flash" and "looming" all look pretty similar to each other.
+
+> What are the degrees of freedom? Again, they seem very high like each condition might be being treated as independent.
+
+See other comments above.
+Generally, unless a mixed model is used, the second value for degrees of freedom, defining F-distributions, is close to the total number of measurements recorded in a study, even if a multivariate analysis of variance is used, and even for nested non-independent designs, such as blocking or repeated measures analysis.
+For our study in particular, the only way to bring the second value for degrees of freedom down, making it closer to the number of cells, rather than to the number of measurements, would be to use a mixed model.
+We used a mixed model in our senstivity / verification test, and observed that it provided qualitatively similar results, as described in the method.
+We however reported a fixed model everywhere else, as it is more straightforward, and, in our opinion, more consistent.
 
@@
 
-> Page 8, lines 2-12.
-"Average firing rate" is a more common term than "spikiness".
-How about "gain" for amplitude tuning?
+> Page 8, lines 2-12. "Average firing rate" is a more common term than "spikiness".
+
+Please see our comments above.
+The term "average firing rate" is typically used to refer to actual average firing rates, either long-term or instaneous, in situations when relatively realistic neural activity is possible, such as in-vivo recordings, or during spontaneous activity.
+We however looked at a rather artificial excitability index, and we would prefer to stress that by naming this index, and defining it within the study.
+
+> How about "gain" for amplitude tuning?
 I see that the authors are using the parameter a to indicate the non-linearity in the tuning curve.
@@
 
----------- TODO ----------- : Argue that average firing rate is usually applied to actual firing rate (either long-term, or instaneous) in realistic situations (in-vivo, or during spontaneous activity), while we look at a rather artificial excitability index.
-Gain and adaptation index should be included in the text, when "tunings" are introduced, but I prefer retaining original "tunings" for repeated use.
+---------- TODO ----------- : Gain and adaptation index should be included in the text, when "tunings" are introduced, but I prefer retaining original "tunings" for repeated use.
 

### 2018-12-10 reviews and responses.md
responses: minor wording

@@
 This is of course true, but while many types of intricate effects of intrinsic plasticity are described in small networks, and especially in oscillatory networks, such as the STG, it is less common to consider these non-trivial effects in large feed-forward excitatory networks, such as networks in the cortex, or superior colliculus.
-It is natural for researchers to limit the complexity of their conceptual and computational models, and it is probably fair to say that as the number of neurons involved in a model increases, researchers typically shift their attention from intrinsic mechanisms to connectomic approaches, approximating neural networks as a collection of nodes, linked with synapses of different strengths (e.g: Cline 2008; Kirby 2013).
+It is natural for researchers to limit the complexity of their conceptual and computational models, and it is probably fair to say that as the number of neurons involved in a model increases, researchers often shift their attention from intrinsic mechanisms to connectomic approaches, approximating neural networks as a collection of nodes, linked with synapses of different strengths (e.g: Cline 2008; Kirby 2013).
 Even realistic biophysical models that represent neurons as multi compartment systems with active dendritic currents often don't assume that these active currents may be modulated in response to activation (Moldwin 2018).
@@
 We also predict that similar effects of temporal tuning may be observed in other systems, such as mammalian cortex.
+
+In the new version of this manuscript, we added a few sentences to the introduction, trying to make our message more clear, and also more nuanced.
+
+&nbsp;
 

### 2018-12-13 main.tex
tex: citations order fixed manually

@@
 
-\usepackage[round, sort, numbers, authoryear]{natbib} % Reference manager, round citations
+\usepackage[round, numbers, authoryear]{natbib} % Reference manager, round citations, unsorted (we keep refs.bib manually sorted)
 % \usepackage[super]{natbib} % Nature-style citations
@@
 \section*{Introduction}
-% Sep 04: 645 words (limit 650)
 
-% Intro: be more specific that we're not talking about STG or spinal.
+% manually sort bib by year, so that citations are also sorted by year, and not alphabetically
+
+% Intro: be more specific that we're not talking about STG or spinal (with refs).
 That in FF intrinsic is often underplayed, and that the same is tru for neuro-inspired machine learning.
-Link to Markram?
-Check the response to elife rejection
+Check my own response to elife rejection, draw from there.
 
@@
 
-It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network}.
+It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network,reimann2017}.
 Biological neurons, however, are tuned in ways that go well beyond adjusting one “strength” value per synapse: cells within the same network often demonstrate variability of activation thresholds \citep{kole2012}, production of bursts \citep{popovic2011}, inactivation by strong inputs \citep{bianchi2012}, and more.
 This diversity of tuning relies on coordinated changes of many parameters across a complex, multivariate landscape \citep{oleary2013}, as neuronal phenotypes are shaped by sensory experiences, and adjusted by modulatory inputs \citep{evans2015}.
-The dysregulation of intrinsic plasticity can affect network dynamics \citep{tien2018}, and lead to a loss of function \citep{marcelin2009}.
-And yet, for many networks, it is still unclear whether variation in intrinsic phenotypes is primarily a result of excitability calibration, or whether it is a defining aspect of network topology and architecture \citep{titley2017}.
+The dysregulation of intrinsic plasticity affects network dynamics \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}.
+And yet, with an obvious exception of oscillatory networks \citep{marder2011,picton2018control}, for many brain areas it is still unclear whether variation of intrinsic phenotypes serves as a defining aspect of network topology and architecture, or whether it is just a consequence of transfer function normalization \citep{titley2017}.
 
@@
 
-While the optic tectum (known as superior colliculus in mammals) is often described as a primarily visual area, it is also involved in heavy multisensory computations \citep{stein2014}.
+While the optic tectum (homologous to superior colliculus in mammals) is often described as a primarily visual area, it is also involved in heavy multisensory computations \citep{stein2014}.
 In tadpoles, it integrates visual information with inputs from mechanosensory, auditory, and lateral line modalities \citep{deeg2009,pratt2009,hiramoto2009,felch2016,truszkowski2017}, but the logic of this integration is still unclear.
@@
 
-In contrast, \textit{within} each experimental group, cells that preferred shorter synaptic inputs tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
+In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
 We calculated differences between the properties of each individual cell and the average for the experimental group it belonged to, and showed these "deviations from respective averages" on one plot (Figure 3F).
-Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (r=$-$0.18, p=0.03, n=151).
+Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (adjusted r=$-$0.18, p=0.03, n=151).
 This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, increasing their ability to respond to unusual patterns of synaptic activation.

### 2019-01-07 dynamic_other_vars.R
Model comparison for spiking in CC and DC

@@ -19,7 +19,10 @@ require(viridis)
 rm(list = ls())  # Clear workspace
 
 # ----- Read the data ----
-d = read.table("Dynamic-clamp-2018-git/Data/data_mainInput.txt",header=T)
+# (Sorry, you'll have to update this one, as R doesn't support relative referencing)
+#d = read.table("Dynamic-clamp-2018-git/Data/data_mainInput.txt",header=T)
+d = read.table("5_Dynamic clamp/Git - Dynamic/Data/data_mainInput.txt",header=T)
+
 d = mutate(d,group = reorder(group, groupid))
 # d_full = d                # Save a copy just in case
 
@@ -28,11 +31,14 @@ d = subset(d,group %in% c('Control','Crash','Flash','Sound','Sync','Async'))
 d = mutate(d, group = recode_factor(group,'Control'='Control','Flash'='Flash','Crash'='Looming',
                                     'Sound'='Sound','Sync'='Sync','Async'='Async'))
 
+# Now let's fix cell coordinates (as they were originally measured a bit weirdly)
 # Estimations from the tectal photo and drawing:
-# Lower lip is has "rostral" of about 325 (which means that original numbers should have been called "caudal")
-# Rostral end of tectum has "rostral" of about 0
-# Tectum edge has "medial" of about 375 (which means that it shold have been called "medial")
-# Tectum midline has "medial" of about -25
+# Lower lip of the tectum has the "rostral" value of about 325 
+# (which means that original numbers should have been actually called "caudal", not "rostral",
+# as larger numbers corresponded to more caudal positioning)
+# Rostral end of tectum has "rostral" of about 0. We'll have to flip it.
+# Tectum side edge has "medial" of about 375 (which means that, again, it shold have been called "medial")
+# Tectum midline has "medial" of about -25. So we flip it, but also shift it.
 
 d$rostral = 1 - d$rostral/325        # Move to true "rostral", and from screen units to %
 d$medial = 1 - (d$medial + 25)/375   # Move to true "medial"
@@ -54,10 +60,10 @@ max(d$medial,na.rm=T)
 
[…]

### 2019-01-07 reviews and responses.md
responses: minor ideas
changes in Fig 4

@@
 
----------- TODO ----------- : This is not true, both parameters are dimensionless, as both conductance and amplitude are treated as ordinal values. Reiterate this.
+---------- TODO ----------- : This is not true, both parameters are dimensionless, as both conductance and amplitude are treated as ordinal values.
+Reiterate this.
+Also, in the Methods, where we describe that we treated these values as ordinal, explain that this is because of the strong non-linearity of effects, and that treating values as ordinal is equivalent to rank-transform, and is arguably better and simpler than any other artificial transform.
 
@@
 
----------- TODO ----------- : Perhaps this will be more clear now, as the Simpson's praradox paragraph is back.
+---------- TODO ----------- : Perhaps this will be more clear now, as the Simpson's paradox paragraph is back.
 Maybe we shoudl also add 1-2 more interpretative sentences to the Simpsons paradox paragraph?
@@
 Of course we would expect such a relationship.
+Why not show the 8 parameter model fit of the current tuning curves?
 
----------- TODO ----------- : Change the description; bring attention to the fact that the correlation exists (as predicted), but is also very bad (surprisinigly bad, in fact).
-Or maybe indeed drop it, and replace it with models predicting temporal and
-
-> Why not show the 8 parameter model fit of the current tuning curves?
-
----------- TODO ----------- : Do they mean a correlation-like plot that has model projection on X and estimations on Y? That would be interesting: do it.
+In the previous version of this paper we tried to show correlations of 2 types of spiking (those recorded in current and dynamic clamp modes) with Na conductance, to illustrate that one of the correlations is much stronger than the other.
+We agree however that showing the 8 parameter model fit is much better way of illustrating this point.
+We now show two scatterplots, for both dynamic and current clamp data, in which values predicted by the 8-parameter model are compared to actual measurements.
+It is clear to see that one of the models (that for current clamp data) works much better than the other one (for the dynamic clamp data).
 
@@
 
----------- TODO ----------- : The section is mostly about mechanisms, but Fig 4 for now is not; once we introduce new fit-figures, we'll be able to claim it.
+Different fields have different criteria for what level of explanation is low enough to count as "mechanistic".
+Had we reliably predicted cell phenotypes (spiking) from their low-level electrophysiological properties, especially across treatment groups, we would have comfortably called it a mechanistic explanation.
+We show that for one type of measurements (current clamp), we have a tolerable level of mechanistic understanding of differences in observed cell excitability, while for more nuanced dynamic clamp experiments this mechanistic understanding is clearly lacking.
 

### 2019-01-07 main.tex
changes in Fig 4

@@
 Across input conductances of different lengths (100, 200, 500, and 1000 ms), neurons exposed to flashes and looming stimuli responded differently than in control (F(1, 677)=25.1; p=7e-7; and F(1,629)=12.0; p=6e-4 respectively).
-In control neurons, longer inputs typically evoked stronger spiking, whereas neurons from stimulated animals had flatter tuning curves, with a plateau, or even a decrease in spike number for longer conductance injections (Fig 1E).
+In control neurons, longer inputs typically evoked stronger spiking, whereas neurons from stimulated animals had flatter tuning curves, with a plateau, or even a decrease in spike number for longer conductance injections (Figure 1E).
 In essence, while control neurons “preferred” longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
@@
 (\textbf{E}).
-One of the explanatory correlations between neuronal spiking in current clamp experiments and an ionic current (in this case, peak Na current).
+The number of spikes registered in current clump mode: values predicted from a linear model, plotted against actually observed values.
+The model works reasonably well (with 61\% of variance explained).
 (\textbf{F}).
-Similar correlation for the dynamic clamp experiments.}
+Similar comparison for the dynamic clamp experiments: the model has very low predictive value (13\% of variance explained).}
 \end{figure}
@@
 Across all cells, the maximal number of spikes observed during current step injections correlated with the average number of spikes in dynamic clamp experiments (Figure 4D; r=0.46, p=2e-9, n=152).
-In agreement with \citep{ciarleglio2015}, spiking in current clamp experiments correlated with peak sodium (INa: r=0.42, p=2e-8, n=152; Figure 4F) and stable potassium currents (IKs: r=0.39, p=2e-7), as well as activation potential for sodium current (VNa: r=0.24, p=0.02).
-Overall, the 8 intrinsic variables described above (Rm, Cm, three peak currents, and three activation potentials) explained 61\% of cell-to-cell variability in the maximal number of spikes from current clamp experiments, comparable to 49\% reported in our previous study \citep{ciarleglio2015}, and noticeably higher than 13\% for dynamic clamp experiments.
+In agreement with \citep{ciarleglio2015}, spiking in current clamp experiments correlated with peak sodium (INa: r=0.42, p=2e-8, n=152) and stable potassium currents (IKs: r=0.39, p=2e-7), as well as activation potential for sodium current (VNa: r=0.24, p=0.02).
+Overall, the 8 intrinsic variables described above (Rm, Cm, three peak currents, and three activation potentials) explained 61\% of cell-to-cell variability in the maximal number of spikes from current clamp experiments (Figure 4E), comparable to 49\% reported in our previous study \citep{ciarleglio2015}, and noticeably higher than 13\% for dynamic clamp experiments (Figure 4F).
 
@@
 Traditionally, cell capacitance is thought of as a relatively immutable parameter that describes cell morphology, and can even be used to estimate its size, yet in the tadpole tectum, we found it to drop both with age, and after strong sensory stimulation, even though cells don't seem to change their visual appearance (\citealt{ciarleglio2015}, Figure 7D).
-An intriguing possibility is that these changes in cell capacitance may be due to electiric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic arbor, soma, and axon initial segment \citep{bollmann2009}.
+An intriguing possibility is that these changes in cell capacitance may be due to electiric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic arbor, soma, and axon initial segment \citep{bollmann2009,jarvis2018morphology}.
 This differential uncoupling may be achieved through either minor changes in cell morphology \citep{leterrier2018axon}, or through target modulation of sodium and potassium channels at key points between the compartments, which would introduce shunting, and so strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.

### 2019-02-01 main.tex
tex: minor changes in layout

@@
 \usepackage[top=0.85in,left=1.5in,right=1.5in,footskip=0.75in]{geometry} % For one-column version
+
 %\usepackage[top=0.85in,left=1in,right=1.0in,footskip=0.75in]{geometry} % For two-column version
@@
 
+% Titles
+\usepackage{titlesec}
+\titlespacing{\section}{0pc}{0.5pc}{0pc}
+
 % Headers and footers
@@
 
-\linenumbers % Comment this to suppress line numbers
+%\linenumbers % Comment this to suppress line numbers
 
@@
 
-% manually sort bib by year, so that citations are also sorted by year, and not alphabetically
+% TODO LIST
+
+% In Discussion, mention that studying post-hyperpolarization currents would be a great next step
 
@@
 The number of spikes registered in current clump mode: values predicted from a linear model, plotted against actually observed values.
-The model works reasonably well (with 61\% of variance explained).
+The model works reasonably well (61\% of variance explained).
 (\textbf{F}).
-Similar comparison for the dynamic clamp experiments: the model has very low predictive value (13\% of variance explained).}
+Similar comparison for the dynamic clamp experiments: the model has very low predictive value (13\% of variance explained).
+Here and in E, both values are adjusted for position.}
 \end{figure}
@@
 
-\subsection*{A comparison between dynamic clamp and current clump experiments}
+\subsection*{A comparison between dynamic clamp and current clamp experiments}
 

### 2019-02-02 reviews and responses.md
minor changes in responses
tex: figure captions, responses to reviewers

@@
 
-These reviews were received on Nov 1st 2018 from J Neurosci, as this paper was rejected by the editors.
-
-Even though the paper was rejected, we decided to include these reviews to our next submission, and to this repository, and provide our responses to each of the critiques.
+These reviews were received on Nov 1st 2018 from J Neurosci, as this paper was rejected by the editor.
+We decided to include these reviews to our next submission, and to this repository, and provide our responses to each of the critiques.
 
@@
 
-In this, updated version of the paper, we are trying to be more explicit about possible next steps other researches could take to study the mechanisms of the curious phenomenon we discovered.
+In this, updated version of the paper, we try to be more explicit about possible next steps that may be taken to study the mechanisms behind the exciting phenomenon we discovered.
 
@@
 
-The number of degrees of freedom in question comes from a full linear model, and does mean that we treated different conditions as independent.
-Typically, to compare the numer of spikes in two conditions we used a 3-way ANCOVA (injection amplitude and duration as ordinal variables; group id as a nominal variable) with interactions, and repeated measures (wieh cell id included as a nominal variable).
+The number of degrees of freedom in question comes from a full linear model, and does not mean that we treated different conditions as independent.
+Typically, to compare the numer of spikes in two conditions we used a 3-way ANCOVA (injection amplitude and duration as ordinal variables; group id as a nominal variable) with interactions, and repeated measures (where cell id included as a nominal variable).
 For example, for a comparison of "Control" group to "Sound" group we used the following R code (see `dynamic_spikes_plot.R` for the full code):
@@
 
-We now included a brief description of our model in the "Results" section; improved the description in the "Methods" section; and added several referrals to the "Methods" section in the "Results" section, to hint that the reader may find full information there.
+In addition to a full description of our analysis approach, as given in the "Methods", we now included a second, shoter description of it in the "Results" section, to make the paper more readable.
+We also improved the description in the "Methods" section; and added several extra referrals to the "Methods" section from the "Results" section, to remind the reader that extra information is available there.
 In particular, in the sentence that reports the first F-value for this study, we now added the following commentary:
@@
 
-"This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, increasing their ability to respond to unusual patterns of synaptic activation."
+"This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patters, and enhancing responses to unusual patterns of synaptic activation."
 
 > 8.	Page 12 the section on position within the tectum feels like it was just tacked onto the end of the paper. This should be integrated earlier in the paper perhaps to go with figure 1A.
+
+We placed the decription of this effect at the very end of the paper, as we prefer to downplay it a bit, as it was described previously (Khakhalin 2012; Hamodi 2012; Ciarleglio 2015), and we don't want to distract the reader from our other findings.
+At the same time, we find it important to mention that we observed a strong correlation with position: first, because it provides an independent replication of previously observed patterns, and second, as the dependency of cellular properties on position necessitated an adjustment for position during analysis (see "Methods"), which needed to be justified.
+The implication for the principle of parameter degeneracy in development (Prinz 2004) is also interesting, and we wanted to point at it, even though within this paper we don't have enough material to fully explore this theme.
 
@@
 
-On references to previous parts, thank you for pointing it out!
-We now tried to link different parts of the paper more tightly together, by reminding the reader about previously made statements every time we make a reference.
+On excessive cross-references between different parts of the paper: thank you for pointing it out!
+We now tried to link different parts of the paper more tightly together, by gently reminding the reader about previously made statements every time we make a reference.
 
-On statistical analysis: we do not pool data points from non-independent cells, but used a repeated measures analysis, verified by mixed model analysis (see Methods, as well as corrections described in our responses to Reviewer 1).
+On statistical analysis: we do not pool data points from non-independent cells, but used a repeated measures analysis, verified by mixed model analysis (see Methods, as well as corrections described above, in our responses to Reviewer 1).
 
-On synaptic blockers: it is true that we measured intrinsic properties without synaptic blockers, but this is considered a standard practice in this preparation, as most earlier studies measured IV curves without synaptic blockers (Aizenman ..
+On synaptic blockers: it is true that we measured intrinsic properties without synaptic blockers, but this is considered a standard practice in this preparation, as most earlier studies measured IV curves without synaptic blockers (Azenman ..
 Cline 2002; Aizenman ..
@@
 
+---------- TODO ----------- :
+
 > Results
@@
 Here, we presented a checkerboard"...
+
+---------- TODO ----------- :
 
@@
 
+---------- TODO ----------- :
+
 > Page 4: Lines 27, 28: What exactly is meant by the amplitude transfer function or amplitude tuning? Is there an equation?
@@
 > Page 4, lines 27 - 33: what figure panels are being described here?
+
+---------- TODO ----------- :
 
@@
 
+---------- TODO ----------- :
+
 > Page 6, line 22: "homologous to superior colliculus"
@@
 The average number of spikes is reported..is this across all conductance curve conditions or just one of them?
+
+---------- TODO ----------- :
 
@@
 
----------- TODO ----------- : Gain and adaptation index should be included in the text, when "tunings" are introduced, but I prefer retaining original "tunings" for repeated use.
+We would really prefer to retain terms "amplitude tuning" and "temporal tuning", as they better represent the main message of our paper, as we are trying to think of these values not in terms of abstract properties each neuron has, but as parameters that can tune a neuron to a certain type of synaptic inputs, in terms of their temporal properties, and their amplitude.
+We however now included words "gain" and "adaptation index" in paragraphs that introduce values of amplitude and temporal tuning, respectively.
 
@@
 
----------- TODO ----------- : This is not true, both parameters are dimensionless, as both conductance and amplitude are treated as ordinal values.
-Reiterate this.
-Also, in the Methods, where we describe that we treated these values as ordinal, explain that this is because of the strong non-linearity of effects, and that treating values as ordinal is equivalent to rank-transform, and is arguably better and simpler than any other artificial transform.
+Both tuning parameters are dimensionless, as both conductance and amplitude were treated as rank-transformed, ordinal values (see methods).
 
@@
 
----------- TODO ----------- : Add asterisks to figures?
+We added asterisks to mark significance in figures.
 
@@
 
----------- TODO ----------- : Perhaps this will be more clear now, as the Simpson's paradox paragraph is back.
-Maybe we shoudl also add 1-2 more interpretative sentences to the Simpsons paradox paragraph?
-Also, do we need a reference there?
+We now added a paragraph describing this situation in detail, and reference a textbook name for this type of situation, when between-group and within-group analyses yield seemily opposite results (Simpson's paradox).
 
@@
 
----------- TODO ----------- : Explain that essentially we are talking about strongly reshaped vs.
-weakly reshaped protocols.
-As we do not have apriory information about what protocols are inherently stronger, we can try to use Fig 2D to separate them into subgroups: weakly affected (Control, Sound, Looming) and storngly reshaped (Flash & both multisensory).
-Explain that it was the reason for creating "supergroups".
-Also downplay "supergroups", and remove this word.
-Make it more casual.
-
-Or maybe indeed just drop it.
-Leave two sentences: one listing r values, and another one mentioning that the negative correlation that exists for full data is entirely driven by these 3 groups, but not by those other 3 groups.
+Removed.
+We attempted a different, more convincing analysis of the interaction between synaptic and intrinsic properties across groups, but when split by group, our analysis lacks power, so we decided to follow the advice and remove this paragraph.
 
@@
 
+---------- TODO ----------- :
+
 > "intrinsic plasticity does not simply adjust neuronal spikiness, but can regulate selectivity for inputs of different dynamics".
@@
 
+---------- TODO ----------- :
+
 > "we show that synaptic and intrinsic temporal properties of neurons are homeostatically co-tuned" what does this mean?
+
+---------- TODO ----------- :
 
@@
 When machine learning approaches are used as a model for brain development, intrinsic excitability is reflected in these models, as a change in activation function of each artificial neuron (Marblestone 2016).
-This type of modeling implicitly assumes, however, that outside of obviously oscillatory networks (spinal cord, thalamus, etc.), intrisic excitability in biological networks is largely confined to overall changes in neuronal "resonsiveness".
+This type of modeling implicitly assumes, however, that outside of obviously oscillatory networks (spinal cord, thalamus, etc.), intrisic excitability in biological networks is largely confined to overall changes in neuronal "responsiveness".
 

### 2019-02-02 main.tex
tex: figure captions, responses to reviewers

@@
 \begin{figure*}
-\includegraphics[width=\linewidth]{fig1.png}
+\includegraphics[width=\linewidth]{fig1.pdf}
 \caption{
@@
 
-We then looked at how an increase in transmembrane conductance translated into increased spike output of neurons, to map their amplitude tuning, or amplitude transfer function.
+We then looked at how an increase in transmembrane conductance translated into increased spike output of neurons, to map their amplitude tuning (also known as amplitude transfer function, or gain).
 Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve, and did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively).
@@
 \begin{figure*}[!t]
-\includegraphics[width=\linewidth]{fig2.png}
+\includegraphics[width=\linewidth]{fig2.pdf}
 \caption{
@@
 (\textbf{B}).
-Amplitude tuning of neurons across different experimental groups.
+Amplitude tuning of neurons across different experimental groups (stars show t-test p<0.05 compared to control).
 (\textbf{C}).
@@
 To visualize and interpret differences in neuronal tuning, we quantified each of the three aspects of intrinsic tuning (average spikiness, amplitude tuning, and temporal tuning) with one value per neuron (see Methods).
-We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value of "temporal tuning" (Figure 2A).
+We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value characterising the "temporal tuning" or adaptation index of each neuron (Figure 2A).
 The numerical values of these "tuning coefficients" are not easily interpretable, but they capture the character of tuning curves for each neuron (Figure 2A).
@@
 We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Figure 3B) differed across experimental groups (Figure 3A; F(5,161)=3.2, p=0.009; see "Methods" for a description of the linear model we used).
-Both Sync and Async multisensory groups had larger early synaptic currents than the Control group (Tukey p=0.03 and 0.04; Cohen d=0.46 and 0.74 on log-transformed data respectively).
+Both Sync and Async multisensory groups had larger early synaptic currents than the Control group (Tukey p=0.03 and 0.04; Cohen d=0.92 and 0.73 on log-transformed data respectively).
 The amplitude of late synaptic currents–produced by recurrent network activation (15-145 ms after the stimulus)–did not differ across groups.
@@
 \begin{figure*}[!t]
-\includegraphics[width=\linewidth]{fig3.png}
+\includegraphics[width=\linewidth]{fig3.pdf}
 \caption{Changes in synaptic transmission, and co-tuning of synaptic and intrinsic neuronal properties.
 (\textbf{A}).
-Amplitudes of early monosynaptic inputs to tectal neurons in all experimental groups (given in log scale, with outliers brought within the axes limits).
+Amplitudes of early monosynaptic inputs to tectal neurons in all experimental groups (in log scale, outliers brought within the axes limits, stars show t-test p<0.05 compared to control).
 (\textbf{B}).
@@
 (\textbf{D}).
-Synaptic current duration was different between experimental groups (see the text).
+Synaptic current durations were different between experimental groups (see text; stars show t-test p<0.05 compared to control).
 (\textbf{E}).
@@
 Within experimental groups, temporal tuning of individual neurons negatively correlated with the duration of synaptic currents they received.
-Axes show within-group deviations of temporal tuning and synaptic current duration from respective averages for each group.
-(\textbf{G}).
-Raw tuning and synaptic duration values for each treatment group, with linear regression lines.}
+Axes show within-group deviations of temporal tuning and synaptic current duration from respective averages for each group.}
 \end{figure*}
@@
 As expected, cells with strong monosynaptic inputs had shorter synaptic currents, while polysynaptic activity made synaptic currents longer (Figure 3C; p=2e-16, r=$-$0.78, n=168).
-We found that the synaptic current duration was different across treatment groups (Figure 3D; F(5,163)=6.3, p=2e-5).
-Cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24 and 304$\pm$40 ms respectively), indicating that prolonged sensory activation with short, frequent stimuli, reshaped synaptic transmission in the tectum, making it faster, because of selective potentiation of visual inputs from the eye.
+The synaptic current duration was different across treatment groups (Figure 3D; F(5,163)=6.3, p=2e-5); cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24 and 304$\pm$40 ms respectively), indicating that prolonged sensory activation with short, frequent stimuli, reshaped synaptic transmission in the tectum, making it faster, because of selective potentiation of visual inputs from the eye.
 
@@
 We calculated differences between the properties of each individual cell and the average for the experimental group it belonged to, and showed these "deviations from respective averages" on one plot (Figure 3F).
-Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (adjusted r=$-$0.18, p=0.03, n=151).
-This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, increasing their ability to respond to unusual patterns of synaptic activation.
+Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (adjusted r=$-$0.19, p=0.02, n=151).
+This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patters, and enhancing responses to unusual patterns of synaptic activation.
 
-%%% --- This section below was commented out in prior submissions
+%%% --- The paragraph below was commented out in prior submissions
 
-Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.04, p=0.7, n=151).
+Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.07, p=0.4, n=151).
 This is a textbook example of a so called "Simpsons paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.
-
-To better understand the interplay between the stimulation-induced retuning of the entire tectal network, and tuning of individual cells within each network, we looked at the interaction of intrinsic and synaptic temporal properties separately for each treatment group (Figure 3G).
-The co-tuning seemed present in Control, Looming, and Sound groups (r=$-$0.11, $-$0.36, and $-$0.47), but was absent in groups that experienced flashes, and so were subjected to stronger retuning (r=0.27, $-$0.01, and 0.01 for Flash, Sync, and Async groups respectively).
-If three slow, and three fast (Flash-like) groups were combined into two larger "supergroups", the Control-Looming-Sound neurons exhibited a homeostatic negative correlation between synaptic duration and intrinsic temporal tuning (r=$-$0.29, p=0.01, n=70), while the Flash-Sync-Async neurons lacked cells preferring slow stimuli, and so lacked the co-tuning (r=0.08, p=0.50, n=80).
-This suggests that when fast visual stimulation made the tectal network selective to short activation patterns, it happened not because all neurons uniformly changed their properties, but because a particular subset of neurons, namely those that receive strong direct inputs from the retina and weak recurrent inputs, become less excitable.
-Normally these neurons experience fast synaptic inputs, but are most responsive to slow conductances; in overstimulated networks however they became selective to fast conductances.
 
@@
 \centering
-\includegraphics[width=3.2in]{fig4.png}
+\includegraphics[width=3.2in]{fig4.pdf}
 \caption{Electrophysiological properties of individual neurons, compared to their spiking in current and dynamic clamp experiments.

### 2019-02-02 dynamic_other_vars.R

@@ -5,21 +5,22 @@
 # install.packages("lme4") # This one is required for lmerTest to work
 # install.packages("lmerTest")
 # install.packages("effsize")
-require(effsize)
-require(ggplot2)
-require(dplyr)
-require(ggbeeswarm)
-require(reshape2)
-require(MASS) # Model selection
-#require(lme4); detach("package:lme4",unload=T)
-require(lmerTest)
 #install.packages("viridis")
-require(viridis)
+
+require(dplyr)
+require(ggplot2)
+require(effsize)
+require(ggbeeswarm) # Suddenly stopped working after an update around Dec 2018; may be a version conflict
+require(reshape2) # needed for some old code
+require(MASS) # Model selection. Note that it annoying masks "select" from dplyr
+require(lmerTest) # Random effects model, requires lme4 as a dependency
+require(viridis) # Pretty colors
 
 rm(list = ls())  # Clear workspace
 
 # ----- Read the data ----
-# (Sorry, you'll have to update this one, as R doesn't support relative referencing)
+# (The address below needs to point at the main data file. 
+# Sadly, R doesn't support relative referencing)
 #d = read.table("Dynamic-clamp-2018-git/Data/data_mainInput.txt",header=T)
 d = read.table("5_Dynamic clamp/Git - Dynamic/Data/data_mainInput.txt",header=T)
 
@@ -27,10 +28,12 @@ d = mutate(d,group = reorder(group, groupid))
 # d_full = d                # Save a copy just in case
 
 names(d)
+# Remove groups that weren't used in the paper
 d = subset(d,group %in% c('Control','Crash','Flash','Sound','Sync','Async'))
 d = mutate(d, group = recode_factor(group,'Control'='Control','Flash'='Flash','Crash'='Looming',
                                     'Sound'='Sound','Sync'='Sync','Async'='Async'))
 
+# --- Cell positions ---
 # Now let's fix cell coordinates (as they were originally measured a bit weirdly)
 # Estimations from the tectal photo and drawing:
[…]

### 2019-02-02 reviews and responses.md
more responses

@@
 
----------- TODO ----------- :
+Reworded: "for the first time we were able to look at tectal network retuning in response to multisensory stimuli in freely behaving tadpoles."
 
@@
 
----------- TODO ----------- :
+Changed to "the stimuli we used in the present study were weaker".
 
@@
 
------------- TODO ----------- : Can we still change something to make it a tad more precise? And then say that it is precise enough?
+We like the word "spiky", as it captures the phenomelogical effect without making assuptions about underlying mechanisms. It is also intuitive and short, which aids understanding.
 
@@
 
----------- TODO ----------- :
+Reworded: "We then mapped the amplitude tuning of neurons (also known as amplitude transfer function, or gain), by looking at how an increase in transmembrane conductance translated into increased spike output."
 
@@
 
--------------------- TODO -------------------: Make sure this piece refers to the equation again.
+At this point we describe tuning as an empirical curve (something that can be plotted in a figure, and compared from cell to cell), but do not yet use any equations.
+Later in the text we parameterize these curves, and provide all related equations.
 
@@
 
----------- TODO ----------- :
+We added a reference to (Fig 1D,E).
 
@@
 
+We introduce adaptation index (parametrized quantification of temporal tuning) later in the text.
+
 > Page 6, lines 10-20. Need to cite Figure 1E
 
----------- TODO ----------- :
+Done.
 
@@
 
-Correction accepted.
+Fixed.
 
@@
 Many issues.
-The average number of spikes is reported..is this across all conductance curve conditions or just one of them?
+The average number of spikes is reported..
+Is this across all conductance curve conditions or just one of them?
 
----------- TODO ----------- :
+The averages were calculated across all testing conditions; we added this info to the sentence: "after four hours of multisensory stimulation, tectal neurons were more excitable than after visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for sync and async respectively, across all testing conditions)."
 
 > Next, in Fig 1E, "sync" and "flash" and "looming" all look pretty similar to each other.
+
+We think that it rather reasonable that effects of going through some stimulation, compared to control, are stonger, than differences between different types of stimulation.
+We explore this question in detail further in the text.
 
@@
 
-On the correlation between monosynaptic amplitude and synaptic duration: this is a very valid observation, and it is also exactly what we claim in the text:
+When comparing temporal properties of synaptic inputs to that of intrinsic tuning, it is important to make the two measures as similar (matching) as possible, as methodologically it is supposed to increase the power of our comparisons.
+In practice, if for intrinsic properties we quantify non-linearity of responses to currents of different duration, then we need to estimate current duration for our synaptic inputs.
+In other words, while synaptic current duration is largerly just a different way to quantify the relative impact of polysynaptic activity, it is a necessary step for a good analysis.
+We now reworded two sentences at the beginning of paragraph in question, to hopefully make this point more clear:
 
-"As expected, cells with strong monosynaptic inputs had shorter synaptic currents, while polysynaptic activity made synaptic currents longer"
-
----------- TODO ----------- : Add a paragraph to the paper, explaining that synaptic duration is necessary, as it is what allows us to compare apples to apples, as we fit the synaptic currents exactly with a waveform we used to assess temporal tuning in dynamic clamp experiments.
-Then reiterate, and cite this paragraph here.
+"To better match and compare temporal properties of synaptic inputs to those of intrinsic tuning, we calculated average "synaptic current duration" for each cell as a temporal "center of mass" of currents within the first 700 ms after optic chiasm stimulation (see "Methods").
+Neurons with different contribution of early and late synaptic responses naturally had different synaptic current duration: cells with strong monosynaptic inputs had shorter currents, while polysynaptic activity made synaptic currents longer (Figure 3C; p=2e-16, r=$-$0.78, n=168)."
 
@@
 
-Removed.
-We attempted a different, more convincing analysis of the interaction between synaptic and intrinsic properties across groups, but when split by group, our analysis lacks power, so we decided to follow the advice and remove this paragraph.
+We now removed this paragraph.
+In response to this comment, we initially attempted a different analysis of the interaction between synaptic and intrinsic properties across groups, but while some reasonable types of comparisons were significant, this analysis lacks power, and relies too much on post-hoc reasoning, so we decided to follow the advice and just remove this paragraph entirely.
+While we still believe that stronger stimulation (in terms of its effect on average intrinsic properties) generally caused stronger disruption of the synaptic-intrinsic correlation, this statement is hard to fully justify with our current data.
 

### 2019-02-02 dynamic_other_vars.R

@@ -225,7 +225,7 @@ model = aov(data=d,smean~rostral+medial+group); summary(model) # Yes: p=0.01
 TukeyHSD(model,which="group") # CF
 anova(lmer(data=d,smean~rostral+medial+group+(1|animal),na.action=na.omit)) # Verification (yes, 0.047)
 bartlett.test(data=d,smean~group) # Variances are different
-ggplot(data=d,aes(group,smean)) + geom_point(alpha=0.3,position=position_jitter(width=0.1)) + theme_bw()
+ggplot(data=d,aes(group,smean)) + geom_point(alpha=0.3,position=position_jitter(w=0.2,h=0)) + theme_bw()
 
 # Which vars are significantly different?
 var.test(data=subset(d,group %in% c("Control","Flash")), smean~group, alternative = "two.sided") # 2e-6
@@ -240,6 +240,8 @@ t.test(data=subset(d,group %in% c("Control","Looming")),smean~group) # 0.1
 t.test(data=subset(d,group %in% c("Control","Sound")),smean~group) # 0.5
 t.test(data=subset(d,group %in% c("Sync","Flash")),smean~group) # 0.2
 t.test(data=subset(d,group %in% c("Async","Flash")),smean~group) # 0.02
+t.test(data=subset(d,group %in% c("Control","Sync")),smean~group) # 0.06
+t.test(data=subset(d,group %in% c("Control","Async")),smean~group) # 0.4
 
 # ------- Analysis of sbend
 model = aov(data=d,sbend~rostral+medial+group); summary(model) # Yes

### 2019-02-02 reviews and responses.md
the rest of responses to reviewers

@@
 
----------- TODO ----------- :
+We reworded the beginning of the discussion, to make sure that we re-state any questions before providing the answers.
 
@@
 
----------- TODO ----------- :
+The "synaptic duration" value is higher for those synaptic inputs that last longer (have a long polysyaptic tail after the original bout of monosynaptic currents), and is smaller for those inputs that are short (mostly limited to monosynaptic currents).
+Therefore, we believe that duration value does capture and reflect the duration.
+We chose the "weighted average" approach (the center of mass), as strictly speaking, in the presence of spontaneous activity there is no point when the synaptic resonse is truly over, and one has to go for a different way to quantify it.
+
+While preparing this paper, we actually also tried a different way to estimate synaptic durations: we attempted to fit all synaptic currents with the same curve that we used for simulated conductances in our dynamic clamp experiments ( g*(t/tau)*exp(1-t/tau) ).
+While this idea seemed good in theory, in practice the synaptic curves were too variable in terms of their shape, decay, latency, and the amount of noise, making most curve fits were really bad, which made us go for a simpler, and a more parsimonuous measure.
 
@@
 
----------- TODO ----------- :
+We now made the Discussion section a bit longer, and so used longer, simpler statements, when describing the co-ordination of synaptic and intrinsic properties.
+For example, the sentece in question was replaced with this sentence: "In answer to our second question, about whether intrinsic and synaptic properties of tectal cells are in any way coordinated, here we show that intrinsic and synaptic temporal properties are co-tuned in the tectum, and moreover, that this co-tuning can be modified by sensory experience."
 

### 2019-02-02 reviews and responses.md
figure: asterisk moved

@@
-Reviews and Authors' Responses for (Busch Khakhalin 2018)
+Reviews and Authors' Responses for (Busch Khakhalin 2019)
 ======================
@@
 
-While preparing this paper, we actually also tried a different way to estimate synaptic durations: we attempted to fit all synaptic currents with the same curve that we used for simulated conductances in our dynamic clamp experiments ( g*(t/tau)*exp(1-t/tau) ).
+While preparing this paper, we actually also tried a different way to estimate synaptic durations: we attempted to fit all synaptic currents with the same curve that we used for simulated conductances in our dynamic clamp experiments `I = g*(t/tau)*exp(1-t/tau)`.
 While this idea seemed good in theory, in practice the synaptic curves were too variable in terms of their shape, decay, latency, and the amount of noise, making most curve fits were really bad, which made us go for a simpler, and a more parsimonuous measure.

### 2019-02-02 main.tex
tex: lots of tiny edits + extra ref

@@
 
-% TODO LIST
-
-% In Discussion, mention that studying post-hyperpolarization currents would be a great next step
-
-% Intro: be more specific that we're not talking about STG or spinal (with refs).
-That in FF intrinsic is often underplayed, and that the same is tru for neuro-inspired machine learning.
-Check my own response to elife rejection, draw from there.
-
-% Explain why homeostatic plasticity in a feature space makes a network more sensitive to unusual stimuli
-
 It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network,reimann2017}.
@@
 The dysregulation of intrinsic plasticity affects network dynamics \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}.
-And yet, with an obvious exception of oscillatory networks \citep{marder2011,picton2018control}, for many brain areas it is still unclear whether variation of intrinsic phenotypes serves as a defining aspect of network topology and architecture, or whether it is just a consequence of transfer function normalization \citep{titley2017}.
+And yet, with the obvious exception of oscillatory networks \citep{marder2011,picton2018control}, for many brain areas it is still unclear whether variation of intrinsic phenotypes serves as a defining aspect of network topology and architecture, or whether it is just a consequence of transfer function normalization \citep{titley2017}.
 
 The optic tectum of the \textit{Xenopus} tadpole is an ideal model for exploring these questions: it is a highly malleable distributed network of about $10^4$ neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}.
-In development, tectal neurons acquire diverse intrinsic and synaptic phenotypes, that are also shaped by sensory experiences \citep{xu2011,ciarleglio2015}.
+In development, tectal neurons acquire diverse intrinsic and synaptic phenotypes that are also shaped by sensory experiences \citep{xu2011,ciarleglio2015}.
 Circuits in the tectum can learn and reproduce the temporal dynamics of inputs to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which is more likely to involve intrinsic temporal tuning \citep{narayanan2008,beatty2014}.
@@
 Second, we checked whether changes in intrinsic properties in the tectum are a homeostatic response to each cell's history of synaptic activation, or if they are independent of synaptic properties.
-In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and also, despite an extensive search, we did not detect signs of temporal tuning (ibid,  figures 2, 4).
-However, we propose that the standard current-clamp protocols used in previous studies \citep{pratt2007,hamodi2014} were not adequate to detect important changes in the function of voltage-gated channels (see "Discussion").
+In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and despite an extensive search, we did not detect signs of temporal tuning (ibid,  figures 2, 4).
+However, we propose that the standard current-clamp protocols used in previous studies \citep{pratt2007,hamodi2014} were not adequate to detect important changes in the function of voltage-gated channels (see Discussion).
 
-Here we show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness, and supports temporal selectivity that can be reshaped by sensory experience.
+Here we show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness and supports temporal selectivity that can be reshaped by sensory experience.
 Furthermore, we show that the tuning of intrinsic properties is coordinated with the duration of synaptic inputs received by each cell.
@@
 First, instead of using current injections, we employed the dynamic clamp technique, which allowed a more realistic simulation of synaptic conductances \citep{prinz2004}.
-Unlike for more common voltage and current clamp techniques, in dynamic clamp, the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time.
-And second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols, and compared their effects on intrinsic tuning.
-The use of different sensory modalities also gave us insight into an unrelated, but equally intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at the traces left by multisensory stimuli in the tectum of freely behaving tadpoles.
+Unlike more common voltage and current clamp techniques, in dynamic clamp the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time.
+Second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols and compared their effects on intrinsic tuning.
+The use of different sensory modalities also gave us insight into an unrelated, but equally intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at tectal network retuning in response to multisensory stimuli in freely behaving tadpoles.
 
@@
 
-All analysis scripts, and summary data for every cell, can be found at:  \url{https://github.com/khakhalin/Dynamic-clamp-2018}
+All analysis scripts and summary data for every cell can be found at:  \url{https://github.com/khakhalin/Dynamic-clamp-2018}
 
@@
 Our first question was whether our stimulation protocols caused changes in intrinsic excitability of tectal neurons.
-From previous studies, we knew that in tadpoles exposed to four hours of LED flashes tectal neurons became more excitable \citep{aizenman2003,ciarleglio2015}.
-However, the stimuli we used were weaker, and similar to those used in behavioral experiments \citep{khakhalin2014,james2015,truszkowski2017}.
-We presented a checkerboard pattern that inverted once a second either instantaneously (Figure 1C left, dubbed “Flash”), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares; Figure 1C right; dubbed “Looming”; see “Methods”).
+From previous studies, we knew that in tadpoles exposed to four hours of LED flashes, tectal neurons became more excitable \citep{aizenman2003,ciarleglio2015}.
+However, the stimuli we used in the present study were weaker, and similar to those used in behavioral experiments \citep{khakhalin2014,james2015,truszkowski2017}.
+We presented a checkerboard pattern that inverted once a second either instantaneously (Figure 1C left, dubbed “Flash”), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares; Figure 1C right; dubbed “Looming”; see Methods).
 
@@
 \caption{
-Overview of experimental design, and summary of dynamic clamp results.
+Overview of experimental design and summary of dynamic clamp results.
 (\textbf{A}).
@@
 (\textbf{C}).
-A schematic of visual conditioning, in “Flash” (left) and “Looming” (right) groups.
+A schematic of visual conditioning in “Flash” (left) and “Looming” (right) groups.
 (\textbf{D}).
@@
 
-After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Figure 1A), and counted spikes produced in dynamic clamp, in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B).
-We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see "Methods").
+After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Figure 1A), and counted spikes produced during dynamic clamp in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B).
+We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see Methods).
 Contrary to our expectations, in tadpoles that were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29.
-Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell id is used as a repeated measures factor; see "Methods" for a detailed description).
+Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell id is used as a repeated measures factor; see Methods for a detailed description).
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25), which was likewise unexpected.
@@
 
-We then looked at how an increase in transmembrane conductance translated into increased spike output of neurons, to map their amplitude tuning (also known as amplitude transfer function, or gain).
-Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve, and did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively).
-The difference in amplitude tuning between these two types of stimulation was not significant (F(1,641)=3.5; p=0.06).
+We then mapped the amplitude tuning of neurons (also known as amplitude transfer function, or gain), by looking at how an increase in transmembrane conductance translated into increased spike output.
+Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (Fig 1D,E), and did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively).
+The flattening of response curves seemed slightly more pronounced for flashes than for looming, but this difference was not significant (F(1,641)=3.5; p=0.06).
 
@@
 The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a fully homeostatic retuning.
-We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation.
+We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation \citep{stemmler1999information}.
 
@@
 This suggests that acoustic stimuli did not strongly activate tectal circuits during conditioning, despite being more behaviorally salient (for our stimuli, at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}).
-As one possible explanation, auditory and mechanosensory inputs may have different cellular or subcellular targets in the tectum \citep{bollmann2009}, or they may differently recruit tectal inhibitory circuits \citep{liu2016,hamodi2016}.
+As one possible explanation, auditory and mechanosensory inputs may have different cellular or subcellular targets in the tectum \citep{bollmann2009}, or they may differentially recruit tectal inhibitory circuits \citep{liu2016,hamodi2016}.
 
@@
 For some animals, we synchronized the instantaneous checkerboard inversions (flashes) with sound clicks (dubbed “Sync”), while for others we staggered visual and acoustic stimuli by half a period (500 ms; dubbed “Async”).
-We found (Fig 1D, E) that, after four hours of multisensory stimulation, tectal neurons were more excitable than after visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for sync and async respectively).
+We found (Fig 1D, E) that, after four hours of multisensory stimulation, tectal neurons were more excitable than after visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for sync and async respectively, across all testing conditions).
 Compared to the “Flash” group, the tuning curves in multisensory groups were less flat, with a stronger effect in the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively).
@@
 (\textbf{B}).
-Amplitude tuning of neurons across different experimental groups (stars show t-test p<0.05 compared to control).
+Amplitude tuning of neurons across different experimental groups (stars show t-test p$<$0.05 compared to control).
 (\textbf{C}).
@@
 Same data as in (C), shown as averages for each group, with 95\% confidence intervals.
-Black arrows show the effects of sound clicks, when they were added to control, and when they were added to “Flashes”, to form two types of multisensory stimuli.}
+Black arrows show the effects of sound clicks, when they were added to control, and when they were added to “Flashes” to form two types of multisensory stimuli.}
 \end{figure*}
@@
 The numerical values of these "tuning coefficients" are not easily interpretable, but they capture the character of tuning curves for each neuron (Figure 2A).
-All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Figure 2C; see "Methods" for model description); F(5,160)=4.8, p=4e-4 for amplitude tuning (Figure 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Figure 2C).
+All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Figure 2C; see Methods for model description); F(5,160)=4.8, p=4e-4 for amplitude tuning (Figure 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Figure 2C).
 
@@
 
-Describing neuronal tuning with only few variables allowed us to compare cell-to-cell variability of tuning in different experimental groups.
+Describing neuronal tuning with only a few variables allowed us to compare cell-to-cell variability of tuning in different experimental groups.
 We found that this variability decreased as neurons were modulated away from the baseline (Bartlett test p=2e-9 for amplitude tuning, p=1e-9 for temporal tuning; Figure 2D).
@@
 To see whether prolonged sensory stimulation affected synaptic inputs received by tectal neurons, we recorded evoked excitatory postsynaptic currents in response to optic chiasm stimulation.
-We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Figure 3B) differed across experimental groups (Figure 3A; F(5,161)=3.2, p=0.009; see "Methods" for a description of the linear model we used).
+We found that the amplitude of the early, monosynaptic component of evoked responses (the average current between 5 and 15 ms after the shock; Figure 3B) differed across experimental groups (Figure 3A; F(5,161)=3.2, p=0.009; see Methods for a description of the linear model we used).
 Both Sync and Async multisensory groups had larger early synaptic currents than the Control group (Tukey p=0.03 and 0.04; Cohen d=0.92 and 0.73 on log-transformed data respectively).
@@
 (\textbf{A}).
-Amplitudes of early monosynaptic inputs to tectal neurons in all experimental groups (in log scale, outliers brought within the axes limits, stars show t-test p<0.05 compared to control).
+Amplitudes of early monosynaptic inputs to tectal neurons in all experimental groups (in log scale, outliers brought within the axes limits, stars show t-test p$<$0.05 compared to control).
 (\textbf{B}).
-A sample synaptic recording, showing all traces (green) and an average trace (blue).
+A sample synaptic recording, showing all traces for one cell (green) and an average trace (blue).
 The black bars show the areas at which early monosynaptic and late polysynaptic currents were measured; the vertical position of each bar represents the respective average current.
@@
 (\textbf{D}).
-Synaptic current durations were different between experimental groups (see text; stars show t-test p<0.05 compared to control).
+Synaptic current durations were different between experimental groups (see text; stars show t-test p$<$0.05 compared to control).
 (\textbf{E}).
@@
 
-Neurons with different contribution of early and late synaptic responses naturally had different synaptic current duration, which we quantified for every cell as a “center of mass” of the current within the first 700 ms after optic chiasm stimulation (see “Methods”).
-As expected, cells with strong monosynaptic inputs had shorter synaptic currents, while polysynaptic activity made synaptic currents longer (Figure 3C; p=2e-16, r=$-$0.78, n=168).
-The synaptic current duration was different across treatment groups (Figure 3D; F(5,163)=6.3, p=2e-5); cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24 and 304$\pm$40 ms respectively), indicating that prolonged sensory activation with short, frequent stimuli, reshaped synaptic transmission in the tectum, making it faster, because of selective potentiation of visual inputs from the eye.
+To better match and compare temporal properties of synaptic inputs to those of intrinsic tuning, we calculated average "synaptic current duration" for each cell as a temporal “center of mass” of currents within the first 700 ms after optic chiasm stimulation (see Methods).
+Neurons with different contribution of early and late synaptic responses naturally had different synaptic current duration: cells with strong monosynaptic inputs had shorter currents, while polysynaptic activity made synaptic currents longer (Figure 3C; p=2e-16, r=$-$0.78, n=168).
+The synaptic current duration was different across treatment groups (Figure 3D; F(5,163)=6.3, p=2e-5).
+Cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24, and 304$\pm$40 ms, respectively), indicating that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye.
 
@@
 To see whether intrinsic and synaptic temporal properties of tectal cells coordinated with each other, we compared intrinsic temporal tuning of every neuron (that is, whether it preferred longer or shorter simulated synaptic inputs in dynamic clamp experiments) to the actual duration of synaptic inputs it received during in-vitro stimulation of the optic chiasm.
-We found that on average, cells exposed to stronger sensory stimuli preferred shorter synaptic inputs, and also received shorter synaptic inputs, leading to a positive correlation between average synaptic and intrinsic properties for each group (Figure 3E; r=0.89, p=0.02, n=5).
-This means that \textit{between} treatment groups, changes in synaptic and intrinsic properties were adaptively coordinated, and the stronger was the average change in synaptic transmission, the more cells reshaped their intrinsic properties to adjust to this change.
+We found that, on average, cells exposed to stronger sensory stimuli preferred shorter synaptic inputs in dynamic clamp and also received shorter synaptic currents during optic chiasm stimulation, leading to a positive correlation between average synaptic and intrinsic properties for each group (Figure 3E; r=0.89, p=0.02, n=5).
+This means that \textit{between} treatment groups, changes in synaptic and intrinsic properties were adaptively coordinated, and the stronger the average change in synaptic transmission, the more cells reshaped their intrinsic properties to adjust to this change.
 
 In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
-We calculated differences between the properties of each individual cell and the average for the experimental group it belonged to, and showed these "deviations from respective averages" on one plot (Figure 3F).
+We calculated differences between the properties of each individual cell and the average for the experimental group to which it belonged, and showed these deviations from respective averages on one plot (Figure 3F).
 Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (adjusted r=$-$0.19, p=0.02, n=151).
-This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patters, and enhancing responses to unusual patterns of synaptic activation.
-
-%%% --- The paragraph below was commented out in prior submissions
+This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patters, and enhancing responses to unusual patterns of synaptic activation \citep{stemmler1999information}.
 
 Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.07, p=0.4, n=151).
-This is a textbook example of a so called "Simpsons paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.
+This is a textbook example of "Simpsons paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.
 
@@
 (\textbf{A}).
-Sample curves for a voltage step experiment; black bars show the areas used to average Na (bottom) and transient K (top) currents (see Methods).
+A set of curves from one voltage step experiment; black bars show the areas used to average Na (bottom) and transient K (top) currents (see Methods).
 (\textbf{B}).
@@
 (\textbf{C}).
-Sample data from a current clamp experiment; spikes are marked with black dots.
+Sample data from one current clamp experiment; spikes are marked with black dots.
 (\textbf{D}).
@@
 
-As our technical resources are rather limited, in this study we don't explicitly address the mechanisms of newly discovered intrinsic temporal tuning.
+As our technical resources were rather limited, in this study we don't explicitly address the mechanisms of newly discovered intrinsic temporal tuning.
 We can however offer two working hypotheses that may explain these results.
@@
 One obvious way of tuning ionic channel inactivation would be for every cell to modulate sodium or transient potassium currents via channel phosphorylation, or by changing the expression of different channel variants, to shift their inactivation dynamics \citep{frank2003nachannels,goldwyn2018a_current}.
-To test this hypothesis, one would need to induce changes in temporal tuning, similarly to how we did it in this paper, but then pharmacologically isolate different ionic currents, and then directly measure their inactivation dynamics.
+To test this hypothesis, one would need to induce changes in temporal tuning, similarly to how we did it in this paper, pharmacologically isolate different ionic currents, and directly measure their inactivation dynamics.
 
@@
 We hypothesize that this adjustment of temporal tuning is the reason why this tuning was so easily disrupted by strong visual stimulation, when for a few hours we drastically changed the statistics of inputs received by every cell.
-Tuning to "unusual stimuli" at the level of individual neurons fits into the narrative of information transfer maximization \citep{brenner2000} and network criticality \citep{rubinov2011}, wherein every element of a network tries to locally maximize its influence over the overall computation.
+Tuning to "unusual stimuli" at the level of individual neurons fits into the narrative of information transfer maximization \citep{stemmler1999information,brenner2000} and network criticality \citep{rubinov2011}, wherein every element of a network tries to locally maximize its influence over the overall computation.
 This may have intriguing consequences for the function and development of sensory networks in the brain, which can be further probed by computational modeling \citep{khakhalin2014,jang2016}, and verified in experiments.

### 2019-02-04 reviews and responses.md
tex & responses: minor edits

@@
 
-No, the order of injections was always the same; it is now decribed in the "Methods".
+No, the order of injections was always the same; it is now decribed in the "Methods": "Conductance curves were always presented in the order from the shortest to the longest, and this sequence was not randomized."
 
@@
 
-We did not quite understand the question, but generally, for this model, monosynaptic component peaks at about 5-20 ms, and is over by 50-100 ms, as described in the "Methods" section.
+We did not completely understand the question, but generally, for this model, monosynaptic component peaks at about 5-20 ms, and is over by 50-100 ms, as described in the "Methods" section.

### 2019-02-04 main.tex
tex & responses: minor edits

@@
 (\textbf{E}).
-A summary of data from (d), presented as averages and 95\% confidence intervals.}
+A summary of data from D, presented as averages and 95\% confidence intervals.}
 \end{figure*}
@@
 Compared to control neurons, cells exposed to sound had slightly lower amplitude tuning coefficients (flatter curve, Cohen’s d=$-$0.29), and more negative (curving down, d=$-$0.27) temporal tuning coefficients (Hotelling t-squared test p=0.2).
-When sounds were added to flashes, however, both transfer functions became less flat (d=0.65 and 0.26 for "Async" compared to “Flash”, for amplitude and temporal tuning respectively), and more like curves for control neurons (Hotteling test p=0.04).
+When sounds were added to flashes, however, both transfer functions became less flat (d=0.65 and 0.26 for "Async" compared to “Flash”, for amplitude and temporal tuning respectively), and more like curves for control neurons (Hotelling test p=0.04).
 Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Figure 2D), but negated the effect of visual stimulation when combined with it.
@@
 Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (adjusted r=$-$0.19, p=0.02, n=151).
-This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patters, and enhancing responses to unusual patterns of synaptic activation \citep{stemmler1999information}.
+This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patterns, and enhancing responses to unusual patterns of synaptic activation \citep{stemmler1999information}.
 
@@
 \includegraphics[width=3.2in]{fig4.pdf}
-\caption{Electrophysiological properties of individual neurons, compared to their spiking in current and dynamic clamp experiments.
+\caption{Electrophysiological properties of individual neurons compared to their spiking in current and dynamic clamp experiments.
 (\textbf{A}).
@@
 (\textbf{B}).
-Processing of ionic currents data, with IV-curves translated into two parameters (threshold potential and peak current) for each ionic conductance.
+Processing of ionic currents data with IV-curves translated into two parameters (threshold potential and peak current) for each ionic conductance.
 (\textbf{C}).
@@
 (\textbf{E}).
-The number of spikes registered in current clump mode: values predicted from a linear model, plotted against actually observed values.
+The number of spikes registered in current clamp mode: values predicted from a linear model plotted against observed values.
 The model works reasonably well (61\% of variance explained).
@@
 
-In all analyses presented above, we adjusted cell properties for rostro-caudal and media-lateral position of each cell within the tectum, as in tadpoles both intrinsic \citep{hamodi2014} and synaptic properties \citep{wu1996,khakhalin2012} are known to differ between older (rostro-medial) and younger (caudal, lateral) parts of the developing tectum.
+In all analyses presented above, we adjusted cell properties for rostro-caudal and medio-lateral position of each cell within the tectum, as in tadpoles both intrinsic \citep{hamodi2014} and synaptic properties \citep{wu1996,khakhalin2012} are known to differ between older (rostro-medial) and younger (caudal, lateral) parts of the developing tectum.
 In this study, most cell properties we measured correlated (p$<$0.05, after correction for treatment group differences) with either medial or rostral position within the tectum (medial: membrane capacitance r=$-$0.17, membrane resistance r=0.25, sodium current activation potential r=$-$0.30, stable potassium current r=$-$0.16, early synaptic amplitude r=$-$0.22, synaptic current duration r=0.29; rostral: peak sodium current r=0.18, late synaptic amplitude r=0.11; n between 168 and 183).
@@
 
-In this study we show that different sensory stimuli retuned neurons in the optic tectum of \textit{Xenopus} tadpoles in different ways, inducing changes in both their temporal tuning, and amplitude transfer functions.
+In this study we show that different sensory stimuli retuned neurons in the optic tectum of \textit{Xenopus} tadpoles in different ways, thereby inducing changes in both their temporal tuning and amplitude transfer functions.
 This addresses our first question about the functional scope of intrinsic plasticity in the optic tectum, and shows that it goes well beyond simple adjustments of neuronal spikiness.
 
-As our technical resources were rather limited, in this study we don't explicitly address the mechanisms of newly discovered intrinsic temporal tuning.
-We can however offer two working hypotheses that may explain these results.
-As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic currents inactivation in different cells.
+As our technical resources were rather limited, in this study we don't explicitly address the mechanisms of this newly discovered intrinsic temporal tuning.
+We can, however, offer two working hypotheses that may explain these results.
+As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic current inactivation in different cells.
 One obvious way of tuning ionic channel inactivation would be for every cell to modulate sodium or transient potassium currents via channel phosphorylation, or by changing the expression of different channel variants, to shift their inactivation dynamics \citep{frank2003nachannels,goldwyn2018a_current}.
-To test this hypothesis, one would need to induce changes in temporal tuning, similarly to how we did it in this paper, pharmacologically isolate different ionic currents, and directly measure their inactivation dynamics.
+To test this hypothesis, one would need to induce changes in temporal tuning similarly to how we did in this paper, pharmacologically isolate different ionic currents, and directly measure their inactivation dynamics.
 
 Another hypothetical mechanism that can underlie our current results is inspired by a yet unexplained finding from our earlier study \citep{ciarleglio2015}: namely, that one of the key electrophysiological parameters regulating excitability of tectal cells is cell membrane capacitance (Cm).
-Traditionally, cell capacitance is thought of as a relatively immutable parameter that describes cell morphology, and can even be used to estimate its size, yet in the tadpole tectum, we found it to drop both with age, and after strong sensory stimulation, even though cells don't seem to change their visual appearance (\citealt{ciarleglio2015}, Figure 7D).
-An intriguing possibility is that these changes in cell capacitance may be due to electiric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic arbor, soma, and axon initial segment \citep{bollmann2009,jarvis2018morphology}.
+Traditionally, cell capacitance is thought of as a relatively immutable parameter that describes cell morphology, and can even be used to estimate its size.
+Yet, in the tadpole tectum, we found it to drop both with age and after strong sensory stimulation, even though cells don't seem to change their visual appearance (\citealt{ciarleglio2015}, Figure 7D).
+An intriguing possibility is that these changes in cell capacitance may be due to electric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic tree, soma, and axon initial segment \citep{bollmann2009,jarvis2018morphology}.
 This differential uncoupling may be achieved through either minor changes in cell morphology \citep{leterrier2018axon}, or through target modulation of sodium and potassium channels at key points between the compartments, which would introduce shunting, and so strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.
@@
 
-In answer to our second question, about whether intrinsic and synaptic properties of tectal cells are in any way coordinated, here we show that intrinsic and synaptic temporal properties are co-tuned in the tectum, and moreover, that this co-tuning can be modified by sensory experience.
+In answer to our second question about whether intrinsic and synaptic properties of tectal cells are in any way coordinated, here we show that intrinsic and synaptic temporal properties are co-tuned in the tectum, and moreover, that this co-tuning can be modified by sensory experience.
 In contrast with earlier studies that report increased excitability post-stimulation \citep{aizenman2003,dong2009,ciarleglio2015}, we found that sensory stimulation led to a suppression of spiking.
@@
 
-Our study described an important difference between the dynamic clamp results (that were affected by stimulation, but could not be explained through low-level intrinsic parameters) and the results obtained in "classical" slow clamp experiments (that were not affected by stimulation, yet better coordinated with intrinsic parameters).
-This different may be interpreted in two ways.
+Our study described an important difference between dynamic clamp results (that were affected by stimulation, but could not be explained through low-level intrinsic parameters) and the results obtained in "classical" slow clamp experiments (that were not affected by stimulation, yet better coordinated with intrinsic parameters).
+This difference may be interpreted in two ways.
 One possible interpretation is to assume that dynamic clamp in the soma provided a bad approximation of peripheral synaptic inputs, as space clamp error is more pronounced for fast voltage fluctuations than for constant current injection \citep{spruston1993,prinz2004}.
-We however find this hypothesis unlikely, as dynamic clamp responses were consistently different in animals with different sensory history, which suggests that at the very least, we have captured some important aspects of intrinsic diversity, even if our estimations were biased.
+We find this hypothesis unlikely, however, as dynamic clamp responses were consistently different in animals with different sensory history, which suggests, at the very least, that we have captured some important aspects of intrinsic diversity, even if our estimations were biased.
 
@@
 In cells with excitable dendrites, channels of the axon initial segment may constitute only a small fraction of all voltage-gated channels, yet have a disproportionately large effect on the spiking output of the cell, and on its temporal tuning \citep{kole2007,hamada2016}.
-Furthermore, prolonged current injections in the soma are likely to quickly inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channels recovery during burst firing \citep{popovic2011,kole2012}.
-Converestly, this effect would still affect spiking in more realistic, fast dynamic clamp experiments.
+Furthermore, prolonged current injections in the soma are likely to quickly inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channel recovery during burst firing \citep{popovic2011,kole2012}.
+Conversely, this effect would still affect spiking in more realistic, fast dynamic clamp experiments.
 
@@
 As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014,jang2016}, a change in temporal tuning should affect collision detection dynamics, which can be verified experimentally.
-More specifically, we predict that visual stimulation that retunes neurons to faster stimuli (Flash) would make tadpoles selectively less responsive to slow collisions, and increase the latency of collision avoidance, due to non-linear dynamics of retinal activation for realistic looming stimuli that is slow in the beginning, and fast towards the end \citep{jang2016}.
+More specifically, we predict that a visual stimulation that retunes neurons to faster stimuli (Flash) would make tadpoles selectively less responsive to slow collisions, and increase the latency of collision avoidance due to non-linear dynamics of retinal activation for realistic looming stimuli that are slow in the beginning and fast towards the end \citep{jang2016}.
 These changes in intrinsic temporal tuning would also reshape the connectivity of tectal networks, as fast-inactivating cells would not support short recurrent loops within the network, thus promoting long-ranged polysynaptic connectivity \citep{fiete2010stdp,clopath2010stdp}.
@@
 
-% An internal comment: technically, Dong 2009 tested collision avoidance after visual stimulation, and got a somewhat opposite result: better avoidance of large dots (roughly equivalent to slow collisions), and worse avoidance to small dots (roughtly equivalent to fast collisions).
-But then, he used LED that we now know (Ciarleglio 2015) to have an opposite effect on intrinsic excitability, so it's hard to argue that Dong 2009 was a veryfication of our prediction.
-It is way too confusing.
+% An internal comment: technically, Dong 2009 tested collision avoidance after visual stimulation, and got a somewhat opposite result: better avoidance of large dots (roughly equivalent to slow collisions), and worse avoidance to small dots (roughly equivalent to fast collisions).
+But then, he used LED that we now know (Ciarleglio 2015) to have an opposite effect on intrinsic excitability, so I don't think Dong 2009 was really a verification of our prediction.
+Even though the experiments seem similar, there are too many unknowns to directly compare them.
 
@@
 Tuning to "unusual stimuli" at the level of individual neurons fits into the narrative of information transfer maximization \citep{stemmler1999information,brenner2000} and network criticality \citep{rubinov2011}, wherein every element of a network tries to locally maximize its influence over the overall computation.
-This may have intriguing consequences for the function and development of sensory networks in the brain, which can be further probed by computational modeling \citep{khakhalin2014,jang2016}, and verified in experiments.
+This may have intriguing consequences for the function and development of sensory networks in the brain, which can be further probed by computational modeling \citep{khakhalin2014,jang2016}, and verified experimentally.
 We also suspect that any cell with a sufficiently large dendritic tree would be able to tune its temporal intrinsic selectivity the way we describe.
@@
 
-% tectal oscillations were described both in post-metamorphic frogs \citep{baranauskas2012}, and in non-amphibian species \citep{sridharan2011,goddard2012,grossberg2016}.
+% tectal oscillations were described both in post-metamorphic frogs: \citep{baranauskas2012}, and in non-amphibian species \citep{sridharan2011,goddard2012,grossberg2016}.
 
@@
 
-We would like to thank Carlos Aizenman (Brown University), Justin Hulbert (Bard College), and Kara Pratt (University of Wyoming) for their feedback on this paper drafts.
+We would like to thank Carlos Aizenman (Brown University), Justin Hulbert (Bard College), and Kara Pratt (University of Wyoming) for their feedback on drafts of this paper.
 Part of this work was supported by the Bard Summer Research Institute (BSRI) program.
@@
 
-% All data reported in this study, as well as the code used for its analysis, is available from the corresponding author (A.S.Kh.) upon request.
-
 \subsection*{Housing and sensory conditioning}
@@
 
-In the beginning of each experiment, a tadpole was put in a Petri dish (diameter of 10 cm) filled with 1-1.2 cm of tadpole rearing medium, placed on top of a CRT monitor, with two speakers connected to the Petri dish with short wooden struts \citep{james2015,truszkowski2017}, and kept there for 4 hours.
+In the beginning of each experiment, a tadpole was put in a Petri dish (diameter of 10 cm) filled with 1-1.2 cm of tadpole rearing medium, placed on top of a CRT monitor with two speakers connected to the Petri dish with short wooden struts \citep{james2015,truszkowski2017}, and kept there for 4 hours.
 The tadpole was visually isolated from the rest of the room with a cardboard box surrounding the apparatus.
@@
 Signals were measured with an Axon Instruments MultiClamp 700B amplifier (Axon Instruments, Foster City, CA), filtered with a 5 kHz band-pass filter, and digitized at 10 kHz a CED Power1401-3 Digitizer (Cambridge Electronic Design; Cambridge, England).
-For synaptic stimulation, a bipolar stimulating electrode (Warner Instruments, Hamden, CT) was placed on the optic chiasm [Wu 1996]; stimuli were controlled by the CED digitizer, and were delivered by A.M.P.I.
+For synaptic stimulation, a bipolar stimulating electrode (Warner Instruments, Hamden, CT) was placed on the optic chiasm \citep{wu1996}; stimuli were controlled by a CED digitizer, and were delivered by A.M.P.I.
 stimulus isolator (AMPI, Jerusalem, Israel).
 
-Each neuron was subjected to a series of electrophysiological measurements protocols (see below for details), closely matching experimental protocols from \citep{ciarleglio2015}.
-For each cell, we measured membrane resistance Rm and capacitance Cm in voltage clamp mode, and then (1) ran a series of voltage steps to measure ionic currents; (2) in current clamp mode, ran a series of current steps to assess cell spiking; (3) in dynamic clamp mode, subjected the cell to different conductance injections; (4) finally, if the cell was still in a good health, ran a synaptic protocol with optic chiasm stimulation.
+Each neuron was subjected to a series of electrophysiological measurement protocols (see below for details), closely matching experimental protocols from \citep{ciarleglio2015}.
+For each cell, we measured membrane resistance Rm and capacitance Cm in voltage clamp mode, and then (1) ran a series of voltage steps to measure ionic currents; (2) in current clamp mode, ran a series of current steps to assess cell spiking; (3) in dynamic clamp mode, subjected the cell to different conductance injections; (4) finally, if the cell was still in good health, we ran a synaptic protocol with optic chiasm stimulation.
 All data was processed offline using custom Matlab scripts (Mathworks, Natick, MA), and analyzed in R.
 In total, we recorded from 188 neurons in 35 tadpoles; of these, 159 cells had readings from all 4 protocols, while 12 lacked synaptic recordings; these 12 cells were scattered across all 6 experimental groups.
-After the recording was over, the position of each recorded cell was visualized with a 10x microscope, marked on a screen, measured in medial and rostral directions, relative to the most lateral caudal point of the tectum, and converted into percentage \citep{hamodi2014}.
+After the recording was over, the position of each recorded cell was visualized with a 10x microscope, marked on a screen, measured in medial and rostral directions relative to the most latero-caudal point of the tectum, and converted into percentage \citep{hamodi2014}.
 
@@
 Each trial also contained a 50 ms long test pre-step of $-$10 mV relative to the baseline.
-During analysis, we averaged transition currents evoked by the leading and trailing edges of the pre-step, then scaled, and subtracted them from the current responses to the main step.
-For remaining active currents, we measured average currents during 0.4-2.7 ms after the step (Na current), 5.7-19.7 ms after the step (Kt, or transient potassium current), and 430-490 ms (Ks, or stable potassium current).
-This approach is standard for recordings from the Xenpus tectum, as ionic currents are slow enough to be separated temporally \citep{aizenman2003}.
+During analysis, we averaged transition currents evoked by the leading and trailing edges of the pre-step, then scaled and subtracted them from the current responses to the main step.
+For remaining active currents, we measured average currents during a 0.4-2.7 ms range after the step (Na current), 5.7-19.7 ms after the step (Kt, or transient potassium current), and 430-490 ms (Ks, or stable potassium current).
+This approach is standard for recordings from the \textit{Xenopus} tectum, as ionic currents are slow enough to be separated temporally \citep{aizenman2003}.
 The ionic conductances were quantified as is \citep{ciarleglio2015}.
@@
 \noindent for Ks current (a shifted piece of exponentially increasing curve with its lower part cut off; not inactivating).
-For equations with inactivation, we used its $I_{max}$ value at a measure of amplitude, and $v_a$ on the rising front such $I(v_a)=I_{max}/2$ as the threshold potential.
+For equations with inactivation, we used its $I_{max}$ value as a measure of amplitude, and $v_a$ on the rising front such that $I(v_a)=I_{max}/2$ calculated the threshold potential.
 For curves without inactivation (Ks) we used $I_{max}$ and the first non-zero point ($v_a=a+\log(e)\cdot b$) for the same purpose.
@@
 As a preliminary verification of our results, we compared the overall structure of our new dataset with the dataset from the 2015 study \citep{ciarleglio2015}.
-The eight cellular parameters described above showed similar pattern of coordination in both datasets: 23 pairwise correlations out of 35 total were significant (p$<$0.05) in this dataset, compared to 21 out of 35 in the 2015 study.
-The average absolute value of correlation coefficient was r=0.38 in this study, compared to r=0.32 in 2015 study.
+The eight cellular parameters described above showed a similar pattern of coordination in both datasets: 23 pairwise correlations out of 35 total were significant (p$<$0.05) in this dataset, compared to 21 out of 35 in the 2015 study.
+The average absolute value of correlation coefficient was r=0.38 in this study, compared to r=0.32 in the 2015 study.
 This suggests that the datasets are similar and representative of true internal variability in the tectum.
@@
 For the current steps protocol, we switched each cell to current clamp mode, and adjusted the stable holding current to bring the resting membrane potential to about $-$60 mV.
-We then subjected the cell to 10 current pulses 150 ms each, delivered every 1 s, with currents ranging from 0 to 180 pA, in 20 pA increments.
+We then subjected the cell to 10 current pulses, each 150 ms in duration, delivered every 1 s, such that currents ranged from 0 to 180 pA in 20 pA increments.
 Cells that did not produce at least one spike in this experiment were considered not-excitable, and were not included in the dataset.
@@
 
-For dynamic clamp experiments, each cell was held at $-$50 mV baseline potential, and was stimulated with 12 different “conductance injections”, each repeated 5 times.
+For dynamic clamp experiments, each cell was held at $-$50 mV baseline potential, and was stimulated with 5 repetitions of 12 different “conductance injections”.
 Conductance curves were generated with a formula $G=g\frac{t}{\tau}\exp(1-\frac{t}{\tau})$ , known as “alpha synapse”, where $g$ and $\tau$ are conductance and decay parameters respectively \citep{destexhe1994}.
-We used four different values of $\tau$, to represent four typical patterns of synaptic activation: 20 ms, corresponding to the total curve length (decay to 10\ of the peak value) of about 100 ms, to approximate short monosynaptic inputs \citep{ciarleglio2015}; 40 ms, corresponding to the total curve length of about 200 ms, as for a typical in-vitro stimulus with polysynaptic activation \citep{xu2011}; 100 ms, to mimic in-vivo inputs to the tectum in response to abrupt disappearance of light (“dark-flash”) \citep{khakhalin2014}; and 200 ms, to mimic retinal inputs in response to a 1 second-long linear looming stimulus \citep{khakhalin2014}.
+We used four different values of $\tau$, to represent four typical patterns of synaptic activation: 20 ms, corresponding to a total curve length (decay to 10\% of the peak value) of about 100 ms, to approximate short, monosynaptic inputs \citep{ciarleglio2015}; 40 ms, corresponding to a total curve length of about 200 ms, as for a typical in-vitro stimulus with polysynaptic activation \citep{xu2011}; 100 ms, to mimic in-vivo inputs to the tectum in response to abrupt disappearance of light (“dark-flash”) \citep{khakhalin2014}; and 200 ms, to mimic retinal inputs in response to a 1 second-long linear looming stimulus \citep{khakhalin2014}.
 Actual decay times to 10\% of peak amplitude were 98, 196, 489, and 978 ms respectively.
@@
 With the cell clamped at $-$50 mV, these conductances would have induced currents that peaked at 10, 25, and 50 pA respectively, matching the range of peak synaptic currents observed in \citep{xu2011,khakhalin2014,ciarleglio2015}.
+Conductance curves were always presented in the order from the shortest to the longest, and this sequence was not randomized.
 
-For each cell, for each of 60 trials, spikes were counted manually, blindly, and independently by both authors, using a custom Matlab data browser script.
+For each cell, for each of 60 trials (5 repetitions of 12 conductances), spikes were counted manually, blindly, and independently by both authors, using a custom Matlab data browser script.
 There was a 98.5\% agreement between spike number estimations on a trace-by-trace basis.
@@
 
-To quantify the “shape” of spiking responses to conductances of different duration (temporal tuning), for every cell we encoded curve duration as an ordinal value (from 1 to 4), fit the spike data as a function of response duration with a quadratic formula ($y = ax^2 + bx +c$), and used the quadratic coefficient $a$ as the measure of response non-linearity.
+To quantify the “shape” of spiking responses to conductances of different duration (temporal tuning), we encoded curve duration as an ordinal value (from 1 to 4) for every cell, fit the spike data as a function of response duration with a quadratic formula ($y = ax^2 + bx +c$), and used the quadratic coefficient $a$ as the measure of response non-linearity.
 While the units and absolute values of this coefficient are not interpretable, it captures the shape of the response curve well, and allows for easy comparisons between cells (Figure 2A).
@@
 
-For synaptic recordings, we switched cells back to voltage clamp mode, holding the membrane potential at $-$45 mV, to isolate excitatory synaptic currents.
-Optic chiasm shocks were delivered 10 times, every 20 s, with stimulation strength between 0.05 and 0.4 mA, and pulse length of 0.2 us.
-In each experiment, we would first find stimulation strength that evoked consistent synaptic responses in the cell we patched, then increased it by 20\%, and kept it constant for all cells recorded from this brain.
+For synaptic recordings, we switched cells back to voltage clamp mode, and held the membrane potential at $-$45 mV to isolate excitatory synaptic currents.
+Optic chiasm shocks were delivered 10 times, every 20 s, with a stimulation strength between 0.05 and 0.4 mA, and with a pulse length of 0.2 us.
+In each experiment, we would first find stimulation strength that evoked consistent synaptic responses in the first cell we patched, then increased it by 20\% and kept it constant for all cells recorded from that brain.
 Recordings were processed offline; for each trial we used the average current between 5 and 15 ms as a measure of monosynaptic response amplitude, and current between 15 and 145 ms as a measure of polysynaptic response amplitude \citep{ciarleglio2015}.
@@
 
-To analyze the numbers of spikes observed in dynamic clamp experiments (Figure 1), we first averaged the number of generated spikes across 5 protocol repetitions, for each cell, and for each combination of conductance curve duration and amplitude, which resulted in 12 values per cell.
+To analyze the numbers of spikes observed in dynamic clamp experiments (Figure 1), we first averaged the number of generated spikes for each combination of conductance curve duration and amplitude, 12 values for each of 5 protocol repetitions for every cell.
 Then we used sequential sum of squares analysis of variance with repeated measures.
-Both different conductance curve amplitudes and durations were represented as ordinal values (1 to 3 for amplitudes, 1 to 4 for durations).
+Both different conductance curve amplitudes and durations were represented as ordinal values (1 to 3 for amplitude, 1 to 4 for duration).
 Differences between experimental groups were assessed as interactions between these ordinal values and the factor variable encoding the experimental group, as we were interested in response shapes (reflected by interactions) rather than average values of spikiness (reflected by independent terms).
@@
 To verify the validity of this approach, we also ran a maximal likelihood mixed-effects model with type III interaction terms, as implemented in R package “lmer”, with “lmerTest” extension to get access to Satterthwaite degrees of freedom and p-value estimations \citep{kuznetsova2017}.
-The results of both methods were numerically very similar.
+The results of both methods were numerically similar, and supported same conclusions.
 
@@
 Position correction was based on a two-way linear regression model without interaction.
-For five variables that were distributed extremely non-normally, this correction for position was performed on transformed values (original values were transformed to normally distributed proxy values, linearly adjusted, and then transformed back): for early and late mean synaptic amplitudes we used a transformation $a'=log(1-a)$; for the variability of synaptic amplitudes $s'=log(1+s)$; for temporal tuning $y_t' = \sqrt{y_t}$ .
+For five variables that were distributed extremely non-normally, this correction for position was performed on transformed values (original values were transformed to normally distributed proxy values, linearly adjusted, and then transformed back): for early and late mean synaptic amplitudes we used a transformation $a'=log(1-a)$; for the variability of synaptic amplitudes $s'=log(1+s)$; and for temporal tuning $y_t' = \sqrt{y_t}$ .
 Where appropriate, we performed the analysis with and without extreme outliers, and reported the difference.
-All analyses presented in the paper were also verified in mixed model analyses, with animal id included as a random factor; the results of these mixed models analyses were similar to that of a fixed model, and are not reported.
+All analyses presented in the paper were also verified in mixed model analyses, with animal id included as a random factor; the results of these mixed model analyses were similar to that of a fixed model, and are not reported.
 

### 2019-02-04 reviews and responses.md
responses to reviewers, final edit

@@
 
-This is a collection of reviews and feedbacks, both official and unofficial, for different working copies of this paper.
-Reviews are split into paragraphs, and Author's responses and comments are shown after each paragraph.
-Reviews, and responses to these revivews, are given in reverese chronological order.
+This is a collection of peer-reviews for different working copies of this paper, and authors' responses to these pieces of feedbacks.
+Reviews are split into paragraphs, with  responses and comments given after each paragraph.
+Reviews are given in reverese chronological order.
 
@@
 We are grateful for the kind words, and agree with the assessment that our paper is largely phenomenological.
-Unfortunatelly, in a small teaching-oriented college, we simply cannot run most experiments needed to probe the mechanisms of intrinsic temporal tuning.
+Unfortunatelly, in a small teaching-oriented college, we simply cannot run most experiments needed to dissect the mechanisms of intrinsic temporal tuning.
 We cannot perform in-vivo experiments with sensory stimulation; and cannot measure or change gene expression in isolated tectal cells.
-Even a detailed electrophysiological study of isolated ionic currents would have taken extra 2-3 years, so we decided to publish this phenomenological report, in a hope that the very phenomenon we describe is interesting enough to be followed up by other labs, potentially in different models.
+Even a detailed electrophysiological study of isolated ionic currents would have taken extra 2-3 years, so we decided to publish this phenomenological report now, hoping that the very phenomenon we describe is interesting enough to be followed up by other labs, and potentially in different models.
 
@@
 The number of degrees of freedom in question comes from a full linear model, and does not mean that we treated different conditions as independent.
-Typically, to compare the numer of spikes in two conditions we used a 3-way ANCOVA (injection amplitude and duration as ordinal variables; group id as a nominal variable) with interactions, and repeated measures (where cell id included as a nominal variable).
+Typically, to compare the numer of spikes in two conditions we used a 4-way ANCOVA (injection amplitude and duration as ordinal variables; group id as a nominal variable) with interactions, and repeated measures (cell id was included as a nominal variable).
 For example, for a comparison of "Control" group to "Sound" group we used the following R code (see `dynamic_spikes_plot.R` for the full code):
@@
 
-We think that there exists a certain dichotomy here, but we agree that our description of it was not clear enough. We now replaced it with the following, longer exposition:
+We think that there exists a certain dichotomy here, but we agree that our description was not clear enough. We now replaced it with the following, longer exposition:
 
@@
 The overall excitability is homeostatic, as neurons became less excitable in response to stronger stimulation.
-The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively *more* responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a homeostatic retuning.
-We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation."
+The temporal retuning however can be better described as "adaptive", as neurons exposed to shorter stimuli (flashes) became relatively *more* responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a purely homeostatic retuning.
+We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation (Stemmler and Koch, 1999)."
 
@@
 
-We placed the decription of this effect at the very end of the paper, as we prefer to downplay it a bit, as it was described previously (Khakhalin 2012; Hamodi 2012; Ciarleglio 2015), and we don't want to distract the reader from our other findings.
-At the same time, we find it important to mention that we observed a strong correlation with position: first, because it provides an independent replication of previously observed patterns, and second, as the dependency of cellular properties on position necessitated an adjustment for position during analysis (see "Methods"), which needed to be justified.
-The implication for the principle of parameter degeneracy in development (Prinz 2004) is also interesting, and we wanted to point at it, even though within this paper we don't have enough material to fully explore this theme.
+We placed the decription of this effect at the very end of the paper to downplay it a bit, as some aspects of this effect were described previously (Khakhalin 2012; Hamodi 2012; Ciarleglio 2015), and also we don't want to distract the reader from our other findings.
+At the same time, it is important to mention that we observed a strong correlation with position: first, because it provides an independent replication of previously observed patterns, and second, as the dependency of cellular properties on position necessitated an adjustment for position during analysis (see "Methods"), and this analysis decision needed to be justified.
+The implication for the principle of parameter degeneracy in development (Prinz 2004) is also interesting, and we wanted to point at it, even though we don't have enough material in our paper to fully explore this theme.
 
@@
 
-We now added "we asked" to both sentences, which makes "we" a subject.
+Fixed.
 
@@
 
-We think that this word well reflects the nature of the property we are describing (the property of being easily excitable, and able to generate spikes), and we also think that we define it rather precisely within thiss paper.
-We prefer it to other alternatives, as they are rather too general ("intrinsic excitability") or too bulky ("ability to produce spikes in response to stimulation").
+We think that this word reflects the nature of the property we are describing rather well (the property of being easily excitable, and able to generate spikes), and we also define it within the paper itself.
+We prefer it to other alternatives, as they are either too general ("intrinsic excitability") or too bulky ("ability to produce spikes in response to stimulation").
 
-Of the two options offered by the reviewer, the first one ("Changes in f-I curve") is both too long, and does not reflect the nature of our measure, as with it we are trying to assess average ability to produce spikes, not a change of any sort.
-The second one sounds good and standard, but is actually somewhat misleading, as the term "Avereage firing rate" is defined rather precisely as the average rate at which a neuron fires in the network; usually either in the context of in-vivo recordings, or in-vitro spontaneous activity.
-Accordingly, a true "Average firing rate" for our neurons would depend both on their intrinsic properties (perhaps the measure we call "spikness here"), *and* the strength of their synaptic inputs, as well as their position within the network.
-In short, while "Average firing rate" is an important property, in this study we did not address it, nor had an opportunity to observe a proxy for it.
+Of the two options offered by the reviewer, the first one ("Changes in f-I curve") is quite long, and also does not reflect the nature of our measure, as with it we are trying to assess average ability to produce spikes, not a change of any sort.
+The second one sounds good and standard, but would actually be misleading in this particular case, as the term "Avereage firing rate" is defined as the average rate at which a neuron fires in the network; usually either in the context of in-vivo recordings, or in-vitro spontaneous activity.
+Accordingly, a true "Average firing rate" for our neurons would depend both on their intrinsic properties (the measure we call "spikness here"), *and* the strength of their synaptic inputs, as well as their position within the network (centrality measure).
+In short, while "Average firing rate" is an important property, we did not address it in this study, and had no opportunity to observe a proxy for it.
 
@@
 
-We like the word "spiky", as it captures the phenomelogical effect without making assuptions about underlying mechanisms. It is also intuitive and short, which aids understanding.
+We like the word "spiky" (see above), as it captures the phenomelogical effect without making assuptions about underlying mechanisms.
+It is also intuitive and short, which aids understanding.
+If the reviewers insist, we can of course replace it with another term, but with this resubmission we hope to give it another try.
 
@@
 
-We did in fact run a linear model with repeated measures that may be vaguely described as multi-variate ANOVA; see responses above.
+We did in fact run a multivariate linear model with repeated measures that may be described as multi-variate ANOVA; see responses above.
 
@@
 
-At this point we describe tuning as an empirical curve (something that can be plotted in a figure, and compared from cell to cell), but do not yet use any equations.
-Later in the text we parameterize these curves, and provide all related equations.
+At this point we describe tuning as the shape of an empirically observed curve (something that can be plotted, and compared from cell to cell), and do not yet use  equations to quantify it.
+Later in the text we parameterize these curves, to capture key differences between them, and provide all related equations.
 
@@
 
-We added a reference to (Fig 1D,E).
+We added a reference to Fig 1D,E.
 
@@
 
-We think that it rather reasonable that effects of going through some stimulation, compared to control, are stonger, than differences between different types of stimulation.
-We explore this question in detail further in the text.
+We think that it rather reasonable that effects of 4 hours of stimulation, compared to control, are stonger than differences between different types of stimulation.
+There are differences however, and we explore this question in detail further in the text.
 
@@
 See other comments above.
-Generally, unless a mixed model is used, the second value for degrees of freedom, defining F-distributions, is close to the total number of measurements recorded in a study, even if a multivariate analysis of variance is used, and even for nested non-independent designs, such as blocking or repeated measures analysis.
+Generally, unless a mixed model is used, the second value for degrees of freedom, defining F-distributions, is close to the total number of measurements recorded in a study, even if a multivariate analysis of variance is used, and even for nested and non-orthogonal designs, such as blocking or repeated measures analysis.
 For our study in particular, the only way to bring the second value for degrees of freedom down, making it closer to the number of cells, rather than to the number of measurements, would be to use a mixed model.
-We used a mixed model in our senstivity / verification test, and observed that it provided qualitatively similar results, as described in the method.
-We however reported a fixed model everywhere else, as it is more straightforward, and, in our opinion, more consistent.
+We used a mixed model (lmer) for a senstivity test, and observed that it provided qualitatively similar results, which is described in the method.
+Everywhere else we report the results from a fixed model, as it allows more straightforward interpretation, and, in our opinion, is more consistent with the experimental design.
 
@@
 1) As described above, we used a family of similar generalized linear models, followed by F-test for the analysis of variance, to compare across conditions.
-This type of analysis may be loosely referred to as ANOVA, although most textbooks would not recommend referring our models as an "ANOVA", as it included two ordinal variables, and a factor to account for repeated measures.
+This type of analysis may be loosely referred to as ANOVA, although it is our understanding that most textbooks would not recommend referring our model as an "ANOVA", as it included two ordinal variables, and a factor to account for repeated measures.
 
@@
 However, all of these comparisons were easily interpretable, as they form a logical progression of stimuli.
-These planned comparisons consistuted a small share of all possible post-hoc comparisons between groups that one could have run on this data (6 out of 30 possible pairs).
+These planned comparisons consistuted a small share of all possible post-hoc comparisons between groups that one could have run on this data (6 out of 15 possible pairs).
 Typically, for planned comparisons, researchers do not use an adjustment for multiple comparisons.
 
-3) Finally, in this paper we report exact numbers all p-values, instead of indicating whether they were above or below any arbitrary threshold.
+3) Finally, in this paper we report exact p-values, instead of indicating whether they were above or below any arbitrary threshold.
 This gives the reader the freedom to interpret our data against any significance threshold of their choice.
-As expected, some p-values were larger, and some were smaller, but we are confident that our overall conclusions are reasonable, expecially if comparing different pieces of evidence across the entire study.
+As expected, some p-values were larger, and some were smaller, but we are confident that our overall conclusions are reasonable, expecially if combining different pieces of evidence across the entire study.
 
-Together, this makes us reasonably confident that a Bonferroni correction would be unnecessarily punitive for this type of analysis.
+Together, this makes us confident that a Bonferroni correction would be unnecessarily punitive for this type of analysis.
 
@@
 We would really prefer to retain terms "amplitude tuning" and "temporal tuning", as they better represent the main message of our paper, as we are trying to think of these values not in terms of abstract properties each neuron has, but as parameters that can tune a neuron to a certain type of synaptic inputs, in terms of their temporal properties, and their amplitude.
-We however now included words "gain" and "adaptation index" in paragraphs that introduce values of amplitude and temporal tuning, respectively.
+We however now included the words "gain" and "adaptation index" in paragraphs that introduce values of amplitude and temporal tuning, respectively.
 
@@
 We wanted our readers to know that a comparison of these values can be interpreted very easily, while exact numbers (say, 0.82) do not carry that much narrative weight.
+As mentioned above, they however do not have units (are dimensionless).
 
@@
 
+Fixed.
+
 > Figure 2B and Figure 3A, 3D don't show any post-hoc comparisons among the groups. Which groups differ? I see it in the text but it is hard to take it home.
 
-We added asterisks to mark significance in figures.
+We added asterisks to mark significance compared to control. As not all pairwise comparisons make sense, we did not include brackets in the figure.
 
@@
 We now removed this paragraph.
-In response to this comment, we initially attempted a different analysis of the interaction between synaptic and intrinsic properties across groups, but while some reasonable types of comparisons were significant, this analysis lacks power, and relies too much on post-hoc reasoning, so we decided to follow the advice and just remove this paragraph entirely.
-While we still believe that stronger stimulation (in terms of its effect on average intrinsic properties) generally caused stronger disruption of the synaptic-intrinsic correlation, this statement is hard to fully justify with our current data.
+In response to this comment, we initially attempted a different analysis of the interaction between synaptic and intrinsic properties across groups, but while some reasonable types of comparisons were significant, this analysis lacks power with our sample sizes, and also relies too much on post-hoc reasoning, so we decided to follow the advice and just remove this paragraph entirely.
+While we still suspect that stronger stimulation (in terms of its effect on average intrinsic properties) generally caused stronger disruption of the synaptic-intrinsic correlation, this statement is hard to fully justify with our current data.
 
@@
 
-In the previous version of this paper we tried to show correlations of 2 types of spiking (those recorded in current and dynamic clamp modes) with Na conductance, to illustrate that one of the correlations is much stronger than the other.
-We agree however that showing the 8 parameter model fit is much better way of illustrating this point.
+In the originally submitted version of this paper, we tried to show correlations betwee two estimations of spikiness (average spiking recorded in current and dynamic clamp modes) with Na conductances, to illustrate that one of the correlations is much stronger than the other.
+We agree however that showing the 8 parameter model fit is a better way of illustrating this point.
 We now show two scatterplots, for both dynamic and current clamp data, in which values predicted by the 8-parameter model are compared to actual measurements.
@@
 Different fields have different criteria for what level of explanation is low enough to count as "mechanistic".
-Had we reliably predicted cell phenotypes (spiking) from their low-level electrophysiological properties, especially across treatment groups, we would have comfortably called it a mechanistic explanation.
-We show that for one type of measurements (current clamp), we have a tolerable level of mechanistic understanding of differences in observed cell excitability, while for more nuanced dynamic clamp experiments this mechanistic understanding is clearly lacking.
+We tried to predict cell spiking phenotypes, and responses to different simulated conductances, from their low-level electrophysiological properties.
+Had we succeeded in that, especially across treatment groups, we would have comfortably called it a mechanistic explanation.
+We show that for one type of measurements (current clamp), we have a tolerable level of mechanistic understanding of differences in observed cell excitability, while for more nuanced dynamic clamp experiments, we cound not predict neither average spiking, nor tuning parameters.
+In the figure 4, we mostly concentrate on average spiking, as it allows a visual comparison between the results obtained via two recording techniques.
 
@@
 
-We reworded the beginning of the discussion, to make sure that we re-state any questions before providing the answers.
+We reworded the beginning of the discussion, to make sure that we re-state all questions before providing the answers.
 
@@
 
-While preparing this paper, we actually also tried a different way to estimate synaptic durations: we attempted to fit all synaptic currents with the same curve that we used for simulated conductances in our dynamic clamp experiments `I = g*(t/tau)*exp(1-t/tau)`.
-While this idea seemed good in theory, in practice the synaptic curves were too variable in terms of their shape, decay, latency, and the amount of noise, making most curve fits were really bad, which made us go for a simpler, and a more parsimonuous measure.
+While preparing the original version of this paper, we also tried a different way to estimate synaptic durations: we attempted to fit all synaptic currents with the same curve that we used for simulated conductances in our dynamic clamp experiments `I = g*(t/tau)*exp(1-t/tau)`.
+While this idea seemed good in theory, as it would have offered an "ideal" comparison with the dynamic clamp data, in practice synaptic curves were too variable in terms of their shape, decay, latency, and the amount of noise, making most curve fits really bad.
+This made us go for a simpler, robust to noise, and parsimonuous measure.
 
@@
 It is natural for researchers to limit the complexity of their conceptual and computational models, and it is probably fair to say that as the number of neurons involved in a model increases, researchers often shift their attention from intrinsic mechanisms to connectomic approaches, approximating neural networks as a collection of nodes, linked with synapses of different strengths (e.g: Cline 2008; Kirby 2013).
-Even realistic biophysical models that represent neurons as multi compartment systems with active dendritic currents often don't assume that these active currents may be modulated in response to activation (Moldwin 2018).
-When machine learning approaches are used as a model for brain development, intrinsic excitability is reflected in these models, as a change in activation function of each artificial neuron (Marblestone 2016).
+Even realistic biophysical models that represent neurons as multi-compartment systems with active dendritic currents often don't assume that these active currents may be modulated in response to activation (Moldwin 2018).
+When machine learning approaches are used as a model for brain development, intrinsic excitability is reflected in these models as a change in activation function of each artificial neuron (Marblestone 2016).
 This type of modeling implicitly assumes, however, that outside of obviously oscillatory networks (spinal cord, thalamus, etc.), intrisic excitability in biological networks is largely confined to overall changes in neuronal "responsiveness".
@@
 We think that it is an interesting observation, that may have far-reaching effects on network computations, and network development.
-We also predict that similar effects of temporal tuning may be observed in other systems, such as mammalian cortex.
+We also suggest that similar effects of temporal tuning may be observed in other systems, such as mammalian cortex.
 
-In the new version of this manuscript, we added a few sentences to the introduction, trying to make our message more clear, and also more nuanced.
+In the new version of this manuscript, we expanded the introduction, trying to make our message more clear, and also more nuanced.
 

### 2019-02-04 main.tex
responses to reviewers, final edit

@@
 
-We then mapped the amplitude tuning of neurons (also known as amplitude transfer function, or gain), by looking at how an increase in transmembrane conductance translated into increased spike output.
+We then mapped the amplitude tuning of neurons (amplitude transfer function, or gain), by looking at how an increase in transmembrane conductance translated into increased spike output.
 Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (Fig 1D,E), and did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively).
@@
 The overall excitability is homeostatic, as neurons became less excitable in response to stronger stimulation.
-The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a fully homeostatic retuning.
+The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a purely homeostatic retuning.
 We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation \citep{stemmler1999information}.

### 2019-02-06 main.tex
tex: header moved to footer (for bioRxiv)

@@
 \usepackage{fancyhdr}
-\pagestyle{fancy}
-\rhead{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
-\cfoot{} % To kill footer page numbers
+\pagestyle{fancy} % Required
+
+% Option with a header:
+
+%\rhead{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
+%\cfoot{} % To kill footer page numbers
+
+% Or (for biorxiv) version with a footer:
+
+\rfoot{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
+\renewcommand{\headrulewidth}{0pt} % To remove top line
+\renewcommand{\footrulewidth}{1pt} % To add bottom line
+\fancyhead{} % Removes all headers
+\cfoot{} % Kills middle footer
 
@@
 The overall excitability is homeostatic, as neurons became less excitable in response to stronger stimulation.
-The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, which is opposite of what one would expect for a purely homeostatic retuning.
+The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, which is the opposite of what one would expect for a purely homeostatic retuning.
 We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation \citep{stemmler1999information}.
@@
 
-In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
+In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs in dynamic clamp tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
 We calculated differences between the properties of each individual cell and the average for the experimental group to which it belonged, and showed these deviations from respective averages on one plot (Figure 3F).
-Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic currents (adjusted r=$-$0.19, p=0.02, n=151).
+Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic inputs in dynamic clamp (adjusted r=$-$0.19, p=0.02, n=151).
 This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patterns, and enhancing responses to unusual patterns of synaptic activation  \citep{stemmler1999information}.
@@
 Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.07, p=0.4, n=151).
-This is a textbook example of "Simpsons paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.
+This is a textbook example of "Simpson's paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.
 
@@
 
-For the comparison or summative descriptions of tuning, and other electrophysiological cell parameters between experimental groups, we report p-values of fixed effect sequential sum of squares linear model (ancova), in which rostral and medial coordinates of each cell within the tectum are included as covariates, and experimental group is used as the main factor.
+For the comparison of summative descriptions of tuning, and other electrophysiological cell parameters between experimental groups, we report p-values of fixed effect sequential sum of squares linear model (ancova), in which rostral and medial coordinates of each cell within the tectum are included as covariates, and experimental group is used as the main factor.
 All comparisons and correlations between cell parameters are performed on values corrected for cell position within the tectum.
@@
 \nolinenumbers
+
+%\pagestyle{plain} % Kills all footers and headers
+
 \bibliographystyle{apalike} % For author-year

### 2019-02-06 main.tex
tex: refs

@@
 Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic inputs in dynamic clamp (adjusted r=$-$0.19, p=0.02, n=151).
-This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patterns, and enhancing responses to unusual patterns of synaptic activation  \citep{stemmler1999information}.
+This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patterns, and enhancing responses to unusual patterns of synaptic activation.
+% \citep{stemmler1999information}.
 

### 2019-04-12 reviews and responses.md
responses: summary reworded
Reviews from J Neurophysiol -> to reviews file

@@
 
-This is a collection of peer-reviews for different working copies of this paper, and authors' responses to these pieces of feedbacks.
+Here you can see peer-reviews for our paper, given in reverse chronological order, and our point-by-point responses to these reviews.
 Reviews are split into paragraphs, with  responses and comments given after each paragraph.
-Reviews are given in reverese chronological order.
+
+--------------------------
+
+# Reviews from J Neurophysiol, 2019 Mar 04 (revise and resubmit)
+
+We address the concerns of Reviewer 3 first, as they were more critical. Then we respond to the suggestions of Reviewer 2.
+
+## Reviewer 3
+
+> Busch and Khakhalin use the Xenopus tadpole tectal model to address the question of
+how neurons modify their intrinsic properties when an animal experiences different
+types of sensory input. Animals that underwent different forms of sensory experience
+had tectal neurons that decreased their overall excitability. This is consistent with the
+idea of homeostatic regulation of intrinsic properties. Surprisingly, when the sensory
+experience involved short pulses of light, neurons because more responsive to short
+inputs even though there was an overall decrease in spiking. This adds a layer of
+complexity to the idea of homeostatic control of a firing rate set point because it shows
+neurons can independently regulate total spiking in the opposite direction from their
+responses to synaptic inputs of different durations. This is a really interesting idea. The
+data are sound and well-analyzed (beautiful figures, open source data, etc.). However,
+from top to bottom, this manuscript was incredibly difficult to read. Due to organizational
+issues, lack of a strong rationale, and inconsistent/confusing wording, I’m not entirely
+sure I understand the main message the authors are trying to convey. My summary is
+largely based on what I was able to pick out of the figures. I strongly suggest the
+authors perform a massive rewrite and really emphasize the main points.
+
+### Major Comments
+
+> Abstract:
+
+> It’s hard to follow what was actually done and found in the paper based on the abstract.
+The abstract starts off with a statement about homeostatic regulation through changes
+in intrinsic properties and then gives a detailed account of what was found without any
+context. It would be easier to assimilate the information if the abstract follows a more
+standard format: start with the area the paper clearly contributes to, build the rationale
+for the study, state the hypothesis (or driving question), describe how this was tested
+and what was found, and say why it’s important.
+
+> Introduction:
+
+> I feel the same way about the introduction as I do the abstract; as written, it doesn’t give
+the reader a great sense of what’s to come. If the setup for the paper is that
+“connectivity isn’t everything— intrinsic properties matter,” this is a good start, but it
+could be made much clearer. Further, the questions of the study are not presented until
+the third paragraph, and there is no rationale for these questions. I suggest the authors
+completely revamp the introduction in way that guides the reader from
+regulation/plasticity of intrinsic properties (the big picture question) to why there’s a
+reason to think neurons in their system can tune their responsiveness to different kinds
+of inputs they receive (a specific hypothesis). This is what the authors actually address,
+but they really don’t provide much of a rationale for their specific experiments, which
+weakens the paper.
+
+> Results and Discussion:
+
+> - The rationale for the use of dynamic clamp and the parameters chosen are not clear.
+Is the dynamic clamp current injection protocol mimicking the physiological synaptic
+input? This should be stated.
+
+> - I think the experiment in this study is pretty straightforward, but the description of the
+results is not. As far as I can tell, tadpoles were exposed to different stimuli (flash,
+looming, multisensory, etc.). Then, tectal neurons were stimulated using either 1)
+dynamic clamp or 2) more physiologically through optic chiasm. This allowed the
+investigators to assess firing when they changed the stimulus intensity and stimulus
+duration of the dynamic clamp or the synaptic response to presynaptic stimulation.
+They then looked how the different types of sensory experience influenced firing
+responses. The rest is data analysis that looks at how the duration, amplitude, total
+spiking, and synaptic input is changed in different sensory contexts and sensory
+stimuli might interact. I think the text can be made much simpler so the basic design
+is easier to grasp. I suggest thinking about what the take home point is for each
+figure and craft the results section around those messages.
+
+> - There is also an inconsistent use terminology. For example, “spikiness” and
+“excitability” are sometimes used in attempt to describe distinct cell characteristics,
+but sometimes it seems like they are being used interchangeably. This makes
+interpreting the written results difficult to follow.
+
+> - “Compared to control, neurons from animals exposed to visual stimuli had a flatter
+amplitude tuning curve (Fig 1D,E).” What is the reader supposed to be looking at in
+the figure? Is this referring to larger conductances for a fixed duration? I think this is
+what the authors’ mean, but more intuitive descriptions that matches the figures or
+vice versa is needed to make the whole results section easier to digest.
+
+> - Excessive wordiness makes the results difficult to read and interpret. For example,
+on pg. 9, 4 paragraphs (411 words) are used to describe two graphs, each showing
+a different linear relationship (Fig. 3E-F). Why not simply say, “A positive relationship
+between temporal tuning and synaptic duration implies a co-tuning of these
+parameters.”
+
+> - In reference to the text at the bottom of page10: Is it possible to include a summary
+figure of data from the stepwise generalized linear model in Fig. 4? The purpose of
+this part of the study was to try and identify electrophysiological mechanism(s) that
+explain the tuning variables. The heart of Fig. 4 should be that they don’t, and figure
+that captures this would be helpful.
+
+> - If these data are interpreted as homeostatic (neurons became less excitable
+following sensory experience), is there any evidence that tectal neurons have
+different firing activities during the different kinds of sensory experience? For
+example, does sound engage tectal neurons less than visual stimuli, and might this
+explain some of the trends in the data?
+
+## Reviewer 2
+
+> Busch and Khakhalin use dynamic clamp to generate synaptic conductances of different durations and
+then measure the number of action potentials the neurons fire in response to the different
+conductances. Using this approach it is found that intrinsic excitability of tectal neurons is temporally
+tuned – meaning that they fire best in response to certain durations of synaptic input. This finding is
+interesting and unique because typically intrinsic excitability is quantified by generating “input-output”
+curves which only vary the amplitude of the synaptic drive, not the duration. Furthermore, the authors
+find that various visual stimuli lead to an “adaptive” – not homeostatic – type of temporal tuning of
+intrinsic properties such that neurons exposed to shorter stimuli became more responsive to shorter
+stimuli and less responsive to longer stimuli., and visa versa. In this study, the effects of visual and
+auditory conditioning (and combos thereof) on temporal tuning of both synaptic and intrinsic
+excitability are determined. Overall, this study makes great use of dynamic clamp. The interpretation of
+the results is limited because the ways in which the conditioning stimuli actually activate tectal neurons
+is not empirically established. Clarification, simplification, and consistent use of terms would improve
+this paper.
+
+### Minor
+
+> Page 5, line 45/46: “As one possible explanation, auditory and mechanosensory inputs may have
+different cellular or subcellular 46 targets in the tectum (Bollmann and Engert, 2009).”
+This Bollmann and Engert reference does not address mechanosensory and auditory inputs. This paper
+shows that the RGC inputs form a topographic map along the proximal-distal axis of individual tectal
+neuron dendrites. This reference should be replaced with an appropriate reference.
+Also, how can having different subcellular targets could explain the results? This concept needs to be
+clarified – an example would be helpful.
+
+> Page 13 line 46: The authors use the term “distributed sensory network” . Is a “distributed” network a
+special type of sensory network?
+
+> Page 3, line 26,27,28: “In the tadpole tectum, looming stimuli are known to elicit stronger responses
+compared to instantaneous inversions, yet the suppression yielded by looming stimuli was weaker”.
+The logic of this sentence is not clear. Why exactly would the authors not expect that the looming
+stimuli that is known to elicit stronger (synaptic?) responses would also cause less suppression (of action
+potentials?) than does flashes?
+
+### Major
+
+> Page 5, line 2,3,4 : But do the authors actually know how/if their conditioning stimuli is altering the
+pattern/strength of synaptic input? If so, this data should be shown. If not, it should be made clear that
+this is an assumption/ theoretical prediction.
+
+> Page 5, line 5: “As changes in intrinsic properties seemed homeostatic (increased activation led to
+reduced spiking), by the same logic, one could expect shorter stimuli (flashes) to selectively suppress
+responses (action potential firing or synaptic responses or both?) to shorter synaptic inputs”.
+What intrinsic properties were measured? It appears that only number of spikes was counted. The
+authors report that long-term increase in activation (by visual stimuli) decreased spiking – but was that
+due to a decrease in intrinsic excitability or because the stimuli decreased synaptic strengths – which in
+turn led to the observed decrease in number of spikes fired? This is critical to define.
+Second, do the authors mean to say that shorter stimuli would actually (somehow) suppress responses?
+How would that work?
+
+> Page 5 line 15: Does the word “preferred” (in quotes) mean that the cells fired more action potentials?
+Maybe refrain from personification.
+
+> Bottom of page 5, “Effects of acoustic and multisensory stimulation:
+
+> - Is the Auditory stim conditioning referred to as “click sounds” the same as the “startle-inducing
+sounds” that is mentioned in the very next sentence? If these are indeed the same stimulus it should
+be referred to by the same name, consistently. If they are not the same stimuli, the differences need to
+be explained.
+
+> - Tadpoles are exposed to 4 hours of click sounds and then intrinsic tuning was measured. No difference
+in spiking was observed. This was interpreted to mean that acoustic stimuli did “not strongly activate
+tectal circuits during conditioning”. How can the authors know this? Instead, why not determine this
+directly by recording click-evoked responses from tectal neurons? Or, if tectal cell responses to auditory
+stimuli have been described in previous work, this should be included here.
+
+> Page 6 line 24: Remove the phrase “are not easily interpretable”. Instead, please interpret your data
+clearly.
+
+> Page 9: The authors report that the synaptic data show that “prolonged sensory activation with short,
+frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective
+potentiation of visual inputs from the eye”.
+How do the authors know the effect is selective for RGC inputs? It appears that they only measured
+RGC-evoked responses. Auditory/mechanosensory -evoked responses were not reported.
+
+> Page 9 line 9: “cells exposed to stronger stimuli preferred shorter synaptic inputs in dynamic clamp…”
+Here, (where “preferred” is not in quotes) does “preferred” mean to fire more action potentials?
+
+> Page 10 (last paragraph): Were action potential thresholds measured? Were there any differences in
+this parameter across groups?
+
+> Page 10 line 8: The “correction for position” is difficult to understand here and in Methods. Why was a
+linear regression used – and how is it determined to generate an accurate “correction”? How do the
+data look without this correction?
+
+> Page 13, line 7: What does “intrinsic spikiness” mean? Is this another term for intrinsic excitability, or is
+this a different parameter? In fact, throughout the manuscript, there are many terms including “intrinsic
+excitability, spikiness, number of spikes, and intrinsic spikiness that probably mean the same thing – or
+maybe not. If these terms all mean the same thing, then one term should be chosen and used
+throughout. If they all refer to different entities, then each one should be clearly defined.
+
+> Page 15 line 34: The average membrane resistance (330 MOhm) seems a bit low for these small immature
+tectal neurons. Were the neurons healthy? What was the average resting membrane potential? Were
+there any set criteria for Rm, Vm, or access resistance?
+
+> Figure 1 D and E: The average number of spikes fired as a function of conductance duration and all at 3
+different peak conductances. Are there any trends at the single cell level? For example, if a given
+control neuron fires relatively few spikes in response to 500 ms duration, does it also tend to fire
+relatively fewer spikes with 1000ms duration? Or maybe if a given neuron fires a relatively high number
+of spikes with 500ms then it will typically fire less at 1000ms duration? Although the individual
+responses are shown in 1D, it is impossible to follow the number of spikes fired by any individual neuron
+in response to the different conductance durations.
+
+> Figure 4 D, E and F: Is “spikiness” synonymous with “N Spikes”? If these terms do not mean the same
+thing, they should be defined. If they do mean the same thing, then one term should be chosen and
+used consistently throughout.
+
+&nbsp;
+
+--------------------------
 
@@
 
+--------------------------
+
 # Reviews from eLife, 2018 Aug 17 (rejection letter)

### 2019-04-12 reviews and responses.md
text: abstract and intro, draft revision

@@
 
-We address the concerns of Reviewer 3 first, as they were more critical. Then we respond to the suggestions of Reviewer 2.
+We address the concerns of Reviewer 3 first, as they were more critical overall. Then we respond to the suggestions of Reviewer 2.
 
@@
 
+We rewrote the abstract, stressing the big question to which the paper contributes (principles of tuning and learning in biological neural networks), and the main message of the paper.
+We also made the account of our findings a bit less detailed.
+
 > Introduction:
@@
 weakens the paper.
+
+We tried to make the introduction more clear, and better organized, from the big problem, to specific questions.
+We moved the presentation of the questions for the study to the very beginning of the second paragraph, and provide a rationale for these questions in the first paragraph.
 
@@
 
-# Reviews from J Neurosci, 2018 Nov 01 (rejection letter)
+# Reviews from J Neurosci, 2018 Nov 01 (rejection)
 

### 2019-04-12 main.tex
text: abstract and intro, draft revision

@@
 
-%\rhead{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
-%\cfoot{} % To kill footer page numbers
+\rhead{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
+\cfoot{} % To kill footer page numbers
 
@@
 
-\rfoot{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
-\renewcommand{\headrulewidth}{0pt} % To remove top line
-\renewcommand{\footrulewidth}{1pt} % To add bottom line
-\fancyhead{} % Removes all headers
-\cfoot{} % Kills middle footer
+%\rfoot{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
+%\renewcommand{\headrulewidth}{0pt} % To remove top line
+%\renewcommand{\footrulewidth}{1pt} % To add bottom line
+%\fancyhead{} % Removes all headers
+%\cfoot{} % Kills middle footer
 
@@
 
-%\linenumbers % Comment this to suppress line numbers
+\linenumbers % Comment this to suppress line numbers
 
@@
 \section*{Abstract}
-% 150 words (149 as or Aug 07)
+% J Neurophysiol: up to 250 words
+% Currently: 184
 
-Homeostatic intrinsic plasticity is often described as an adjustment of neuronal excitability to maintain stable spiking output.
+For a biological neural network to be functional, its neurons need to be connected to each other with synapses of appropriate strength, but also each neuron needs to appropriately respond to its synaptic inputs.
+This second aspect of network tuning is maintained by intrinsic plasticity; yet it is often considered secondary to changes in connectivity, and mostly limited to adjustments of overall excitability of each neuron.
+Here we argue that individual neurons are also tuned to inputs of different temporal dynamics, and that they can routinely adjust this tuning to match the statistics of their synaptic activation.
+Using the dynamic clamp technique, we show that in the tectum of Xenopus tadpoles, neurons become selective for faster inputs in animals that were exposed to fast visual stimulation, but remain responsive to longer inputs in animals exposed to looming or multisensory stimulation.
+We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties of individual tectal cells.
+These results expand our understanding of plasticity in the brain, and suggest that there may exist a whole extra dimension of network tuning that was so far overlooked.
+
+%Old version: Homeostatic intrinsic plasticity is often described as an adjustment of neuronal excitability to maintain stable spiking output.
 Here we report that intrinsic plasticity in the tectum of Xenopus tadpoles also supports temporal tuning, wherein neurons independently adjust spiking responses to fast and slow patterns of synaptic activation.
@@
 
-\section*{Significance statement}
-% 119 words (limit 120)
-%TC:endignore
-With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, most researchers concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning.
+%\section*{Significance statement}
+%%%TC:endignore
+%With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, most researchers concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning.
 Here we show that in a sensory network in Xenopus tadpoles, different neurons are tuned, and respond stronger, to either short or long synaptic inputs.
@@
 This observation shows that even in networks that don't generate oscillations, neurons reshape their temporal selectivity, to optimize their impact on distributed calculations.
-%TC:ignore 
+%%%TC:ignore 
 \bigskip
@@
 It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network,reimann2017}.
-Biological neurons, however, are tuned in ways that go well beyond adjusting one “strength” value per synapse: cells within the same network often demonstrate variability of activation thresholds \citep{kole2012}, production of bursts \citep{popovic2011}, inactivation by strong inputs \citep{bianchi2012}, and more.
-This diversity of tuning relies on coordinated changes of many parameters across a complex, multivariate landscape \citep{oleary2013}, as neuronal phenotypes are shaped by sensory experiences, and adjusted by modulatory inputs \citep{evans2015}.
-The dysregulation of intrinsic plasticity affects network dynamics \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}.
-And yet, with the obvious exception of oscillatory networks \citep{marder2011,picton2018control}, for many brain areas it is still unclear whether variation of intrinsic phenotypes serves as a defining aspect of network topology and architecture, or whether it is just a consequence of transfer function normalization \citep{titley2017}.
+However, biological neurons also demonstrate complex and multifaceted intrinsic tuning  \citep{oleary2013,evans2015}, with cells within a single network having different activation thresholds \citep{kole2012}, bursting behaviors \citep{popovic2011}, and inactivation profiles \citep{bianchi2012}.
+Dysregulation of intrinsic plasticity affects the dynamics of networks  \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}.
+And yet, with the possible exception of oscillatory networks \citep{marder2011,picton2018control}, the logic of intrinsic plasticity, and its contribution to network tuning, remain unclear.
+We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but biophysically, they often also have the means to become tuned to different temporal patterns of activation \citep{jarvis2018morphology,ohtsuki2018bursting}.
+Do they rely on this type of tuning in practice?
 
-The optic tectum of the \textit{Xenopus} tadpole is an ideal model for exploring these questions: it is a highly malleable distributed network of about $10^4$ neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}.
-In development, tectal neurons acquire diverse intrinsic and synaptic phenotypes that are also shaped by sensory experiences \citep{xu2011,ciarleglio2015}.
-Circuits in the tectum can learn and reproduce the temporal dynamics of inputs to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which is more likely to involve intrinsic temporal tuning \citep{narayanan2008,beatty2014}.
-Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, and is one of the targets for intrinsic plasticity \citep{bianchi2012}.
+In this paper, we investigate whether exposure to sensory stimuli of different temporal dynamics would change intrinsic temporal tuning of sensory neurons in the optic tectum of \textit{Xenopus} tadpoles.
+Tadpole tectum is an ideal model for exploring this question: it is a highly malleable distributed network of about 10\textsuperscript{4} neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}.
+In development, tectal neurons acquire diverse phenotypes, that are then shaped by sensory experiences \citep{xu2011,ciarleglio2015}.
+Circuits in the tectum can learn and reproduce temporal patterns to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which would be easier to achieve through intrinsic temporal tuning \citep{narayanan2008,beatty2014}.
+Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, and is a known target for intrinsic plasticity mechanisms \citep{bianchi2012}.
 
-In this study, we asked two specific questions about the properties of intrinsic plasticity in tectal networks.
-First, we asked whether intrinsic plasticity is limited to changes in excitability, or whether it is more nuanced and can differentially adjust neuronal responsiveness to inputs with different dynamics.
-Second, we checked whether changes in intrinsic properties in the tectum are a homeostatic response to each cell's history of synaptic activation, or if they are independent of synaptic properties.
-In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and despite an extensive search, we did not detect signs of temporal tuning (ibid,  figures 2, 4).
-However, we propose that the standard current-clamp protocols used in previous studies \citep{pratt2007,hamodi2014} were not adequate to detect important changes in the function of voltage-gated channels (see Discussion).
+Specifically, we ask two questions about the properties of intrinsic plasticity in tectal networks.
+First, we check whether intrinsic plasticity is limited to changes in overall excitability, or whether it differentially retunes neuronal responses to faster and slower inputs.
+Second, we ask whether intrinsic tuning of tectal cells is coordinated with  the typical length of synaptic currents they receive, or whether two types of tuning are independent.
+In our previously published large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and observed no signs of temporal tuning (ibid,  figures 2, 4).
+We argue however, that the current clamp protocol used in previous studies was not adequate for the task (see Discussion for a rationale).
 
-Here we show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness and supports temporal selectivity that can be reshaped by sensory experience.
-Furthermore, we show that the tuning of intrinsic properties is coordinated with the duration of synaptic inputs received by each cell.
-These results rely on two methodological innovations.
-First, instead of using current injections, we employed the dynamic clamp technique, which allowed a more realistic simulation of synaptic conductances \citep{prinz2004}.
+Instead, here we rely on two methodological innovations.
+First, we use the dynamic clamp technique, that allows a more realistic simulation of synaptic conductances \citep{prinz2004}.
 Unlike more common voltage and current clamp techniques, in dynamic clamp the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time.
 Second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols and compared their effects on intrinsic tuning.
-The use of different sensory modalities also gave us insight into an unrelated, but equally intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at tectal network retuning in response to multisensory stimuli in freely behaving tadpoles.
+We show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness, and supports temporal selectivity, that is shaped by sensory experience, and is coordinated with the typical duration of synaptic inputs received by each cell.
+Moreover, the use of different sensory modalities for stimulation gave us an insight into an unrelated, but intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at tectal retuning in response to multisensory experience in freely behaving tadpoles.
 

### 2019-04-19 reviews and responses.md
Introduction: both text and responses

@@
 
-We tried to make the introduction more clear, and better organized, from the big problem, to specific questions.
-We moved the presentation of the questions for the study to the very beginning of the second paragraph, and provide a rationale for these questions in the first paragraph.
+We now made the introduction clearer, and better organized, going from the big problem, to specific questions.
+We moved the presentation of the questions for the study to the very beginning of the second paragraph, and provided a rationale for these questions in the first paragraph.
 
@@
 > - The rationale for the use of dynamic clamp and the parameters chosen are not clear.
-Is the dynamic clamp current injection protocol mimicking the physiological synaptic
+
+Previously a detailed justification for the use of dynamic clamp was only given in the Discussion; we now added it to the end of Introduction.
+
+> Is the dynamic clamp current injection protocol mimicking the physiological synaptic
 input? This should be stated.
+
+We added this statement to the sentence: "...counted spikes produced during dynamic clamp in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B), **mimicking synaptic conductances typically observed in tadpole brains (see Methods)**"
 
@@
 figure and craft the results section around those messages.
+
+Thank you; we tried to follow this advice in this revised version of the manuscript!
 
@@
 neuron dendrites. This reference should be replaced with an appropriate reference.
-Also, how can having different subcellular targets could explain the results? This concept needs to be
+
+We replaced this sentence with the following sentence: "This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular (Pratt and Aizenman, 2009; Felch et al., 2016) and subcellular (Hiramoto and Cline,2009) targets in the tectum, and thus can recruit tectal networks to a different extent.
+
+> Also, how can having different subcellular targets could explain the results? This concept needs to be
 clarified – an example would be helpful.
+
+TODO: add an explanation here that we addressed this issue in the next paragraph, when the effects of multisensory stimulation are discussed. Because those WERE suprising.
 
@@
 
+In the submitted document, these lines said:
+
+"We then examined whether different types of sensory activation would differentially reshape  
+temporal intrinsic tuning in tectal neurons. As changes in intrinsic properties seemed  
+homeostatic (increased activation led to reduced spiking), by the same logic, one could..."
+
+TODO: make clear that we are not talking about synaptic changes after the fact, but during the stimulation. And that we kind of know from Khakhalin 2014.
+
 > Page 5, line 5: “As changes in intrinsic properties seemed homeostatic (increased activation led to
@@
 How would that work?
+
+All our measurements of the number of spikes relied on the dynamic clamp experiments, that used simulated, and not real synaptic inputs.
+It means that any changes in spiking we observed in the previous section of the results is necessarily coming from the change in intrinsic properties.
+While a change in the synaptic strength in response to sensory stimulation is possible, and indeed is investigated below in this paper, it would not have affected the number of spikes we reported in figures 1 and 2, as they were entirely recorded in dynamic clamp experiments.
+
+To make this clearer to the reader, we TODO!
 

### 2019-04-19 main.tex
Introduction: both text and responses

@@
 % J Neurophysiol: up to 250 words
-% Currently: 184
+% Currently: ?
 
-For a biological neural network to be functional, its neurons need to be connected to each other with synapses of appropriate strength, but also each neuron needs to appropriately respond to its synaptic inputs.
+For a biological neural network to be functional, its neurons need to be connected to each other with synapses of appropriate strength, and each neuron needs to appropriately respond to its synaptic inputs.
 This second aspect of network tuning is maintained by intrinsic plasticity; yet it is often considered secondary to changes in connectivity, and mostly limited to adjustments of overall excitability of each neuron.
-Here we argue that individual neurons are also tuned to inputs of different temporal dynamics, and that they can routinely adjust this tuning to match the statistics of their synaptic activation.
-Using the dynamic clamp technique, we show that in the tectum of Xenopus tadpoles, neurons become selective for faster inputs in animals that were exposed to fast visual stimulation, but remain responsive to longer inputs in animals exposed to looming or multisensory stimulation.
+Here we argue that individual neurons can also be tuned to inputs of different temporal dynamics, and that they can routinely adjust this tuning to match the statistics of their synaptic activation.
+Using the dynamic clamp technique, we show that in the tectum of Xenopus tadpoles, neurons become selective for faster inputs when animals are exposed to fast visual stimuli, but remain responsive to longer inputs in animals exposed to slower, looming or multisensory stimulation.
 We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties of individual tectal cells.
@@
 
-%\section*{Significance statement}
-%%%TC:endignore
-%With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, most researchers concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning.
-Here we show that in a sensory network in Xenopus tadpoles, different neurons are tuned, and respond stronger, to either short or long synaptic inputs.
-This tuning tended to be opposite to the actual dynamics of synaptic inputs each cell received, such that neurons that normally receive shorter inputs generated stronger spiking in response to longer testing currents, and the other way around.
-This observation shows that even in networks that don't generate oscillations, neurons reshape their temporal selectivity, to optimize their impact on distributed calculations.
-%%%TC:ignore 
 \bigskip
@@
 Dysregulation of intrinsic plasticity affects the dynamics of networks  \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}.
-And yet, with the possible exception of oscillatory networks \citep{marder2011,picton2018control}, the logic of intrinsic plasticity, and its contribution to network tuning, remain unclear.
-We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but biophysically, they often also have the means to become tuned to different temporal patterns of activation \citep{jarvis2018morphology,ohtsuki2018bursting}.
+And yet, with the possible exception of oscillatory networks \citep{marder2011,picton2018control}, the exact ways in which intrinsic plasticity contributes to network tuning, remain unclear.
+We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but we also know that biophysically, they often have the means to become tuned to different temporal patterns of activation \citep{branco2010dendritic,jarvis2018morphology,ohtsuki2018bursting}.
 Do they rely on this type of tuning in practice?
 
-In this paper, we investigate whether exposure to sensory stimuli of different temporal dynamics would change intrinsic temporal tuning of sensory neurons in the optic tectum of \textit{Xenopus} tadpoles.
+In this paper, we investigate whether exposure to sensory stimuli with different temporal dynamics would change intrinsic temporal tuning of sensory neurons in the optic tectum of \textit{Xenopus} tadpoles.
 Tadpole tectum is an ideal model for exploring this question: it is a highly malleable distributed network of about 10\textsuperscript{4} neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}.
 In development, tectal neurons acquire diverse phenotypes, that are then shaped by sensory experiences \citep{xu2011,ciarleglio2015}.
-Circuits in the tectum can learn and reproduce temporal patterns to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which would be easier to achieve through intrinsic temporal tuning \citep{narayanan2008,beatty2014}.
+Circuits in the tectum can learn and reproduce temporal patterns to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which may be easier to achieve through intrinsic temporal tuning \citep{narayanan2008,beatty2014}.
 Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, and is a known target for intrinsic plasticity mechanisms \citep{bianchi2012}.
@@
 Specifically, we ask two questions about the properties of intrinsic plasticity in tectal networks.
-First, we check whether intrinsic plasticity is limited to changes in overall excitability, or whether it differentially retunes neuronal responses to faster and slower inputs.
-Second, we ask whether intrinsic tuning of tectal cells is coordinated with  the typical length of synaptic currents they receive, or whether two types of tuning are independent.
+First, we check whether intrinsic plasticity in response to sensory stimulation is limited to changes in overall excitability, or whether it also retunes neuronal sensitivity to faster and slower inputs.
+Second, we ask whether intrinsic temporal tuning of tectal cells is coordinated with the typical length of synaptic currents they receive, or whether two types of tuning are independent.
 In our previously published large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and observed no signs of temporal tuning (ibid,  figures 2, 4).
-We argue however, that the current clamp protocol used in previous studies was not adequate for the task (see Discussion for a rationale).
+We argue however, that the current clamp protocol used in earlier studies was not adequate for the task, so in this paper we relied on a dynamic clamp technique.
 
-Instead, here we rely on two methodological innovations.
-First, we use the dynamic clamp technique, that allows a more realistic simulation of synaptic conductances \citep{prinz2004}.
-Unlike more common voltage and current clamp techniques, in dynamic clamp the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time.
-Second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols and compared their effects on intrinsic tuning.
-We show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness, and supports temporal selectivity, that is shaped by sensory experience, and is coordinated with the typical duration of synaptic inputs received by each cell.
+The main benefit of the dynamic clamp approach, compared to commonly used current step injections, is that it allows a more realistic simulation neuronal response to synaptic conductances \citep{prinz2004}.
+In dynamic clamp, the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time.
+This means that with dynamic clamp recordings we can excite a neuron in a controlled manner, but still allow both its voltage and transmembrane current to change, preserving feedback interactions between active currents and transient voltage-gated channels inactivation \citep{ma1996dynamic}, which may be an important mechanism for intrinsic temporal tuning \citep{platkiewicz2011}.
+Also, as a second methodological innovation, instead of relying on one type of sensory stimulation, here we used five different stimulation protocols, and compared their effects on intrinsic tuning.
+
+We show that the intrinsic plasticity of tectal neurons supports temporal selectivity, which is shaped by sensory experience, and is coordinated with the typical duration of synaptic inputs received by each cell.
 Moreover, the use of different sensory modalities for stimulation gave us an insight into an unrelated, but intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at tectal retuning in response to multisensory experience in freely behaving tadpoles.
@@
 
-After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Figure 1A), and counted spikes produced during dynamic clamp in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B).
+After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Figure 1A), and counted spikes produced during dynamic clamp in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B), mimicking synaptic conductances typically observed in tadpole brains (see Methods).
 We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see Methods).
@@
 While the optic tectum (homologous to superior colliculus in mammals) is often described as a primarily visual area, it is also involved in heavy multisensory computations \citep{stein2014}.
-In tadpoles, it integrates visual information with inputs from mechanosensory, auditory, and lateral line modalities \citep{deeg2009,pratt2009,hiramoto2009,felch2016,truszkowski2017}, but the logic of this integration is still unclear.
+In tadpoles, it integrates visual information with inputs from mechanosensory, auditory, and lateral line modalities \citep{deeg2009,pratt2009trigeminal,hiramoto2009,felch2016,truszkowski2017}, but the logic of this integration is still unclear.
 We wondered whether acoustic stimuli would reshape intrinsic properties of tectal neurons, and whether this retuning would be similar to that produced by visual stimuli.
@@
 This suggests that acoustic stimuli did not strongly activate tectal circuits during conditioning, despite being more behaviorally salient (for our stimuli, at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}).
-As one possible explanation, auditory and mechanosensory inputs may have different cellular or subcellular targets in the tectum \citep{bollmann2009}, or they may differentially recruit tectal inhibitory circuits \citep{liu2016,hamodi2016}.
+This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular \citep{pratt2009trigeminal,felch2016} and subcellular \citep{hiramoto2009} targets in the tectum, and thus can recruit tectal networks to a different extent.
 
@@
 We found (Fig 1D, E) that, after four hours of multisensory stimulation, tectal neurons were more excitable than after visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for sync and async respectively, across all testing conditions).
-Compared to the “Flash” group, the tuning curves in multisensory groups were less flat, with a stronger effect in the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively).
+However, compared to the “Flash” group, the tuning curves in multisensory groups were less flat, with a stronger effect in the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively).
 This suggests that on their own sound clicks had little effect on tectal excitability, but when added to visual flashes, sound clicks negated effects of retuning that visual stimulation would have had (Fig 2C).
+
+% Make this paragraph above more clear, lead the reader throught the tension.
+Also, add an interpretation below, and there say that it's either inhibition, or changes at the level of individual dendritic trees.
+Make it clear that this result WAS surprising.
+And if it's dendritic processing, then explain how it may help.
+
+% Here we may reference Bollmann 2009 back, to show that dendritic processing probably does happen here.
+
+% Citations that may be used, when talking about inhibition: and may also differentially recruit tectal inhibitory circuits \citep{liu2016,hamodi2016}.
+
+% Also reference Deeg with her independent intrinsic tuning (in the same neuron!) to visual and mechanosensory inputs (does it suggest a dendritic tree?)
 
@@
 
-Alternatively, and in our opinion more likely, intrinsic excitability of tectal cells is affected by properties that are not easily accessible by standard slow voltage and current clamp protocols, such as axon initial segment relocation, or targeted modulation of axonal voltage-gated channels we described above \citep{grubb2010activity,kole2012}.
+It seems more reasonable however, that intrinsic excitability of tectal cells is shaped by mechanisms that are not easily accessible by standard slow voltage and current clamp protocols, such as axon initial segment relocation, or targeted modulation of axonal voltage-gated channels we described above \citep{grubb2010activity,kole2012}.
 In cells with excitable dendrites, channels of the axon initial segment may constitute only a small fraction of all voltage-gated channels, yet have a disproportionately large effect on the spiking output of the cell, and on its temporal tuning \citep{kole2007,hamada2016}.
@@
 Recordings were restricted to the middle of the tectum, as in earlier studies \citep{ciarleglio2015}, from 25\% to 53\% of brain half-width medially from the lateral edge, and from 36\% to 69\% of tectum length rostrally from the caudal edge of the tectum (Figure 1A).
-Care was taken to record only from “deep” primary tectal cells (that are located superficially in our preparation), and not from MV cells \citep{pratt2009} or superficial layer cells (that are located deep in the tectum in our preparation) \citep{liu2016}.
+Care was taken to record only from “deep” primary tectal cells (that are located superficially in our preparation), and not from MV cells \citep{pratt2009trigeminal} or superficial layer cells (that are located deep in the tectum in our preparation) \citep{liu2016}.
 Glass electrodes (1.5x0.86 mm borosilicate glass; Sutter instruments, Novato, CA) were pulled on a Sutter P-1000 puller (Sutter instruments), to a tip resistance of 8-12 MOhm.

### 2019-04-19 reviews and responses.md
Methods: around figure 3

@@
 
-We added this statement to the sentence: "...counted spikes produced during dynamic clamp in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B), **mimicking synaptic conductances typically observed in tadpole brains (see Methods)**"
+We updated the next sentence, by adding a reference to it: "We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits in vivo (Xu et al.
+2011; Khakhalin et al.
+2014; Ciarleglio et al.
+2015; see Methods)."
 
@@
 
+In this updated version, we consistently use "spikiness" as a name for the variable, for the first time introduced in Figure 2C.
+For earlier results section, we replaced "spikiness" with "average number of spikes", and in all instances when we talked about the general idea of neuronal excitability, we called it neuronal excitability.
+As the only exception to this rule, we opted for the word "spikness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
+
 > - “Compared to control, neurons from animals exposed to visual stimuli had a flatter
@@
 
+This refers to smaller (flat, not increasing) spiking output as a function of conductance duration. To make it clear, we improved the sentence:
+
+"Compared to control, neurons from animals exposed to visual stimuli had a flatter **(constant or hill-shaped, rather than increasing)** amplitude tuning curve (Fig 1D,E), **as they** did not increase their spiking as fast in response to larger conductances..."
+
 > - Excessive wordiness makes the results difficult to read and interpret. For example,
@@
 a different linear relationship (Fig. 3E-F). Why not simply say, “A positive relationship
-between temporal tuning and synaptic duration implies a co-tuning of these
+between temporal tuning and synaptic duration implies a co-tuning of preferr
 parameters.”
+
+Of these four paragraphs, the last one reports a negative result that is not shown in Figure 3.
+The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot replace them with one sentence, as the statement we are making is not that obvious statistically.
+We believe that an attempt to gloss it over by pushing the statistical analysis to the methods section would not be fair.
+
+The issue, as we describe in the text, is that while graphs 3E and 3F have very similar axes, and both show a linear dependency, they have opposite slopes.
+Had the slopes be the same, we would have just reported a correlation, in one sentence.
+But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative.
+
+We indeed received some conflicting advice in the past about the level of detail necessary to communicate this message: for example, people who have studied Simpson's paradox in their statistics classes had found our use of this term very helpful, while people who haven't heard it before, found it distracting.
+For now, we opted to include it, but we are aware that what makes the text more relatable to one group of researchers may make it less transparent for other groups.
+
+Nevertheless, in current version of the paper, we shortened this section from 411 to 294 words.
 
@@
 Maybe refrain from personification.
+
+We hope that the word "prefer" is intuitive enough to most readers; it is also way shorter than "responded with more spikes", or "produced more action potentials", which allows for easier writing.
+We also believe that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are usually a bit more relaxed when talking about cells, channels, receptors etc.
+
+Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is just our normal word use (we use this word 6 times in the paper), and not an allegory.
 

### 2019-04-19 main.tex
Methods: around figure 3

@@
 
-Our first question was whether our stimulation protocols caused changes in intrinsic excitability of tectal neurons.
+First we asked whether our stimulation protocols caused any changes in intrinsic excitability of tectal neurons.
 From previous studies, we knew that in tadpoles exposed to four hours of LED flashes, tectal neurons became more excitable \citep{aizenman2003,ciarleglio2015}.
 However, the stimuli we used in the present study were weaker, and similar to those used in behavioral experiments \citep{khakhalin2014,james2015,truszkowski2017}.
-We presented a checkerboard pattern that inverted once a second either instantaneously (Figure 1C left, dubbed “Flash”), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares; Figure 1C right; dubbed “Looming”; see Methods).
+We presented a checkerboard pattern that inverted once a second either instantaneously (dubbed “Flash”; Figure 1C left), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares, dubbed “Looming”; Figure 1C right).
 
@@
 
-After conditioning, we excised the brain, obtained whole cell patch clamp recordings from neurons in the tectum (Figure 1A), and counted spikes produced during dynamic clamp in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B), mimicking synaptic conductances typically observed in tadpole brains (see Methods).
-We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (see Methods).
-Contrary to our expectations, in tadpoles that were exposed to instantaneous checkerboard inversions (flashes), tectal neurons on average became not more, but less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29.
-Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell id is used as a repeated measures factor; see Methods for a detailed description).
-Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25), which was likewise unexpected.
-In the tadpole tectum, looming stimuli are known to elicit stronger responses compared to instantaneous inversions \citep{khakhalin2014}, yet the suppression yielded by looming stimuli was weaker.
+After conditioning, we excised the brain, performed whole cell patch clamp on tectal neurons (Figure 1A), and counted spikes produced in dynamic clamp mode in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B).
+We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (\citealt{xu2011,khakhalin2014,ciarleglio2015}; see Methods).
+Based on prior research, we expected neurons exposed to flashes (checkerboard inversions) to be more excitable, but contrary to our expectations, they were on average less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29).
+(Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell id is used as a repeated measures factor; see Methods for a detailed description).
+Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25).
+This was likewise unexpected, as in the tadpole tectum, looming stimuli are known to elicit stronger responses compared to instantaneous inversions \citep{khakhalin2014}, yet the effect yielded by looming stimuli was weaker.
+To sum up, both the expected sign of the effect, and the relative
 
 We then mapped the amplitude tuning of neurons (amplitude transfer function, or gain), by looking at how an increase in transmembrane conductance translated into increased spike output.
-Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (Fig 1D,E), and did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively).
+Compared to control, neurons from animals exposed to visual stimuli had a flatter (constant or hill-shaped, rather than increasing) amplitude tuning curve (Fig 1D,E), as they did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively).
 The flattening of response curves seemed slightly more pronounced for flashes than for looming, but this difference was not significant (F(1,641)=3.5; p=0.06).
@@
 In control neurons, longer inputs typically evoked stronger spiking, whereas neurons from stimulated animals had flatter tuning curves, with a plateau, or even a decrease in spike number for longer conductance injections (Figure 1E).
-In essence, while control neurons “preferred” longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
+In essence, while control neurons preferred longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
 This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, follow two different kinds of logic.
@@
 To test this question, we exposed tadpoles to four hours of behaviorally salient “click” sounds \citep{james2015,truszkowski2017}, provided at the same frequency (every second) as visual stimuli in the first set of experiments.
-We found (Fig 1D, E) that exposure to startle-inducing sounds (group “Sound”) did not lead to significant changes in either average spikiness (0.8$\pm$0.7 spikes; F(1,689)=1.7; p=0.2; n=28, 30), amplitude transfer function (F(1,689)=2.0; p=0.2), or temporal tuning curve (F(1,689)=2.0; p=0.2).
+We found (Fig 1D, E) that exposure to startle-inducing sounds (group “Sound”) did not lead to significant changes in either average number of spikes (0.8$\pm$0.7 spikes; F(1,689)=1.7; p=0.2; n=28, 30), amplitude transfer function (F(1,689)=2.0; p=0.2), or temporal tuning curve (F(1,689)=2.0; p=0.2).
 This suggests that acoustic stimuli did not strongly activate tectal circuits during conditioning, despite being more behaviorally salient (for our stimuli, at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}).
@@
 
-To see whether intrinsic and synaptic temporal properties of tectal cells coordinated with each other, we compared intrinsic temporal tuning of every neuron (that is, whether it preferred longer or shorter simulated synaptic inputs in dynamic clamp experiments) to the actual duration of synaptic inputs it received during in-vitro stimulation of the optic chiasm.
-We found that, on average, cells exposed to stronger sensory stimuli preferred shorter synaptic inputs in dynamic clamp and also received shorter synaptic currents during optic chiasm stimulation, leading to a positive correlation between average synaptic and intrinsic properties for each group (Figure 3E; r=0.89, p=0.02, n=5).
-This means that \textit{between} treatment groups, changes in synaptic and intrinsic properties were adaptively coordinated, and the stronger the average change in synaptic transmission, the more cells reshaped their intrinsic properties to adjust to this change.
+To see whether intrinsic and synaptic temporal properties of tectal cells coordinated with each other, we compared intrinsic temporal tuning of every neuron (that is, whether it preferred longer or shorter simulated synaptic inputs in dynamic clamp experiments) to the actual duration of synaptic inputs it received, assessed by optic chiasm stimulation.
+We found that, \textit{on average}, in animals exposed to stronger sensory stimuli, neurons were more responsive to shorter synaptic inputs, and also received shorter synaptic currents, leading to a positive correlation between these values across experimental groups (Figure 3E; r=0.89, p=0.02, n=5).
+%This means that \textit{between} treatment groups, changes in synaptic and intrinsic properties were adaptively coordinated, and the stronger the average change in synaptic transmission, the more cells reshaped their intrinsic properties to adjust to this change.
 
-In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs in dynamic clamp tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
-We calculated differences between the properties of each individual cell and the average for the experimental group to which it belonged, and showed these deviations from respective averages on one plot (Figure 3F).
-Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic inputs in dynamic clamp (adjusted r=$-$0.19, p=0.02, n=151).
-This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patterns, and enhancing responses to unusual patterns of synaptic activation.
-% \citep{stemmler1999information}.
+In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs in dynamic clamp tended to receive longer actual synaptic currents, and vice versa (F(1,145)=4.9, p=0.03).
+The deviations of neuronal properties from their respective group averages are shown in Figure 3F.
+Cells that received shorter synaptic currents, compared to other cells, tended to be more responsive to longer synaptic inputs (adjusted r=$-$0.19, p=0.02, n=151).
+This suggests that during normal brain development, individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, enhancing responses to unusual patterns of synaptic activation.
+It also means that the correlation of intrinsic and synaptic properties had opposite signs between-groups (Figure 3E; positive) and within-groups (Figure 3F; negative), which is a textbook case of a so-called "Simpson's paradox" in data analysis.
 
-Note that the correlation of intrinsic and synaptic properties had opposite signs between-groups (positive) and within-groups (negative), so if we lumped all cells from all groups together, we would have found no correlation between these two variables (r=$-$0.07, p=0.4, n=151).
-This is a textbook example of "Simpson's paradox", wherein a pattern holds within subgroups, but disappears or is reversed on a full set because of pronounced differences between groups.
+% \citep{stemmler1999information}
+
+% , so if all cells from all groups were lumped together in one simple correlation analysis, there was correlation between these two variables (r=$-$0.07, p=0.4, n=151) (
 
@@
 When analyzed separately, the between-groups and within-groups correlations were also insignificant.
-A similar analysis for amplitudes of late synaptic currents also did not yield reliable results.
 
@@
 (\textbf{D}).
-Estimations of spikiness from current clamp experiments (horizontal axis) and dynamic clamp experiments (vertical axis) correlate.
+Estimations of excitability from current clamp experiments (horizontal axis) and dynamic clamp experiments (vertical axis) correlate.
 (\textbf{E}).
@@
 In this study we show that different sensory stimuli retuned neurons in the optic tectum of \textit{Xenopus} tadpoles in different ways, thereby inducing changes in both their temporal tuning and amplitude transfer functions.
-This addresses our first question about the functional scope of intrinsic plasticity in the optic tectum, and shows that it goes well beyond simple adjustments of neuronal spikiness.
+This addresses our first question about the functional scope of intrinsic plasticity in the optic tectum, and shows that it goes well beyond simple adjustments of neuronal excitability.
 
@@
 This suppression then triggered a “second-order” homeostatic compensation \citep{turrigiano2011,tien2018}, making neurons spikier.
-In our current experiments, however, synaptic inputs were not suppressed, and neuronal activation during sensory conditioning was stronger than in control, causing a decrease in intrinsic spikiness.
+In our current experiments, however, synaptic inputs were not suppressed, and neuronal activation during sensory conditioning was stronger than in control, causing a decrease in intrinsic excitability.
 

### 2019-04-19 reviews and responses.md
Responses around figure 1

@@
 
-This refers to smaller (flat, not increasing) spiking output as a function of conductance duration. To make it clear, we improved the sentence:
+We improved the sentence:
 
-"Compared to control, neurons from animals exposed to visual stimuli had a flatter **(constant or hill-shaped, rather than increasing)** amplitude tuning curve (Fig 1D,E), **as they** did not increase their spiking as fast in response to larger conductances..."
+Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (**less of a difference between columns of Figure 1D, or different curves in each panel of Figure 1E**), as they did not increase their spiking as fast in response to larger conductances
 
@@
 that captures this would be helpful.
+
+TODO: How to make a figure like that? They refer to a text about the stepwise generalized linear model. Is there a good visualization here?
 

### 2019-05-03 reviews and responses.md
More responses: moved to reviewer 2

@@
 
-We address the concerns of Reviewer 3 first, as they were more critical overall. Then we respond to the suggestions of Reviewer 2.
+We address the concerns of Reviewer 3 first, as they were overall more critical. Then we respond to the suggestions of Reviewer 2.
 
@@
 
-Previously a detailed justification for the use of dynamic clamp was only given in the Discussion; we now added it to the end of Introduction.
+Previously a detailed justification for the use of dynamic clamp was only given in the Discussion section; we now added it to the end of Introduction.
 
@@
 For earlier results section, we replaced "spikiness" with "average number of spikes", and in all instances when we talked about the general idea of neuronal excitability, we called it neuronal excitability.
-As the only exception to this rule, we opted for the word "spikness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
+As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
 
@@
 
-Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (**less of a difference between columns of Figure 1D, or different curves in each panel of Figure 1E**), as they did not increase their spiking as fast in response to larger conductances
+Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (**less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E**), as they did not increase their spiking as fast in response to larger conductances
 
@@
 Of these four paragraphs, the last one reports a negative result that is not shown in Figure 3.
-The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot replace them with one sentence, as the statement we are making is not that obvious statistically.
+The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot in good faith replace them with one sentence, as the statement we are making is not statistically obvious.
 We believe that an attempt to gloss it over by pushing the statistical analysis to the methods section would not be fair.
+The issue, as we describe in the text, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes.
+Had the slopes be the same, we would have just reported a correlation in one sentence.
+But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is typical for larger datasets, but that some readers may not be familiar with.
 
-The issue, as we describe in the text, is that while graphs 3E and 3F have very similar axes, and both show a linear dependency, they have opposite slopes.
-Had the slopes be the same, we would have just reported a correlation, in one sentence.
-But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative.
-
-We indeed received some conflicting advice in the past about the level of detail necessary to communicate this message: for example, people who have studied Simpson's paradox in their statistics classes had found our use of this term very helpful, while people who haven't heard it before, found it distracting.
-For now, we opted to include it, but we are aware that what makes the text more relatable to one group of researchers may make it less transparent for other groups.
+We are aware that this section is read differently by different readers, and we received some conflicting advice in the past about the level of details needed to communicate this message.
+For example, those who have explicitly discussed Simpson's paradox in their statistics classes typically find our use of this term very helpful, while those who haven't used this term before, may find it distracting.
+For now, we opt to include it, even though it seems to be appreciated by only one half of our target audience.
 
@@
 explain some of the trends in the data?
+
+> TODO: that is what we are suggesting in one of the paragraphs. Cite that.
 
@@
 
+These are the same stimuli, and we changes these two sentences to better reflect that:
+
+"To test this question, we exposed tadpoles to four hours of behaviorally salient, startle-inducing “click” sounds, provided at the same frequency (every second) as visual stimuli in the first set of experiments.
+We found (Fig 1D, E) that exposure to these sounds..."
+
 > - Tadpoles are exposed to 4 hours of click sounds and then intrinsic tuning was measured. No difference
@@
 
+Unfortunately, recording of tectal reponses to sounds in tadpoles does not seem to be possible in present, not just in our lab (where we don't posess the technical capability to perform in-vivo experiments), but in most labs.
+Technically, the problem amounts to two limitations: one, to record from a tadpole, one has to paralyze it with a nicotinic receptor anatagonist, which seems to disrupt hearing.
+Second, even if this limitation is overcome, the sounds has to be strong enough to stimulate the inner ear, but weak enough not to disrupt a recording.
+Conceivably, both challenges may be overcocme with the use of high speed calcum imaging in freely moving tadpoles, but this is also challenging, and to our knowledge no lab has attempted these recordings yet.
+
+To show that our statement is just a conjecture, we replaced "suggets" with "may suggest" in this sentence: "This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning..."
+
 > Page 6 line 24: Remove the phrase “are not easily interpretable”. Instead, please interpret your data
 clearly.
+
+We now removed this phrase from the main text.
 
@@
 
+Stimulation in the optic chiam evokes two types of synaptic responses in tectal cells: direct short-latency responses, and delayed recurrent inputs from other cells in the tectum.
+By looking at average currents early and later after the chiasm shock, we can independently assess the contribution of direct and recurrent inputs.
+In the paper, in a paragraph before the sentence in question, we report that after stimulation, direct current increased in amplitude, while recurrent currents remained unchanged.
+This is what we call selective potentiation of direct inputs, as opposed to recurrent inputs.
+We do not claim that mechanosensory inputs did not change, as we have not recorded auditory responses in this study (recordings of auditory responses are considerably more difficult; see Felch 2016).
+
+To make sure that we are not misunderstood by the reader, we replaced the original sentence with the following two sentences: "This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum that remained unchanged.
+In this study, we did not perform a similar analysis for acoustic projections from the hindbrain."
+
 > Page 9 line 9: “cells exposed to stronger stimuli preferred shorter synaptic inputs in dynamic clamp…”
 Here, (where “preferred” is not in quotes) does “preferred” mean to fire more action potentials?
+
+Yes, as we answered above, we now don't use quotation marks for any of the words that aid writing and understanding, so "preferred" consistently means "responded preferably", or "produced stronger responses".
 
@@
 
+We did not measure action potential thresholds, as we knew from the previous study (Ciarleglio Khakhalin 2015) that potential threshold measurements in tadpole tectal neurons are unreliable, in the sence that they strongly depend on the current that is used to evoke the spikes; this is almost certainly due to rapid Na channels inactivation.
+
 > Page 10 line 8: The “correction for position” is difficult to understand here and in Methods. Why was a
@@
 data look without this correction?
+
+The linear regression is used because it is the simplest way to compensate for a confounding variable (see ANCOVA, or linear models with confounding variables in general).
+Linear models are the "default" approach in statistics, and are typically used when the exact relation between two variables is unknown, or when the amount of noise is so high that practically there is no difference between linear and conceivable curvilinear regressions.
+Both situations apply here.
+
+There is no way for us to determine whether our adjustment is "accurate", as there is no experimental way to make more caudal (and thus younger) cells in the tectum older.
+This situation is not unique however, as it arises in any study that uses linear models, in any field, from ecology to social sciences.
+When running a study in a human population, if a variable of interest depends on age, one would typically adjust for age by including age as a covariate in the linear model.
+Here we perform the same standard procedure.
+After rereading the manuscript, we realized that we used terms "adjustment", "correction", and, in one case, "compensation" interchangeably, which might have led to some confusion.
+To stress that we are talking about a basic statistical technique of covarate elimination, we now consistently use the term "adjustment" throughout the manuscript.
+
+In the paper, we do not report how the data would have looked without this adjustment for covariates, as it would not be statistically sound to run a linear model with a known covariate without including it.
+It would underestimate effects for analyses across groups (as the effect of the covarate would be included in the error), and overestimate effects for explanatory linear models in the second half of the paper (as the covariate would contribute to both the dependent, and the independent variables in the model).
+If the reviewers would like us to numerically re-run any part of the analysis without a position adjustment, please let us know which part you would like to see.
+Also, all of our technical visualizations and analyses related to this adjustment are available for inspection at:
+https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/dynamic_other_vars.R
 

### 2019-05-04 dynamic_other_vars.R
Sensitivity analysis for position adjustment (requested by reviewers)

@@ -5,12 +5,12 @@
 # install.packages("lme4") # This one is required for lmerTest to work
 # install.packages("lmerTest")
 # install.packages("effsize")
-#install.packages("viridis")
+# install.packages("viridis")
 
 require(dplyr)
 require(ggplot2)
 require(effsize)
-require(ggbeeswarm) # Suddenly stopped working after an update around Dec 2018; may be a version conflict
+# require(ggbeeswarm) # Suddenly stopped working after an update around Dec 2018; may be a version conflict
 require(reshape2) # needed for some old code
 require(MASS) # Model selection. Note that it annoying masks "select" from dplyr
 require(lmerTest) # Random effects model, requires lme4 as a dependency
@@ -103,7 +103,7 @@ summary(aov(data=d,ktv~group+rostral+medial)) # no
 summary(aov(data=d,ksi~group+rostral+medial)) # medial
 summary(aov(data=d,ksv~group+rostral+medial)) # no
 # Drop of values across the entire tectum: 
-f = lm(data=d,cm ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # -2.4 pA
+f = lm(data=d,cm ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # -2.4 pF
 f = lm(data=d,rm ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # 250 kOhm
 f = lm(data=d,nav ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # -12 mV
 f = lm(data=d,ksi ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # -276 pA
@@ -112,6 +112,7 @@ f = lm(data=d,nai ~ group+medial+rostral); coef(f)['rostral']*(0.69-0.36) # 156 
 # Based on (Hamodi Pratt), they observed ~150 pA change in nai, and ~200 pA in ki (?),
 # while comparing 0-30% and 60-80% of the OT. If ~ 55% of width gave them these differences,
 # with our ~30% of range we can expect ~70-100 pA diff for nai and ki.
+# Our values are a bit higher, but not that higher.
 
 ggplot(data=d) + theme_bw() + geom_point(aes(medial,nav)) # We also see it, but it's not striking
 
[…]

### 2019-05-04 reviews and responses.md
Membrane resistance: the units are GOhms

@@
 
-We address the concerns of Reviewer 3 first, as they were overall more critical. Then we respond to the suggestions of Reviewer 2.
-
-## Reviewer 3
-
-> Busch and Khakhalin use the Xenopus tadpole tectal model to address the question of
-how neurons modify their intrinsic properties when an animal experiences different
-types of sensory input. Animals that underwent different forms of sensory experience
-had tectal neurons that decreased their overall excitability. This is consistent with the
-idea of homeostatic regulation of intrinsic properties. Surprisingly, when the sensory
-experience involved short pulses of light, neurons because more responsive to short
-inputs even though there was an overall decrease in spiking. This adds a layer of
-complexity to the idea of homeostatic control of a firing rate set point because it shows
-neurons can independently regulate total spiking in the opposite direction from their
-responses to synaptic inputs of different durations. This is a really interesting idea. The
-data are sound and well-analyzed (beautiful figures, open source data, etc.). However,
-from top to bottom, this manuscript was incredibly difficult to read. Due to organizational
-issues, lack of a strong rationale, and inconsistent/confusing wording, I’m not entirely
-sure I understand the main message the authors are trying to convey. My summary is
-largely based on what I was able to pick out of the figures. I strongly suggest the
-authors perform a massive rewrite and really emphasize the main points.
-
-### Major Comments
-
-> Abstract:
-
-> It’s hard to follow what was actually done and found in the paper based on the abstract.
-The abstract starts off with a statement about homeostatic regulation through changes
-in intrinsic properties and then gives a detailed account of what was found without any
-context. It would be easier to assimilate the information if the abstract follows a more
-standard format: start with the area the paper clearly contributes to, build the rationale
-for the study, state the hypothesis (or driving question), describe how this was tested
-and what was found, and say why it’s important.
-
-We rewrote the abstract, stressing the big question to which the paper contributes (principles of tuning and learning in biological neural networks), and the main message of the paper.
-We also made the account of our findings a bit less detailed.
-
-> Introduction:
-
-> I feel the same way about the introduction as I do the abstract; as written, it doesn’t give
-the reader a great sense of what’s to come. If the setup for the paper is that
-“connectivity isn’t everything— intrinsic properties matter,” this is a good start, but it
-could be made much clearer. Further, the questions of the study are not presented until
-the third paragraph, and there is no rationale for these questions. I suggest the authors
-completely revamp the introduction in way that guides the reader from
-regulation/plasticity of intrinsic properties (the big picture question) to why there’s a
-reason to think neurons in their system can tune their responsiveness to different kinds
-of inputs they receive (a specific hypothesis). This is what the authors actually address,
-but they really don’t provide much of a rationale for their specific experiments, which
-weakens the paper.
-
-We now made the introduction clearer, and better organized, going from the big problem, to specific questions.
-We moved the presentation of the questions for the study to the very beginning of the second paragraph, and provided a rationale for these questions in the first paragraph.
-
-> Results and Discussion:
-
-> - The rationale for the use of dynamic clamp and the parameters chosen are not clear.
-
-Previously a detailed justification for the use of dynamic clamp was only given in the Discussion section; we now added it to the end of Introduction.
-
-> Is the dynamic clamp current injection protocol mimicking the physiological synaptic
-input? This should be stated.
-
-We updated the next sentence, by adding a reference to it: "We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits in vivo (Xu et al.
-2011; Khakhalin et al.
-2014; Ciarleglio et al.
-2015; see Methods)."
-
-> - I think the experiment in this study is pretty straightforward, but the description of the
-results is not. As far as I can tell, tadpoles were exposed to different stimuli (flash,
-looming, multisensory, etc.). Then, tectal neurons were stimulated using either 1)
-dynamic clamp or 2) more physiologically through optic chiasm. This allowed the
-investigators to assess firing when they changed the stimulus intensity and stimulus
-duration of the dynamic clamp or the synaptic response to presynaptic stimulation.
-They then looked how the different types of sensory experience influenced firing
-responses. The rest is data analysis that looks at how the duration, amplitude, total
-spiking, and synaptic input is changed in different sensory contexts and sensory
-stimuli might interact. I think the text can be made much simpler so the basic design
-is easier to grasp. I suggest thinking about what the take home point is for each
-figure and craft the results section around those messages.
-
-Thank you; we tried to follow this advice in this revised version of the manuscript!
-
-> - There is also an inconsistent use terminology. For example, “spikiness” and
-“excitability” are sometimes used in attempt to describe distinct cell characteristics,
-but sometimes it seems like they are being used interchangeably. This makes
-interpreting the written results difficult to follow.
-
-In this updated version, we consistently use "spikiness" as a name for the variable, for the first time introduced in Figure 2C.
-For earlier results section, we replaced "spikiness" with "average number of spikes", and in all instances when we talked about the general idea of neuronal excitability, we called it neuronal excitability.
-As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
-
-> - “Compared to control, neurons from animals exposed to visual stimuli had a flatter
-amplitude tuning curve (Fig 1D,E).” What is the reader supposed to be looking at in
-the figure? Is this referring to larger conductances for a fixed duration? I think this is
-what the authors’ mean, but more intuitive descriptions that matches the figures or
-vice versa is needed to make the whole results section easier to digest.
-
-We improved the sentence:
-
-Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (**less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E**), as they did not increase their spiking as fast in response to larger conductances
-
-> - Excessive wordiness makes the results difficult to read and interpret. For example,
-on pg. 9, 4 paragraphs (411 words) are used to describe two graphs, each showing
-a different linear relationship (Fig. 3E-F). Why not simply say, “A positive relationship
-between temporal tuning and synaptic duration implies a co-tuning of preferr
-parameters.”
-
-Of these four paragraphs, the last one reports a negative result that is not shown in Figure 3.
-The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot in good faith replace them with one sentence, as the statement we are making is not statistically obvious.
-We believe that an attempt to gloss it over by pushing the statistical analysis to the methods section would not be fair.
-The issue, as we describe in the text, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes.
-Had the slopes be the same, we would have just reported a correlation in one sentence.
-But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is typical for larger datasets, but that some readers may not be familiar with.
-
-We are aware that this section is read differently by different readers, and we received some conflicting advice in the past about the level of details needed to communicate this message.
-For example, those who have explicitly discussed Simpson's paradox in their statistics classes typically find our use of this term very helpful, while those who haven't used this term before, may find it distracting.
-For now, we opt to include it, even though it seems to be appreciated by only one half of our target audience.
-
-Nevertheless, in current version of the paper, we shortened this section from 411 to 294 words.
-
-> - In reference to the text at the bottom of page10: Is it possible to include a summary
-figure of data from the stepwise generalized linear model in Fig. 4? The purpose of
-this part of the study was to try and identify electrophysiological mechanism(s) that
-explain the tuning variables. The heart of Fig. 4 should be that they don’t, and figure
-that captures this would be helpful.
-
-TODO: How to make a figure like that? They refer to a text about the stepwise generalized linear model. Is there a good visualization here?
-
-> - If these data are interpreted as homeostatic (neurons became less excitable
-following sensory experience), is there any evidence that tectal neurons have
-different firing activities during the different kinds of sensory experience? For
-example, does sound engage tectal neurons less than visual stimuli, and might this
-explain some of the trends in the data?
-
-> TODO: that is what we are suggesting in one of the paragraphs. Cite that.
+The reviews included Reviewer 2, and Reviwer 3, but no Reviewer 1.
 
@@
 
-Unfortunately, recording of tectal reponses to sounds in tadpoles does not seem to be possible in present, not just in our lab (where we don't posess the technical capability to perform in-vivo experiments), but in most labs.
+Unfortunately, recording of tectal reponses to sounds in tadpoles does not seem to be possible at present, not just in our lab (where we don't posess the technical capability to perform in-vivo experiments), but in most labs.
 Technically, the problem amounts to two limitations: one, to record from a tadpole, one has to paralyze it with a nicotinic receptor anatagonist, which seems to disrupt hearing.
@@
 In the paper, we do not report how the data would have looked without this adjustment for covariates, as it would not be statistically sound to run a linear model with a known covariate without including it.
-It would underestimate effects for analyses across groups (as the effect of the covarate would be included in the error), and overestimate effects for explanatory linear models in the second half of the paper (as the covariate would contribute to both the dependent, and the independent variables in the model).
-If the reviewers would like us to numerically re-run any part of the analysis without a position adjustment, please let us know which part you would like to see.
+In most cases, it may be expected to underestimate effects for analyses across groups (as the effect of the covarate would be included in the error), and overestimate effects for explanatory linear models in the second half of the paper (as the covariate would contribute to both the dependent, and the independent variables in the model).
+For each particular comparison, however, both d, F and p values would differ by a small random value.
+For example, when the measure of "spikness" (one of the three tuning parameters) is compared across groups, a correct analysis with adjustment for position (smean~rostral+medial+group) produces a p-value of 0.01.
+Without adjustment (smean~group) we get a p-value of 0.03.
+For temporal tuning, correct analysis (sbend~rostral+medial+group) gives p=0.0304, and if covariate is left unadjusted (sbend~gropu) we get p=0.029.
+Similarly, for amplitude tuning, we get p=0.00209 for correct analysis, and p=0.0024 for unadjusted analysis.
+For the analyses in which temporal tuning and ampliltude coefficients were explained through intrinsic parameters, the optimal models were not qualitatively different between adjusted and unadjusted data, but all values in the table were slightly different.
+
+If you would like us to numerically re-run any part of the analysis without a position adjustment, please let us know which part you would like to see.
 Also, all of our technical visualizations and analyses related to this adjustment are available for inspection at:
@@
 
+In this updated version, we consistently use "spikiness" as a name for the variable that is for the first time introduced in Figure 2C.
+For earlier results section, we replaced "spikiness" with "average number of spikes", and in all instances when we talked about the general idea of neuronal excitability, we called it neuronal excitability.
+As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
+
+"Intrinsic spikiness" is no longer used.
+
+"Intrinsic excitability" is used as a name for the phenomenon, that in this particular study we assess mostly using the "spikness" variable, although arguably the number of spikes observed in current clamp experiments can also be considered a different quantification of the same variable.
+In the text, we say "intrinsic excitability" when we make inferences about the actual properties of the neuron, and "spikiness" when we are talking about the actual value we calculated to assess and quantify this intrinsic excitability.
+
 > Page 15 line 34: The average membrane resistance (330 MOhm) seems a bit low for these small immature
@@
 there any set criteria for Rm, Vm, or access resistance?
+
+Thank you for noticing that: we have an order of magnitude mistake here (and we are duly ashamed of it). The average membrane resistance was 3.30 GOhm.
+
+TODO: is it even true? Or are these the Gigaseal values, pre-patch?
+
+Smallest membrane resistance observed was 1 GOhm, maximal access resistance 110 MOhm, with the average of 30 MOhm.
+We did not measure Vm, but measured the holding current necessary to bring the cell to -60 mV; the mean value of this I_hold is -8.16 pA, the resting membrane potential can be estimated from this value with a formula Vm = -60 mV + Rm*I_hold.
+
+All data for all cells is available at:
+https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/Data/data_mainInput.txt
+(In this dataset, groups "Naive", "SlowF", and "SlowC" should be ignored, as they were not included in the study.
+Note also that github doesn't show columns correctly, so it may be better to download the file if you want to study it closerly)
 
@@
 used consistently throughout.
+
+## Reviewer 3
+
+> Busch and Khakhalin use the Xenopus tadpole tectal model to address the question of
+how neurons modify their intrinsic properties when an animal experiences different
+types of sensory input. Animals that underwent different forms of sensory experience
+had tectal neurons that decreased their overall excitability. This is consistent with the
+idea of homeostatic regulation of intrinsic properties. Surprisingly, when the sensory
+experience involved short pulses of light, neurons because more responsive to short
+inputs even though there was an overall decrease in spiking. This adds a layer of
+complexity to the idea of homeostatic control of a firing rate set point because it shows
+neurons can independently regulate total spiking in the opposite direction from their
+responses to synaptic inputs of different durations. This is a really interesting idea. The
+data are sound and well-analyzed (beautiful figures, open source data, etc.). However,
+from top to bottom, this manuscript was incredibly difficult to read. Due to organizational
+issues, lack of a strong rationale, and inconsistent/confusing wording, I’m not entirely
+sure I understand the main message the authors are trying to convey. My summary is
+largely based on what I was able to pick out of the figures. I strongly suggest the
+authors perform a massive rewrite and really emphasize the main points.
+
+### Major Comments
+
+> Abstract:
+
+> It’s hard to follow what was actually done and found in the paper based on the abstract.
+The abstract starts off with a statement about homeostatic regulation through changes
+in intrinsic properties and then gives a detailed account of what was found without any
+context. It would be easier to assimilate the information if the abstract follows a more
+standard format: start with the area the paper clearly contributes to, build the rationale
+for the study, state the hypothesis (or driving question), describe how this was tested
+and what was found, and say why it’s important.
+
+We rewrote the abstract, stressing the big question to which the paper contributes (principles of tuning and learning in biological neural networks), and the main message of the paper.
+We also made the account of our findings a bit less detailed.
+
+> Introduction:
+
+> I feel the same way about the introduction as I do the abstract; as written, it doesn’t give
+the reader a great sense of what’s to come. If the setup for the paper is that
+“connectivity isn’t everything— intrinsic properties matter,” this is a good start, but it
+could be made much clearer. Further, the questions of the study are not presented until
+the third paragraph, and there is no rationale for these questions. I suggest the authors
+completely revamp the introduction in way that guides the reader from
+regulation/plasticity of intrinsic properties (the big picture question) to why there’s a
+reason to think neurons in their system can tune their responsiveness to different kinds
+of inputs they receive (a specific hypothesis). This is what the authors actually address,
+but they really don’t provide much of a rationale for their specific experiments, which
+weakens the paper.
+
+We now made the introduction clearer, and better organized, going from the big problem, to specific questions.
+We moved the presentation of the questions for the study to the very beginning of the second paragraph, and provided a rationale for these questions in the first paragraph.
+
+> Results and Discussion:
+
+> - The rationale for the use of dynamic clamp and the parameters chosen are not clear.
+
+Previously a detailed justification for the use of dynamic clamp was only given in the Discussion section; we now moved it to the end of Introduction.
+
+> Is the dynamic clamp current injection protocol mimicking the physiological synaptic
+input? This should be stated.
+
+We updated the next sentence, by adding a reference to it: "We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits in vivo (Xu et al.
+2011; Khakhalin et al.
+2014; Ciarleglio et al.
+2015; see Methods)."
+
+> - I think the experiment in this study is pretty straightforward, but the description of the
+results is not. As far as I can tell, tadpoles were exposed to different stimuli (flash,
+looming, multisensory, etc.). Then, tectal neurons were stimulated using either 1)
+dynamic clamp or 2) more physiologically through optic chiasm. This allowed the
+investigators to assess firing when they changed the stimulus intensity and stimulus
+duration of the dynamic clamp or the synaptic response to presynaptic stimulation.
+They then looked how the different types of sensory experience influenced firing
+responses. The rest is data analysis that looks at how the duration, amplitude, total
+spiking, and synaptic input is changed in different sensory contexts and sensory
+stimuli might interact. I think the text can be made much simpler so the basic design
+is easier to grasp. I suggest thinking about what the take home point is for each
+figure and craft the results section around those messages.
+
+Thank you; we tried to follow this advice in this revised version of the manuscript!
+
+> - There is also an inconsistent use terminology. For example, “spikiness” and
+“excitability” are sometimes used in attempt to describe distinct cell characteristics,
+but sometimes it seems like they are being used interchangeably. This makes
+interpreting the written results difficult to follow.
+
+As described in our responses to Reviewer 2, in this updated version, we consistently use "spikiness" as a name for the variable, for the first time introduced in Figure 2C.
+For earlier results section, we replaced "spikiness" with "average number of spikes", and in all instances when we talked about the general idea of neuronal excitability, we called it neuronal excitability.
+As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
+
+> - “Compared to control, neurons from animals exposed to visual stimuli had a flatter
+amplitude tuning curve (Fig 1D,E).” What is the reader supposed to be looking at in
+the figure? Is this referring to larger conductances for a fixed duration? I think this is
+what the authors’ mean, but more intuitive descriptions that matches the figures or
+vice versa is needed to make the whole results section easier to digest.
+
+We improved the sentence:
+
+Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (**less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E**), as they did not increase their spiking as fast in response to larger conductances
+
+> - Excessive wordiness makes the results difficult to read and interpret. For example,
+on pg. 9, 4 paragraphs (411 words) are used to describe two graphs, each showing
+a different linear relationship (Fig. 3E-F). Why not simply say, “A positive relationship
+between temporal tuning and synaptic duration implies a co-tuning of preferr
+parameters.”
+
+Of these four paragraphs, the last one reports a negative result that is not shown in Figure 3.
+The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot in good faith replace them with one sentence, as the statement we are making is not statistically obvious.
+We believe that an attempt to gloss it over by pushing the statistical analysis to the methods section would not be fair.
+The issue, as we describe in the text, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes.
+Had the slopes be the same, we would have just reported a correlation in one sentence.
+But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is typical for larger datasets, but that some readers may not be familiar with.
+
+We are aware that this section is read differently by different readers, and we received some conflicting advice in the past about the level of details needed to communicate this message.
+For example, those who have explicitly discussed Simpson's paradox in their statistics classes typically find our use of this term very helpful, while those who haven't used this term before, may find it distracting.
+For now, we opt to include it, even though it seems to be appreciated by only one half of our target audience.
+
+Nevertheless, in current version of the paper, we shortened this section from 411 to 294 words.
+
+> - In reference to the text at the bottom of page10: Is it possible to include a summary
+figure of data from the stepwise generalized linear model in Fig. 4? The purpose of
+this part of the study was to try and identify electrophysiological mechanism(s) that
+explain the tuning variables. The heart of Fig. 4 should be that they don’t, and figure
+that captures this would be helpful.
+
+We are not sure how this fact can be illustrated.
+We searched for papers that use stepwise linear models, and it seems they do not usually include summary figures to describe these models.
+(They often include tables, listing R-squared, F, df, and p-values for every component, but as in this paper we are not particularly concerned by the precise composition of our models, we doubt a table like that would be useful here).
+Do you have any specific type of illustration in mind, in which case, could you provide a reference, or maybe describe it?
+The only type of illustration we could come up with is a scatterplot that compares values predicted from the model to actual values, but it is already shown in the paper, as Figure 4E.
+
+> - If these data are interpreted as homeostatic (neurons became less excitable
+following sensory experience), is there any evidence that tectal neurons have
+different firing activities during the different kinds of sensory experience? For
+example, does sound engage tectal neurons less than visual stimuli, and might this
+explain some of the trends in the data?
+
+> TODO: that is what we are suggesting in one of the paragraphs. Cite that.
 

### 2019-05-04 dynamic_other_vars.R

@@ -104,7 +104,7 @@ summary(aov(data=d,ksi~group+rostral+medial)) # medial
 summary(aov(data=d,ksv~group+rostral+medial)) # no
 # Drop of values across the entire tectum: 
 f = lm(data=d,cm ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # -2.4 pF
-f = lm(data=d,rm ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # 250 kOhm
+f = lm(data=d,rm ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # 2.5 GOhm
 f = lm(data=d,nav ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # -12 mV
 f = lm(data=d,ksi ~ group+medial+rostral); coef(f)['medial']*(0.53-0.25) # -276 pA
 f = lm(data=d,nai ~ group+medial+rostral); coef(f)['rostral']*(0.69-0.36) # 156 pA
@@ -115,6 +115,7 @@ f = lm(data=d,nai ~ group+medial+rostral); coef(f)['rostral']*(0.69-0.36) # 156 
 # Our values are a bit higher, but not that higher.
 
 ggplot(data=d) + theme_bw() + geom_point(aes(medial,nav)) # We also see it, but it's not striking
+ggplot(data=d) + theme_bw() + geom_point(aes(medial,rm))
 
 # Different stories for 2 types of spiking
 summary(aov(data=d,stepspike~group+rostral+medial)) # medial

### 2019-05-29 Matlab code/dynamic_iv_reader.m
Trying to estimate Rm from CC recordings: linear approach (seems to have failed)

@@ -1,17 +1,16 @@
 function dynamic_iv_reader()
 % function dynamic_iv_reader
 %
-% reads and processes IV curve files for Silas' data.
+% Reads and processes IV curve files for Silas' data.
 
-% Oct 29 2017: last improved
 
 folderName = 'C:\_Data\_Silas\';
 flagConsoleOutput = 1;              % Whether reading files should be reported
-flagFitPassiveParams = 0;           % Use fancy exponential fit to estimate passive properties
+flagFitPassiveParams = 1;           % Use fancy exponential fit to estimate passive properties
 flagRunIVAnalysis = 0;              % Once I(V) are calculated, whether they should be fit, for each cell
 
-showFigPassive = 0;                 % If we want to see passive fit figure
-showFigActive = 1;                  % Whether figures are to be shown
+showFigPassive = 1;                 % If we want to see passive fit figure
+showFigActive = 0;                  % Whether figures are to be shown
 
 map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
 % S has the following fields that are all arrays:
@@ -21,7 +20,7 @@ map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
 nCells = length(map.id);
 cellList = 1:nCells;
 
-cellList = 51; % Uncomment for testing, Comment for a normal run. First 2 rows don't have an iv file
+% cellList = 51; % Uncomment for testing, Comment for a normal run. First 2 rows don't have an iv file
 
 z_l =  [100 450];           % Zero level
 prestep_l =  [504 1000];    % Test step area
@@ -69,9 +68,9 @@ for(iCell=cellList)
             passiveCurve = passiveCurve(maxPoint:end);          % Leave only the exponential part
             [coeff,gof2] = fit((1:length(passiveCurve))',passiveCurve,fit_f,fit_s);
             if(showFigPassive)
-                figure; hold on; 
+                figure('Color','w'); hold on; 
                 %plot(passiveCurve,'b-'); 
-                timeFrame = (prestep_l(1)-10):(prestep_l(2)+10);
+                timeFrame = (prestep_l(1)-10):(prestep_l(2)+100);
                 plot(timeFrame,mean(y(timeFrame,:),2),'b-');
[…]

### 2019-05-29 Matlab code/dynamic_steps_reader.m

@@ -1,18 +1,16 @@
 function dynamic_steps_reader()
 % function dynamic_synaptic_reader
 %
-% reads and processes current step files from Silas' data.
+% Reads and processes current step files from Silas' data.
 
-% Dec 20 17: Modified from dynamic_iv_reader
-% Jan 09 18: Curve fit for the alpha curve
-% Jan 12 18: Modified from dynamic_synaptic_reader
-% Jun 06 18: Raw visualization added
-% Jun 12 18: Small improvements in vis
 
 folderName = 'C:\_Data\_Silas\';
 showFigures = 1;                    % Whether figures are to be shown
 figureType = 'pile';                % 'full', 'pile', or 'train'
-consoleOutput = 1;                  % Whether reading files should be reported
+consoleOutput = 0;                  % Whether reading files should be reported
+flagFitCurrent = 1;                 % Whether the depolarization curve needs to be measured (dV/dt)
+flagFinalOutput = 0;                % Whether final table is to be shown
+
 
 map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
 % S has the following fields that are all arrays:
@@ -23,11 +21,12 @@ nCells = length(map.id);
 cellList=1:nCells;
 badCells = [];                              % 84: recorded in CC
 cellList = setdiff(cellList,badCells);
-cellList = 180:190;                         % Uncomment for testing (to work with selected few recordings only)
-% cellList = [141 198 205];                 % Some random cells for testing
+% cellList = 180:190;                         % Uncomment for testing (to work with selected few recordings only)
+cellList = [141 198 205];                 % Some random cells for testing
+% cellList = 198;
 nCells = length(cellList);
 
-xZero =  [10 4900];                         % Region ot measure zero level
+xZero =  [30 4900];                         % Region ot measure zero level
 xSignal = [5005 7000];                      % Region of the actual signal
 
 zThreshold = 0.02;                          % Spike detection threshold. 0.03 is kinda medium; 0.05 is conservative, 0.02 permissive
@@ -35,7 +34,7 @@ zThreshold = 0.02;                          % Spike detection threshold. 0.03 is
 bag = [];                                   % That's where the data will be collected
 
 for(iCell=cellList)
[…]

### 2019-05-29 Matlab code/dynamic_synaptic_reader.m

@@ -1,10 +1,8 @@
 function dynamic_synaptic_reader()
 % function dynamic_synaptic_reader
 %
-% reads and processes synaptic files from Silas' data.
+% Reads and processes synaptic files from Silas' data.
 
-% Dec 20 17: Modified from dynamic_iv_reader
-% Jan 09 18: Curve fit for the alpha curve
 
 folderName = 'C:\_Data\_Silas\';
 showFigures = 1;                    % Whether figures are to be shown

### 2019-05-29 Matlab code/dynamic_what_is_where.m

@@ -35,6 +35,8 @@ function res = big_array()
 % 256	4	193	201	20160322	34	35	36	37	38 - dynamic removed (crashes the reader)
 % 258	4	183	223	20160322	44	45	46	47	48 - dynamic removed (crashes the reader)
 
+%                           iv  min ist dyn syn
+
 res = [
 1	8	121	188	20151009	NaN	NaN	NaN	NaN	NaN
 2	8	117	183	20151009	NaN	NaN	NaN	NaN	NaN

### 2019-05-30 Matlab code/dynamic_steps_reader.m
Rm directly extracted from CC cfs meta data.

@@ -5,7 +5,7 @@ function dynamic_steps_reader()
 
 
 folderName = 'C:\_Data\_Silas\';
-showFigures = 1;                    % Whether figures are to be shown
+showFigures = 0;                    % Whether figures are to be shown
 figureType = 'pile';                % 'full', 'pile', or 'train'
 consoleOutput = 0;                  % Whether reading files should be reported
 flagFitCurrent = 1;                 % Whether the depolarization curve needs to be measured (dV/dt)
@@ -22,7 +22,7 @@ cellList=1:nCells;
 badCells = [];                              % 84: recorded in CC
 cellList = setdiff(cellList,badCells);
 % cellList = 180:190;                         % Uncomment for testing (to work with selected few recordings only)
-cellList = [141 198 205];                 % Some random cells for testing
+% cellList = [141 198 205];                 % Some random cells for testing
 % cellList = 198;
 nCells = length(cellList);
 
@@ -59,21 +59,43 @@ for(iCell=cellList)
         y = bsxfun(@plus,y,-zero);                              % Set baseline to zero
         
         [fb,fa] = butter(3,0.2);                                % Low-pass filter
-        temp = y;
-        temp = filter(fb,fa,temp);
-        d1 = diff(temp); d1 = [d1(ones(1,nSweeps)); d1];        % First derivative
+        yFiltered = y;
+        yFiltered = filter(fb,fa,yFiltered);
+        d1 = diff(yFiltered); d1 = [d1(ones(1,nSweeps)); d1];   % First derivative
         
         if(flagFitCurrent)
             K = mean(d1(xSignal(1)+(1:30),2))*1e4/1000;         % Multiplied by 1e4 because 1tick = 0.1 ms; then translated from mV/s to V/s
             stepSize = mean(ds.data(2).y(xSignal(1)+(1:10),2)) - mean(ds.data(2).y(30+(1:10),2));
             
-            % fprintf("%4d\t%f\t%3.0f\n", map.id(iCell) , K , stepSize);
+            if(0) % This approach doesn't work as average resistance goes down obviously as channels close
+                avRtot = 0;
+                for(iSweep=1:length(ds.data))
+                    avRtot = avRtot + ds.data(iSweep).vars(35).value;
+                    temp(iSweep) = ds.data(iSweep).vars(35).value;
+                end
+                avRtot = avRtot/length(ds.data);
+                figure; plot(temp);
+
[…]

### 2019-05-31 reviews and responses.md
Rm question resolved, numbers validated

@@
 
-Thank you for noticing that: we have an order of magnitude mistake here (and we are duly ashamed of it). The average membrane resistance was 3.30 GOhm.
+Thank you for catching this error!
+We had an order of magnitude typo here, and the average membrane resistance was in fact 3.2±1.5 GOhm.
+This value is a bit higher than reported earlier (1.2±0.8 GOhm in Ciarleglio Khakhalin 2015; ~1.1 in Khakhalin 2011), but within what can be reasonably expected for healthy neurons of this size.
+To make sure that this number reflects our observations, for the purpose of this response, we verified this value by reanalyzing our data offline, and obtained a similar estimation for the average membrane resistance (2.9±1.4 GOhm).
+We have several reasons to believe that the cells included in this study were healthy.
+First, the access resistances obtained were good (30±14 MOhm, which is similar to benchmark 50±23 in Ciarleglio Khakhalin 2015, and ~20-30 MOhm in Khakhalin 2011), indicating that higher membrane resistance is not likely to be due to poor access.
+Second, our neurons reliably produced spikes in current clamp mode, and active currents in response to membrane depolarization in voltage clamp mode, and the quantification of these active conductances yielded numbers similar to those reported before (Ciarleglio Khakhalin 2015).
+The quality of voltage clamp, as judged by the absence of escaping active currents in IV protocols, was good in the majority of neurons (82% of all neurons recorded).
+Finally, a few cells that had their membrane resistance change drastically during the recording session, were discarded at the data collection stage.
+We did not measure the resting potential directly, but measured the holding current necessary to bring the cell to -60 mV in voltage clamp mode, and the mean value of this I_hold value was -8.2±4.8 pA, which is not higher tha what was previously recorded in the literature (19.8±16.6 in Ciearleglio Khakhalin 2015).
 
-TODO: is it even true? Or are these the Gigaseal values, pre-patch?
+Overall, these arguments make us believe that the quality of our patches was good enough to draw the conclusions reported in the study.
+Note that all data for all cells is available at the following address:
+https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/Data/data_mainInput.txt
+In this dataset, groups "Naive", "SlowF", and "SlowC" should be ignored, as they were not included in the study.
+Note also that github doesn't show columns correctly, so if you want to inspect the data, we recommend that you download it and open it in a spreadsheet.
 
-Smallest membrane resistance observed was 1 GOhm, maximal access resistance 110 MOhm, with the average of 30 MOhm.
-We did not measure Vm, but measured the holding current necessary to bring the cell to -60 mV; the mean value of this I_hold is -8.16 pA, the resting membrane potential can be estimated from this value with a formula Vm = -60 mV + Rm*I_hold.
-
-All data for all cells is available at:
-https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/Data/data_mainInput.txt
-(In this dataset, groups "Naive", "SlowF", and "SlowC" should be ignored, as they were not included in the study.
-Note also that github doesn't show columns correctly, so it may be better to download the file if you want to study it closerly)
+As the mistake your noticed (thank you again for being so thorough!) was a typo in the text, and not a mistake in the data, it does not affect any other calculations reported in this paper.
 

### 2019-05-31 Matlab code/dynamic_iv_reader.m

@@ -6,11 +6,11 @@ function dynamic_iv_reader()
 
 folderName = 'C:\_Data\_Silas\';
 flagConsoleOutput = 1;              % Whether reading files should be reported
-flagFitPassiveParams = 1;           % Use fancy exponential fit to estimate passive properties
+flagFitPassiveParams = 0;           % Use fancy exponential fit to estimate passive properties
 flagRunIVAnalysis = 0;              % Once I(V) are calculated, whether they should be fit, for each cell
 
-showFigPassive = 1;                 % If we want to see passive fit figure
-showFigActive = 0;                  % Whether figures are to be shown
+showFigPassive = 0;                 % If we want to see passive fit figure
+showFigActive = 1;                  % Whether figures are to be shown
 
 map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
 % S has the following fields that are all arrays:
@@ -41,7 +41,7 @@ fit_s = fitoptions('Method','NonlinearLeastSquares',...
 
 nCells = length(cellList);
 for(iCell=cellList)
-    if(~isnan(map.iv(iCell)))
+    if(~isnan(map.iv(iCell)) & map.group(iCell)<=5)     % This time, only analyze those groups that matter for the study (not Naive and slow ones)
         fileName = [folderName map.folder{iCell} '\' num2str(map.prefix(iCell)) '_' sprintf('%03d',map.iv(iCell)) '.cfs'];
         if(0)
             fprintf('%4d \t%4d \t%10s \t%s\n',iCell,map.id(iCell),map.folder{iCell},fileName);

### 2019-05-31 dynamic_other_vars.R

@@ -1,6 +1,5 @@
 # Dynamic study of intrinsic plasticity:
 # Analysis of everything that isn't raw spike data.
-# Version Dec 09 2018
 
 # install.packages("lme4") # This one is required for lmerTest to work
 # install.packages("lmerTest")
@@ -60,9 +59,20 @@ sd(d$medial,na.rm=T)
 min(d$medial,na.rm=T)
 max(d$medial,na.rm=T)
 
-d$rm = d$rm/10  # The original data file used weird units. Now it's in GOhm
+# --- Passive values, basics ---
+mean(d$ra, na.rm=T) # 30 MOhm
+sd(d$ra, na.rm=T) # 14 MOhm
 
-# Tuck down two extreme outlier cells
+mean(d$rm, na.rm=T) # 3.19 GOhm
+sd(d$rm, na.rm=T) # 1.46
+min(d$rm, na.rm=T) # 1
+ggplot(data=d,aes(rm)) + theme_minimal() + geom_bar()
+
+mean(d$ihold)
+sd(d$ihold)
+ggplot(data=d,aes(ihold)) + theme_minimal() + geom_bar(width=1)
+
+# Tuck down two extreme cells with outlier values of estimated tuning (but preserve ranks)
 ggplot(data=d) + theme_bw() + geom_point(aes(samp,sbend))
 domit = d
 domit = mutate(domit, sbend = ifelse(sbend<0.5,sbend,0.5)) # From 1 to 0.5

### 2019-05-31 reviews and responses.md
Response on cross-correlations between spiking in response to currents of diff duration.

@@
 
+At least for high-spiking neurons, the answer to this question can actually be inferred from Figure 1D: those curves that are placed high on the graph for duration of 500 ms, also tend to remain high for 1000 ms, indicating that high-spiking neurons tend to be high-spiking across the range of durations.
+Numerically, the correlation coefficient between the average number of spikes in response to 500 and 1000 ms, across all neurons, is r=0.94.
+Arguably, this was to be expected as intrinsic excitability of neurons (whether the neuron is spiky or not) is a much stronger feature than the temporal tuning.
+(Temporal tuning in the tectum was not even described until this paper, while the variation in intrinsic excitability in the tectum is well known for more than 20 years).
+
 > Figure 4 D, E and F: Is “spikiness” synonymous with “N Spikes”? If these terms do not mean the same
@@
 used consistently throughout.
+
+As described above, "spikiness" is now consistently used across the manuscript as the name of one of three variables used to quantify intrinsic tuning of tectal neurons.
 

### 2019-05-31 dynamic_spikes_plot.R

@@ -1,16 +1,16 @@
 # Dynamic Clamp spiking data analyzer
-# version Dec 09 2018
 
 require(ggplot2)
 require(dplyr)
 require(reshape2)
+require(tidyr)
 # install.packages("lmerTest") # Mixed ANOVAs
 require(lmerTest)
 
 rm(list = ls())  # Clear workspace
 
 # ----- Read and prepare spike data ----
-d = read.table("Dynamic-clamp-2018-git/Data/data_outDataset.txt",header=T) # Update the path as necessary
+d = read.table("5_Dynamic clamp/Git - Dynamic/Data/data_outDataset.txt",header=T) # Update the path as necessary
 d = subset(d,is.element(Group,c(0,1,2,3,4,5))) # Remove slow and naive
 d = mutate(d,Group = recode_factor(Group,"0"="Control","2"="Flash","1"="Looming",
                 "3"="Sound","4"="Sync","5"="Async","6"="Slowc","7"="Slowf","8"="Naive"))
@@ -42,9 +42,18 @@ d1 = d %>% group_by(Cell) %>%
   summarize(Cell=Cell,ms=ms,sa=coef(fsa)[2],ss=coef(fss)[3],ms2=coef(fsa)[1])
 head(d1)
 
-
-# Sence-check if mean term is too different from simple mean (they are almost the same)
+# Sence-check if mean term is too different from simple mean (they are pretty similar)
 ggplot() + theme_bw() + geom_point(data=d1,aes(ms,ms2)) # Basically the same, doesn't matter
+
+# One of reviewres asked whether spiking at 500 ms is a predictor for spiking at 1000 ms
+head(d)
+temp <- d %>% filter(Shape %in% c(3,4)) %>% 
+  group_by(Cell,Shape) %>% 
+  summarize(m=mean(Spikes))
+temp <- spread(temp,Shape,m)
+temp <- temp %>% dplyr::select(Cell,t3=2,t4=3) # These 2 and 3 here are col numbers, not col names
+head(temp)
+cor.test(temp$t3,temp$t4)
 
 # Testbed for quadratic lm formulas we use:
 t = c(1,2,3,4)-1

### 2019-05-31 reviews and responses.md
fighting markdown syntax

@@
 For each particular comparison, however, both d, F and p values would differ by a small random value.
-For example, when the measure of "spikness" (one of the three tuning parameters) is compared across groups, a correct analysis with adjustment for position (smean~rostral+medial+group) produces a p-value of 0.01.
-Without adjustment (smean~group) we get a p-value of 0.03.
-For temporal tuning, correct analysis (sbend~rostral+medial+group) gives p=0.0304, and if covariate is left unadjusted (sbend~gropu) we get p=0.029.
+For example, when the measure of "spikness" (one of the three tuning parameters) is compared across groups, a correct analysis with adjustment for position (`smean~ rostral+medial+group`) produces a p-value of 0.01.
+Without adjustment (smean \~ group) we get a p-value of 0.03.
+For temporal tuning, correct analysis (sbend \~ rostral+medial+group) gives p=0.0304, and if covariate is left unadjusted (sbend~gropu) we get p=0.029.
 Similarly, for amplitude tuning, we get p=0.00209 for correct analysis, and p=0.0024 for unadjusted analysis.

### 2019-05-31 reviews and responses.md
more markdown syntax

--- 2019-05-31 reviews and responses.md
@@
 For each particular comparison, however, both d, F and p values would differ by a small random value.
-For example, when the measure of "spikness" (one of the three tuning parameters) is compared across groups, a correct analysis with adjustment for position (smean~rostral+medial+group) produces a p-value of 0.01.
-Without adjustment (smean~group) we get a p-value of 0.03.
-For temporal tuning, correct analysis (sbend~rostral+medial+group) gives p=0.0304, and if covariate is left unadjusted (sbend~gropu) we get p=0.029.
+For example, when the measure of "spikness" (one of the three tuning parameters) is compared across groups, a correct analysis with adjustment for position (`smean~rostral+medial+group`) produces a p-value of 0.01.
+Without adjustment (`smean~group`) we get a p-value of 0.03.
+For temporal tuning, correct analysis (`sbend~rostral+medial+group`) gives p=0.0304, and if covariate is left unadjusted (`sbend~group`) we get p=0.029.
 Similarly, for amplitude tuning, we get p=0.00209 for correct analysis, and p=0.0024 for unadjusted analysis.
@@
 We had an order of magnitude typo here, and the average membrane resistance was in fact 3.2±1.5 GOhm.
-This value is a bit higher than reported earlier (1.2±0.8 GOhm in Ciarleglio Khakhalin 2015; ~1.1 in Khakhalin 2011), but within what can be reasonably expected for healthy neurons of this size.
+This value is a bit higher than reported earlier (1.2±0.8 GOhm in Ciarleglio Khakhalin 2015; about 1.1 in Khakhalin 2011), but within what can be reasonably expected for healthy neurons of this size.
 To make sure that this number reflects our observations, for the purpose of this response, we verified this value by reanalyzing our data offline, and obtained a similar estimation for the average membrane resistance (2.9±1.4 GOhm).
 We have several reasons to believe that the cells included in this study were healthy.
-First, the access resistances obtained were good (30±14 MOhm, which is similar to benchmark 50±23 in Ciarleglio Khakhalin 2015, and ~20-30 MOhm in Khakhalin 2011), indicating that higher membrane resistance is not likely to be due to poor access.
+First, the access resistances obtained were good (30±14 MOhm, which is similar to benchmark 50±23 in Ciarleglio Khakhalin 2015, and about 20-30 MOhm in Khakhalin 2011), indicating that higher membrane resistance is not likely to be due to poor access.
 Second, our neurons reliably produced spikes in current clamp mode, and active currents in response to membrane depolarization in voltage clamp mode, and the quantification of these active conductances yielded numbers similar to those reported before (Ciarleglio Khakhalin 2015).

### 2019-05-31 reviews and responses.md
Finished all responses + Discussion improved

@@
 
-We replaced this sentence with the following sentence: "This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular (Pratt and Aizenman, 2009; Felch et al., 2016) and subcellular (Hiramoto and Cline,2009) targets in the tectum, and thus can recruit tectal networks to a different extent.
+We replaced this sentence with the following sentence: "This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular targets in the tectum (Pratt and Aizenman, 2009; Felch et al., 2016; Truszkowski et al., 2017), and thus can recruit tectal excitatory and inhibitory networks to a different extent."
 
@@
 
-TODO: add an explanation here that we addressed this issue in the next paragraph, when the effects of multisensory stimulation are discussed. Because those WERE suprising.
+We now added the following sentence to the text: "Alternatively, acoustic stimuli may be inherently weaker in triggering plasticity effects in tectal neurons, as compared to visual inputs, they arrive at different subcellular compartments within the dendritic tree (Hiramoto and Cline, 2009; Deeg et al., 2009), which can affect their influence on neuronal plasticity (Richards and Lillicrap, 2019)."
+
+The actual rationale here is that inputs to different parts of the dentritic tree can trigger action potentials of different shape, and differentially affect calcium dynamics in the neuron, which, together with non-linear processing in dendrites may make different types of inputs unequal in terms of their effects on neuronal activity at one hand, and their impact on their tuning on the other.
+Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, and inputs to the apical dendrites of pyramidal cells in the cortex.
+However, we feel that this topic is really deep, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition to this short sentence with a reference.
 
@@
 special type of sensory network?
+
+Technically, even two neurons form a network (a true mathematician would probably argue that even one neuron forms a network!), so we tried to remind the reader that the tectal network is a relatively large one, with broad recurrent excitation, and in which different parts of the sensory input are processed in parallel.
+Thus we used the word "distributed", as in "distributed computations", as opposed to more local and covergent networks, such as, for example, the Mauthner cell network in the hindbrain.
+If you think that this word is not appropriate here, please let us know, and we'll remove it.
 
@@
 potentials?) than does flashes?
+
+This was unexpected as intrinsic plasticity is typically described as a homeostatic mechanism, and thus a stronger stimulus should, in principle, cause stronger suppression of spiking.
+To make it more clear, we now changed this sentence:
+
+"This was likewise unexpected, as compared to flashes, looming stimuli are known to elicit stronger tectal responses (Khakhalin et al., 2014; Khakhalin, 2019), yet their effect on neuronal excitability was weaker, seemingly violating the principle of homeostatic plasticity (Pratt and Aizenman, 2007; Turrigiano, 2007)."
 
@@
 temporal intrinsic tuning in tectal neurons. As changes in intrinsic properties seemed  
-homeostatic (increased activation led to reduced spiking), by the same logic, one could..."
+homeostatic (increased activation led to reduced spiking), by the same logic, one could
+expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs."
 
-TODO: make clear that we are not talking about synaptic changes after the fact, but during the stimulation. And that we kind of know from Khakhalin 2014.
+Here we are not talking about our conditional stimuli alterning the pattern of synaptic inputs; we just refer to the fact that during the stimulation, shorter stimuli (such as instantaneous flashes, that are technically the shortest stimuli possible) would cause faster visual inputs to the tectum, compared to longer stimuli (second-long continuous transitions) that would cause slower inputs.
+In this study, we did not measure actual synaptic responses in the tectum during conditioning, but from previous studies we know that responses to flashes are actually much shorter than responses to looming stimuli (Khakhalin 2014), as described in the beginning of the "Results" section, and then again in the "Methods".
+
+We now changed the wording of this sentence, to make this logic clearer.
+
+"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (flashes; Khakhalin et al.
+2014) would selectively suppress spiking in repsonse to shorter synaptic inputs."
 
@@
 
-All our measurements of the number of spikes relied on the dynamic clamp experiments, that used simulated, and not real synaptic inputs.
+All our measurements of the number of spikes relied on the dynamic clamp experiments, that used simulated synaptic inputs, and not real synaptic stimulation.
 It means that any changes in spiking we observed in the previous section of the results is necessarily coming from the change in intrinsic properties.
-While a change in the synaptic strength in response to sensory stimulation is possible, and indeed is investigated below in this paper, it would not have affected the number of spikes we reported in figures 1 and 2, as they were entirely recorded in dynamic clamp experiments.
+While a change in the synaptic strength in response to sensory stimulation is possible, and indeed is investigated below in this paper, it would not have affected the number of spikes we reported in figures 1 and 2, as they were recorded in dynamic clamp experiments.
 
-To make this clearer to the reader, we TODO!
+As described above, to make this point more clear, we now reworded this sentence:
+
+"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (flashes; Khakhalin et al.
+2014) would selectively suppress spiking in repsonse to shorter synaptic inputs."
 
@@
 
-We hope that the word "prefer" is intuitive enough to most readers; it is also way shorter than "responded with more spikes", or "produced more action potentials", which allows for easier writing.
-We also believe that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are usually a bit more relaxed when talking about cells, channels, receptors etc.
-
-Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is just our normal word use (we use this word 6 times in the paper), and not an allegory.
+We hope that the word "prefer" is intuitive enough to most readers, and it is also way shorter than "responded with more spikes", or "produced more action potentials", which allows for easier writing, and hopefully better reading.
+Realistically, we believe that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are intentionally a bit more relaxed when writing about cells, channels, receptors etc.
+Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is not an antropomorphic allegory, but just a normal word use.
+Overall, we use the word "prefer" 6 times in the paper, always in the same way, when comparing spiking responses to different stimuli.
 
@@
 
-We now removed this phrase from the main text.
+We removed this phrase from the main text.
 
@@
 If you would like us to numerically re-run any part of the analysis without a position adjustment, please let us know which part you would like to see.
-Also, all of our technical visualizations and analyses related to this adjustment are available for inspection at:
+All scripts that produce technical checks, visualizations, and analyses related to this adjustment are available for inspection at:
 https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/dynamic_other_vars.R
@@
 
-"Intrinsic spikiness" is no longer used.
+The expression "Intrinsic spikiness" is no longer used in the text.
 
-"Intrinsic excitability" is used as a name for the phenomenon, that in this particular study we assess mostly using the "spikness" variable, although arguably the number of spikes observed in current clamp experiments can also be considered a different quantification of the same variable.
-In the text, we say "intrinsic excitability" when we make inferences about the actual properties of the neuron, and "spikiness" when we are talking about the actual value we calculated to assess and quantify this intrinsic excitability.
+The expression "Intrinsic excitability" is now used only as a name for the general phenomenon, that technically may be probed with different alternative protocols and measures.
+In this  study, we mostly assess it using a more narrowly defined "spikness" variable, and then, towards the end, using a less informative measure of the number of spikes observed in current clamp experiments.
+In the text, we now consistely use "intrinsic excitability" when we make inferences about the actual properties of the neuron, and use "spikiness" when we talk about the actual value we calculated to assess and quantify intrinsic excitability.
 
@@
 
-> TODO: that is what we are suggesting in one of the paragraphs. Cite that.
+This may indeed explain some of the trends in the data, but unfortately, as we described above, recording of tadpole tectal reponses to sounds does not seem to be possible in our lab, and is fundamentally technically problematic in principle.
+We can only guess that stimuli so different as flashes, looms, and sound clicks, would produce different responses in the tectum, as their dynamics is drastically different, as they engage different circuits before they rich the tectum (retinal for visual stimuli, hindbrain for acoustic), which undoubtedly shapes the dynamics of tectal activation (based on Khakhalin 2014, Felch 2016, Truszkowski 2017, Khakhalin 2019).
+
+We now make this point more clear by referencing it in the beginning of the paper (as described above), and then again, at the very end of Discussion, by describing how our observations can be used to predict actual, and yet unobserved, activation of the tectum during multisensory stimulation in vivo:
+
+"Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro (Felch et al., 2016; Truszkowski et al., 2017), it would be likely to reduce peak activation in vivo."
 

### 2019-05-31 main.tex
Finished all responses + Discussion improved

@@
 And yet, with the possible exception of oscillatory networks \citep{marder2011,picton2018control}, the exact ways in which intrinsic plasticity contributes to network tuning, remain unclear.
-We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but we also know that biophysically, they often have the means to become tuned to different temporal patterns of activation \citep{branco2010dendritic,jarvis2018morphology,ohtsuki2018bursting}.
-Do they rely on this type of tuning in practice?
+We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but we also know that intrinsic properties affect neuronal tuning to different temporal patterns of activation \citep{azouz2000threshold,branco2010dendritic,fontaine2014threshold,jarvis2018morphology,ohtsuki2018bursting,zbili2019axonnav}.
+That begs the question: do neurons dynamically adjust this type of tuning in practice?
 
@@
 Circuits in the tectum can learn and reproduce temporal patterns to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which may be easier to achieve through intrinsic temporal tuning \citep{narayanan2008,beatty2014}.
-Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, and is a known target for intrinsic plasticity mechanisms \citep{bianchi2012}.
+Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, can support temporal tuning \citep{clay2012optimal,fontaine2014threshold,zbili2019axonnav}, and is a known target for plasticity mechanisms \citep{bianchi2012}.
 
-Specifically, we ask two questions about the properties of intrinsic plasticity in tectal networks.
-First, we check whether intrinsic plasticity in response to sensory stimulation is limited to changes in overall excitability, or whether it also retunes neuronal sensitivity to faster and slower inputs.
-Second, we ask whether intrinsic temporal tuning of tectal cells is coordinated with the typical length of synaptic currents they receive, or whether two types of tuning are independent.
-In our previously published large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and observed no signs of temporal tuning (ibid,  figures 2, 4).
-We argue however, that the current clamp protocol used in earlier studies was not adequate for the task, so in this paper we relied on a dynamic clamp technique.
+Specifically, we ask three questions about the properties of intrinsic plasticity in tectal networks.
+First, we test whether the intrinsic temporal tuning to either faster (more synchronous) or slower (asynchronous) inputs would change in response to sensory stimulation.
+Then, we ask whether intrinsic temporal tuning of individual tectal cells is coordinated with the typical length of synaptic currents they receive.
+Finally, we try to identify the mechanisms that may underlie temporal tuning variability.
 
-The main benefit of the dynamic clamp approach, compared to commonly used current step injections, is that it allows a more realistic simulation neuronal response to synaptic conductances \citep{prinz2004}.
-In dynamic clamp, the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time.
-This means that with dynamic clamp recordings we can excite a neuron in a controlled manner, but still allow both its voltage and transmembrane current to change, preserving feedback interactions between active currents and transient voltage-gated channels inactivation \citep{ma1996dynamic}, which may be an important mechanism for intrinsic temporal tuning \citep{platkiewicz2011}.
-Also, as a second methodological innovation, instead of relying on one type of sensory stimulation, here we used five different stimulation protocols, and compared their effects on intrinsic tuning.
+In our previously published large-scale census of tectal cells \citep{ciarleglio2015}, we observed no signs of intrinsic temporal tuning (figures 2, 4), and no interaction between intrinsic and synaptic phenotypes.
+We argue however, that the current clamp protocols used in earlier studies were not adequate for the task, so in this paper we rely on a dynamic clamp technique.
+The main benefit of the dynamic clamp, compared to commonly used current step injections, is that it allows a more realistic simulation of neuronal responses to synaptic conductances \citep{prinz2004}.
+In dynamic clamp, the current injected into the cell is adjusted in real-time, based on a predefined formula that depends on time and cell membrane potential.
+This means that with dynamic clamp recordings we can excite a neuron in a controlled manner, but still allow both its voltage and transmembrane currents to change, preserving feedback interactions between active currents and transient voltage-gated channels inactivation \citep{ma1996dynamic,zbili2019axonnav}, which is an important mechanism for temporal tuning \citep{branco2010dendritic,platkiewicz2011}.
+As a second methodological innovation, instead of relying on one type of sensory stimulation \citep{ciarleglio2015}, here we used five different stimulation protocols, and compared to each other their effects on intrinsic tuning.
 
@@
 
-First we asked whether our stimulation protocols caused any changes in intrinsic excitability of tectal neurons.
-From previous studies, we knew that in tadpoles exposed to four hours of LED flashes, tectal neurons became more excitable \citep{aizenman2003,ciarleglio2015}.
+First we checked whether our stimulation protocols caused any changes in intrinsic excitability of tectal neurons.
+From previous studies, we knew that in tadpoles exposed to LED flashes, tectal neurons became more excitable \citep{aizenman2003,ciarleglio2015}.
 However, the stimuli we used in the present study were weaker, and similar to those used in behavioral experiments \citep{khakhalin2014,james2015,truszkowski2017}.
-We presented a checkerboard pattern that inverted once a second either instantaneously (dubbed “Flash”; Figure 1C left), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares, dubbed “Looming”; Figure 1C right).
+We presented a checkerboard pattern that inverted once a second, for four hours; either instantaneously (dubbed “Flash”; Figure 1C left), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares, dubbed “Looming”; Figure 1C right).
 
@@
 
-After conditioning, we excised the brain, performed whole cell patch clamp on tectal neurons (Figure 1A), and counted spikes produced in dynamic clamp mode in response to simulated synaptic conductances of different durations and amplitudes (Figure 1B).
+After conditioning, we excised the brain, performed whole cell patch clamp on tectal neurons (Figure 1A), and counted spikes produced in response to dynamically simulated synaptic conductances (Figure 1B).
 We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits \textit{in vivo} (\citealt{xu2011,khakhalin2014,ciarleglio2015}; see Methods).
-Based on prior research, we expected neurons exposed to flashes (checkerboard inversions) to be more excitable, but contrary to our expectations, they were on average less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29).
+Based on prior research \citep{aizenman2003,ciarleglio2015}, we expected neurons exposed to instantaneous checkerboard inversions (flashes) to become more excitable, but surprisingly, they were on average less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29).
 (Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell id is used as a repeated measures factor; see Methods for a detailed description).
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25).
-This was likewise unexpected, as in the tadpole tectum, looming stimuli are known to elicit stronger responses compared to instantaneous inversions \citep{khakhalin2014}, yet the effect yielded by looming stimuli was weaker.
-To sum up, both the expected sign of the effect, and the relative
+This was likewise unexpected, as compared to flashes, looming stimuli are known to elicit stronger tectal responses \citep{khakhalin2014,khakhalin2019graph}, yet their effect on neuronal excitability was weaker, seemingly violating the principle of homeostatic plasticity \citep{pratt2007,turrigiano2007}.
 
-We then mapped the amplitude tuning of neurons (amplitude transfer function, or gain), by looking at how an increase in transmembrane conductance translated into increased spike output.
-Compared to control, neurons from animals exposed to visual stimuli had a flatter (constant or hill-shaped, rather than increasing) amplitude tuning curve (Fig 1D,E), as they did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming transitions respectively).
-The flattening of response curves seemed slightly more pronounced for flashes than for looming, but this difference was not significant (F(1,641)=3.5; p=0.06).
+We then mapped the amplitude tuning of neurons (their amplitude transfer function, or gain), by looking at how an increase in transmembrane conductance translated into increased spike output.
+Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E), as they did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming respectively, compared to control).
+%The flattening of response curves seemed slightly more pronounced for flashes than for looming, but this difference was not significant (F(1,641)=3.5; p=0.06).
 
 These results show that prolonged stimulation had an effect on intrinsic excitability, but its direction was opposite to what was previously described \citep{aizenman2003,ciarleglio2015}, as neurons became less excitable.
-Moreover, while looming stimuli are known to be more salient, both behaviorally and physiologically \citep{khakhalin2014}, they had a weaker long-term effect on neuronal excitability in comparison to less salient flashes.
+Moreover, while looming stimuli are known to be more salient, both behaviorally and physiologically \citep{khakhalin2014}, they had a weaker effect on neuronal excitability in comparison to less salient flashes.
 We conjecture that the difference in the direction of change is due to our stimuli being weaker than those used in earlier studies (see Discussion), and we further explore the difference between flashes and looming stimuli below.
@@
 
-We then examined whether different types of sensory activation would differentially reshape temporal intrinsic tuning in tectal neurons.
-As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs.
-Alternatively, shorter stimuli could reshape the network, making neurons better adjusted to working with short bursts of activation, as  previously described for synaptic processing \citep{aizenman2007} and recurrent activity in the tectum \citep{pratt2007,shen2011}.
+We then examined whether different types of sensory activation would differently reshape temporal intrinsic tuning in tectal neurons.
+As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (flashes; \citealt{khakhalin2014}) would selectively suppress spiking in response to shorter synaptic inputs.
+Alternatively, shorter stimuli could make neurons better adjusted to working with short bursts of activation \citep{stemmler1999information}, as  described for synaptic processing \citep{aizenman2007} and recurrent activity in the tectum \citep{pratt2007,shen2011}.
 
-Across input conductances of different lengths (100, 200, 500, and 1000 ms), neurons exposed to flashes and looming stimuli responded differently than in control (F(1, 677)=25.1; p=7e-7; and F(1,629)=12.0; p=6e-4 respectively).
-In control neurons, longer inputs typically evoked stronger spiking, whereas neurons from stimulated animals had flatter tuning curves, with a plateau, or even a decrease in spike number for longer conductance injections (Figure 1E).
-In essence, while control neurons preferred longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
+We found that compared to control, neurons exposed to flashes and looming stimuli had different response curves when tested across input conductances of different lengths (F(1, 677)=25.1; p=7e-7; and F(1,629)=12.0; p=6e-4 respectively).
+In control neurons, longer inputs (500 and 1000 ms) typically evoked stronger spiking than shorter inputs (100 and 200 ms), but neurons from stimulated animals had flatter tuning curves, with a plateau, or even a decrease in spike output for longer conductance injections (Figure 1E).
+In other words, while control neurons preferred longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
 This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, follow two different kinds of logic.
 The overall excitability is homeostatic, as neurons became less excitable in response to stronger stimulation.
-The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, which is the opposite of what one would expect for a purely homeostatic retuning.
-We chose to call this type of plasticity "adaptive", as presumably it means that after exposure to faster stimuli, neurons become more equipped to process faster patterns of activation \citep{stemmler1999information}.
+The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, making them more equipped to process faster, more synchronous patterns of activation \citep{stemmler1999information,fontaine2014threshold}.
 
@@
 
-While the optic tectum (homologous to superior colliculus in mammals) is often described as a primarily visual area, it is also involved in heavy multisensory computations \citep{stein2014}.
-In tadpoles, it integrates visual information with inputs from mechanosensory, auditory, and lateral line modalities \citep{deeg2009,pratt2009trigeminal,hiramoto2009,felch2016,truszkowski2017}, but the logic of this integration is still unclear.
+While the optic tectum (homologous to superior colliculus in mammals) is often described as a visual area, it is also involved in heavy multisensory computations \citep{stein2014}.
+In tadpoles, it integrates visual information with inputs from mechanosensory, auditory, and lateral line modalities \citep{deeg2009,pratt2009trigeminal,hiramoto2009,felch2016,truszkowski2017}, but the logic of this integration is unclear.
 We wondered whether acoustic stimuli would reshape intrinsic properties of tectal neurons, and whether this retuning would be similar to that produced by visual stimuli.
 
-To test this question, we exposed tadpoles to four hours of behaviorally salient “click” sounds \citep{james2015,truszkowski2017}, provided at the same frequency (every second) as visual stimuli in the first set of experiments.
-We found (Fig 1D, E) that exposure to startle-inducing sounds (group “Sound”) did not lead to significant changes in either average number of spikes (0.8$\pm$0.7 spikes; F(1,689)=1.7; p=0.2; n=28, 30), amplitude transfer function (F(1,689)=2.0; p=0.2), or temporal tuning curve (F(1,689)=2.0; p=0.2).
-This suggests that acoustic stimuli did not strongly activate tectal circuits during conditioning, despite being more behaviorally salient (for our stimuli, at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}).
-This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular \citep{pratt2009trigeminal,felch2016} and subcellular \citep{hiramoto2009} targets in the tectum, and thus can recruit tectal networks to a different extent.
+To test this question, we exposed tadpoles to four hours of behaviorally salient, startle-inducing “click” sounds \citep{james2015,truszkowski2017}, provided at the same frequency (every second) as visual stimuli in the first set of experiments.
+We found (Fig 1D, E) that exposure to these sounds (group “Sound”) did not lead to significant changes in either average number of spikes (0.8$\pm$0.7 spikes; F(1,689)=1.7; p=0.2; n=28, 30), amplitude transfer function (F(1,689)=2.0; p=0.2), or temporal tuning curve (F(1,689)=2.0; p=0.2).
+This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning, despite being more behaviorally salient (at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}).
+This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular targets in the tectum \citep{pratt2009trigeminal,felch2016,truszkowski2017}, and thus can recruit tectal excitatory and inhibitory networks to a different extent.
+Alternatively, acoustic stimuli may be inherently weaker in triggering plasticity effects in tectal neurons, as compared to visual inputs, they arrive at different subcellular compartments within the dendritic tree \citep{hiramoto2009,deeg2009}, which can affect their influence on neuronal plasticity \citep{richards2019dendritic}.
 
 We then combined visual and acoustic stimuli in two different ways and looked at the effects of multisensory stimulation on the intrinsic properties of tectal neurons.
-For some animals, we synchronized the instantaneous checkerboard inversions (flashes) with sound clicks (dubbed “Sync”), while for others we staggered visual and acoustic stimuli by half a period (500 ms; dubbed “Async”).
-We found (Fig 1D, E) that, after four hours of multisensory stimulation, tectal neurons were more excitable than after visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for sync and async respectively, across all testing conditions).
-However, compared to the “Flash” group, the tuning curves in multisensory groups were less flat, with a stronger effect in the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively).
-This suggests that on their own sound clicks had little effect on tectal excitability, but when added to visual flashes, sound clicks negated effects of retuning that visual stimulation would have had (Fig 2C).
-
-% Make this paragraph above more clear, lead the reader throught the tension.
-Also, add an interpretation below, and there say that it's either inhibition, or changes at the level of individual dendritic trees.
-Make it clear that this result WAS surprising.
-And if it's dendritic processing, then explain how it may help.
-
-% Here we may reference Bollmann 2009 back, to show that dendritic processing probably does happen here.
-
-% Citations that may be used, when talking about inhibition: and may also differentially recruit tectal inhibitory circuits \citep{liu2016,hamodi2016}.
-
-% Also reference Deeg with her independent intrinsic tuning (in the same neuron!) to visual and mechanosensory inputs (does it suggest a dendritic tree?)
+For some animals, we synchronized the instantaneous checkerboard inversions (flashes) with sound clicks (dubbed “Sync”), while for others, we staggered visual and acoustic stimuli by half a period (500 ms; dubbed “Async”).
+We found (Fig 1D, E) that multisensory stimulation suppressed excitability of tectal neurons less strongly than visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for Sync and Async respectively, compared to Flash, across all testing conditions).
+Moreover, both temporal and amplitude tuning curves in multisensory groups were less flat than in the Flash group, with a stronger effect in the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively).
+This suggests that while on their own sound clicks had little effect on tectal excitability, when added to visual flashes, they negated some of the retuning effects that visual stimulation would have had.
 
@@
 An illustration of how “Temporal tuning” and “Amplitude tuning” values were calculated.
-For the temporal tuning measure, the value of zero corresponds to linear dependency (blue line), positive values - to an accelerating, supralinear curve (red), and negative values - to a plateau-shaped curve (purple, yellow).
+For the temporal tuning measure, the value of zero corresponds to linear dependency (blue line), positive values - to an accelerating, supralinear curve (red), and negative values - to plateau- and hill-shaped curves (gray, orange, green).
 For amplitude tuning, higher values correspond to faster increase in spiking with increased conductance.
@@
 (\textbf{C}).
-Temporal tuning and average spikiness of neurons in different experimental groups; in each plot all neurons across all groups are shown in gray, while neurons from one target group are shown in color; means are shown as black dots; ellipses represent 95\% normal confidence regions.
+Temporal tuning and spikiness of neurons in different experimental groups.
+Neurons from each target group are shown in color, while all neurons from all groups are shown in light gray, as a reference; groups means are shown as black dots; ellipses represent 95\% normal confidence regions.
 Two outliers (top right corner) are brought within the axes limits.
@@
 Same data as in (C), shown as averages for each group, with 95\% confidence intervals.
-Black arrows show the effects of sound clicks, when they were added to control, and when they were added to “Flashes” to form two types of multisensory stimuli.}
+Black arrows show the effects of sound clicks, when they were added to control (red), and when they were added to "Flashes" (brown), to form two types of multisensory stimuli.}
 \end{figure*}
@@
 
-To visualize and interpret differences in neuronal tuning, we quantified each of the three aspects of intrinsic tuning (average spikiness, amplitude tuning, and temporal tuning) with one value per neuron (see Methods).
-We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value characterising the "temporal tuning" or adaptation index of each neuron (Figure 2A).
-The numerical values of these "tuning coefficients" are not easily interpretable, but they capture the character of tuning curves for each neuron (Figure 2A).
+To better visualize and interpret differences in neuronal tuning after different types of stimulation, we quantified three aspects of intrinsic excitability (average spikiness, amplitude tuning, and temporal tuning) with one value per neuron (see Methods).
+We used the mean number of spikes across all conditions as the measure of "spikiness"; the linear slope of the number of spikes as a function of conductance amplitude as the measure of "amplitude tuning", and the quadratic term of the curvilinear regression for the number of spikes as a function of input duration as the value to characterize the "temporal tuning" of each neuron (Figure 2A).
+These "tuning coefficients" capture the character of tuning curves for each neuron (Figure 2A).
 All three parameters differed across experimental groups: F(5,160)=3.1, p=0.01 for average spikiness (Figure 2C; see Methods for model description); F(5,160)=4.8, p=4e-4 for amplitude tuning (Figure 2B); and F(5,160)=3.6, p=4e-3 for temporal tuning (Figure 2C).
 
-A visual comparison of neuronal tuning in different experimental groups (Fig 2C) shows that acoustic stimulation had opposite effects when provided on its own (without visual stimulation) than when added to visual flashes.
-Compared to control neurons, cells exposed to sound had slightly lower amplitude tuning coefficients (flatter curve, Cohen’s d=$-$0.29), and more negative (curving down, d=$-$0.27) temporal tuning coefficients (Hotelling t-squared test p=0.2).
-When sounds were added to flashes, however, both transfer functions became less flat (d=0.65 and 0.26 for "Async" compared to “Flash”, for amplitude and temporal tuning respectively), and more like curves for control neurons (Hotelling test p=0.04).
-Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Figure 2D), but negated the effect of visual stimulation when combined with it.
-This may imply that multisensory integration in the tectum is dominated by inhibition (see Discussion).
-Note also that looming stimuli seemed to have weaker effects on neuronal tuning compared to flashes, both in terms of amplitude (d=0.44) and temporal tuning (d=0.22).
+A visual comparison of neuronal tuning in different experimental groups (Fig 2C) shows that acoustic stimulation had opposite effects when provided on its own (without visual stimulation), compared to when it was added to visual flashes.
+Compared to control neurons, cells exposed to sound clicks seemed to have lower amplitude (Cohen’s d=$-$0.29) and temporal (d=$-$0.27) tuning coefficients (Hotelling t-squared test p=0.2).
+When sounds were added to flashes, however, both tuning coefficients increased (d=0.65 and 0.26 for amplitude and temporal tuning respectively, "Async" compared to “Flash”), making neurons more similar to control neurons (Hotelling test p=0.04).
+Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Figure 2D), but it negated the effects of visual stimulation the two were combined.
+This effect is likely to be either a consequence of strong inhibitory recruitment during multisensory integration in the tectum \citep{liu2016,hamodi2016}, or a sign of highly non-linear interactions between acoustic and visual inputs within the dendritic trees of individual tectal neurons \citep{deeg2011,felch2016,truszkowski2017}.
 
-Describing neuronal tuning with only a few variables allowed us to compare cell-to-cell variability of tuning in different experimental groups.
-We found that this variability decreased as neurons were modulated away from the baseline (Bartlett test p=2e-9 for amplitude tuning, p=1e-9 for temporal tuning; Figure 2D).
+Somewhat similarly, looming stimuli seemed to have weaker effects on intrinsic properties, compared to flashes, both in terms of amplitude (d=0.44) and temporal tuning (d=0.22), despite them eliciting stronger responses in-vivo \citep{khakhalin2014,khakhalin2019graph}.
+This suggests that intrinsic retuning depends on stimuli synchronicity, rather than simply the total number of spikes generated by the network, as more synchronous stimuli (Flash, Sync) had stronger effects on tuning than comparable asynchronous stimuli (Async, Looming).
+
+% Here we may reference Bollmann 2009 back, to show that dendritic processing probably does happen here.
+
+Describing neuronal tuning with only a few variables also allowed us to compare cell-to-cell variability of tuning in different experimental groups.
+We found that, as it can be guessed from Figure 2D, this variability decreased as neurons were modulated away from the baseline (Bartlett test p=2e-9 for amplitude tuning, p=1e-9 for temporal tuning).
 Groups that were significantly different in average values also had different variances (F-test with p$<$0.05), such as Control vs.
@@
 Looming for both amplitude and temporal tuning.
-This expands on a finding in our previous study \citep{ciarleglio2015} that prolonged patterned stimulation reduces diversity of tuning profiles in the network, reshaping them according to the spatiotemporal characteristics of the stimulus, with stronger stimuli having stronger effects on tuning diversity.
+This expands on the findings of our previous study \citep{ciarleglio2015}, where we showed that prolonged patterned stimulation reduces diversity of tuning profiles in the network, reshaping them according to the spatiotemporal characteristics of the stimulus.
+We now show that stimuli that reshape the network stronger, also have a more restrictive effect on tuning diversity.
 
@@
 Both Sync and Async multisensory groups had larger early synaptic currents than the Control group (Tukey p=0.03 and 0.04; Cohen d=0.92 and 0.73 on log-transformed data respectively).
-The amplitude of late synaptic currents–produced by recurrent network activation (15-145 ms after the stimulus)–did not differ across groups.
+The amplitude of late synaptic currents produced by recurrent network activation (15-145 ms after the stimulus) did not differ across groups.
 
@@
 The synaptic current duration was different across treatment groups (Figure 3D; F(5,163)=6.3, p=2e-5).
-Cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24, and 304$\pm$40 ms, respectively), indicating that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye.
+Cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24, and 304$\pm$40 ms, respectively).
+This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum that remained unchanged.
+In this study, we did not perform a similar analysis for acoustic projection from the hindbrain.
 
@@
 We found that, \textit{on average}, in animals exposed to stronger sensory stimuli, neurons were more responsive to shorter synaptic inputs, and also received shorter synaptic currents, leading to a positive correlation between these values across experimental groups (Figure 3E; r=0.89, p=0.02, n=5).
-%This means that \textit{between} treatment groups, changes in synaptic and intrinsic properties were adaptively coordinated, and the stronger the average change in synaptic transmission, the more cells reshaped their intrinsic properties to adjust to this change.
 
@@
 It also means that the correlation of intrinsic and synaptic properties had opposite signs between-groups (Figure 3E; positive) and within-groups (Figure 3F; negative), which is a textbook case of a so-called "Simpson's paradox" in data analysis.
-
-% \citep{stemmler1999information}
-
-% , so if all cells from all groups were lumped together in one simple correlation analysis, there was correlation between these two variables (r=$-$0.07, p=0.4, n=151) (
 
@@
 We ran a stepwise generalized linear model selection analysis (R package stepAIC, \citealt{venables2013}) to explain the intrinsic tuning of cells recorded in all experimental groups through these eight variables.
-We found that the average spikiness (after compensation for position within the tectum; see Methods) was best described by a combination of sodium peak current (INa) and membrane resistance (Rm) variables, but these variables explained only 8\% and 2\% of cell-to-cell variance respectively (F(1,130)=11.3, and F(1,130)=4.5; Figure 3E).
+We found that the average spikiness (after adjustment for cell position within the tectum; see below) was best described by a combination of sodium peak current (INa) and membrane resistance (Rm) variables, but these variables explained only 8\% and 2\% of cell-to-cell variance respectively (F(1,130)=11.3, and F(1,130)=4.5; Figure 3E).
 Together, all eight cellular parameters described only 13\% of variance in average spikiness.
@@
 For amplitude tuning, the proposed best model included peak sodium current (INa: 6\%, F(1,163)=10.0) and sodium activation potential (VNa: 2\%, F(1,1,163)=3.5), with all eight variables accounting for 10\% of variance.
-This very low total explained variance suggests that while ionic currents and their activation potentials clearly affected intrinsic tuning of tectal cells, most cell-to-cell variability in intrinsic phenotypes stemmed from some other properties that were different between cells.
-In agreement with this assessment, the effect of experimental group on either mean spiking, temporal, or amplitude tuning curves remained significant even after compensating for all 8 intrinsic properties (sequential sum of squares analysis of variance p=0.03, 0.001, and 0.003 respectively), suggesting that changes in tuning across experimental groups was mediated by other factors.
+This very low total explained variance indicates that while ionic currents and their activation potentials clearly affected intrinsic tuning of tectal cells, most cell-to-cell variability in intrinsic phenotypes stemmed from some other properties that we did not measure in voltage-clamp experiments.
+In agreement with this assessment, the effect of experimental group on either mean spiking, temporal, or amplitude tuning curves remained significant even after compensating for all 8 intrinsic properties (sequential sum of squares analysis of variance p=0.03, 0.001, and 0.003 respectively).
 
@@
 
-The inability to predict spiking of tectal neurons through their isolated electrophysiological properties was unexpected, and stood in a seeming contradiction with our previous study \citep{ciarleglio2015}.
+The inability to predict spiking of tectal neurons from their isolated electrophysiological properties was unexpected, and stood in a seeming contradiction with our previous study \citep{ciarleglio2015}.
 Fortunately, in the current study, we recorded spiking traces in response to “classic” current steps (Figure 4C), which allowed a direct comparison between the results of current clamp and dynamic clamp protocols.
@@
 In agreement with \citep{ciarleglio2015}, spiking in current clamp experiments correlated with peak sodium (INa: r=0.42, p=2e-8, n=152) and stable potassium currents (IKs: r=0.39, p=2e-7), as well as activation potential for sodium current (VNa: r=0.24, p=0.02).
-Overall, the 8 intrinsic variables described above (Rm, Cm, three peak currents, and three activation potentials) explained 61\% of cell-to-cell variability in the maximal number of spikes from current clamp experiments (Figure 4E), comparable to 49\% reported in our previous study \citep{ciarleglio2015}, and noticeably higher than 13\% for dynamic clamp experiments (Figure 4F).
+Together, the 8 intrinsic variables described above (Rm, Cm, three peak currents, and three activation potentials) explained 61\% of cell-to-cell variability in the maximal number of spikes from current clamp experiments (Figure 4E), which is comparable to 49\% reported in \citep{ciarleglio2015}, and noticeably higher than 13\% for dynamic clamp experiments (Figure 4F).
 
-We can therefore conclude that our set of eight cellular parameters can better predict spiking during current step injections (61\% of variance) than in dynamic clamp experiments (13\% of variance).
-This suggests the existence of internal properties that strongly affect spiking in dynamic clamp experiments, but are inaccessible through standard current and voltage step protocols (see Discussion).
-Our hypothesis is indirectly supported by two more observations: that of the eight cellular parameters only one was significantly (p$<$0.05) different across treatment groups (NaV: F(5,175)=3.7, p=0.003), and that the number of spikes detected in current clamp experiments did not differ across experimental groups (F(5,165)=0.8, p=0.6).
+We can therefore conclude that our set of eight cellular parameters can much better predict spiking during current step injections (61\% of variance), compared to more physiologically realistic dynamic clamp experiments (13\% of variance).
+This suggests the existence of intrinsic properties that strongly affect spiking in dynamic clamp experiments, but are inaccessible through simple voltage step protocols, such as the amount of voltage-gated channels inactivation (\citealt{zbili2019axonnav}; see Discussion).
+Our hypothesis is also indirectly supported by the observation that of only one out of eight cellular parameterswas significantly (p$<$0.05) different across treatment groups (NaV: F(5,175)=3.7, p=0.003), and that the number of spikes detected in current clamp experiments did not differ across experimental groups (F(5,165)=0.8, p=0.6).
 
@@
 
-In all analyses presented above, we adjusted cell properties for rostro-caudal and medio-lateral position of each cell within the tectum, as in tadpoles both intrinsic \citep{hamodi2014} and synaptic properties \citep{wu1996,khakhalin2012} are known to differ between older (rostro-medial) and younger (caudal, lateral) parts of the developing tectum.
-In this study, most cell properties we measured correlated (p$<$0.05, after correction for treatment group differences) with either medial or rostral position within the tectum (medial: membrane capacitance r=$-$0.17, membrane resistance r=0.25, sodium current activation potential r=$-$0.30, stable potassium current r=$-$0.16, early synaptic amplitude r=$-$0.22, synaptic current duration r=0.29; rostral: peak sodium current r=0.18, late synaptic amplitude r=0.11; n between 168 and 183).
+In all analyses presented above, we adjusted cell properties for rostro-caudal and medio-lateral position of each cell within the tectum, as in tadpoles both intrinsic \citep{hamodi2014} and synaptic properties \citep{wu1996,khakhalin2012} differ between older (rostro-medial) and younger (caudal, lateral) parts of the developing tectum.
+Most cell properties we measured in this study correlated (p$<$0.05 after adjustment for treatment group differences) with either medial or rostral position within the tectum (medial: membrane capacitance r=$-$0.17, membrane resistance r=0.25, sodium current activation potential r=$-$0.30, stable potassium current r=$-$0.16, early synaptic amplitude r=$-$0.22, synaptic current duration r=0.29; rostral: peak sodium current r=0.18, late synaptic amplitude r=0.11; n between 168 and 183).
 Curiously, neither of the three measures of intrinsic tuning (average spikiness, temporal tuning, and amplitude tuning) correlated with position (p$>$0.1, n=168).
-This may suggest that while low-level properties of tectal cells depended on their age, their spiking phenotypes were largely age-independent.
-Thus, different cells seemed to achieve similar spiking behaviors through different combinations of underlying parameters, relying on the principle of “parameter degeneracy” \citep{prinz2004degeneracy,drion2015}.
+This seems to suggest that while low-level properties of tectal cells depended on their developmental age, their spiking phenotypes were age-independent.
+It means that different cells achieved similar spiking behaviors through different combinations of underlying parameters, relying on the principle of “parameter degeneracy” \citep{prinz2004degeneracy,drion2015}.
 
@@
 We can, however, offer two working hypotheses that may explain these results.
-As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic current inactivation in different cells.
+As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic current inactivation in different cells \citep{azouz2000threshold,fontaine2014threshold}.
 One obvious way of tuning ionic channel inactivation would be for every cell to modulate sodium or transient potassium currents via channel phosphorylation, or by changing the expression of different channel variants, to shift their inactivation dynamics \citep{frank2003nachannels,goldwyn2018a_current}.
-To test this hypothesis, one would need to induce changes in temporal tuning similarly to how we did in this paper, pharmacologically isolate different ionic currents, and directly measure their inactivation dynamics.
+To test this hypothesis, one would need to induce changes in temporal tuning similarly to how we did in this paper, pharmacologically isolate different ionic currents, and directly measure their inactivation dynamics \citep{zbili2019axonnav}.
 
-Another hypothetical mechanism that can underlie our current results is inspired by a yet unexplained finding from our earlier study \citep{ciarleglio2015}: namely, that one of the key electrophysiological parameters regulating excitability of tectal cells is cell membrane capacitance (Cm).
-Traditionally, cell capacitance is thought of as a relatively immutable parameter that describes cell morphology, and can even be used to estimate its size.
-Yet, in the tadpole tectum, we found it to drop both with age and after strong sensory stimulation, even though cells don't seem to change their visual appearance (\citealt{ciarleglio2015}, Figure 7D).
+Another hypothetical mechanism that can underlie our results is inspired by a yet unexplained finding from our earlier study \citep{ciarleglio2015}: namely, that one of the key electrophysiological parameters regulating excitability of tectal cells is cell membrane capacitance (Cm).
+Traditionally, cell capacitance is thought to be a relatively immutable parameter that describes cell morphology, and can even be used to estimate cell size.
+Yet, in the tadpole tectum, we found it to decrease both with age and after strong sensory stimulation, even though cells don't seem to change their visual appearance (\citealt{ciarleglio2015}, Figure 7D).
 An intriguing possibility is that these changes in cell capacitance may be due to electric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic tree, soma, and axon initial segment \citep{bollmann2009,jarvis2018morphology}.
-This differential uncoupling may be achieved through either minor changes in cell morphology \citep{leterrier2018axon}, or through target modulation of sodium and potassium channels at key points between the compartments, which would introduce shunting, and so strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.
+This differential uncoupling may be achieved through either minor changes in cell morphology \citep{leterrier2018axon}, or through target modulation of potassium channels at key points between the compartments, to introduce shunting \citep{murakoshi1997kv2phosphorilation}, and strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.
 One way to test this hypothesis could be to perform immunostaining of cleared tectum preparation after sensory stimulation, and if any changes in the distribution of sodium and potassium channels is discovered, to validate the effect of these changes in a computational model.
@@
 This difference may be interpreted in two ways.
-One possible interpretation is to assume that dynamic clamp in the soma provided a bad approximation of peripheral synaptic inputs, as space clamp error is more pronounced for fast voltage fluctuations than for constant current injection \citep{spruston1993,prinz2004}.
-We find this hypothesis unlikely, however, as dynamic clamp responses were consistently different in animals with different sensory history, which suggests, at the very least, that we have captured some important aspects of intrinsic diversity, even if our estimations were biased.
+One approach would be to argue that dynamic clamp in the soma offered a bad approximation of peripheral synaptic inputs, as space clamp error is expected to be more pronounced for fast voltage fluctuations than for constant current injections \citep{spruston1993,prinz2004}.
+We find this hypothesis unlikely, however, as our dynamic clamp responses were consistently different in animals with different sensory history, which suggests that we have captured some important aspects of intrinsic diversity, even if our estimations were biased.
 
-It seems more reasonable however, that intrinsic excitability of tectal cells is shaped by mechanisms that are not easily accessible by standard slow voltage and current clamp protocols, such as axon initial segment relocation, or targeted modulation of axonal voltage-gated channels we described above \citep{grubb2010activity,kole2012}.
+Another, and in our opinion more likely explanation, is that intrinsic excitability of tectal cells is shaped by mechanisms such as axon initial segment relocation, or targeted modulation of voltage-gated channels \citep{grubb2010activity, kole2012}, that both are not easily accessible by standard slow voltage and current clamp protocols.
 In cells with excitable dendrites, channels of the axon initial segment may constitute only a small fraction of all voltage-gated channels, yet have a disproportionately large effect on the spiking output of the cell, and on its temporal tuning \citep{kole2007,hamada2016}.
-Furthermore, prolonged current injections in the soma are likely to quickly inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channel recovery during burst firing \citep{popovic2011,kole2012}.
-Conversely, this effect would still affect spiking in more realistic, fast dynamic clamp experiments.
+Furthermore, prolonged current injections in the soma are likely to quickly inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channel recovery during burst firing \citep{popovic2011,kole2012,fontaine2014threshold}.
+At the same time, these effects would still strongly affect spiking in more realistic, fast dynamic clamp experiments \citep{clay2012optimal,zbili2019axonnav}.
 
@@
 These changes in intrinsic temporal tuning would also reshape the connectivity of tectal networks, as fast-inactivating cells would not support short recurrent loops within the network, thus promoting long-ranged polysynaptic connectivity \citep{fiete2010stdp,clopath2010stdp}.
-Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it would be likely to reduce peak activation in vivo.
+Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it is be likely to reduce peak activation in vivo.
 
@@
 But then, he used LED that we now know (Ciarleglio 2015) to have an opposite effect on intrinsic excitability, so I don't think Dong 2009 was really a verification of our prediction.
-Even though the experiments seem similar, there are too many unknowns to directly compare them.
+Even though the experiments seem similar, there are way too many unknowns to directly compare them.
 
@@
 Electrodes were placed in an Axon headstage (Molecular Devices, Sunnyvale, CA), controlled by a motorized micromanipulator (MX7600, Siskiyou, Grants Pass, OR).
-Whole cell patch clamp was established as usual \citep{ciarleglio2015}, with typical final access resistance of 30 MOhm, and membrane resistance Rm of 0.33 GOhm.
+Whole cell patch clamp was established as usual \citep{ciarleglio2015}, with typical final access resistance of 30 MOhm, and membrane resistance Rm of 3.2 GOhm.
 Signals were measured with an Axon Instruments MultiClamp 700B amplifier (Axon Instruments, Foster City, CA), filtered with a 5 kHz band-pass filter, and digitized at 10 kHz a CED Power1401-3 Digitizer (Cambridge Electronic Design; Cambridge, England).
@@
 To quantify the “shape” of spiking responses to conductances of different duration (temporal tuning), we encoded curve duration as an ordinal value (from 1 to 4) for every cell, fit the spike data as a function of response duration with a quadratic formula ($y = ax^2 + bx +c$), and used the quadratic coefficient $a$ as the measure of response non-linearity.
-While the units and absolute values of this coefficient are not interpretable, it captures the shape of the response curve well, and allows for easy comparisons between cells (Figure 2A).
+While the numerical values of this dimensionless coefficient are not easily interpretable, it captures the shape of the response curve well, and allows for easy comparisons between cells (Figure 2A).
 The case of $a=0$ corresponds to spiking output linearly increasing with duration increase; $a>0$ means supralinear preference for long conductances (curving up); about $-0.25<a<0$ corresponds to a plateau-shaped curves, while $a<-0.25$ would mean heavy spike inactivation for longer conductance injections.
@@
 For the comparison of summative descriptions of tuning, and other electrophysiological cell parameters between experimental groups, we report p-values of fixed effect sequential sum of squares linear model (ancova), in which rostral and medial coordinates of each cell within the tectum are included as covariates, and experimental group is used as the main factor.
-All comparisons and correlations between cell parameters are performed on values corrected for cell position within the tectum.
-Position correction was based on a two-way linear regression model without interaction.
-For five variables that were distributed extremely non-normally, this correction for position was performed on transformed values (original values were transformed to normally distributed proxy values, linearly adjusted, and then transformed back): for early and late mean synaptic amplitudes we used a transformation $a'=log(1-a)$; for the variability of synaptic amplitudes $s'=log(1+s)$; and for temporal tuning $y_t' = \sqrt{y_t}$ .
+All comparisons and correlations between cell parameters are performed on values adjusted for cell position within the tectum.
+Position adjustment was based on a two-way linear regression model without interaction.
+For five variables that were distributed extremely non-normally, this adjustment for position was performed on transformed values (original values were transformed to normally distributed proxy values, linearly adjusted, and then transformed back): for early and late mean synaptic amplitudes we used a transformation $a'=log(1-a)$; for the variability of synaptic amplitudes $s'=log(1+s)$; and for temporal tuning $y_t' = \sqrt{y_t}$ .
 Where appropriate, we performed the analysis with and without extreme outliers, and reported the difference.

### 2019-06-03 reviews and responses.md
Responses to reviewers: polished

--- 2019-05-31 reviews and responses.md
@@
 
-We replaced this sentence with the following sentence: "This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular (Pratt and Aizenman, 2009; Felch et al., 2016) and subcellular (Hiramoto and Cline,2009) targets in the tectum, and thus can recruit tectal networks to a different extent.
-
 > Also, how can having different subcellular targets could explain the results? This concept needs to be
@@
 
-TODO: add an explanation here that we addressed this issue in the next paragraph, when the effects of multisensory stimulation are discussed. Because those WERE suprising.
+We replaced this sentence with the following one: "This was not necessarily surprising, as mechanosensory and visual inputs have different cellular targets in the tectum (Pratt and Aizenman, 2009; Felch et al., 2016; Truszkowski et al., 2017), potentially leading to different recruitment of tectal excitatory and inhibitory circuits.
+Acoustic stimuli may also be inherently weaker than visual stimuli in triggering plasticity effects in tectal neurons, as they arrive at different compartments within the dendritic tree (Hiramoto and Cline, 2009; Deeg et al., 2009), which may shape their influence on neuronal plasticity (Richards and Lillicrap, 2019)."
+
+Here, the actual rationale for the second explanation (a difference in subcellular targets) is that inputs to different parts of the dentritic tree can trigger action potentials of different shape, and differentially affect calcium dynamics in the neuron, which, together with non-linear processing in dendrites may make different types of inputs unequal in terms of their effects on neuronal activity, and neuronal tuning, respectively.
+Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, and the impact of inputs to the apical dendrites of pyramidal cells in the cortex.
+We feel, however, that this topic is really deep, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition to it by short sentence and a good recent reference.
 
@@
 special type of sensory network?
+
+Technically, even two neurons form a network (and a true mathematician would probably argue that even one neuron forms a network!), yet the tectal network is a relatively large one, with broad recurrent excitation, and in which different parts of the sensory input are processed in parallel.
+To subtly remind the reader about that, we used a word "distributed", as in "distributed computations", as opposed to more local and covergent networks, such as, for example, the Mauthner cell network in the hindbrain.
+This word is often used in writing (a Google Scholar search for `"distributed network" brain` returns 27000 hits), but admittedly it is not a precisely defined term, but rather a useful qualifier.
+If you think that this word is not appropriate here, please let us know, and we will remove it.
 
@@
 
+This was unexpected as intrinsic plasticity is typically described as a homeostatic mechanism, and thus a stronger stimulus could, in principle, cause stronger suppression of spiking.
+To make this point more clear, we now changed this sentence:
+
+"This was likewise unexpected, as compared to flashes, looming stimuli are known to elicit stronger tectal responses (Khakhalin et al., 2014; Khakhalin, 2019), yet their effect on neuronal excitability was weaker, seemingly in contradiction with the principle of homeostatic plasticity (Pratt and Aizenman, 2007; Turrigiano, 2007)."
+
 ### Major
@@
 
-In the submitted document, these lines said:
+In the originally submitted pdf, lines 2 to 5 read:
 
@@
 temporal intrinsic tuning in tectal neurons. As changes in intrinsic properties seemed  
-homeostatic (increased activation led to reduced spiking), by the same logic, one could..."
+homeostatic (increased activation led to reduced spiking), by the same logic, one could
+expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs."
 
-TODO: make clear that we are not talking about synaptic changes after the fact, but during the stimulation. And that we kind of know from Khakhalin 2014.
+Here we are not implying that our conditional stimuli altered the pattern of synaptic inputs; rather, we refer to the fact that _during_ the stimulation, shorter stimuli (such as instantaneous flashes, which technically makes them the shortest stimuli possible) would cause faster visual inputs to the tectum, compared to longer, continuous transitions (second-long looms).
+Within this study, we did not measure actual synaptic responses in the tectum during conditioning, but from previous studies, we know that responses to flashes are indeed much shorter than responses to looming stimuli (Khakhalin 2014, Khakhalin 2019).
+We refer to these studies in the beginning of the "Results" section, and then again in the "Methods".
+
+For page 5, we now changed the wording, to make this logic clearer.
+
+"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; Khakhalin et al.
+2014) would selectively suppress spiking in response to faster synaptic inputs."
 
@@
 
-All our measurements of the number of spikes relied on the dynamic clamp experiments, that used simulated, and not real synaptic inputs.
-It means that any changes in spiking we observed in the previous section of the results is necessarily coming from the change in intrinsic properties.
-While a change in the synaptic strength in response to sensory stimulation is possible, and indeed is investigated below in this paper, it would not have affected the number of spikes we reported in figures 1 and 2, as they were entirely recorded in dynamic clamp experiments.
+Our measurements of spiking output relied on dynamic clamp experiments, in which we used simulated synaptic inputs, and not real synaptic stimulation.
+It means that any changes in spiking output we report in this paper are necessarily coming from the change in intrinsic properties.
+While a change in the strength of synaptic inputs  in response to sensory stimulation is possible, and indeed was observed and investigated in later sections of this paper, it would not have affected the number of spikes we reported in figures 1 and 2, as they were recorded in dynamic clamp experiments.
 
-To make this clearer to the reader, we TODO!
+With the new wording of this sentence, we tried to make this point more clear:
+
+"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; Khakhalin et al.
+2014) would selectively suppress spiking in response to faster synaptic inputs."
 
@@
 
-We hope that the word "prefer" is intuitive enough to most readers; it is also way shorter than "responded with more spikes", or "produced more action potentials", which allows for easier writing.
-We also believe that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are usually a bit more relaxed when talking about cells, channels, receptors etc.
-
-Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is just our normal word use (we use this word 6 times in the paper), and not an allegory.
+We hope that the word "prefer" is intuitive, and it has a benefit of being way shorter than "responded with more spikes", or "produced more action potentials", which hopefully makes reading easier.
+Realistically, we hope that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are intentionally a bit more relaxed when writing about cells, channels, receptors etc.
+Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is not an antropomorphic allegory, but just a normal word use.
+Overall, we use the word "prefer" 6 times in the paper, always in the same way: when comparing spiking responses to different stimuli, to describe the stimulus that produced sronger outputs in a given set of neurons.
 
@@
 
-Unfortunately, recording of tectal reponses to sounds in tadpoles does not seem to be possible at present, not just in our lab (where we don't posess the technical capability to perform in-vivo experiments), but in most labs.
-Technically, the problem amounts to two limitations: one, to record from a tadpole, one has to paralyze it with a nicotinic receptor anatagonist, which seems to disrupt hearing.
-Second, even if this limitation is overcome, the sounds has to be strong enough to stimulate the inner ear, but weak enough not to disrupt a recording.
-Conceivably, both challenges may be overcocme with the use of high speed calcum imaging in freely moving tadpoles, but this is also challenging, and to our knowledge no lab has attempted these recordings yet.
+Unfortunately, electrophysiological recording of tectal reponses to sounds in tadpoles does not seem to be technically feasible, not just in our lab (where we don't even have the technical capability to perform in-vivo experiments), but in most labs.
+From the technical point of view, the problem amounts to two limitations: one, to record from a tadpole, one has to paralyze it with a nicotinic receptor anatagonist, which seems to disrupt hearing.
+Second, even if this limitation could be overcome, the sounds have to be strong enough to stimulate the inner ear, but weak enough not to mechanically disrupt the recording.
+Conceivably, both challenges may circumvented with the use of high speed calcum imaging in freely moving tadpoles, but to our knowledge no lab has attempted these recordings yet.
 
@@
 
-We now removed this phrase from the main text.
+We removed this phrase.
 
@@
 This is what we call selective potentiation of direct inputs, as opposed to recurrent inputs.
-We do not claim that mechanosensory inputs did not change, as we have not recorded auditory responses in this study (recordings of auditory responses are considerably more difficult; see Felch 2016).
+We do not claim that mechanosensory inputs did not change, as we have not recorded auditory responses in this study (recording of auditory responses is considerably more difficult; see Felch 2016).
 
-To make sure that we are not misunderstood by the reader, we replaced the original sentence with the following two sentences: "This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum that remained unchanged.
-In this study, we did not perform a similar analysis for acoustic projections from the hindbrain."
+To make sure that we are not misunderstood by the reader, we replaced the original sentence with the following two sentences: "This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum, that remained unchanged.
+In this study, we did not probe changes in acoustic and mechanosensory projections from the hindbrain."
 
@@
 
-Yes, as we answered above, we now don't use quotation marks for any of the words that aid writing and understanding, so "preferred" consistently means "responded preferably", or "produced stronger responses".
+As described above, we now don't use quotation marks for any basic words, so "preferred" is used without quotation marks, and consistently means "responded preferably", or "produced stronger responses".
 
@@
 
-We did not measure action potential thresholds, as we knew from the previous study (Ciarleglio Khakhalin 2015) that potential threshold measurements in tadpole tectal neurons are unreliable, in the sence that they strongly depend on the current that is used to evoke the spikes; this is almost certainly due to rapid Na channels inactivation.
+We did not measure action potential thresholds, as we know from the previous study (Ciarleglio Khakhalin 2015) that threshold measurements in tadpole tectal neurons are highly sensitive to the current that is used to evoke the spikes, due to rapid Na channels inactivation (Azouz 2000; Fontaine 2014).
 
@@
 
-The linear regression is used because it is the simplest way to compensate for a confounding variable (see ANCOVA, or linear models with confounding variables in general).
-Linear models are the "default" approach in statistics, and are typically used when the exact relation between two variables is unknown, or when the amount of noise is so high that practically there is no difference between linear and conceivable curvilinear regressions.
-Both situations apply here.
+It was a mental typo: we should have used the standard term "adjusted for position"; thank you for noticing that!
+We performed a standard adjustment for a covariate, as used in ANCOVA and other types of general linear model analysis.
+We used a linear model, as it is a "default" approach when the exact relation between two variables is unknown, and the amount of noise is high enough to make the difference between linear and curvilinear regressions negligible (both cases apply here).
 
-There is no way for us to determine whether our adjustment is "accurate", as there is no experimental way to make more caudal (and thus younger) cells in the tectum older.
-This situation is not unique however, as it arises in any study that uses linear models, in any field, from ecology to social sciences.
+There is no way for us to determine whether our adjustment is "accurate", as there is no clear way to make more caudal (and thus developmentally younger) cells in the tectum older.
+This situation is not unique however, as it arises in any field that uses linear models, from ecology to social sciences.
 When running a study in a human population, if a variable of interest depends on age, one would typically adjust for age by including age as a covariate in the linear model.
 Here we perform the same standard procedure.
-After rereading the manuscript, we realized that we used terms "adjustment", "correction", and, in one case, "compensation" interchangeably, which might have led to some confusion.
-To stress that we are talking about a basic statistical technique of covarate elimination, we now consistently use the term "adjustment" throughout the manuscript.
+After rereading the manuscript, we realized that we used terms "adjustment", "correction", and, in one case, "compensation" interchangeably, which obviously led to confusion.
+We now consistently use the term "adjustment" throughout the manuscript.
 
-In the paper, we do not report how the data would have looked without this adjustment for covariates, as it would not be statistically sound to run a linear model with a known covariate without including it.
-In most cases, it may be expected to underestimate effects for analyses across groups (as the effect of the covarate would be included in the error), and overestimate effects for explanatory linear models in the second half of the paper (as the covariate would contribute to both the dependent, and the independent variables in the model).
-For each particular comparison, however, both d, F and p values would differ by a small random value.
+In the paper, we do not report how the data would have looked without an adjustment for covariates, as it would not be statistically sound to run a linear model with a known covariate without including this covariate in the analysis.
+For this response, we ran some of the analyses without a covariate, and did not find qualitative differences, although numerical values of "uncorrected" d, F and p values were of course different from those reported in the paper.
 For example, when the measure of "spikness" (one of the three tuning parameters) is compared across groups, a correct analysis with adjustment for position (`smean~rostral+medial+group`) produces a p-value of 0.01.
 Without adjustment (`smean~group`) we get a p-value of 0.03.
-For temporal tuning, correct analysis (`sbend~rostral+medial+group`) gives p=0.0304, and if covariate is left unadjusted (`sbend~group`) we get p=0.029.
-Similarly, for amplitude tuning, we get p=0.00209 for correct analysis, and p=0.0024 for unadjusted analysis.
-For the analyses in which temporal tuning and ampliltude coefficients were explained through intrinsic parameters, the optimal models were not qualitatively different between adjusted and unadjusted data, but all values in the table were slightly different.
+For temporal tuning, correct analysis (`sbend~rostral+medial+group`) gives p=0.030, and if covariate is left unadjusted (`sbend~group`) we get p=0.029.
+For amplitude tuning, we get p=0.0021 for correct analysis, and p=0.0024 for unadjusted analysis.
+For the analyses in which temporal tuning and ampliltude coefficients were explained through intrinsic parameters, optimal models were not different between adjusted and unadjusted data, but all values in the table were slightly different.
+If you would like us to numerically re-run any other part of the analysis without a position adjustment, please let us know which part you would like to see.
+Also, all scripts that produce technical checks, visualizations, and analyses related to this adjustment are available for inspection at:
 
-If you would like us to numerically re-run any part of the analysis without a position adjustment, please let us know which part you would like to see.
-Also, all of our technical visualizations and analyses related to this adjustment are available for inspection at:
 https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/dynamic_other_vars.R
@@
 
+Thank you for making us get more consistent here!
 In this updated version, we consistently use "spikiness" as a name for the variable that is for the first time introduced in Figure 2C.
-For earlier results section, we replaced "spikiness" with "average number of spikes", and in all instances when we talked about the general idea of neuronal excitability, we called it neuronal excitability.
-As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
-
-"Intrinsic spikiness" is no longer used.
-
-"Intrinsic excitability" is used as a name for the phenomenon, that in this particular study we assess mostly using the "spikness" variable, although arguably the number of spikes observed in current clamp experiments can also be considered a different quantification of the same variable.
-In the text, we say "intrinsic excitability" when we make inferences about the actual properties of the neuron, and "spikiness" when we are talking about the actual value we calculated to assess and quantify this intrinsic excitability.
+When writing about the average number of spikes, we now just call it the "average number of spikes", and not "spikiness".
+As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text, even though strictly speaking it is a sentence about intrinsic excitability.
+The expression "intrinsic spikiness" is no longer used.
+The expression "intrinsic excitability" is now used only as a name for the underlying property of the neuron, that may be probed with different alternative protocols and measures.
+In this study, we mostly assess intrinsic excitability using a more narrowly defined "spikiness" variable, but towards the end of the paper, we also compare it to a less informative measure of the number of spikes observed in current clamp experiments.
+We use "intrinsic excitability" when we make inferences about the actual properties of the neuron, and use "spikiness" when we talk about the actual numerical value calculated to assess and quantify intrinsic excitability.
 
@@
 Thank you for catching this error!
-We had an order of magnitude typo here, and the average membrane resistance was in fact 3.2±1.5 GOhm.
-This value is a bit higher than reported earlier (1.2±0.8 GOhm in Ciarleglio Khakhalin 2015; about 1.1 in Khakhalin 2011), but within what can be reasonably expected for healthy neurons of this size.
-To make sure that this number reflects our observations, for the purpose of this response, we verified this value by reanalyzing our data offline, and obtained a similar estimation for the average membrane resistance (2.9±1.4 GOhm).
+We had an order of magnitude typo here, as the average membrane resistance was in fact 3.2 GOhm.
+This value is a bit higher than reported in earlier studies (1.2±0.8 GOhm in Ciarleglio Khakhalin 2015; about 1.1 in Khakhalin 2011), but within what can be reasonably expected for healthy neurons of this size.
+To make sure that this number is right, for the purpose of this response, we also verified it by reanalyzing our data offline, and obtained a similar estimation for the average membrane resistance (2.9±1.4 GOhm).
+
 We have several reasons to believe that the cells included in this study were healthy.
-First, the access resistances obtained were good (30±14 MOhm, which is similar to benchmark 50±23 in Ciarleglio Khakhalin 2015, and about 20-30 MOhm in Khakhalin 2011), indicating that higher membrane resistance is not likely to be due to poor access.
-Second, our neurons reliably produced spikes in current clamp mode, and active currents in response to membrane depolarization in voltage clamp mode, and the quantification of these active conductances yielded numbers similar to those reported before (Ciarleglio Khakhalin 2015).
+First, the access resistances obtained were good (30±14 MOhm, which is similar to benchmarks of 50±23 in Ciarleglio Khakhalin 2015, and about 20-30 MOhm in Khakhalin 2011), indicating that higher membrane resistance is not likely to be due to poor access.
+Second, our neurons reliably produced spikes in current clamp mode, and active currents in response to membrane depolarization in voltage clamp mode.
+Moreover, our quantification of these active conductances yielded numbers similar to those reported before (Ciarleglio Khakhalin 2015).
 The quality of voltage clamp, as judged by the absence of escaping active currents in IV protocols, was good in the majority of neurons (82% of all neurons recorded).
-Finally, a few cells that had their membrane resistance change drastically during the recording session, were discarded at the data collection stage.
-We did not measure the resting potential directly, but measured the holding current necessary to bring the cell to -60 mV in voltage clamp mode, and the mean value of this I_hold value was -8.2±4.8 pA, which is not higher tha what was previously recorded in the literature (19.8±16.6 in Ciearleglio Khakhalin 2015).
+Finally, a few cells that had their membrane resistance change drastically during the recording, were discarded at the data collection stage, and not included in this study.
 
-Overall, these arguments make us believe that the quality of our patches was good enough to draw the conclusions reported in the study.
-Note that all data for all cells is available at the following address:
+We did not measure the resting membrane potential directly, but measured the holding current necessary to bring the cell to -60 mV in voltage clamp mode, and the mean value of this I_hold value was -8.2±4.8 pA, which is similar (most importnatly, not higher) than what was previously reported in the literature (-19.8±16.6 in Ciearleglio Khakhalin 2015).
+
+Together, these arguments make us believe that the quality of our patches was good enough to draw the conclusions reported in the study. Note that all data for all cells is available here:
+
 https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/Data/data_mainInput.txt
-In this dataset, groups "Naive", "SlowF", and "SlowC" should be ignored, as they were not included in the study.
-Note also that github doesn't show columns correctly, so if you want to inspect the data, we recommend that you download it and open it in a spreadsheet.
 
-As the mistake your noticed (thank you again for being so thorough!) was a typo in the text, and not a mistake in the data, it does not affect any other calculations reported in this paper.
+In this full dataset, groups "Naive", "SlowF", and "SlowC" should be ignored, as they were not included in the study.
+Note also that if you open this file on github, the columns may look misplaced, as github does not render tab-separated files correctly, so if you want to inspect the data, we recommend that you download it and open it in a spreadsheet.
+
+As the mistake your noticed (thank you again for being so thorough!) was a typo in the text, and not a mistake in the data, it does not affect any calculations reported in this paper.
 
@@
 
-At least for high-spiking neurons, the answer to this question can actually be inferred from Figure 1D: those curves that are placed high on the graph for duration of 500 ms, also tend to remain high for 1000 ms, indicating that high-spiking neurons tend to be high-spiking across the range of durations.
+At least for high-spiking neurons, the answer to this question can be inferred from Figure 1D: those curves that are placed high on the graph for duration of 500 ms, also tend to remain high for 1000 ms, indicating that high-spiking neurons tend to be high-spiking across the range of durations.
 Numerically, the correlation coefficient between the average number of spikes in response to 500 and 1000 ms, across all neurons, is r=0.94.
-Arguably, this was to be expected as intrinsic excitability of neurons (whether the neuron is spiky or not) is a much stronger feature than the temporal tuning.
+This is to be expected, as intrinsic excitability of neurons (whether the neuron is spiky or not) is a much stronger feature than the temporal tuning.
 (Temporal tuning in the tectum was not even described until this paper, while the variation in intrinsic excitability in the tectum is well known for more than 20 years).
@@
 
-As described above, "spikiness" is now consistently used across the manuscript as the name of one of three variables used to quantify intrinsic tuning of tectal neurons.
+As described above, "spikiness" is now consistently used across the manuscript as the name of one of three variables used to quantify intrinsic tuning of tectal neurons (alongside with temporal tuning and amplitude tuning).
 
@@
 
-Previously a detailed justification for the use of dynamic clamp was only given in the Discussion section; we now moved it to the end of Introduction.
+Previously a justification for the use of dynamic clamp was only given in the Discussion section; we now moved it to the end of Introduction.
 
@@
 
-We updated the next sentence, by adding a reference to it: "We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits in vivo (Xu et al.
+We updated next sentence, stressing that the dynamic clamp protocol mimicked physiological synaptic inputs: "We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits in vivo (Xu et al.
 2011; Khakhalin et al.
@@
 
-As described in our responses to Reviewer 2, in this updated version, we consistently use "spikiness" as a name for the variable, for the first time introduced in Figure 2C.
-For earlier results section, we replaced "spikiness" with "average number of spikes", and in all instances when we talked about the general idea of neuronal excitability, we called it neuronal excitability.
-As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
+As described in our responses to Reviewer 2, in this updated version, we consistently use "spikiness" as a name for the high-level variable, for the first time introduced in Figure 2C; we use "average number of spikes" for the average number of spikes; and "neuronal excitability" in all instances when we talk about the general, undelying idea of neuronal excitability.
+As the only exception to this rule, we opt for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.
 
@@
 
-Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (**less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E**), as they did not increase their spiking as fast in response to larger conductances
+"Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E), as they did not increase their spiking as fast in response to larger conductances."
 
@@
 Of these four paragraphs, the last one reports a negative result that is not shown in Figure 3.
-The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot in good faith replace them with one sentence, as the statement we are making is not statistically obvious.
+The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot in a good faith replace them with one sentence, as the statement we make there is not statistically obvious.
 We believe that an attempt to gloss it over by pushing the statistical analysis to the methods section would not be fair.
-The issue, as we describe in the text, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes.
+The issue, as we describe it, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes.
 Had the slopes be the same, we would have just reported a correlation in one sentence.
-But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is typical for larger datasets, but that some readers may not be familiar with.
+But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is not uncommon for large datasets, but that some readers may not be intimately familiar with.
 
-We are aware that this section is read differently by different readers, and we received some conflicting advice in the past about the level of details needed to communicate this message.
-For example, those who have explicitly discussed Simpson's paradox in their statistics classes typically find our use of this term very helpful, while those who haven't used this term before, may find it distracting.
+We are aware that this section may read differently for different readers, and we received some conflicting advice in the past, about the level of details that is optimal for communicating this message.
+For example, readers who remember discussing Simpson's paradox in their statistics classes typically find our mentioning of this term helpful, while those who haven't encountered this term before, tend to find it distracting.
 For now, we opt to include it, even though it seems to be appreciated by only one half of our target audience.
-
-Nevertheless, in current version of the paper, we shortened this section from 411 to 294 words.
+Nevertheless, in this new version of the paper, we shortened this section from 411 to 294 words.
 
@@
 We are not sure how this fact can be illustrated.
-We searched for papers that use stepwise linear models, and it seems they do not usually include summary figures to describe these models.
-(They often include tables, listing R-squared, F, df, and p-values for every component, but as in this paper we are not particularly concerned by the precise composition of our models, we doubt a table like that would be useful here).
-Do you have any specific type of illustration in mind, in which case, could you provide a reference, or maybe describe it?
-The only type of illustration we could come up with is a scatterplot that compares values predicted from the model to actual values, but it is already shown in the paper, as Figure 4E.
+We searched for papers that use stepwise linear models, and it seems that researchers do not typically include summary figures to describe combinatorial model optimization.
+Some papers that use this method include tables, listing R-squared, F, df, and p-values for every component, but as in our paper we are not particularly concerned with the precise composition of the model, we are not sure that a table like that would be useful.
+If you have some specific type of illustration in mind, please kindly describe it, or reference it.
+The only type of illustration we could come up with is a scatterplot that compares values predicted by the model to actual values, as shown on Figure 4E.
+Some technical papers sometimes also present the model information factor penalty as a function of the number of terms included in the model, but again, we are not sure how useful this type of presentation would be for our paper, as we are not particularly concerned with the composition of the model, and the quality of the information criterion minimum, as our main point here is that the prediction quality of this whole family of models is not great, and we cannot even overfit, as temporal tuning cannot be predicted from standard voltage-clamp-based electrophysiological variables.
+
+For references, see for example: Stine, R. A. (2004). Model selection using information theory and the MDL principle. Sociological Methods & Research, 33(2), 230-260.
 
@@
 
-> TODO: that is what we are suggesting in one of the paragraphs. Cite that.
+This may indeed explain some of the trends in the data, but unfortately, as we described above, recording of tadpole tectal reponses to sounds does not seem to be possible in our lab, and is fundamentally technically problematic in principle.
+We can only guess that stimuli so different as flashes, looms, and sound clicks, would produce different responses in the tectum, as their dynamics is drastically different, and as they engage different circuits before reaching the tectum (retinal circuits for visual stimuli, hindbrain for acoustic), which undoubtedly shapes the dynamics of tectal activation (based on Khakhalin 2014, Felch 2016, Truszkowski 2017, Khakhalin 2019).
+We now make this point more clear by referencing it in the beginning of the paper (as described above), and then again, at the very end of Discussion, by describing how our observations can be used to predict actual, unobserved activation of the tectum during multisensory stimulation in vivo:
+
+"Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro (Felch et al., 2016; Truszkowski et al., 2017), it may reduce peak activation in vivo."
 

### 2019-06-03 Matlab code/dynamic_steps_reader.m
Side-quest on quantifying Na inactivation from spike thresholds

@@ -7,9 +7,9 @@ function dynamic_steps_reader()
 folderName = 'C:\_Data\_Silas\';
 showFigures = 0;                    % Whether figures are to be shown
 figureType = 'pile';                % 'full', 'pile', or 'train'
-consoleOutput = 0;                  % Whether reading files should be reported
-flagFitCurrent = 1;                 % Whether the depolarization curve needs to be measured (dV/dt)
-flagFinalOutput = 0;                % Whether final table is to be shown
+consoleOutput = 1;                  % Report files as they are read
+flagFitCurrent = 0;                 % Measure depolarizatoin curve (dV/dt), report Rtotal from the metadata
+flagFinalOutput = 1;                % Show final table (variable "bag");
 
 
 map = dynamic_what_is_where();      % Retrieve a hard-coded map of file names
@@ -24,6 +24,7 @@ cellList = setdiff(cellList,badCells);
 % cellList = 180:190;                         % Uncomment for testing (to work with selected few recordings only)
 % cellList = [141 198 205];                 % Some random cells for testing
 % cellList = 198;
+% cellList = [48 55 63 68];               % A selection of cells with very different threshold dynamics
 nCells = length(cellList);
 
 xZero =  [30 4900];                         % Region ot measure zero level
@@ -108,6 +109,8 @@ for(iCell=cellList)
         points = [];
         maxSpikes = 0;   
         minInflectionV = NaN;
+        firstSpikeSize = NaN;
+        thresholds = nan(1,nSweeps); 
         for(iSweep=1:nSweeps)
             points{iSweep} = find((z(2:end,iSweep)>=zThreshold)&(z(1:end-1,iSweep)<zThreshold)); % kink points (only positive)
             points{iSweep} = points{iSweep}(points{iSweep}>xSignal(1) & points{iSweep}<xSignal(2));
@@ -115,15 +118,21 @@ for(iCell=cellList)
                 closestPoint = max(points{iSweep}(points{iSweep}<firstMax(iSweep)));    % Last kink point before max
                 points{iSweep} = points{iSweep}(points{iSweep}>=closestPoint);          % Drop all other kink points before this poine
             end
-            if(maxSpikes==0 && length(points{iSweep})>0)        % First sweep to have a spike
-                minInflectionV = y(min(points{iSweep}),iSweep);
-                firstSpikeSize = y(firstMax(iSweep),iSweep) - minInflectionV;  % Max y minus kink point
[…]

### 2019-06-03 main.tex
Tex updates: routine improvements

@@
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25).
-This was likewise unexpected, as compared to flashes, looming stimuli are known to elicit stronger tectal responses \citep{khakhalin2014,khakhalin2019graph}, yet their effect on neuronal excitability was weaker, seemingly violating the principle of homeostatic plasticity \citep{pratt2007,turrigiano2007}.
+This was likewise unexpected, as compared to flashes, looming stimuli are known to elicit stronger tectal responses \citep{khakhalin2014,khakhalin2019graph}, yet their effect on neuronal excitability was weaker, seemingly in contradiction with the principle of homeostatic plasticity \citep{pratt2007,turrigiano2007}.
 
@@
 We then examined whether different types of sensory activation would differently reshape temporal intrinsic tuning in tectal neurons.
-As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (flashes; \citealt{khakhalin2014}) would selectively suppress spiking in response to shorter synaptic inputs.
-Alternatively, shorter stimuli could make neurons better adjusted to working with short bursts of activation \citep{stemmler1999information}, as  described for synaptic processing \citep{aizenman2007} and recurrent activity in the tectum \citep{pratt2007,shen2011}.
+As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; \citealt{khakhalin2014}) would selectively suppress spiking in response to faster synaptic inputs.
+As an alternative to this hypothesis, however, one could argue that exposure to shorter stimuli could make neurons better adjusted to working with fast synaptic currents \citep{stemmler1999information}, similar to changes described for synaptic plasticity \citep{aizenman2007} and recurrent activity in the tectum \citep{pratt2007, shen2011}.
 
@@
 In other words, while control neurons preferred longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
-This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, follow two different kinds of logic.
-The overall excitability is homeostatic, as neurons became less excitable in response to stronger stimulation.
-The temporal retuning however can be better described as “adaptive”, as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, making them more equipped to process faster, more synchronous patterns of activation \citep{stemmler1999information,fontaine2014threshold}.
+This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, followed two different kinds of logic.
+The overall excitability was homeostatic, as neurons became less excitable in response to stronger stimulation.
+The temporal retuning however can be better described as "adaptive", as neurons exposed to shorter stimuli (flashes) became relatively \textit{more} responsive to shorter stimuli, and less responsive to longer stimuli, making them equipped to process faster, synchronous patterns of activation \citep{stemmler1999information, fontaine2014threshold}.
 
@@
 This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning, despite being more behaviorally salient (at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}).
-This was not necessarily surprising, as auditory and mechanosensory inputs are known to have different cellular targets in the tectum \citep{pratt2009trigeminal,felch2016,truszkowski2017}, and thus can recruit tectal excitatory and inhibitory networks to a different extent.
-Alternatively, acoustic stimuli may be inherently weaker in triggering plasticity effects in tectal neurons, as compared to visual inputs, they arrive at different subcellular compartments within the dendritic tree \citep{hiramoto2009,deeg2009}, which can affect their influence on neuronal plasticity \citep{richards2019dendritic}.
+This was not necessarily surprising, as mechanosensory and visual inputs have different cellular targets in the tectum \citep{pratt2009trigeminal, felch2016, truszkowski2017}, potentially leading to different recruitment of tectal excitatory and inhibitory circuits.
+Acoustic stimuli may also be inherently weaker than visual stimuli in triggering plasticity effects in tectal neurons, as they arrive at different compartments within the dendritic tree \citep{hiramoto2009, deeg2009}, which may shape their influence on neuronal plasticity \citep{richards2019dendritic}.
 
@@
 Cells in Flash, Sync, and Async groups all received shorter synaptic inputs than Control cells (Tukey p$<$0.05, mean duration of 267$\pm$36, 253$\pm$39, 268$\pm$24, and 304$\pm$40 ms, respectively).
-This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum that remained unchanged.
-In this study, we did not perform a similar analysis for acoustic projection from the hindbrain.
+This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum, that remained unchanged.
+In this study, we did not probe changes in acoustic and mechanosensory projections from the hindbrain.
 
@@
 We can, however, offer two working hypotheses that may explain these results.
-As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic current inactivation in different cells \citep{azouz2000threshold,fontaine2014threshold}.
+As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic current inactivation in different cells \citep{azouz2000threshold, fontaine2014threshold}.
 One obvious way of tuning ionic channel inactivation would be for every cell to modulate sodium or transient potassium currents via channel phosphorylation, or by changing the expression of different channel variants, to shift their inactivation dynamics \citep{frank2003nachannels,goldwyn2018a_current}.
@@
 These changes in intrinsic temporal tuning would also reshape the connectivity of tectal networks, as fast-inactivating cells would not support short recurrent loops within the network, thus promoting long-ranged polysynaptic connectivity \citep{fiete2010stdp,clopath2010stdp}.
-Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it is be likely to reduce peak activation in vivo.
+Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it may reduce peak activation in vivo.
 

### 2019-06-05 reviews and responses.md
Sensitivity analysis for AP thresholds

@@
 
-We did not measure action potential thresholds, as we know from the previous study (Ciarleglio Khakhalin 2015) that threshold measurements in tadpole tectal neurons are highly sensitive to the current that is used to evoke the spikes, due to rapid Na channels inactivation (Azouz 2000; Fontaine 2014).
+The paragraph in question read: "We ran a stepwise generalized linear model selection analysis (R package stepAIC,
+Venables and Ripley 2013) to explain the intrinsic tuning of cells recorded in all
+experimental groups through these eight variables. We found that the average spikiness
+(after compensation for position within the tectum; see Methods) was best described by a
+combination of sodium peak current (INa) and membrane resistance (Rm) variables, but
+these variables explained only 8% and 2% of cell-to-cell variance respectively
+F(1,130)=11.3, and F(1,130)=4.5; Figure 3E)." etc.
+
+We measured action potential thresholds, but did not report them, as we know from earlier studies (Ciarleglio Khakhalin 2015) that AP threshold measurements in tectal neurons are highly sensitive to the current that is used to evoke the spikes, due to rapid Na channels inactivation.
+At the analysis phase, we briefly tried to use AP thresholds from current clamp experiments to estimate the prominence of Na channels inactivation in individual tectal neurons (Azouz 2000; Fontaine 2014), but these attempts did not lead to conclusive results, and as they are also not based on established analysis methods, they are not reported in the paper.
+Neither minimal threshold for generating an action potential, nor the slope of AP threshold with increase in holding current, different across groups (ANOVA p=0.7 and 0.3 respectively).
 

### 2019-06-05 dynamic_other_vars.R

@@ -330,8 +330,8 @@ cohen.d(data=subset(dadj,group %in% c("Flash","Async")),samp~group) # 0.65, 0.64
 # -------------- Big flexible visualizations
 # Full analysis plot of each one variable
 # Set the variable & its name in two rows below
-d$best = d$smean # Put any value from names() here
-valName = 'smean' # How to label y-axis below
+d$best = d$thslope # Put any value from names() here
+valName = 'thslope' # How to label y-axis below
 transformNeeded = F # Transformation; set to T for sbend
 dclean = na.omit(d)
 if(transformNeeded) {
@@ -351,9 +351,18 @@ d_sum = summarize(group_by(dclean,group),
              m=mean(proxy,na.rm=T),
              n=n(),
              ci=sd(proxy,na.rm=T)/sqrt(n)*qt(0.025,df=n-1))
+# Version with beeswarm that stopped working for some reason:
 ggplot(data=d_sum, aes(group,m)) + 
   theme_bw() + theme(text=element_text(size=8)) + 
   geom_beeswarm(data=dclean,aes(group,proxy,color=group),cex=1,alpha=0.5,shape=16,size=2) +
+  geom_point(shape=1) +
+  geom_errorbar(aes(ymin=m-ci,ymax=m+ci),width=0.1) +
+  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank()) +
+  xlab('Group') + ylab(valName)
+# Similar thing, but with jitter:
+ggplot(data=d_sum, aes(group,m)) + 
+  theme_bw() + theme(text=element_text(size=8)) + 
+  geom_jitter(data=dclean,aes(group,proxy,color=group),alpha=0.5,shape=16,size=2,height=0,width=0.2) +
   geom_point(shape=1) +
   geom_errorbar(aes(ymin=m-ci,ymax=m+ci),width=0.1) +
   theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank()) +
@@ -479,7 +488,7 @@ stepAIC(fit, direction="both") # nai+rm
 ### ---- Sbend analysis
 # it's important to use dadj instead of d, as sbend is tricky to position-compensate
 # because of non-normality, but we've done it properly above.
[…]

### 2019-06-06 reviews and responses.md
sb edits R2 minor

@@
 Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, and the impact of inputs to the apical dendrites of pyramidal cells in the cortex.
-We feel, however, that this topic is really deep, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition to it by short sentence and a good recent reference.
+We feel, however, that this topic is very complex, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition into it by a short sentence and a good, recent reference.
+
+SILAS-SAYS: For the climbing fiber to purkinje cell example, it may be worth noting that the climbing fiber makes hundreds of synapses along pretty much all of the primary dendritic arbor of the purkinje cell.
+So It doesn't really represent a spatially specific input to the dendritic arbor, except that there aren't really as many CF inputs to the distal most dendrites, so it is slightly proximal leaning.
+Also, I'm reading a paper now by Davie, Clark, and Hausser 2008 where they use DC to show that CF mediated dendritic spikes don't actually influence the axosomatic generated complex spike.
+Instead the huge Ca influx from CF input mediates LTD at Parallel fiber-purkinje cell synapses, so it is absolutely a great example to show the importance of calcium dynamics mediated by dendritic input on plasticity.
 
@@
 
-This was unexpected as intrinsic plasticity is typically described as a homeostatic mechanism, and thus a stronger stimulus could, in principle, cause stronger suppression of spiking.
+This was unexpected as intrinsic plasticity is often described as a homeostatic mechanism.
+Thus a stronger stimulus could, in principle, cause stronger suppression of spiking.
 To make this point more clear, we now changed this sentence:

### 2019-06-06 reviews and responses.md
sb edits R2 major

@@
 
+SILAS-SAYS: While I think you answered the question, I don't think R2 will like the change.
+I think they want us to write in the text something like this: "As previous studies show that synaptic responses to flashes are much shorter than responses to looming stimuli in the tectum (Khakhalin 2014, Khakhalin 2019), and changes in intrinsic properties seemed homeostatic (ie increased activation led to reduced spiking), one could expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs." This uses your response to the reviewer to write what may be a clearer version of that particular sentence.
+When I get to the manuscript I will make a note about this comment at that place.
+
 > Page 5, line 5: “As changes in intrinsic properties seemed homeostatic (increased activation led to
@@
 
+SILAS-SAYS: My suggestion for this sentence, in the comment above, does not help to elaborate this point that R2 brings up, but I'm also not sure if your rewrite is resolving the confusion of R2.
+Maybe we just need an additional sentence before the problem sentence saying something along these lines: "One could expect that, if activity can induce a homeostatic suppression of excitability, then a specific profile of activity, such as a short duration, may cause a calibrated homeostatic suppression of a cell's excitability to that specific input profile."
+
 > Page 5 line 15: Does the word “preferred” (in quotes) mean that the cells fired more action potentials?
@@
 Overall, we use the word "prefer" 6 times in the paper, always in the same way: when comparing spiking responses to different stimuli, to describe the stimulus that produced sronger outputs in a given set of neurons.
+
+SILAS-SAYS: I'm kinda with the reviewer on this one.
+I agree that it's nice to use a potentially more intuitive word that shortens things, but at the very least I think we should explicitely state that prefered here means spiked more ("While control neurons produced increasing spikes in response to increasing input durations, exhibiting a preference for long synaptic inputs, neurons exposed to flashes..." ).
+Another issue R2 may be feeling but not saying explicitely is that in saying prefered, we seem to be suggesting a specific hypothesis about the goal of intrinsic plasticity of intrinsic excitability (ie retuning contributes something specific to the intake and export of information in a tectal neuron).
+Of course, we think that it is very important, but we don't have follow up experiments displaying what specific affects tectal retuning could have on sensory processing.
 
@@
 Second, even if this limitation could be overcome, the sounds have to be strong enough to stimulate the inner ear, but weak enough not to mechanically disrupt the recording.
-Conceivably, both challenges may circumvented with the use of high speed calcum imaging in freely moving tadpoles, but to our knowledge no lab has attempted these recordings yet.
+Conceivably, both challenges may be circumvented with the use of high speed calcum imaging in freely moving tadpoles, but to our knowledge no lab has attempted these recordings yet.
 
@@
 By looking at average currents early and later after the chiasm shock, we can independently assess the contribution of direct and recurrent inputs.
-In the paper, in a paragraph before the sentence in question, we report that after stimulation, direct current increased in amplitude, while recurrent currents remained unchanged.
+In the paper, in a paragraph before the sentence in question, we report that after stimulation, direct input mediated current increased in amplitude, while recurrent input mediated currents remained unchanged.
 This is what we call selective potentiation of direct inputs, as opposed to recurrent inputs.
@@
 
-To make sure that we are not misunderstood by the reader, we replaced the original sentence with the following two sentences: "This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum, that remained unchanged.
+To make sure that we are not misunderstood by the reader, we replaced the original sentence with the following two sentences: "This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum that remained unchanged.
 In this study, we did not probe changes in acoustic and mechanosensory projections from the hindbrain."
@@
 
-We measured action potential thresholds, but did not report them, as we know from earlier studies (Ciarleglio Khakhalin 2015) that AP threshold measurements in tectal neurons are highly sensitive to the current that is used to evoke the spikes, due to rapid Na channels inactivation.
-At the analysis phase, we briefly tried to use AP thresholds from current clamp experiments to estimate the prominence of Na channels inactivation in individual tectal neurons (Azouz 2000; Fontaine 2014), but these attempts did not lead to conclusive results, and as they are also not based on established analysis methods, they are not reported in the paper.
-Neither minimal threshold for generating an action potential, nor the slope of AP threshold with increase in holding current, different across groups (ANOVA p=0.7 and 0.3 respectively).
+We measured action potential thresholds, but did not report them, as we know from earlier studies (Ciarleglio Khakhalin 2015) that AP threshold measurements in tectal neurons are highly sensitive to the current that is used to evoke the spikes, due to rapid Na channel inactivation.
+At the analysis phase, we briefly tried to use AP thresholds from current clamp experiments to estimate the prominence of Na channel inactivation in individual tectal neurons (Azouz 2000; Fontaine 2014), but these attempts did not lead to conclusive results, and as they are also not based on established analysis methods, they are not reported in the paper.
+Neither minimal threshold for generating an action potential, nor the slope of AP threshold with increased holding current, were different across groups (ANOVA p=0.7 and 0.3, respectively).
 
@@
 
+SILAS-SAYS: While you've certainly explained our approach to R2, I wonder if R2 will want us to make the same explicit statements about what each term mean in the manuscript itself.
+
 > Page 15 line 34: The average membrane resistance (330 MOhm) seems a bit low for these small immature
@@
 
-We did not measure the resting membrane potential directly, but measured the holding current necessary to bring the cell to -60 mV in voltage clamp mode, and the mean value of this I_hold value was -8.2±4.8 pA, which is similar (most importnatly, not higher) than what was previously reported in the literature (-19.8±16.6 in Ciearleglio Khakhalin 2015).
+We did not measure the resting membrane potential directly, but measured the holding current necessary to bring the cell to -60 mV in voltage clamp mode, and the mean value of this I_hold value was -8.2±4.8 pA, which is similar (most importantly, not higher) than what was previously reported in the literature (-19.8±16.6 in Ciearleglio Khakhalin 2015).
 
@@
 
-As the mistake your noticed (thank you again for being so thorough!) was a typo in the text, and not a mistake in the data, it does not affect any calculations reported in this paper.
+Since the mistake that you noticed (thank you again for being so thorough!) was a typo in the text, and not a mistake in the data, it does not affect any calculations reported in this paper.
 
@@
 (Temporal tuning in the tectum was not even described until this paper, while the variation in intrinsic excitability in the tectum is well known for more than 20 years).
+
+SILAS-SAYS: It seems R2 is asking if most cells follow the pattern of spike increase with duration increase as highlighted by the mean, or if the sum of many different activation patterns just happens to generate that average.
+I think that your point about the correlation coefficient puts that to rest, but you may want to say that more explicitely because it is legitimately difficult to look at the individual data points to this level of precision without seeing the mean trend.
 

### 2019-06-06 reviews and responses.md
AKh responses to SB responses to reviewer's responses

@@
 Here, the actual rationale for the second explanation (a difference in subcellular targets) is that inputs to different parts of the dentritic tree can trigger action potentials of different shape, and differentially affect calcium dynamics in the neuron, which, together with non-linear processing in dendrites may make different types of inputs unequal in terms of their effects on neuronal activity, and neuronal tuning, respectively.
-Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, and the impact of inputs to the apical dendrites of pyramidal cells in the cortex.
+Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, or the impact of inputs to the apical dendrites of pyramidal cells in the cortex.
 We feel, however, that this topic is very complex, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition into it by a short sentence and a good, recent reference.
-
-SILAS-SAYS: For the climbing fiber to purkinje cell example, it may be worth noting that the climbing fiber makes hundreds of synapses along pretty much all of the primary dendritic arbor of the purkinje cell.
-So It doesn't really represent a spatially specific input to the dendritic arbor, except that there aren't really as many CF inputs to the distal most dendrites, so it is slightly proximal leaning.
-Also, I'm reading a paper now by Davie, Clark, and Hausser 2008 where they use DC to show that CF mediated dendritic spikes don't actually influence the axosomatic generated complex spike.
-Instead the huge Ca influx from CF input mediates LTD at Parallel fiber-purkinje cell synapses, so it is absolutely a great example to show the importance of calcium dynamics mediated by dendritic input on plasticity.
 
@@
 
-"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; Khakhalin et al.
-2014) would selectively suppress spiking in response to faster synaptic inputs."
-
-SILAS-SAYS: While I think you answered the question, I don't think R2 will like the change.
-I think they want us to write in the text something like this: "As previous studies show that synaptic responses to flashes are much shorter than responses to looming stimuli in the tectum (Khakhalin 2014, Khakhalin 2019), and changes in intrinsic properties seemed homeostatic (ie increased activation led to reduced spiking), one could expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs." This uses your response to the reviewer to write what may be a clearer version of that particular sentence.
-When I get to the manuscript I will make a note about this comment at that place.
+"We knew from earlier studies that fast tectal responses can be evoked with instantaneous flashes, while looming stimuli cause slower, and more prolonged tectal activation (Khakhalin et al., 2014; Khakhalin, 2019).
+As overall changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to flashes would selectively suppress spiking in1response to fast synaptic inputs."
 
@@
 
-"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; Khakhalin et al.
-2014) would selectively suppress spiking in response to faster synaptic inputs."
-
-SILAS-SAYS: My suggestion for this sentence, in the comment above, does not help to elaborate this point that R2 brings up, but I'm also not sure if your rewrite is resolving the confusion of R2.
-Maybe we just need an additional sentence before the problem sentence saying something along these lines: "One could expect that, if activity can induce a homeostatic suppression of excitability, then a specific profile of activity, such as a short duration, may cause a calibrated homeostatic suppression of a cell's excitability to that specific input profile."
+"We knew from earlier studies that fast tectal responses can be evoked with instantaneous flashes, while looming stimuli cause slower, and more prolonged tectal activation (Khakhalin et al., 2014; Khakhalin, 2019).
+As overall changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to flashes would selectively suppress spiking in1response to fast synaptic inputs."
 
@@
 Realistically, we hope that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are intentionally a bit more relaxed when writing about cells, channels, receptors etc.
-Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is not an antropomorphic allegory, but just a normal word use.
+Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is not an antropomorphic allegory, but just a normal word use, and also added a clarification:
+
+"In other words, while control neurons preferred longer inputs (responded to them with more spikes), stimulated neurons developed a preference for shorter synaptic inputs..."
+
 Overall, we use the word "prefer" 6 times in the paper, always in the same way: when comparing spiking responses to different stimuli, to describe the stimulus that produced sronger outputs in a given set of neurons.
-
-SILAS-SAYS: I'm kinda with the reviewer on this one.
-I agree that it's nice to use a potentially more intuitive word that shortens things, but at the very least I think we should explicitely state that prefered here means spiked more ("While control neurons produced increasing spikes in response to increasing input durations, exhibiting a preference for long synaptic inputs, neurons exposed to flashes..." ).
-Another issue R2 may be feeling but not saying explicitely is that in saying prefered, we seem to be suggesting a specific hypothesis about the goal of intrinsic plasticity of intrinsic excitability (ie retuning contributes something specific to the intake and export of information in a tectal neuron).
-Of course, we think that it is very important, but we don't have follow up experiments displaying what specific affects tectal retuning could have on sensory processing.
 
@@
 
-SILAS-SAYS: While you've certainly explained our approach to R2, I wonder if R2 will want us to make the same explicit statements about what each term mean in the manuscript itself.
-
 > Page 15 line 34: The average membrane resistance (330 MOhm) seems a bit low for these small immature
@@
 (Temporal tuning in the tectum was not even described until this paper, while the variation in intrinsic excitability in the tectum is well known for more than 20 years).
-
-SILAS-SAYS: It seems R2 is asking if most cells follow the pattern of spike increase with duration increase as highlighted by the mean, or if the sum of many different activation patterns just happens to generate that average.
-I think that your point about the correlation coefficient puts that to rest, but you may want to say that more explicitely because it is legitimately difficult to look at the individual data points to this level of precision without seeing the mean trend.
 

### 2019-06-06 reviews and responses.md
sb edits R3 all

--- 2019-06-06 reviews and responses.md
@@
 The issue, as we describe it, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes.
-Had the slopes be the same, we would have just reported a correlation in one sentence.
+Had the slopes been the same, we would have just reported a correlation in one sentence.
 But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is not uncommon for large datasets, but that some readers may not be intimately familiar with.
@@
 We are aware that this section may read differently for different readers, and we received some conflicting advice in the past, about the level of details that is optimal for communicating this message.
-For example, readers who remember discussing Simpson's paradox in their statistics classes typically find our mentioning of this term helpful, while those who haven't encountered this term before, tend to find it distracting.
+For example, readers who discussed Simpson's paradox in their statistics classes typically find our mentioning of this term helpful, while those who haven't encountered this term before, tend to find it distracting.
 For now, we opt to include it, even though it seems to be appreciated by only one half of our target audience.
@@
 This may indeed explain some of the trends in the data, but unfortately, as we described above, recording of tadpole tectal reponses to sounds does not seem to be possible in our lab, and is fundamentally technically problematic in principle.
-We can only guess that stimuli so different as flashes, looms, and sound clicks, would produce different responses in the tectum, as their dynamics is drastically different, and as they engage different circuits before reaching the tectum (retinal circuits for visual stimuli, hindbrain for acoustic), which undoubtedly shapes the dynamics of tectal activation (based on Khakhalin 2014, Felch 2016, Truszkowski 2017, Khakhalin 2019).
-We now make this point more clear by referencing it in the beginning of the paper (as described above), and then again, at the very end of Discussion, by describing how our observations can be used to predict actual, unobserved activation of the tectum during multisensory stimulation in vivo:
+We can only guess that stimuli so different as flashes, looms, and sound clicks, would produce different responses in the tectum, as their dynamics are drastically different, and as they engage different circuits before reaching the tectum (retinal circuits for visual stimuli, hindbrain for acoustic), which undoubtedly shapes the dynamics of tectal activation (based on Khakhalin 2014, Felch 2016, Truszkowski 2017, Khakhalin 2019).
+We now make this point more clear by referencing it in the beginning of the paper (as described above), and then again, at the very end of the Discussion, by describing how our observations can be used to predict actual, unobserved activation of the tectum during multisensory stimulation in vivo:
 

### 2019-06-07 dynamic_spikes_plot.R
Summarized p-values for group-to-group comparisons

@@ -81,7 +81,7 @@ head(dfull)
 ggplot() + theme_bw() + geom_point(data=dfull,aes(ss,bend)) # Simple bendiness and fancy bendiness correlate well
 
 # Output
-write.csv(d1,"spike shapes.txt",row.names=F)
+# write.csv(d1,"spike shapes.txt",row.names=F)
 
 d2 = inner_join(ds,d1,by="Cell")
 # Plot everything
@@ -121,22 +121,26 @@ ggplot(data=subset(d_diff,Group!="Control"), aes(sn,diff,color=Amp,group=Amp)) +
   theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank()) +
   xlab('Conductance curve length, ms') + ylab('Spike suppression')
 
-# Compare any set of groups to each other
+# --- Compare any set of groups to each other
 # Uncomment any single row among the options below
+
 # ds = subset(d,is.element(Group,c("Control","Flash","Looming")))
 # ds = subset(d,is.element(Group,c("Flash","Sound","Sync","Async")))
 # ds = subset(d,is.element(Group,c("Control","Flash")))
 # ds = subset(d,is.element(Group,c("Control","Looming")))
 # ds = subset(d,is.element(Group,c("Flash","Looming")))
-# ds = subset(d,is.element(Group,c("Control","Async")))
-# ds = subset(d,is.element(Group,c("Control","Sou#nd")))
+# ds = subset(d,is.element(Group,c("Control","Sync"))) # yes aov, yes lmer
+# ds = subset(d,is.element(Group,c("Control","Async"))) # no aov, no lmer
+ds = subset(d,is.element(Group,c("Sync","Async"))) # yes, no
+# ds = subset(d,is.element(Group,c("Control","Sound"))) # no, no
 # ds = subset(d,is.element(Group,c("Flash","Sound")))
-ds = subset(d,is.element(Group,c("Flash","Sync")))
-# ds = subset(d,is.element(Group,c("Flash","Async")))
+# ds = subset(d,is.element(Group,c("Flash","Sync"))) # yes aov, no lmer
+# ds = subset(d,is.element(Group,c("Flash","Async"))) # yes aov, yes lmer
 # ds = d # To compare all
 
 dsflat <- ds %>% group_by(Group,Cell,Amp,Shape) %>% summarize(Spikes=mean(Spikes,na.rm=T))
[…]

### 2019-06-07 main.tex
Text updates + diff to submission

@@
 % J Neurophysiol: up to 250 words
-% Currently: ?
+% Currently: 186
 
-For a biological neural network to be functional, its neurons need to be connected to each other with synapses of appropriate strength, and each neuron needs to appropriately respond to its synaptic inputs.
+For a biological neural network to be functional, its neurons need to be connected with synapses of appropriate strength, and each neuron needs to appropriately respond to its synaptic inputs.
 This second aspect of network tuning is maintained by intrinsic plasticity; yet it is often considered secondary to changes in connectivity, and mostly limited to adjustments of overall excitability of each neuron.
-Here we argue that individual neurons can also be tuned to inputs of different temporal dynamics, and that they can routinely adjust this tuning to match the statistics of their synaptic activation.
+Here we argue that even non-oscillatory neurons can be tuned to inputs of different temporal dynamics, and that they can routinely adjust this tuning to match the statistics of their synaptic activation.
 Using the dynamic clamp technique, we show that in the tectum of Xenopus tadpoles, neurons become selective for faster inputs when animals are exposed to fast visual stimuli, but remain responsive to longer inputs in animals exposed to slower, looming or multisensory stimulation.
 We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties of individual tectal cells.
-These results expand our understanding of plasticity in the brain, and suggest that there may exist a whole extra dimension of network tuning that was so far overlooked.
-
-%Old version: Homeostatic intrinsic plasticity is often described as an adjustment of neuronal excitability to maintain stable spiking output.
-Here we report that intrinsic plasticity in the tectum of Xenopus tadpoles also supports temporal tuning, wherein neurons independently adjust spiking responses to fast and slow patterns of synaptic activation.
-Using the dynamic clamp technique, and five different types of visual, acoustic, and multisensory conditioning, we show that in tadpoles exposed to light flashes, tectal neurons became selective for fast synaptic inputs, while neurons exposed to looming and multisensory stimuli remained responsive to longer inputs.
-We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties in tectal cells, as neurons that naturally received fast synaptic inputs tended to be most responsive to long-lasting synaptic conductances, and the other way around.
-These results expand our understanding of plasticity in the brain, and inform future work on the mechanisms of sensorimotor transformation.
-
-% Acoustic stimuli had different effects when delivered alone, or when combined with visual stimuli.
+These results expand our understanding of intrinsic plasticity in the brain, and suggest that there may exist an additional dimension of network tuning that has been so far overlooked.
 
@@
 
-It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network,reimann2017}.
-However, biological neurons also demonstrate complex and multifaceted intrinsic tuning  \citep{oleary2013,evans2015}, with cells within a single network having different activation thresholds \citep{kole2012}, bursting behaviors \citep{popovic2011}, and inactivation profiles \citep{bianchi2012}.
-Dysregulation of intrinsic plasticity affects the dynamics of networks  \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}.
+It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014, hildebrand2017, bassett2017network, reimann2017}.
+However, biological neurons also demonstrate complex and multifaceted intrinsic tuning  \citep{oleary2013,evans2015}, where cells within a single network having different activation thresholds \citep{kole2012}, bursting behaviors \citep{popovic2011}, and inactivation profiles \citep{bianchi2012}.
+Dysregulation of intrinsic plasticity affects the network dynamics  \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}.
 And yet, with the possible exception of oscillatory networks \citep{marder2011,picton2018control}, the exact ways in which intrinsic plasticity contributes to network tuning, remain unclear.
-We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but we also know that intrinsic properties affect neuronal tuning to different temporal patterns of activation \citep{azouz2000threshold,branco2010dendritic,fontaine2014threshold,jarvis2018morphology,ohtsuki2018bursting,zbili2019axonnav}.
-That begs the question: do neurons dynamically adjust this type of tuning in practice?
+We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but we also know that intrinsic properties can affect more subtle neuronal tuning to different temporal patterns of activation \citep{azouz2000threshold, branco2010dendritic, fontaine2014threshold, jarvis2018morphology, ohtsuki2018bursting, zbili2019axonnav}.
+This begs the question: do neurons use this type of tuning in practice, dynamically adjusting it to the temporal dynamics of their inputs?
 
 In this paper, we investigate whether exposure to sensory stimuli with different temporal dynamics would change intrinsic temporal tuning of sensory neurons in the optic tectum of \textit{Xenopus} tadpoles.
-Tadpole tectum is an ideal model for exploring this question: it is a highly malleable distributed network of about 10\textsuperscript{4} neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}.
+The tadpole tectum is an ideal model for exploring this question: it is a highly malleable distributed network of about 10\textsuperscript{4} neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}.
 In development, tectal neurons acquire diverse phenotypes, that are then shaped by sensory experiences \citep{xu2011,ciarleglio2015}.
@@
 In dynamic clamp, the current injected into the cell is adjusted in real-time, based on a predefined formula that depends on time and cell membrane potential.
-This means that with dynamic clamp recordings we can excite a neuron in a controlled manner, but still allow both its voltage and transmembrane currents to change, preserving feedback interactions between active currents and transient voltage-gated channels inactivation \citep{ma1996dynamic,zbili2019axonnav}, which is an important mechanism for temporal tuning \citep{branco2010dendritic,platkiewicz2011}.
-As a second methodological innovation, instead of relying on one type of sensory stimulation \citep{ciarleglio2015}, here we used five different stimulation protocols, and compared to each other their effects on intrinsic tuning.
+This means that with dynamic clamp recordings we can excite a neuron in a controlled manner, but still allow both its voltage and transmembrane currents to change, preserving feedback interactions between active currents and transient voltage-gated channel inactivation \citep{ma1996dynamic,zbili2019axonnav}, which is an important mechanism for temporal tuning \citep{branco2010dendritic,platkiewicz2011}.
+As a second methodological innovation, instead of relying on one type of sensory stimulation \citep{ciarleglio2015}, here we used five different stimulation protocols, and compared their individual effects on intrinsic tuning.
 
@@
 Based on prior research \citep{aizenman2003,ciarleglio2015}, we expected neurons exposed to instantaneous checkerboard inversions (flashes) to become more excitable, but surprisingly, they were on average less spiky, and generated 0.4$\pm$0.4 spikes, across all types of dynamic clamp inputs, compared to 0.9$\pm$1.0 spikes in control (Figure 1D, left column; F(1,677)=30.4, p=5e-8, n cells=28, 29).
-(Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell id is used as a repeated measures factor; see Methods for a detailed description).
+(Here and below, F-values are reported for a multivariate fixed effects analysis of variance with selected interactions, where cell ID is used as a repeated measures factor; see Methods for a detailed description).
 Neurons exposed to looming transitions also spiked less than control neurons (0.6$\pm$0.4 spikes; F(1,629)=9.6; p=0.002; n=28, 25), but more than those exposed to instantaneous "flashes" (F(1,641)=3.7; p=4e-6; n=29, 25).
@@
 Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E), as they did not increase their spiking as fast in response to larger conductances (F(1,677)=15.9, p=8e-5; and F(1,629)=8.3, p=0.004 for flash- and looming respectively, compared to control).
-%The flattening of response curves seemed slightly more pronounced for flashes than for looming, but this difference was not significant (F(1,641)=3.5; p=0.06).
+The flattening of response curves seemed slightly more pronounced for flashes than for looming (F(1,641)=3.5; p=0.06).
 
@@
 
-We then examined whether different types of sensory activation would differently reshape temporal intrinsic tuning in tectal neurons.
-As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; \citealt{khakhalin2014}) would selectively suppress spiking in response to faster synaptic inputs.
-As an alternative to this hypothesis, however, one could argue that exposure to shorter stimuli could make neurons better adjusted to working with fast synaptic currents \citep{stemmler1999information}, similar to changes described for synaptic plasticity \citep{aizenman2007} and recurrent activity in the tectum \citep{pratt2007, shen2011}.
+We then examined whether different types of sensory activation would differently reshape intrinsic temporal tuning in tectal neurons.
+We knew from earlier studies that fast tectal responses can be evoked with instantaneous flashes, while looming stimuli cause slower, and more prolonged tectal activation \citep{khakhalin2014, khakhalin2019graph}.
+As overall changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to flashes would selectively suppress spiking in response to fast synaptic inputs.
+On the other hand, one could argue that exposure to shorter stimuli could make neurons better adjusted to working with fast synaptic currents \citep{stemmler1999information}, similar to changes described for synaptic plasticity \citep{aizenman2007} and recurrent activity in the tectum \citep{pratt2007, shen2011}.
 
@@
 In control neurons, longer inputs (500 and 1000 ms) typically evoked stronger spiking than shorter inputs (100 and 200 ms), but neurons from stimulated animals had flatter tuning curves, with a plateau, or even a decrease in spike output for longer conductance injections (Figure 1E).
-In other words, while control neurons preferred longer inputs, stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
+In other words, while control neurons preferred longer inputs (responded to them with more spikes), stimulated neurons developed a preference for shorter synaptic inputs, and this change was more pronounced in neurons exposed to flashes than in those exposed to looming stimuli (F(1,641)=7.5; p=0.006).
 This suggests that the change in overall intrinsic excitability, and the change in temporal tuning, followed two different kinds of logic.
@@
 We found (Fig 1D, E) that exposure to these sounds (group “Sound”) did not lead to significant changes in either average number of spikes (0.8$\pm$0.7 spikes; F(1,689)=1.7; p=0.2; n=28, 30), amplitude transfer function (F(1,689)=2.0; p=0.2), or temporal tuning curve (F(1,689)=2.0; p=0.2).
-This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning, despite being more behaviorally salient (at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015,truszkowski2017}).
+This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning, despite being more behaviorally salient (at the onset of stimulation, acoustic clicks evoked startle responses in about 50-80\% of cases, compared to 5-10\% for checkerboard inversions \citep{james2015, truszkowski2017}).
 This was not necessarily surprising, as mechanosensory and visual inputs have different cellular targets in the tectum \citep{pratt2009trigeminal, felch2016, truszkowski2017}, potentially leading to different recruitment of tectal excitatory and inhibitory circuits.
-Acoustic stimuli may also be inherently weaker than visual stimuli in triggering plasticity effects in tectal neurons, as they arrive at different compartments within the dendritic tree \citep{hiramoto2009, deeg2009}, which may shape their influence on neuronal plasticity \citep{richards2019dendritic}.
+Acoustic stimuli may also be inherently weaker than visual stimuli in triggering plasticity effects in tectal neurons, as they arrive at different compartments within the dendritic tree \citep{hiramoto2009, deeg2009}, which may define their influence on neuronal plasticity \citep{richards2019dendritic}.
 
@@
 For some animals, we synchronized the instantaneous checkerboard inversions (flashes) with sound clicks (dubbed “Sync”), while for others, we staggered visual and acoustic stimuli by half a period (500 ms; dubbed “Async”).
-We found (Fig 1D, E) that multisensory stimulation suppressed excitability of tectal neurons less strongly than visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for Sync and Async respectively, compared to Flash, across all testing conditions).
-Moreover, both temporal and amplitude tuning curves in multisensory groups were less flat than in the Flash group, with a stronger effect in the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively).
+We found (Fig 1D, E) that multisensory stimulation did not suppress excitability of tectal neurons as strongly as visual stimulation alone (0.6$\pm$0.4 spikes, F(1,689)=11.2, p=8e-4; and 0.7$\pm$0.6 spikes, F(1,665)=41.7, p=2e-10, for Sync and Async respectively, compared to Flash, across all testing conditions).
+Moreover, both temporal and amplitude tuning curves in multisensory groups were less flat than in the Flash group, which was especially noticeable for the Async group (for amplitude tuning: F(1,689)=1.3, p=0.3, and F(1,665)=2.4, p=0.02 in Sync and Async groups respectively; for temporal tuning: F(1,689)=9.3, p=0.002, and F(1,665)=22.8, p=2e-6 respectively).
 This suggests that while on their own sound clicks had little effect on tectal excitability, when added to visual flashes, they negated some of the retuning effects that visual stimulation would have had.
@@
 When sounds were added to flashes, however, both tuning coefficients increased (d=0.65 and 0.26 for amplitude and temporal tuning respectively, "Async" compared to “Flash”), making neurons more similar to control neurons (Hotelling test p=0.04).
-Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Figure 2D), but it negated the effects of visual stimulation the two were combined.
-This effect is likely to be either a consequence of strong inhibitory recruitment during multisensory integration in the tectum \citep{liu2016,hamodi2016}, or a sign of highly non-linear interactions between acoustic and visual inputs within the dendritic trees of individual tectal neurons \citep{deeg2011,felch2016,truszkowski2017}.
+Thus, acoustic stimulation tended to tune the network in the same direction as visual stimulation when delivered alone (Figure 2D), but it negated the effects of visual stimulation when the two were combined.
+This effect is likely to be either a consequence of strong inhibitory recruitment during multisensory integration in the tectum \citep{liu2016,hamodi2016}, or a sign of highly non-linear interactions between acoustic and visual inputs within the dendritic trees of individual tectal neurons \citep{deeg2011, felch2016, truszkowski2017}.
 
-Somewhat similarly, looming stimuli seemed to have weaker effects on intrinsic properties, compared to flashes, both in terms of amplitude (d=0.44) and temporal tuning (d=0.22), despite them eliciting stronger responses in-vivo \citep{khakhalin2014,khakhalin2019graph}.
+Somewhat similarly, looming stimuli seemed to have weaker effects on intrinsic properties, compared to flashes, both in terms of amplitude (d=0.44) and temporal tuning (d=0.22), despite them eliciting stronger responses in-vivo \citep{khakhalin2014, khakhalin2019graph}.
 This suggests that intrinsic retuning depends on stimuli synchronicity, rather than simply the total number of spikes generated by the network, as more synchronous stimuli (Flash, Sync) had stronger effects on tuning than comparable asynchronous stimuli (Async, Looming).
-
-% Here we may reference Bollmann 2009 back, to show that dendritic processing probably does happen here.
 
@@
 This suggests that during normal brain development, individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, enhancing responses to unusual patterns of synaptic activation.
+This tuning to "unusual stimuli" fits into the narrative of information transfer maximization \citep{stemmler1999information, brenner2000} and network criticality \citep{rubinov2011}, wherein every element of a network tries to maximize its influence on the overall computation.
 It also means that the correlation of intrinsic and synaptic properties had opposite signs between-groups (Figure 3E; positive) and within-groups (Figure 3F; negative), which is a textbook case of a so-called "Simpson's paradox" in data analysis.
@@
 This suggests the existence of intrinsic properties that strongly affect spiking in dynamic clamp experiments, but are inaccessible through simple voltage step protocols, such as the amount of voltage-gated channels inactivation (\citealt{zbili2019axonnav}; see Discussion).
-Our hypothesis is also indirectly supported by the observation that of only one out of eight cellular parameterswas significantly (p$<$0.05) different across treatment groups (NaV: F(5,175)=3.7, p=0.003), and that the number of spikes detected in current clamp experiments did not differ across experimental groups (F(5,165)=0.8, p=0.6).
+Our hypothesis is also indirectly supported by the observation that only one out of eight cellular parameters was significantly (p$<$0.05) different across treatment groups (NaV: F(5,175)=3.7, p=0.003), and that the number of spikes detected in current clamp experiments did not differ across experimental groups (F(5,165)=0.8, p=0.6).
 
@@
 This seems to suggest that while low-level properties of tectal cells depended on their developmental age, their spiking phenotypes were age-independent.
-It means that different cells achieved similar spiking behaviors through different combinations of underlying parameters, relying on the principle of “parameter degeneracy” \citep{prinz2004degeneracy,drion2015}.
+This means that different cells achieved similar spiking behaviors through different combinations of underlying parameters, relying on the principle of “parameter degeneracy” \citep{prinz2004degeneracy,drion2015}.
 
@@
 
-In this study we show that different sensory stimuli retuned neurons in the optic tectum of \textit{Xenopus} tadpoles in different ways, thereby inducing changes in both their temporal tuning and amplitude transfer functions.
-This addresses our first question about the functional scope of intrinsic plasticity in the optic tectum, and shows that it goes well beyond simple adjustments of neuronal excitability.
+In this study, we show that stimuli of different temporal dynamics differentially retune \textit{Xenopus} tectal neurons, changing both their temporal and amplitude transfer functions (Figure 2).
+This addresses the first question of this study, about the functional scope of intrinsic plasticity in the tectum, and shows that it goes well beyond simple adjustments of neuronal excitability.
 
-As our technical resources were rather limited, in this study we don't explicitly address the mechanisms of this newly discovered intrinsic temporal tuning.
-We can, however, offer two working hypotheses that may explain these results.
-As tadpole tectal cells don't express "true" resonance currents, such as h-currents \citep{ciarleglio2015}, most temporal tuning effects we observed seem to be due to differences in ionic current inactivation in different cells \citep{azouz2000threshold, fontaine2014threshold}.
-One obvious way of tuning ionic channel inactivation would be for every cell to modulate sodium or transient potassium currents via channel phosphorylation, or by changing the expression of different channel variants, to shift their inactivation dynamics \citep{frank2003nachannels,goldwyn2018a_current}.
-To test this hypothesis, one would need to induce changes in temporal tuning similarly to how we did in this paper, pharmacologically isolate different ionic currents, and directly measure their inactivation dynamics \citep{zbili2019axonnav}.
+In answer to our second question about whether intrinsic and synaptic temporal properties of tectal cells are in any way coordinated, we show that they are weakly co-tuned, and moreover, that this co-tuning is modified by sensory experience (Figure 3).
+In contrast with earlier studies that reported increased excitability after sensory stimulation \citep{aizenman2003, dong2009, ciarleglio2015}, we found that stimulation led to a suppression of spiking, and potentiation of fast monosynaptic inputs from the eye.
+We believe that the reason for this difference is that in earlier studies, the visual stimulation was provided with very bright, high-contrasted LEDs, which caused a suppression of synaptic inputs via a polyamine block of AMPA receptors \citep{aizenman2003}.
+This suppression then triggered a "second-order" homeostatic compensation \citep{turrigiano2011, tien2018}, making neurons spikier.
+In our current experiments, synaptic inputs were not suppressed, and so synaptic drive during sensory conditioning had to be stronger than in control \citep{khakhalin2014}, causing a decrease in intrinsic excitability.
 
-Another hypothetical mechanism that can underlie our results is inspired by a yet unexplained finding from our earlier study \citep{ciarleglio2015}: namely, that one of the key electrophysiological parameters regulating excitability of tectal cells is cell membrane capacitance (Cm).
-Traditionally, cell capacitance is thought to be a relatively immutable parameter that describes cell morphology, and can even be used to estimate cell size.
-Yet, in the tadpole tectum, we found it to decrease both with age and after strong sensory stimulation, even though cells don't seem to change their visual appearance (\citealt{ciarleglio2015}, Figure 7D).
-An intriguing possibility is that these changes in cell capacitance may be due to electric uncoupling of three major compartments of \textit{Xenopus} tectal cells: their dendritic tree, soma, and axon initial segment \citep{bollmann2009,jarvis2018morphology}.
-This differential uncoupling may be achieved through either minor changes in cell morphology \citep{leterrier2018axon}, or through target modulation of potassium channels at key points between the compartments, to introduce shunting \citep{murakoshi1997kv2phosphorilation}, and strongly affect cell excitability \citep{grubb2010activity,kuba2010initial}.
-One way to test this hypothesis could be to perform immunostaining of cleared tectum preparation after sensory stimulation, and if any changes in the distribution of sodium and potassium channels is discovered, to validate the effect of these changes in a computational model.
+Trying to answer the third question, about the potential mechanism behind the intrinsic temporal tuning variability, we found that tuning of individual tectal cells could not be reliably predicted from their lower-level electrophysiological properties (Figure 4).
+This made our dynamic clamp results (Figure 1) very different from the results of a "classic" current clamp protocol (Figure 4C).
+While in dynamic clamp spiking responses were temporally tuned, affected by stimulation, and did not coordinate with low-level intrinsic parameters, spiking recorded in a standard current clamp mode did not show temporal tuning \citep{ciarleglio2015}, was not shaped by stimulation (in this study), yet was well coordinated with intrinsic parameters.
 
-In answer to our second question about whether intrinsic and synaptic properties of tectal cells are in any way coordinated, here we show that intrinsic and synaptic temporal properties are co-tuned in the tectum, and moreover, that this co-tuning can be modified by sensory experience.
-In contrast with earlier studies that report increased excitability post-stimulation \citep{aizenman2003,dong2009,ciarleglio2015}, we found that sensory stimulation led to a suppression of spiking.
-The reason for that, most probably, is that the visual stimulation used in earlier studies was provided with a LED box, which was so bright and of so high contrast that it caused a suppression of retinal synaptic inputs via a polyamine block of AMPA receptors \citep{aizenman2003}.
-This suppression then triggered a “second-order” homeostatic compensation \citep{turrigiano2011,tien2018}, making neurons spikier.
-In our current experiments, however, synaptic inputs were not suppressed, and neuronal activation during sensory conditioning was stronger than in control, causing a decrease in intrinsic excitability.
+This difference between neuronal responses in the dynamic clamp and fixed current clamp experiments may be interpreted in two ways.
+A pessimistic take would be to argue that the dynamic clamp in the soma offered a bad approximation of peripheral synaptic inputs, as space clamp errors are known to be more pronounced for fast voltage waveforms than for constant current injections \citep{spruston1993, prinz2004}.
+We however find this hypothesis unlikely, as our dynamic clamp responses were consistently different in animals with different sensory history, suggesting that we have captured some important aspects of intrinsic tuning diversity, even if our estimations were biased.
 
-Our study described an important difference between dynamic clamp results (that were affected by stimulation, but could not be explained through low-level intrinsic parameters) and the results obtained in "classical" slow clamp experiments (that were not affected by stimulation, yet better coordinated with intrinsic parameters).
-This difference may be interpreted in two ways.
-One approach would be to argue that dynamic clamp in the soma offered a bad approximation of peripheral synaptic inputs, as space clamp error is expected to be more pronounced for fast voltage fluctuations than for constant current injections \citep{spruston1993,prinz2004}.
-We find this hypothesis unlikely, however, as our dynamic clamp responses were consistently different in animals with different sensory history, which suggests that we have captured some important aspects of intrinsic diversity, even if our estimations were biased.
+Another, and in our opinion more likely explanation, is that intrinsic excitability of tectal cells is shaped by mechanisms that are not easily accessible by slow voltage- and current-clamp protocols, such as changes in voltage-gated channel inactivation \citep{azouz2000threshold}, and axon initial segment decoupling \citep{grubb2010activity, kuba2010initial, kole2012}.
+Let us address these two potential mechanisms separately.
 
-Another, and in our opinion more likely explanation, is that intrinsic excitability of tectal cells is shaped by mechanisms such as axon initial segment relocation, or targeted modulation of voltage-gated channels \citep{grubb2010activity, kole2012}, that both are not easily accessible by standard slow voltage and current clamp protocols.
-In cells with excitable dendrites, channels of the axon initial segment may constitute only a small fraction of all voltage-gated channels, yet have a disproportionately large effect on the spiking output of the cell, and on its temporal tuning \citep{kole2007,hamada2016}.
-Furthermore, prolonged current injections in the soma are likely to quickly inactivate transient channels in the axon, obscuring any possible interplay between action potential width and Na channel recovery during burst firing \citep{popovic2011,kole2012,fontaine2014threshold}.
-At the same time, these effects would still strongly affect spiking in more realistic, fast dynamic clamp experiments \citep{clay2012optimal,zbili2019axonnav}.
+First, while tectal neurons lack "true" resonant currents, such as Ih currents \citep{ciarleglio2015}, much of temporal tuning can be achieved through the adjustment of sodium and potassium current inactivation \citep{azouz2000threshold, fontaine2014threshold}, either via channel phosphorylation, or through the expression of channels with different inactivation dynamics \citep{frank2003nachannels, goldwyn2018a_current}.
+Crucially however, if these channels are located far from the soma, a prolonged current injection would quickly inactivate them, obscuring any possible interplay between action potential shape and sodium channel recovery that are critical for burst firing \citep{popovic2011, kole2012, fontaine2014threshold}.
+These effects however would be fully at play during responses to faster, and more biophysically realistic dynamic clamp experiments \citep{clay2012optimal, zbili2019axonnav}.
 
-Our findings lead to several verifiable predictions.
-As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014,jang2016}, a change in temporal tuning should affect collision detection dynamics, which can be verified experimentally.
-More specifically, we predict that a visual stimulation that retunes neurons to faster stimuli (Flash) would make tadpoles selectively less responsive to slow collisions, and increase the latency of collision avoidance due to non-linear dynamics of retinal activation for realistic looming stimuli that are slow in the beginning and fast towards the end \citep{jang2016}.
-These changes in intrinsic temporal tuning would also reshape the connectivity of tectal networks, as fast-inactivating cells would not support short recurrent loops within the network, thus promoting long-ranged polysynaptic connectivity \citep{fiete2010stdp,clopath2010stdp}.
-Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it may reduce peak activation in vivo.
+Second, we know that some subcellular compartments, such as the axon initial segment or excitable dendrites, have a disproportionally strong influence on neuronal tuning \citep{jarvis2018morphology, moldwin2019perceptron}.
+Even a minor change in electrical coupling between these compartments, either because of structural changes in cell morphology \citep{grubb2010activity, kuba2010initial, leterrier2018axon}, or due to modulation of channels at key integrative positions within the dendritic tree \citep{murakoshi1997kv2phosphorilation}, may lead to drastic changes in neuronal responses.
+And yet, the  channels at these key positions may constitute only a small fraction of all voltage-gated channels in the cell, making them practically "invisible" in classic current clamp experiments \citep{kole2007, hamada2016}.
+
+The hypothesis that tuning of tectal neurons may rely on subtle reorganization of their dendritic trees, or axons branching from these trees \citep{lazar1973golgi}, is also particularly exciting in view of the unexplained finding from our earlier study, in which cell membrane capacitance (Cm) was found to decrease after strong sensory stimulation (\citealt{ciarleglio2015}, Figure 7D).
+Cell membrane capacitance is often thought to be relatively immutable, and is even used to estimate cell size.
+For this reason, the change in electrical coupling between different compartments of a cell may be one the few plausible explanations for the rapid modulation of this parameter in response to sensory stimulation.
+
+The best way to differentiate between these two hypotheses would be to explicitly measure sodium and potassium current inactivation \citep{zbili2019axonnav} in tadpoles exposed to different types of sensory stimulation.
+One could also use pharmacological interventions to provide negative and positive control groups for this study.
+It would be even better to follow it up with immunostaining of cleared tectal preparations, and look whether the distribution of sodium and potassium channels is changed after sensory stimulation.
+Finally, all these observations can be validated in a biophysical computational model of a tectal neuron.
+
+Our findings also lead to several verifiable predictions.
+As rapid inactivation of spiking in tectal neurons plays a role in collision detection \citep{khakhalin2014, jang2016}, a change in temporal tuning should affect loom detection, which can be verified experimentally.
+We predict that instantaneous flashes that suppress responses to slow inputs would selectively disrupt slow collision avoidance \citep{khakhalin2014}.
+The changes in intrinsic temporal tuning would also reshape tectal connectivity, as fast-inactivating cells would not support short recurrent loops within the network, thus indirectly promoting long-ranged polysynaptic connectivity \citep{fiete2010stdp, clopath2010stdp, khakhalin2019graph}.
+Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro \citep{felch2016,truszkowski2017}, it may actually reduce peak activation in vivo.
 
@@
 
-To sum up, we present a novel case of temporal selectivity in non-oscillatory neurons in a distributed sensory network, and demonstrate that intrinsic temporal tuning of neural cells correlates with their synaptic properties.
-It is particularly interesting that the temporal co-tuning we observed was homeostatic in nature, as cells tended to be selective for inputs of dynamics they did not usually experience.
-We hypothesize that this adjustment of temporal tuning is the reason why this tuning was so easily disrupted by strong visual stimulation, when for a few hours we drastically changed the statistics of inputs received by every cell.
-Tuning to "unusual stimuli" at the level of individual neurons fits into the narrative of information transfer maximization \citep{stemmler1999information,brenner2000} and network criticality \citep{rubinov2011}, wherein every element of a network tries to locally maximize its influence over the overall computation.
-This may have intriguing consequences for the function and development of sensory networks in the brain, which can be further probed by computational modeling \citep{khakhalin2014,jang2016}, and verified experimentally.
-We also suspect that any cell with a sufficiently large dendritic tree would be able to tune its temporal intrinsic selectivity the way we describe.
-We expect that in most cases these changes would not be noticeable in experiments with standard voltage- and current-clamp protocols, but can be probed with a dynamic clamp technique.
-It would therefore be very interesting to see whether our results will replicate in other sensory systems, such as the mammalian cortex.
+To sum up, we present a novel case of temporal selectivity in non-oscillatory neurons in a sensory network, and demonstrate that intrinsic temporal tuning of neural cells correlates with their synaptic properties, and is modified by sensory experiences.
+We also argue that any cell with a sufficiently complex morphology could be able to tune its intrinsic temporal selectivity in ways we describe in this paper.
+Crucially, we expect that in many cases this tuning would not be noticeable in experiments that use standard voltage- and current-clamp protocols, yet can be easily uncovered with a dynamic clamp technique.
+It would therefore be interesting to see whether our results will replicate in other sensory systems.
 
@@
 For Control and Sound groups, the monitor was on, but showed a uniform 50\% gray background.
-For Flash, Sync and Async groups the screen showed a black-and-white checkerboard pattern, with each square in the pattern being 14 mm wide; this pattern flipped (inverted) every 1 second.
+For Flash, Sync, and Async groups the screen showed a black-and-white checkerboard pattern, with each square in the pattern being 14 mm wide; this pattern flipped (inverted) every 1 second.
 For the Looming group, the inversion of the pattern was not instantaneous, but lasted for one second, with old black squares linearly shrinking into white background, and new black squares appearing and linearly expanding in the middle of each white square (Figure 1C).
@@
 In total, we recorded from 188 neurons in 35 tadpoles; of these, 159 cells had readings from all 4 protocols, while 12 lacked synaptic recordings; these 12 cells were scattered across all 6 experimental groups.
-After the recording was over, the position of each recorded cell was visualized with a 10x microscope, marked on a screen, measured in medial and rostral directions relative to the most latero-caudal point of the tectum, and converted into percentage \citep{hamodi2014}.
+After the recording was over, the position of each recorded cell was visualized with a 10x microscope, marked on a screen, measured in medial and rostral directions relative to the most latero-caudal point of the tectum, and converted into a percentage \citep{hamodi2014}.
 

### 2019-06-10 reviews and responses.md
Chagnes accepted, + slight rewording for the last paragraph.
Official resubmission

@@
 This word is often used in writing (a Google Scholar search for `"distributed network" brain` returns 27000 hits), but admittedly it is not a precisely defined term, but rather a useful qualifier.
-If you think that this word is not appropriate here, please let us know, and we will remove it.
+We removed the word "distributed" from this sentence, in the interest of brevity, but retained it in the second paragraph of the Introduction.
 
@@
 
-To show that our statement is just a conjecture, we replaced "suggets" with "may suggest" in this sentence: "This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning..."
+To show that our statement is just a conjecture, we replaced "suggests" with "may suggest" in this sentence: "This may suggest that acoustic stimuli did not activate tectal circuits strongly enough during conditioning..."
 

### 2019-06-10 merged.tex
Official resubmission

--- 2019-06-07 main.tex
@@
 
+\usepackage{filecontents}
+\begin{filecontents}{localref.bib}
+
+@article{lazar1973golgi,
+  title={The development of the optic tectum in Xenopus laevis: a Golgi study.},
+  author={Lazar, GY},
+  journal={Journal of Anatomy},
+  volume={116},
+  number={Pt 3},
+  pages={347},
+  year={1973},
+  publisher={Wiley-Blackwell}
+}
+
+@article{meredith1983,
+  title={Interactions among converging sensory inputs in the superior colliculus},
+  author={Meredith, M Alex and Stein, Barry E},
+  journal={Science},
+  volume={221},
+  number={4608},
+  pages={389--391},
+  year={1983},
+  publisher={American Association for the Advancement of Science}
+}
+
+@article{spruston1993,
+  title={Voltage-and space-clamp errors associated with the measurement of electrotonically remote synaptic events},
+  author={Spruston, Nelson and Jaffe, David B and Williams, Stephen H and Johnston, Daniel},
+  journal={Journal of Neurophysiology},
+  volume={70},
+  number={2},
+  pages={781--802},
+  year={1993},
+  publisher={Am Physiological Soc}
+}
+
+@article{destexhe1994,
+  title={Synthesis of models for excitable membranes, synaptic transmission and neuromodulation using a common kinetic formalism},
+  author={Destexhe, Alain and Mainen, Zachary F and Sejnowski, Terrence J},
+  journal={Journal of computational neuroscience},
+  volume={1},
+  number={3},
+  pages={195--230},
+  year={1994},
+  publisher={Springer}
+}
+
+@book{nieuwkoop1994,
+  title={Normal table of Xenopus laevis (Daudin): A Systematical and Chronological Survey of the Development from the Fertilized Egg till the end of Metamorphosis.},
+  author={Nieuwkoop, Pieter D and Faber, Jacob},
+  year={1994}
+}
+
+@article{ma1996dynamic,
+  title={The role of K+ currents in frequency-dependent spike broadening in Aplysia R20 neurons: a dynamic-clamp analysis},
+  author={Ma, Minghong and Koester, John},
+  journal={Journal of Neuroscience},
+  volume={16},
+  number={13},
+  pages={4089--4101},
+  year={1996},
+  publisher={Soc Neuroscience}
+}
+
+@article{wu1996,
+  title={Maturation of a central glutamatergic synapse},
+  author={Wu, G-Y and Malinow, R and Cline, HT},
+  journal={Science},
+  volume={274},
+  number={5289},
+  pages={972--976},
+  year={1996},
+  publisher={American Association for the Advancement of Science}
+}
+
+@article{debanne1997,
+  title={Action-potential propagation gated by an axonal I A-like K+ conductance in hippocampus},
+  author={Debanne, Dominique and Guerineau, Nathalie C and G{\"a}hwiler, Beat H and Thompson, Scott M},
+  journal={Nature},
+  volume={389},
+  number={6648},
+  pages={286},
+  year={1997},
+  publisher={Nature Publishing Group}
+}
+
+@article{murakoshi1997kv2phosphorilation,
+  title={Phosphorylation of the Kv2. 1 K+ channel alters voltage-dependent activation},
+  author={Murakoshi, Hideyuki and Shi, Gongyi and Scannevin, Robert H and Trimmer, James S},
+  journal={Molecular pharmacology},
+  volume={52},
+  number={5},
+  pages={821--828},
+  year={1997},
+  publisher={ASPET}
+}
+
+@article{jaeger1999,
+  title={Synaptic control of spiking in cerebellar Purkinje cells: dynamic current clamp based on model conductances},
+  author={Jaeger, Dieter and Bower, James M},
+  journal={Journal of Neuroscience},
+  volume={19},
+  number={14},
+  pages={6090--6101},
+  year={1999},
+  publisher={Soc Neuroscience}
+}
+
+@article{kanold1999transient_k,
+  title={Transient potassium currents regulate the discharge patterns of dorsal cochlear nucleus pyramidal cells},
+  author={Kanold, Patrick O and Manis, Paul B},
+  journal={Journal of Neuroscience},
+  volume={19},
+  number={6},
+  pages={2195--2208},
+  year={1999},
+  publisher={Soc Neuroscience}
+}
+
+@article{stemmler1999information,
+  title={How voltage-dependent conductances can adapt to maximize the information encoded by neuronal firing rate},
+  author={Stemmler, Martin and Koch, Christof},
+  journal={Nature neuroscience},
+  volume={2},
+  number={6},
+  pages={521},
+  year={1999},
+  publisher={Nature Publishing Group}
+}
+
+@article{azouz2000threshold,
+  title={Dynamic spike threshold reveals a mechanism for synaptic coincidence detection in cortical neurons in vivo},
+  author={Azouz, Rony and Gray, Charles M},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={97},
+  number={14},
+  pages={8110--8115},
+  year={2000},
+  publisher={National Acad Sciences}
+}
+
+@article{brenner2000,
+  title={Adaptive rescaling maximizes information transmission},
+  author={Brenner, Naama and Bialek, William and Van Steveninck, Rob de Ruyter},
+  journal={Neuron},
+  volume={26},
+  number={3},
+  pages={695--702},
+  year={2000},
+  publisher={Elsevier}
+}
+
+@article{hutcheon2000,
+  title={Resonance, oscillation and the intrinsic frequency preferences of neurons},
+  author={Hutcheon, Bruce and Yarom, Yosef},
+  journal={Trends in neurosciences},
+  volume={23},
+  number={5},
+  pages={216--222},
+  year={2000},
+  publisher={Elsevier}
+}
+
+@article{goldman2001,
+  title={Global structure, robustness, and modulation of neuronal models},
+  author={Goldman, Mark S and Golowasch, Jorge and Marder, Eve and Abbott, LF},
+  journal={Journal of Neuroscience},
+  volume={21},
+  number={14},
+  pages={5229--5238},
+  year={2001},
+  publisher={Soc Neuroscience}
+}
+
+@article{aizenman2002,
+  title={Visually driven modulation of glutamatergic synaptic transmission is mediated by the regulation of intracellular polyamines},
+  author={Aizenman, Carlos D and Munoz-Elias, Guillermo and Cline, Hollis T},
+  journal={Neuron},
+  volume={34},
+  number={4},
+  pages={623--634},
+  year={2002},
+  publisher={Elsevier}
+}
+
+@article{golowasch2002,
+  title={Failure of averaging in the construction of a conductance-based neuron model},
+  author={Golowasch, Jorge and Goldman, Mark S and Abbott, LF and Marder, Eve},
+  journal={Journal of Neurophysiology},
+  volume={87},
+  number={2},
+  pages={1129--1131},
+  year={2002},
+  publisher={Am Physiological Soc}
+}
+
+@article{aizenman2003,
+  title={Visually driven regulation of intrinsic neuronal excitability improves stimulus detection in vivo},
+  author={Aizenman, Carlos D and Akerman, Colin J and Jensen, Kendall R and Cline, Hollis T},
+  journal={Neuron},
+  volume={39},
+  number={5},
+  pages={831--842},
+  year={2003},
+  publisher={Elsevier}
+}
+
+@article{frank2003nachannels,
+  title={Overview of the voltage-gated sodium channel family},
+  author={Frank, H Yu and Catterall, William A},
+  journal={Genome biology},
+  volume={4},
+  number={3},
+  pages={207},
+  year={2003},
+  publisher={BioMed Central}
+}
+
+@article{prinz2004,
+  title={The dynamic clamp comes of age},
+  author={Prinz, Astrid A and Abbott, LF and Marder, Eve},
+  journal={Trends in neurosciences},
+  volume={27},
+  number={4},
+  pages={218--224},
+  year={2004},
+  publisher={Elsevier}
+}
+
+@article{prinz2004degeneracy,
+  title={Similar network activity from disparate circuit parameters},
+  author={Prinz, Astrid A and Bucher, Dirk and Marder, Eve},
+  journal={Nature neuroscience},
+  volume={7},
+  number={12},
+  pages={1345},
+  year={2004},
+  publisher={Nature Publishing Group}
+}
+
+@article{ishikane2005,
+  title={Synchronized retinal oscillations encode essential information for escape behavior in frogs},
+  author={Ishikane, Hiroshi and Gangi, Mie and Honda, Shoko and Tachibana, Masao},
+  journal={Nature neuroscience},
+  volume={8},
+  number={8},
+  pages={1087},
+  year={2005},
+  publisher={Nature Publishing Group}
+}
+
+@article{sporns2005,
+  title={The human connectome: a structural description of the human brain},
+  author={Sporns, Olaf and Tononi, Giulio and K{\"o}tter, Rolf},
+  journal={PLoS computational biology},
+  volume={1},
+  number={4},
+  pages={e42},
+  year={2005},
+  publisher={Public Library of Science}
+}
+
+@article{achard2006,
+  title={Complex parameter landscape for a complex neuron model},
+  author={Achard, Pablo and De Schutter, Erik},
+  journal={PLoS computational biology},
+  volume={2},
+  number={7},
+  pages={e94},
+  year={2006},
+  publisher={Public Library of Science}
+}
+
+@article{akerman2006,
+  title={Depolarizing GABAergic conductances regulate the balance of excitation to inhibition in the developing retinotectal circuit in vivo},
+  author={Akerman, Colin J and Cline, Hollis T},
+  journal={Journal of Neuroscience},
+  volume={26},
+  number={19},
+  pages={5117--5130},
+  year={2006},
+  publisher={Soc Neuroscience}
+}
+
+@article{kuba2006,
+  title={Axonal site of spike initiation enhances auditory coincidence detection},
+  author={Kuba, Hiroshi and Ishii, Takahiro M and Ohmori, Harunori},
+  journal={Nature},
+  volume={444},
+  number={7122},
+  pages={1069},
+  year={2006},
+  publisher={Nature Publishing Group}
+}
+
+@article{marder2006,
+  title={Variability, compensation and homeostasis in neuron and network function},
+  author={Marder, Eve and Goaillard, Jean-Marc},
+  journal={Nature Reviews Neuroscience},
+  volume={7},
+  number={7},
+  pages={563},
+  year={2006},
+  publisher={Nature Publishing Group}
+}
+
+@article{schulz2006,
+  title={Variable channel expression in identified single and electrically coupled neurons in different animals},
+  author={Schulz, David J and Goaillard, Jean-Marc and Marder, Eve},
+  journal={Nature neuroscience},
+  volume={9},
+  number={3},
+  pages={356},
+  year={2006},
+  publisher={Nature Publishing Group}
+}
+
+@article{aizenman2007,
+  title={Enhanced visual activity in vivo forms nascent synapses in the developing retinotectal projection},
+  author={Aizenman, Carlos D and Cline, Hollis T},
+  journal={Journal of neurophysiology},
+  volume={97},
+  number={4},
+  pages={2949--2957},
+  year={2007},
+  publisher={Am Physiological Soc}
+}
+
+@article{kole2007,
+  title={Axon initial segment Kv1 channels control axonal action potential waveform and synaptic efficacy},
+  author={Kole, Maarten HP and Letzkus, Johannes J and Stuart, Greg J},
+  journal={Neuron},
+  volume={55},
+  number={4},
+  pages={633--647},
+  year={2007},
+  publisher={Elsevier}
+}
+
+@article{pratt2007,
+  title={Homeostatic regulation of intrinsic excitability and synaptic transmission in a developing visual circuit},
+  author={Pratt, Kara G and Aizenman, Carlos D},
+  journal={Journal of Neuroscience},
+  volume={27},
+  number={31},
+  pages={8268--8277},
+  year={2007},
+  publisher={Soc Neuroscience}
+}
+
+@article{turrigiano2007,
+  title={Homeostatic signaling: the positive side of negative feedback},
+  author={Turrigiano, Gina},
+  journal={Current opinion in neurobiology},
+  volume={17},
+  number={3},
+  pages={318--324},
+  year={2007},
+  publisher={Elsevier}
+}
+
+@article{cline2008,
+  title={The regulation of dendritic arbor development and plasticity by glutamatergic synaptic input: a review of the synaptotrophic hypothesis},
+  author={Cline, Hollis and Haas, Kurt},
+  journal={The Journal of physiology},
+  volume={586},
+  number={6},
+  pages={1509--1517},
+  year={2008},
+  publisher={Wiley Online Library}
+}
+
+@article{ewald2008,
+  title={Roles of NR2A and NR2B in the development of dendritic arbor morphology in vivo},
+  author={Ewald, Rebecca C and Van Keuren-Jensen, Kendall R and Aizenman, Carlos D and Cline, Hollis T},
+  journal={Journal of Neuroscience},
+  volume={28},
+  number={4},
+  pages={850--861},
+  year={2008},
+  publisher={Soc Neuroscience}
+}
+
+@article{kole2008,
+  title={Action potential generation requires a high sodium channel density in the axon initial segment},
+  author={Kole, Maarten HP and Ilschner, Susanne U and Kampa, Bj{\"o}rn M and Williams, Stephen R and Ruben, Peter C and Stuart, Greg J},
+  journal={Nature neuroscience},
+  volume={11},
+  number={2},
+  pages={178},
+  year={2008},
+  publisher={Nature Publishing Group}
+}
+
+@article{narayanan2008,
+  title={The h channel mediates location dependence and plasticity of intrinsic phase response in rat hippocampal neurons},
+  author={Narayanan, Rishikesh and Johnston, Daniel},
+  journal={Journal of Neuroscience},
+  volume={28},
+  number={22},
+  pages={5846--5860},
+  year={2008},
+  publisher={Soc Neuroscience}
+}
+
+@article{pratt2008,
+  title={Development and spike timing--dependent plasticity of recurrent excitation in the Xenopus optic tectum},
+  author={Pratt, Kara G and Dong, Wei and Aizenman, Carlos D},
+  journal={Nature neuroscience},
+  volume={11},
+  number={4},
+  pages={467},
+  year={2008},
+  publisher={Nature Publishing Group}
+}
+
+@article{bollmann2009,
+  title={Subcellular topography of visually driven dendritic activity in the vertebrate visual system},
+  author={Bollmann, Johann H and Engert, Florian},
+  journal={Neuron},
+  volume={61},
+  number={6},
+  pages={895--905},
+  year={2009},
+  publisher={Elsevier}
+}
+
+@article{deeg2009,
+  title={Development of multisensory convergence in the Xenopus optic tectum},
+  author={Deeg, Katherine E and Sears, Irina B and Aizenman, Carlos D},
+  journal={Journal of Neurophysiology},
+  volume={102},
+  number={6},
+  pages={3392--3404},
+  year={2009},
+  publisher={American Physiological Society Bethesda, MD}
+}
+
+@article{dong2009,
+  title={Visual avoidance in Xenopus tadpoles is correlated with the maturation of visual responses in the optic tectum},
+  author={Dong, Wei and Lee, Ryan H and Xu, Heng and Yang, Shelley and Pratt, Kara G and Cao, Vania and Song, Yoon-Kyu and Nurmikko, Arto and Aizenman, Carlos D},
+  journal={Journal of neurophysiology},
+  volume={101},
+  number={2},
+  pages={803--815},
+  year={2009},
+  publisher={Am Physiological Soc}
+}
+
+@article{giocomo2009,
+  title={Knock-out of HCN1 subunit flattens dorsal--ventral frequency gradient of medial entorhinal neurons in adult mice},
+  author={Giocomo, Lisa M and Hasselmo, Michael E},
+  journal={Journal of Neuroscience},
+  volume={29},
+  number={23},
+  pages={7625--7630},
+  year={2009},
+  publisher={Soc Neuroscience}
+}
+
+@article{goaillard2009,
+  title={Functional consequences of animal-to-animal variation in circuit parameters},
+  author={Goaillard, Jean-Marc and Taylor, Adam L and Schulz, David J and Marder, Eve},
+  journal={Nature neuroscience},
+  volume={12},
+  number={11},
+  pages={1424},
+  year={2009},
+  publisher={Nature Publishing Group}
+}
+
+@article{hiramoto2009,
+  title={Convergence of multisensory inputs in Xenopus tadpole tectum},
+  author={Hiramoto, Masaki and Cline, Hollis T},
+  journal={Developmental neurobiology},
+  volume={69},
+  number={14},
+  pages={959--971},
+  year={2009},
+  publisher={Wiley Online Library}
+}
+
+@article{lukovsevivcius2009,
+  title={Reservoir computing approaches to recurrent neural network training},
+  author={Luko{\v{s}}evi{\v{c}}ius, Mantas and Jaeger, Herbert},
+  journal={Computer Science Review},
+  volume={3},
+  number={3},
+  pages={127--149},
+  year={2009},
+  publisher={Elsevier}
+}
+
+@article{marcelin2009,
+  title={H channel-dependent deficit of theta oscillation resonance and phase shift in temporal lobe epilepsy},
+  author={Marcelin, B{\'e}atrice and Chauvi{\`e}re, La{\"e}titia and Becker, Albert and Migliore, Michele and Esclapez, Monique and Bernard, Christophe},
+  journal={Neurobiology of disease},
+  volume={33},
+  number={3},
+  pages={436--447},
+  year={2009},
+  publisher={Elsevier}
+}
+
+@article{pratt2009trigeminal,
+  title={Multisensory integration in mesencephalic trigeminal neurons in Xenopus tadpoles},
+  author={Pratt, Kara G and Aizenman, Carlos D},
+  journal={Journal of neurophysiology},
+  volume={102},
+  number={1},
+  pages={399--412},
+  year={2009},
+  publisher={Am Physiological Soc}
+}
+
+@article{taylor2009,
+  title={How multiple conductances determine electrophysiological properties in a multicompartment model},
+  author={Taylor, Adam L and Goaillard, Jean-Marc and Marder, Eve},
+  journal={Journal of Neuroscience},
+  volume={29},
+  number={17},
+  pages={5573--5586},
+  year={2009},
+  publisher={Soc Neuroscience}
+}
+
+@article{branco2010dendritic,
+  title={Dendritic discrimination of temporal input sequences in cortical neurons},
+  author={Branco, Tiago and Clark, Beverley A and H{\"a}usser, Michael},
+  journal={Science},
+  volume={329},
+  number={5999},
+  pages={1671--1675},
+  year={2010},
+  publisher={American Association for the Advancement of Science}
+}
+
+@article{clopath2010stdp,
+  title={Connectivity reflects coding: a model of voltage-based STDP with homeostasis},
+  author={Clopath, Claudia and B{\"u}sing, Lars and Vasilaki, Eleni and Gerstner, Wulfram},
+  journal={Nature neuroscience},
+  volume={13},
+  number={3},
+  pages={344},
+  year={2010},
+  publisher={Nature Publishing Group}
+}
+
+@article{grashow2010,
+  title={Compensation for variable intrinsic neuronal excitability by circuit-synaptic interactions},
+  author={Grashow, Rachel and Brookings, Ted and Marder, Eve},
+  journal={Journal of Neuroscience},
+  volume={30},
+  number={27},
+  pages={9145--9156},
+  year={2010},
+  publisher={Soc Neuroscience}
+}
+
+@article{grubb2010activity,
+  title={Activity-dependent relocation of the axon initial segment fine-tunes neuronal excitability},
+  author={Grubb, Matthew S and Burrone, Juan},
+  journal={Nature},
+  volume={465},
+  number={7301},
+  pages={1070},
+  year={2010},
+  publisher={Nature Publishing Group}
+}
+
+@article{fiete2010stdp,
+  title={Spike-time-dependent plasticity and heterosynaptic competition organize networks to produce long scale-free sequences of neural activity},
+  author={Fiete, Ila R and Senn, Walter and Wang, Claude ZH and Hahnloser, Richard HR},
+  journal={Neuron},
+  volume={65},
+  number={4},
+  pages={563--576},
+  year={2010},
+  publisher={Elsevier}
+}
+
+@article{kuba2010initial,
+  title={Presynaptic activity regulates Na+ channel distribution at the axon initial segment},
+  author={Kuba, Hiroshi and Oichi, Yuki and Ohmori, Harunori},
+  journal={Nature},
+  volume={465},
+  number={7301},
+  pages={1075},
+  year={2010},
+  publisher={Nature Publishing Group}
+}
+
+@article{markram2010,
+  title={The intense world theory--a unifying theory of the neurobiology of autism},
+  author={Markram, Kamila and Markram, Henry},
+  journal={Frontiers in human neuroscience},
+  volume={4},
+  pages={224},
+  year={2010},
+  publisher={Frontiers}
+}
+
+@misc{calabrese2011,
+  title={Coping with variability in small neuronal networks},
+  author={Calabrese, Ronald L and Norris, Brian J and Wenning, Angela and Wright, Terrence M},
+  year={2011},
+  publisher={Oxford University Press}
+}
+
+@article{deeg2011,
+  title={Sensory modality--specific homeostatic plasticity in the developing optic tectum},
+  author={Deeg, Katherine E and Aizenman, Carlos D},
+  journal={Nature neuroscience},
+  volume={14},
+  number={5},
+  pages={548},
+  year={2011},
+  publisher={Nature Publishing Group}
+}
+
+@article{marder2011,
+  title={Multiple models to capture the variability in biological neurons and networks},
+  author={Marder, Eve and Taylor, Adam L},
+  journal={Nature neuroscience},
+  volume={14},
+  number={2},
+  pages={133},
+  year={2011},
+  publisher={Nature Publishing Group}
+}
+
+@article{platkiewicz2011,
+  title={Impact of fast sodium channel inactivation on spike threshold dynamics and synaptic integration},
+  author={Platkiewicz, Jonathan and Brette, Romain},
+  journal={PLoS computational biology},
+  volume={7},
+  number={5},
+  pages={e1001129},
+  year={2011},
+  publisher={Public Library of Science}
+}
+
+@article{popovic2011,
+  title={The spatio-temporal characteristics of action potential initiation in layer 5 pyramidal neurons: a voltage imaging study},
+  author={Popovic, Marko A and Foust, Amanda J and McCormick, David A and Zecevic, Dejan},
+  journal={The Journal of physiology},
+  volume={589},
+  number={17},
+  pages={4167--4187},
+  year={2011},
+  publisher={Wiley Online Library}
+}
+
+@article{rubinov2011,
+  title={Neurobiologically realistic determinants of self-organized criticality in networks of spiking neurons},
+  author={Rubinov, Mikail and Sporns, Olaf and Thivierge, Jean-Philippe and Breakspear, Michael},
+  journal={PLoS computational biology},
+  volume={7},
+  number={6},
+  pages={e1002038},
+  year={2011},
+  publisher={Public Library of Science}
+}
+
+@article{shen2011,
+  title={Inhibition to excitation ratio regulates visual system responses and behavior in vivo},
+  author={Shen, Wanhua and McKeown, Caroline R and Demas, James A and Cline, Hollis T},
+  journal={Journal of neurophysiology},
+  volume={106},
+  number={5},
+  pages={2285--2302},
+  year={2011},
+  publisher={American Physiological Society Bethesda, MD}
+}
+
+@article{sridharan2011,
+  title={Space coding by gamma oscillations in the barn owl optic tectum},
+  author={Sridharan, Devarajan and Boahen, Kwabena and Knudsen, Eric I},
+  journal={Journal of neurophysiology},
+  volume={105},
+  number={5},
+  pages={2005--2017},
+  year={2011},
+  publisher={American Physiological Society Bethesda, MD}
+}
+
+@article{turrigiano2011,
+  title={Too many cooks? Intrinsic and synaptic homeostatic mechanisms in cortical circuit refinement},
+  author={Turrigiano, Gina},
+  journal={Annual review of neuroscience},
+  volume={34},
+  pages={89--103},
+  year={2011},
+  publisher={Annual Reviews}
+}
+
+@article{xu2011,
+  title={Visual experience-dependent maturation of correlated neuronal activity patterns in a developing visual system},
+  author={Xu, Heng and Khakhalin, Arseny S and Nurmikko, Arto V and Aizenman, Carlos D},
+  journal={Journal of Neuroscience},
+  volume={31},
+  number={22},
+  pages={8025--8036},
+  year={2011},
+  publisher={Soc Neuroscience}
+}
+
+@article{baranauskas2012,
+  title={20 Hz membrane potential oscillations are driven by synaptic inputs in collision-detecting neurons in the frog optic tectum},
+  author={Baranauskas, Gytis and Svirskiene, Natasa and Svirskis, Gytis},
+  journal={Neuroscience letters},
+  volume={528},
+  number={2},
+  pages={196--200},
+  year={2012},
+  publisher={Elsevier}
+}
+
+@article{bianchi2012,
+  title={On the mechanisms underlying the depolarization block in the spiking dynamics of CA1 pyramidal neurons},
+  author={Bianchi, Daniela and Marasco, Addolorata and Limongiello, Alessandro and Marchetti, Cristina and Marie, Helene and Tirozzi, Brunello and Migliore, Michele},
+  journal={Journal of computational neuroscience},
+  volume={33},
+  number={2},
+  pages={207--225},
+  year={2012},
+  publisher={Springer}
+}
+
+@article{clay2012optimal,
+  title={Ionic mechanism underlying optimal stimuli for neuronal excitation: role of Na+ channel inactivation},
+  author={Clay, John R and Forger, Daniel B and Paydarfar, David},
+  journal={PloS one},
+  volume={7},
+  number={9},
+  pages={e45983},
+  year={2012},
+  publisher={Public Library of Science}
+}
+
+@article{goddard2012,
+  title={Gamma oscillations are generated locally in an attention-related midbrain network},
+  author={Goddard, C Alex and Sridharan, Devarajan and Huguenard, John R and Knudsen, Eric I},
+  journal={Neuron},
+  volume={73},
+  number={3},
+  pages={567--580},
+  year={2012},
+  publisher={Elsevier}
+}
+
+@article{khakhalin2012,
+  title={GABAergic transmission and chloride equilibrium potential are not modulated by pyruvate in the developing optic tectum of Xenopus laevis tadpoles},
+  author={Khakhalin, Arseny S and Aizenman, Carlos D},
+  journal={PLoS One},
+  volume={7},
+  number={4},
+  pages={e34446},
+  year={2012},
+  publisher={Public Library of Science}
+}
+
+@article{kole2012,
+  title={Signal processing in the axon initial segment},
+  author={Kole, Maarten HP and Stuart, Greg J},
+  journal={Neuron},
+  volume={73},
+  number={2},
+  pages={235--247},
+  year={2012},
+  publisher={Elsevier}
+}
+
+@article{kuba2012,
+  title={Structural tuning and plasticity of the axon initial segment in auditory neurons},
+  author={Kuba, Hiroshi},
+  journal={The Journal of physiology},
+  volume={590},
+  number={22},
+  pages={5571--5579},
+  year={2012},
+  publisher={Wiley Online Library}
+}
+
+@article{bengio2013,
+  title={Representation learning: A review and new perspectives},
+  author={Bengio, Yoshua and Courville, Aaron and Vincent, Pascal},
+  journal={IEEE transactions on pattern analysis and machine intelligence},
+  volume={35},
+  number={8},
+  pages={1798--1828},
+  year={2013},
+  publisher={IEEE}
+}
+
+@article{colgin2013,
+  title={Mechanisms and functions of theta rhythms},
+  author={Colgin, Laura Lee},
+  journal={Annual review of neuroscience},
+  volume={36},
+  pages={295--312},
+  year={2013},
+  publisher={Annual Reviews}
+}
+
+@article{kirkby2013,
+  title={A role for correlated spontaneous activity in the assembly of neural circuits},
+  author={Kirkby, Lowry A and Sack, Georgeann S and Firl, Alana and Feller, Marla B},
+  journal={Neuron},
+  volume={80},
+  number={5},
+  pages={1129--1144},
+  year={2013},
+  publisher={Elsevier}
+}
+
+@article{oleary2013,
+  title={Correlations in ion channel expression emerge from homeostatic tuning rules},
+  author={O'Leary, Timothy and Williams, Alex H and Caplan, Jonathan S and Marder, Eve},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={110},
+  number={28},
+  pages={E2645--E2654},
+  year={2013},
+  publisher={National Acad Sciences}
+}
+
+@article{pratt2013,
+  title={Modeling human neurodevelopmental disorders in the Xenopus tadpole: from mechanisms to therapeutic targets},
+  author={Pratt, Kara G and Khakhalin, Arseny S},
+  journal={Disease models \& mechanisms},
+  pages={dmm--012138},
+  year={2013},
+  publisher={The Company of Biologists Ltd}
+}
+
+@book{venables2013,
+  title={Modern applied statistics with S-PLUS},
+  author={Venables, William N and Ripley, Brian D},
+  year={2013},
+  publisher={Springer Science \& Business Media}
+}
+
+@article{bates2014,
+  title={Fitting linear mixed-effects models using lme4},
+  author={Bates, Douglas and M{\"a}chler, Martin and Bolker, Ben and Walker, Steve},
+  journal={arXiv preprint arXiv:1406.5823},
+  year={2014}
+}
+
+@article{beatty2014,
+  title={Cell-type-specific resonances shape the responses of striatal neurons to synaptic input},
+  author={Beatty, Joseph A and Song, Soomin C and Wilson, Charles J},
+  journal={Journal of neurophysiology},
+  volume={113},
+  number={3},
+  pages={688--700},
+  year={2014},
+  publisher={American Physiological Society Bethesda, MD}
+}
+
+@article{fontaine2014threshold,
+  title={Spike-threshold adaptation predicted by membrane potential dynamics in vivo},
+  author={Fontaine, Bertrand and Pe{\~n}a, Jos{\'e} Luis and Brette, Romain},
+  journal={PLoS computational biology},
+  volume={10},
+  number={4},
+  pages={e1003560},
+  year={2014},
+  publisher={Public Library of Science}
+}
+
+@article{hamodi2014,
+  title={Region-specific regulation of voltage-gated intrinsic currents in the developing optic tectum of the Xenopus tadpole},
+  author={Hamodi, Ali S and Pratt, Kara G},
+  journal={Journal of neurophysiology},
+  volume={112},
+  number={7},
+  pages={1644--1655},
+  year={2014},
+  publisher={Am Physiological Soc}
+}
+
+@article{khakhalin2014,
+  title={Excitation and inhibition in recurrent networks mediate collision avoidance in Xenopus tadpoles},
+  author={Khakhalin, Arseny S and Koren, David and Gu, Jenny and Xu, Heng and Aizenman, Carlos D},
+  journal={European Journal of Neuroscience},
+  volume={40},
+  number={6},
+  pages={2948--2962},
+  year={2014},
+  publisher={Wiley Online Library}
+}
+
+@article{stein2014,
+  title={Development of multisensory integration from the perspective of the individual neuron},
+  author={Stein, Barry E and Stanford, Terrence R and Rowland, Benjamin A},
+  journal={Nature Reviews Neuroscience},
+  volume={15},
+  number={8},
+  pages={520},
+  year={2014},
+  publisher={Nature Publishing Group}
+}
+
+@article{takemura2014,
+  title={Connectome of the fly visual circuitry},
+  author={Takemura, Shin-ya},
+  journal={Microscopy},
+  volume={64},
+  number={1},
+  pages={37--44},
+  year={2014},
+  publisher={Oxford University Press}
+}
+
+@article{ciarleglio2015,
+  title={Multivariate analysis of electrophysiological diversity of Xenopus visual neurons during development and plasticity},
+  author={Ciarleglio, Christopher M and Khakhalin, Arseny S and Wang, Angelia F and Constantino, Alexander C and Yip, Sarah P and Aizenman, Carlos D},
+  journal={Elife},
+  volume={4},
+  year={2015},
+  publisher={eLife Sciences Publications, Ltd}
+}
+
+@article{drion2015,
+  title={Ion channel degeneracy enables robust and tunable neuronal firing rates},
+  author={Drion, Guillaume and O’Leary, Timothy and Marder, Eve},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={112},
+  number={38},
+  pages={E5361--E5370},
+  year={2015},
+  publisher={National Acad Sciences}
+}
+
+@article{evans2015,
+  title={Rapid modulation of axon initial segment length influences repetitive spike firing},
+  author={Evans, Mark D and Dumitrescu, Adna S and Kruijssen, Dennis LH and Taylor, Samuel E and Grubb, Matthew S},
+  journal={Cell reports},
+  volume={13},
+  number={6},
+  pages={1233--1245},
+  year={2015},
+  publisher={Elsevier}
+}
+
+@article{james2015,
+  title={Valproate-induced neurodevelopmental deficits in Xenopus laevis tadpoles},
+  author={James, Eric J and Gu, Jenny and Ramirez-Vizcarrondo, Carolina M and Hasan, Mashfiq and Truszkowski, Torrey LS and Tan, Yuqi and Oupravanh, Phouangmaly M and Khakhalin, Arseny S and Aizenman, Carlos D},
+  journal={Journal of Neuroscience},
+  volume={35},
+  number={7},
+  pages={3218--3229},
+  year={2015},
+  publisher={Soc Neuroscience}
+}
+
+@article{lecun2015,
+  title={Deep learning},
+  author={LeCun, Yann and Bengio, Yoshua and Hinton, Geoffrey},
+  journal={Nature},
+  volume={521},
+  number={7553},
+  pages={436},
+  year={2015},
+  publisher={Nature Publishing Group}
+}
+
+@book{mccarthy2015,
+  title={Getting Started with P5. js: Making Interactive Graphics in JavaScript and Processing},
+  author={McCarthy, Lauren and Reas, Casey and Fry, Ben},
+  year={2015},
+  publisher={Maker Media, Inc.}
+}
+
+@article{radford2015,
+  title={Unsupervised representation learning with deep convolutional generative adversarial networks},
+  author={Radford, Alec and Metz, Luke and Chintala, Soumith},
+  journal={arXiv preprint arXiv:1511.06434},
+  year={2015}
+}
+
+@article{cropper2016,
+  title={Consequences of degeneracy in network function},
+  author={Cropper, Elizabeth C and Dacks, Andrew M and Weiss, Klaudiusz R},
+  journal={Current opinion in neurobiology},
+  volume={41},
+  pages={62--67},
+  year={2016},
+  publisher={Elsevier}
+}
+
+@article{felch2016,
+  title={Multisensory integration in the developing tectum is constrained by the balance of excitation and inhibition},
+  author={Felch, Daniel L and Khakhalin, Arseny S and Aizenman, Carlos D},
+  journal={Elife},
+  volume={5},
+  year={2016},
+  publisher={eLife Sciences Publications, Ltd}
+}
+
+@article{grossberg2016,
+  title={Resonant cholinergic dynamics in cognitive and motor decision-making: attention, category learning, and choice in neocortex, superior colliculus, and optic tectum},
+  author={Grossberg, Stephen and Palma, Jesse and Versace, Massimiliano},
+  journal={Frontiers in neuroscience},
+  volume={9},
+  pages={501},
+  year={2016},
+  publisher={Frontiers}
+}
+
+@article{hamada2016,
+  title={Covariation of axon initial segment location and dendritic tree normalizes the somatic action potential},
+  author={Hamada, Mustafa S and Goethals, Sarah and de Vries, Sharon I and Brette, Romain and Kole, Maarten HP},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={113},
+  number={51},
+  pages={14841--14846},
+  year={2016},
+  publisher={National Acad Sciences}
+}
+
+@article{hamodi2016,
+  title={An NMDA receptor-dependent mechanism for subcellular segregation of sensory inputs in the tadpole optic tectum},
+  author={Hamodi, Ali S and Liu, Zhenyu and Pratt, Kara G},
+  journal={eLife},
+  volume={5},
+  year={2016},
+  publisher={eLife Sciences Publications, Ltd}
+}
+
+@article{jang2016,
+  title={Emergence of Selectivity to Looming Stimuli in a Spiking Network Model of the Optic Tectum},
+  author={Jang, Eric V and Ramirez-Vizcarrondo, Carolina and Aizenman, Carlos D and Khakhalin, Arseny S},
+  journal={Frontiers in neural circuits},
+  volume={10},
+  pages={95},
+  year={2016},
+  publisher={Frontiers}
+}
+
+@article{liu2016,
+  title={A population of gap junction-coupled neurons drives recurrent network activity in a developing visual circuit},
+  author={Liu, Zhenyu and Ciarleglio, Christopher M and Hamodi, Ali S and Aizenman, Carlos D and Pratt, Kara G},
+  journal={Journal of neurophysiology},
+  volume={115},
+  number={3},
+  pages={1477--1486},
+  year={2016},
+  publisher={Am Physiological Soc}
+}
+
+@article{thompson2016,
+  title={Functional profiles of visual-, auditory-, and water flow-responsive neurons in the zebrafish tectum},
+  author={Thompson, Andrew W and Vanwalleghem, Gilles C and Heap, Lucy A and Scott, Ethan K},
+  journal={Current Biology},
+  volume={26},
+  number={6},
+  pages={743--754},
+  year={2016},
+  publisher={Elsevier}
+}
+
+@article{bassett2017network,
+  title={Network neuroscience},
+  author={Bassett, Danielle S and Sporns, Olaf},
+  journal={Nature neuroscience},
+  volume={20},
+  number={3},
+  pages={353},
+  year={2017},
+  publisher={Nature Publishing Group}
+}
+
+@article{kuznetsova2017,
+  title={lmerTest package: Tests in linear mixed effects models},
+  author={Kuznetsova, Alexandra and Brockhoff, Per B and Christensen, Rune HB},
+  journal={Journal of Statistical Software},
+  volume={82},
+  number={13},
+  pages={1--26},
+  year={2017}
+}
+
+@article{hildebrand2017,
+  title={Whole-brain serial-section electron microscopy in larval zebrafish},
+  author={Hildebrand, David Grant Colburn and Cicconet, Marcelo and Torres, Russel Miguel and Choi, Woohyuk and Quan, Tran Minh and Moon, Jungmin and Wetzel, Arthur Willis and Champion, Andrew Scott and Graham, Brett Jesse and Randlett, Owen and others},
+  journal={Nature},
+  volume={545},
+  number={7654},
+  pages={345},
+  year={2017},
+  publisher={Nature Publishing Group}
+}
+
+@article{reimann2017,
+  title={Cliques of neurons bound into cavities provide a missing link between structure and function},
+  author={Reimann, Michael W and Nolte, Max and Scolamiero, Martina and Turner, Katharine and Perin, Rodrigo and Chindemi, Giuseppe and D{\l}otko, Pawe{\l} and Levi, Ran and Hess, Kathryn and Markram, Henry},
+  journal={Frontiers in computational neuroscience},
+  volume={11},
+  pages={48},
+  year={2017},
+  publisher={Frontiers}
+}
+
+@article{titley2017,
+  title={Toward a neurocentric view of learning},
+  author={Titley, Heather K and Brunel, Nicolas and Hansel, Christian},
+  journal={Neuron},
+  volume={95},
+  number={1},
+  pages={19--32},
+  year={2017},
+  publisher={Elsevier}
+}
+
+@article{truszkowski2017,
+  title={A cellular mechanism for inverse effectiveness in multisensory integration},
+  author={Truszkowski, Torrey LS and Carrillo, Oscar A and Bleier, Julia and Ramirez-Vizcarrondo, Carolina M and Felch, Daniel L and McQuillan, Molly and Truszkowski, Christopher P and Khakhalin, Arseny S and Aizenman, Carlos D},
+  journal={Elife},
+  volume={6},
+  year={2017},
+  publisher={eLife Sciences Publications, Ltd}
+}
+
+@article{bashivan2018neural,
+  title={Neural Population Control via Deep Image Synthesis},
+  author={Bashivan, Pouya and Kar, Kohitij and DiCarlo, James},
+  journal={bioRxiv},
+  pages={461525},
+  year={2018},
+  publisher={Cold Spring Harbor Laboratory}
+}
+
+@article{goldwyn2018a_current,
+  title={Gain control with A-type potassium current: IA as a switch between divisive and subtractive inhibition},
+  author={Goldwyn, Joshua H and Slabe, Bradley R and Travers, Joseph B and Terman, David},
+  journal={arXiv preprint arXiv:1802.04794},
+  year={2018}
+}
+
+@article{jarvis2018morphology,
+  title={Neuronal gain modulability is determined by dendritic morphology: A computational optogenetic study},
+  author={Jarvis, Sarah and Nikolic, Konstantin and Schultz, Simon R},
+  journal={PLoS computational biology},
+  volume={14},
+  number={3},
+  pages={e1006027},
+  year={2018},
+  publisher={Public Library of Science}
+}
+
+@article{leterrier2018axon,
+  title={The axon initial segment: an updated viewpoint},
+  author={Leterrier, Christophe},
+  journal={Journal of Neuroscience},
+  volume={38},
+  number={9},
+  pages={2135--2145},
+  year={2018},
+  publisher={Soc Neuroscience}
+}
+
+@article{ohtsuki2018bursting,
+  title={Synaptic potential and plasticity of an SK2 channel gate regulate spike burst activity in cerebellar Purkinje cells},
+  author={Ohtsuki, Gen and Hansel, Christian},
+  journal={iScience},
+  volume={1},
+  pages={49--54},
+  year={2018},
+  publisher={Elsevier}
+}
+
+@article{picton2018control,
+  title={Control of Xenopus Tadpole Locomotion via Selective Expression of Ih in Excitatory Interneurons},
+  author={Picton, Laurence D and Sillar, Keith T and Zhang, Hong-Yan},
+  journal={Current Biology},
+  year={2018},
+  publisher={Elsevier}
+}
+
+@article{tien2018,
+  title={Homeostatic plasticity in neural development},
+  author={Tien, Nai-Wen and Kerschensteiner, Daniel},
+  journal={Neural development},
+  volume={13},
+  number={1},
+  pages={9},
+  year={2018},
+  publisher={BioMed Central}
+}
+
+@article{beniaguev2019singledeep,
+  title={Single Cortical Neurons as Deep Artificial Neural Networks},
+  author={Beniaguev, David and Segev, Idan and London, Michael},
+  journal={bioRxiv},
+  pages={613141},
+  year={2019},
+  publisher={Cold Spring Harbor Laboratory}
+}
+
+@article{khakhalin2019graph,
+  title={Graph analysis of looming-selective networks in the tectum, and its replication in a simple computational model},
+  author={Khakhalin, Arseny},
+  journal={BioRxiv},
+  pages={589887},
+  year={2019},
+  publisher={Cold Spring Harbor Laboratory}
+}
+
+@article {moldwin2019perceptron,
+	author = {Moldwin, Toviah and Segev, Idan},
+	title = {Perceptron learning and classification in a modeled cortical pyramidal cell},
+	elocation-id = {464826},
+	year = {2019},
+	doi = {10.1101/464826},
+	publisher = {Cold Spring Harbor Laboratory},
+	URL = {https://www.biorxiv.org/content/early/2019/05/02/464826},
+	journal = {bioRxiv}
+}
+
+@article{richards2019dendritic,
+  title={Dendritic solutions to the credit assignment problem},
+  author={Richards, Blake A and Lillicrap, Timothy P},
+  journal={Current opinion in neurobiology},
+  volume={54},
+  pages={28--36},
+  year={2019},
+  publisher={Elsevier}
+}
+
+@article{zbili2019axonnav,
+  title={Axonal Na+ channels detect and transmit levels of input synchrony in local brain circuits},
+  author={Zbili, Mickael and Rama, Sylvain and Yger, Pierre and Inglebert, Yanis and Boumedine-Guignon, Norah and Fronzaroli-Molinieres, Laure and Brette, Romain and Russier, Michael and Debanne, Dominique},
+  journal={bioRxiv},
+  pages={618710},
+  year={2019},
+  publisher={Cold Spring Harbor Laboratory}
+}
+
+\end{filecontents}
+
 \begin{document} % --------------------- Document start ----------------
@@
 
-\linenumbers % Comment this to suppress line numbers
+% \linenumbers % Comment this to suppress line numbers
 
@@
 % J Neurophysiol: up to 250 words
-% Currently: 186
+% Currently: 182
 
@@
 \begin{figure*}
-\includegraphics[width=\linewidth]{fig1.pdf}
+%\includegraphics[width=\linewidth,bb=0 0 7.16in 7.68in]{fig1.pdf}
+\includegraphics[width=\linewidth,bb=0 0 516 553]{fig1.pdf}
 \caption{
@@
 \begin{figure*}[!t]
-\includegraphics[width=\linewidth]{fig2.pdf}
+%\includegraphics[width=\linewidth,natwidth=9.81in,natheight=6.
+\includegraphics[width=\linewidth,bb=0 0 9.81in 6.59in]{fig2.pdf}
 \caption{
@@
 \begin{figure*}[!t]
-\includegraphics[width=\linewidth]{fig3.pdf}
+%\includegraphics[width=\linewidth,natwidth=8.83in,natheight=5.02in]{fig3.pdf}
+\includegraphics[width=\linewidth,bb=0 0 8.83in 5.02in]{fig3.pdf}
 \caption{Changes in synaptic transmission, and co-tuning of synaptic and intrinsic neuronal properties.
@@
 \centering
-\includegraphics[width=3.2in]{fig4.pdf}
+%\includegraphics[width=3.2in,natwidth=4.57in,natheight=5.71in]{fig4.pdf}
+\includegraphics[width=3.2in,bb=0 0 4.57in 5.71in]{fig4.pdf}
 \caption{Electrophysiological properties of individual neurons compared to their spiking in current and dynamic clamp experiments.
@@
 %\bibliographystyle{unsrtnat} % For Nature-style
-\bibliography{refs}
+\bibliography{localref}
 

### 2019-06-11 merged.tex
Merged text for submission: figure captions to the end

@@
 
-In our previously published large-scale census of tectal cells \citep{ciarleglio2015}, we observed no signs of intrinsic temporal tuning (figures 2, 4), and no interaction between intrinsic and synaptic phenotypes.
+In our previously published large-scale census of tectal cells \citep{ciarleglio2015}, we observed no signs of intrinsic temporal tuning (Figures 2, 4), and no interaction between intrinsic and synaptic phenotypes.
 We argue however, that the current clamp protocols used in earlier studies were not adequate for the task, so in this paper we rely on a dynamic clamp technique.
@@
 We presented a checkerboard pattern that inverted once a second, for four hours; either instantaneously (dubbed “Flash”; Figure 1C left), or with a slow transition over the course of a second (old black squares shrank to white, while new black squares grew from old white squares, dubbed “Looming”; Figure 1C right).
-
-\begin{figure*}
-%\includegraphics[width=\linewidth,bb=0 0 7.16in 7.68in]{fig1.pdf}
-\includegraphics[width=\linewidth,bb=0 0 516 553]{fig1.pdf}
-\caption{
-Overview of experimental design and summary of dynamic clamp results.
-(\textbf{A}).
-Positions of tectal neurons that were recorded.
-(\textbf{B}).
-Sample data from a dynamic clamp experiment.
-Bottom row: the dynamics of conductances G(t) of four different durations simulated by the dynamic clamp system.
-Middle row: the currents I(t) dynamically injected into a cell based on conductances of 4 different durations and 3 different amplitudes.
-Top row: resulting voltage traces V(t) that were recorded and analyzed.
-(\textbf{C}).
-A schematic of visual conditioning in “Flash” (left) and “Looming” (right) groups.
-(\textbf{D}).
-The number of spikes produced by all neurons in all experiments, split by input peak conductance, and plotted against conductance duration.
-Black lines show respective averages.
-(\textbf{E}).
-A summary of data from D, presented as averages and 95\% confidence intervals.}
-\end{figure*}
 
@@
 This suggests that while on their own sound clicks had little effect on tectal excitability, when added to visual flashes, they negated some of the retuning effects that visual stimulation would have had.
-
-\begin{figure*}[!t]
-%\includegraphics[width=\linewidth,natwidth=9.81in,natheight=6.
-\includegraphics[width=\linewidth,bb=0 0 9.81in 6.59in]{fig2.pdf}
-\caption{
-Quantification of changes in temporal tuning in response to sensory experience.
-(\textbf{A}).
-An illustration of how “Temporal tuning” and “Amplitude tuning” values were calculated.
-For the temporal tuning measure, the value of zero corresponds to linear dependency (blue line), positive values - to an accelerating, supralinear curve (red), and negative values - to plateau- and hill-shaped curves (gray, orange, green).
-For amplitude tuning, higher values correspond to faster increase in spiking with increased conductance.
-(\textbf{B}).
-Amplitude tuning of neurons across different experimental groups (stars show t-test p$<$0.05 compared to control).
-(\textbf{C}).
-Temporal tuning and spikiness of neurons in different experimental groups.
-Neurons from each target group are shown in color, while all neurons from all groups are shown in light gray, as a reference; groups means are shown as black dots; ellipses represent 95\% normal confidence regions.
-Two outliers (top right corner) are brought within the axes limits.
-(\textbf{D}).
-Same data as in (C), shown as averages for each group, with 95\% confidence intervals.
-Black arrows show the effects of sound clicks, when they were added to control (red), and when they were added to "Flashes" (brown), to form two types of multisensory stimuli.}
-\end{figure*}
 
@@
 
-\begin{figure*}[!t]
-%\includegraphics[width=\linewidth,natwidth=8.83in,natheight=5.02in]{fig3.pdf}
-\includegraphics[width=\linewidth,bb=0 0 8.83in 5.02in]{fig3.pdf}
-\caption{Changes in synaptic transmission, and co-tuning of synaptic and intrinsic neuronal properties.
-(\textbf{A}).
-Amplitudes of early monosynaptic inputs to tectal neurons in all experimental groups (in log scale, outliers brought within the axes limits, stars show t-test p$<$0.05 compared to control).
-(\textbf{B}).
-A sample synaptic recording, showing all traces for one cell (green) and an average trace (blue).
-The black bars show the areas at which early monosynaptic and late polysynaptic currents were measured; the vertical position of each bar represents the respective average current.
-The second, longer bar does not completely fit within the figure at this scale.
-(\textbf{C}).
-Synaptic current duration (vertical axis) was mostly defined by the amplitude of early monosynaptic inputs (horizontal axis).
-(\textbf{D}).
-Synaptic current durations were different between experimental groups (see text; stars show t-test p$<$0.05 compared to control).
-(\textbf{E}).
-Across experiments, average temporal tuning in each group positively correlated with the average durations of synaptic currents they received.
-(\textbf{F}).
-Within experimental groups, temporal tuning of individual neurons negatively correlated with the duration of synaptic currents they received.
-Axes show within-group deviations of temporal tuning and synaptic current duration from respective averages for each group.}
-\end{figure*}
-
 To better match and compare temporal properties of synaptic inputs to those of intrinsic tuning, we calculated average "synaptic current duration" for each cell as a temporal “center of mass” of currents within the first 700 ms after optic chiasm stimulation (see Methods).
@@
 Together with cell membrane resistance (Rm) and capacitance (Cm) it gave us eight intrinsic parameters for every cell: peak amplitudes for sodium current, early (transient) potassium current, and late (stable) potassium current (INa, IKt, IKs respectively), and activation potentials for these three currents (VNa, VKt, and VKs).
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[width=3.2in,natwidth=4.57in,natheight=5.71in]{fig4.pdf}
-\includegraphics[width=3.2in,bb=0 0 4.57in 5.71in]{fig4.pdf}
-\caption{Electrophysiological properties of individual neurons compared to their spiking in current and dynamic clamp experiments.
-(\textbf{A}).
-A set of curves from one voltage step experiment; black bars show the areas used to average Na (bottom) and transient K (top) currents (see Methods).
-(\textbf{B}).
-Processing of ionic currents data with IV-curves translated into two parameters (threshold potential and peak current) for each ionic conductance.
-(\textbf{C}).
-Sample data from one current clamp experiment; spikes are marked with black dots.
-(\textbf{D}).
-Estimations of excitability from current clamp experiments (horizontal axis) and dynamic clamp experiments (vertical axis) correlate.
-(\textbf{E}).
-The number of spikes registered in current clamp mode: values predicted from a linear model plotted against observed values.
-The model works reasonably well (61\% of variance explained).
-(\textbf{F}).
-Similar comparison for the dynamic clamp experiments: the model has very low predictive value (13\% of variance explained).
-Here and in E, both values are adjusted for position.}
-\end{figure}
 
@@
 
+\subsection*{Figure captions}
+
+\textbf{Figure 1}
+
+Overview of experimental design and summary of dynamic clamp results.
+(\textbf{A}).
+Positions of tectal neurons that were recorded.
+(\textbf{B}).
+Sample data from a dynamic clamp experiment.
+Bottom row: the dynamics of conductances G(t) of four different durations simulated by the dynamic clamp system.
+Middle row: the currents I(t) dynamically injected into a cell based on conductances of 4 different durations and 3 different amplitudes.
+Top row: resulting voltage traces V(t) that were recorded and analyzed.
+(\textbf{C}).
+A schematic of visual conditioning in “Flash” (left) and “Looming” (right) groups.
+(\textbf{D}).
+The number of spikes produced by all neurons in all experiments, split by input peak conductance, and plotted against conductance duration.
+Black lines show respective averages.
+(\textbf{E}).
+A summary of data from D, presented as averages and 95\% confidence intervals
+
+\textbf{Figure 2}
+
+Quantification of changes in temporal tuning in response to sensory experience.
+(\textbf{A}).
+An illustration of how “Temporal tuning” and “Amplitude tuning” values were calculated.
+For the temporal tuning measure, the value of zero corresponds to linear dependency (blue line), positive values - to an accelerating, supralinear curve (red), and negative values - to plateau- and hill-shaped curves (gray, orange, green).
+For amplitude tuning, higher values correspond to faster increase in spiking with increased conductance.
+(\textbf{B}).
+Amplitude tuning of neurons across different experimental groups (stars show t-test p$<$0.05 compared to control).
+(\textbf{C}).
+Temporal tuning and spikiness of neurons in different experimental groups.
+Neurons from each target group are shown in color, while all neurons from all groups are shown in light gray, as a reference; groups means are shown as black dots; ellipses represent 95\% normal confidence regions.
+Two outliers (top right corner) are brought within the axes limits.
+(\textbf{D}).
+Same data as in (C), shown as averages for each group, with 95\% confidence intervals.
+Black arrows show the effects of sound clicks, when they were added to control (red), and when they were added to "Flashes" (brown), to form two types of multisensory stimuli.
+
+\textbf{Figure 3}
+
+Changes in synaptic transmission, and co-tuning of synaptic and intrinsic neuronal properties.
+(\textbf{A}).
+Amplitudes of early monosynaptic inputs to tectal neurons in all experimental groups (in log scale, outliers brought within the axes limits, stars show t-test p$<$0.05 compared to control).
+(\textbf{B}).
+A sample synaptic recording, showing all traces for one cell (green) and an average trace (blue).
+The black bars show the areas at which early monosynaptic and late polysynaptic currents were measured; the vertical position of each bar represents the respective average current.
+The second, longer bar does not completely fit within the figure at this scale.
+(\textbf{C}).
+Synaptic current duration (vertical axis) was mostly defined by the amplitude of early monosynaptic inputs (horizontal axis).
+(\textbf{D}).
+Synaptic current durations were different between experimental groups (see text; stars show t-test p$<$0.05 compared to control).
+(\textbf{E}).
+Across experiments, average temporal tuning in each group positively correlated with the average durations of synaptic currents they received.
+(\textbf{F}).
+Within experimental groups, temporal tuning of individual neurons negatively correlated with the duration of synaptic currents they received.
+Axes show within-group deviations of temporal tuning and synaptic current duration from respective averages for each group.
+
+\textbf{Figure 4}
+
+Electrophysiological properties of individual neurons compared to their spiking in current and dynamic clamp experiments.
+(\textbf{A}).
+A set of curves from one voltage step experiment; black bars show the areas used to average Na (bottom) and transient K (top) currents (see Methods).
+(\textbf{B}).
+Processing of ionic currents data with IV-curves translated into two parameters (threshold potential and peak current) for each ionic conductance.
+(\textbf{C}).
+Sample data from one current clamp experiment; spikes are marked with black dots.
+(\textbf{D}).
+Estimations of excitability from current clamp experiments (horizontal axis) and dynamic clamp experiments (vertical axis) correlate.
+(\textbf{E}).
+The number of spikes registered in current clamp mode: values predicted from a linear model plotted against observed values.
+The model works reasonably well (61\% of variance explained).
+(\textbf{F}).
+Similar comparison for the dynamic clamp experiments: the model has very low predictive value (13\% of variance explained).
+Here and in E, both values are adjusted for position.
+
 %TC:endignore
